### 2011-02-09 trunk/documents/thesis/propuesta/Propuesta.tex
Propuesta

\documentclass[12pt,letterpaper,spanish]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{setspace}
\onehalfspacing

\usepackage{babel}
\addto\shorthandsspanish{\spanishdeactivate{~<>}}

\begin{document}

\title{FACULTAD DE INGENIERÍA \\
Vicedecanatura Académica\\
POSGRADOS\\
PRESENTACIÓN PROPUESTA}

\maketitle
TESIS DE MAESTRÍA:

\section{PROPONENTE: }

Alexander Pinzón Fernández

CÓDIGO: 02 299802

\section{PROGRAMA: }

Maestría en Ingeniería de Sistemas y Computación

\section{DIRECTOR PROPUESTO: }

Eduardo Romero Castro

DEPARTAMENTO: Ingeniería de Sistemas e Industrial.

\section{TÍTULO}

Extracción y seguimiento del esqueleto de un cuerpo a partir de múltiples
vistas. 
\begin{description}
\item [{ÁREA:}] Ciencias de la Computación 
\item [{LÍNEA~DE~INVESTIGACIÓN:}] Computación grafica, procesamiento
de imágenes, procesamiento de video.
\item [{NOTA:}] La metodología de este proyecto está orientada por los
resultados y organizada en paquetes de trabajo, tal y como se hace
de manera estándar en todos los proyectos de la Unión Europea (Condición
impuesta por mi director de tesis).
\end{description}

\section{ANTECEDENTES Y JUSTIFICACIÓN:}

La medición realizada por un observador de la posición con respecto
al tiempo de una partícula en un sistema de referencia. Es denominada
registro de movimiento.

El estudio y registro del movimiento de un cuerpo con extremidades
articuladas, como una persona o un animal, ha sido de interés en varias
aéreas del conocimiento. Por ejemplo, la anatomía humana y animal,
la ingeniería y las artes. El registro de movimiento ha sido usado
para resolver distintos tipos de problemas, por ejemplo: en el diagnostico
de patologías asociadas a la marcha en seres humanos, la captura del
movimiento de un actor para dar vida a un personaje animado, o el
análisis ergonómico para el diseño de productos y herramientas \cite{Remondino2004}.

La extracción y seguimiento de esqueletos se logra mediante la utilización
de un conjunto de actividades organizadas dentro de un proceso. Estas
actividades son: la adquisición de datos desde un objeto real, la
reconstrucción 3D a partir de los datos de la captura, la extracción
del esqueleto del objeto tridimensional reconstruido, y el seguimiento
del esqueleto tomado como un proceso iterativo de captura con un esqueleto
invariante topológicamente en el tiempo.

Los esqueletos son estructuras 1D que representan una simplificada
versión de la geometría y topología de un objeto 3D. Son en esencia
una entidad geométrica que abstrae el volumen del objeto. Por esta
razón muchos métodos de extracción del esqueleto requieren una representación
discreta del volumen del modelo de entrada. Sin embargo la mayoría
de modelos usados en aplicaciones de computación grafica son disponibles
únicamente como una representación de su superficie, tales como las
mallas de polígonos \cite{Au2008}.

\subsection{Adquisición de datos}

Existen diferentes enfoques en la adquisición de la información espacial
de objetos reales, algunos basados en el procesamiento de imágenes,
otros basados en sensores (mecánicos, electromagnéticos, e inerciales
entre otros), y otros como el escáner de laser, la tomografía, el
ultrasonido, etc \cite{Cheung2003}.

Los métodos de adquisición basados en el procesamiento de señales
utilizan las secuencias de imágenes producidas por una o varias cámaras.
Cuando se utilizan varias cámaras se explota la coherencia espacial
dada por la visión estereoscópica, mediante el uso de puntos característicos
como marcadores (luminosos, reflectivos, o detectados mediante filtros),
y las siluetas de los objetos obtenidos mediante la segmentación de
las imágenes \cite{Lin2008}. Cuando se utiliza una única imagen se
hace uso de modelos a priori y además se añaden restricciones en las
búsquedas de soluciones, estos modelos pueden basarse en aproximaciones
probabilísticas o aprendizaje de máquina.

\subsubsection{Segmentación de imágenes}

La segmentación de imágenes son un conjunto de métodos para dividir
una imagen en regiones, dadas ciertas características. La segmentación
puede ser automática es decir sin interacción del usuario, o semiautomáticas
que requieren la supervisión manual \cite{Jin2007}. A continuación
mostraremos algunos de los métodos de segmentación más usados:
\begin{itemize}
\item Métodos de segmentación de contorno activos \cite{Flagg2009}.
\item Método Snake con uso de filtros de gradiente de dirección \cite{Ma2003}.
\item Métodos que utilizan la coherencia espacio temporal de formas limitantes
especialmente cajas y elipses \cite{Landabaso2008}.
\item Métodos probabilísticos con redes bayesianas para modelar la interacción
de campos \cite{Slabaugh2004}.
\end{itemize}

\subsubsection{Captura mediante sensores}

Este tipo de técnicas ofrecen gran precisión y libertad para la captura
del movimiento, pues no presentan problemas de oclusión presentes
en los métodos de procesamiento de imágenes \cite{Kry2006}.

Algunas desventajas son:
\begin{itemize}
\item No proporcionan información de la forma y superficie del objeto.
\item Es necesario el uso de trajes especiales que restringen la captura
de la textura del cuerpo. Además algunos mecanismos no son inalámbricos
lo que restringe la movilidad.
\item Son equipos costosos.
\item Los sistemas requieren estar próximos a los objetos, no permitiendo
grandes translaciones en el espacio \cite{HernandezEsteban2002}.
\end{itemize}

\subsubsection{Escáner tridimensional de laser}

Ofrecen la mayor calidad y precisión en la captura de la forma y detalles
de la superficie del objeto, siendo de los métodos más utilizados
en industrias como la del cine, la paleontología, la arqueología,
entre otros \cite{Aguiar2008}. La mayor desventaja de esto método
son los altísimos costos de estos dispositivos.

\subsection{Reconstrucción tridimensional}

La reconstrucción tridimensional, son un conjunto de técnicas mediante
las cuales objetos reales, son representados mediante estructuras
de datos o funciones, haciendo énfasis en características como volumen
y forma. Existe actualmente una gran cantidad de técnicas de reconstrucción
y métodos de mallado 3D \cite{Aguiar2005}, dado un conjunto de puntos
3D no conectados.

\subsubsection{Reconstrucción basada en imágenes }

La reconstrucción basada en imágenes, tiene dos enfoques importantes
uno con el uso de marcas, y otro sin ellas, además hay que tomar en
cuenta los parámetros intrínsecos (distancia focal, distorsión, etc.)
y extrínsecos (posición, orientación, etc.) de la cámara \cite{Campos2006a}.

En la reconstrucción con el uso de marcas se hace un filtrado de la
imagen para localizar estos marcadores los cuales son en general puntos
de algún color poco presente en la escena como el blanco, un rojo
o verde intenso, también se usan marcadores que emiten luz como pequeños
bombillos, o el uso de imágenes en blanco y negro que tienen un patrón
dado reconocible. Con estos puntos segmentados y localizados en las
imágenes se procede a realizar la solución de las ecuaciones de las
transformaciones lineales correspondientes basadas en un sistema estéreo
con un modelo de cámara pinhole \cite{Thormahlen2008}.

\subsection{Extracción del esqueleto}

La extracción del esqueleto es un problema que actualmente es tratado
desde distintos enfoques, algunos realizan estimaciones del esqueleto
en 2D, y luego utilizan información a priori para estimar como fue
transformado el esqueleto tridimensional real \cite{Remondino2003},
otros enfoques realizan una reducción iterativa del número de polígonos
con ciertas restricciones de contracción y minimización de energía,
hasta encontrar un esqueleto irreducible \cite{Au2008}. Otros métodos
utilizan distintas representaciones topológicas de un objeto tridimensional
mediante grafos, luego realizan una simplificación de este grafo,
y por ultimo utilizan un esqueleto modelo el cual transforman para
minimizar el error entre el esqueleto y el grafo dado por medio de
alguna métrica basada en heurísticas \cite{Aguiar2008}.

\section{IDENTIFICACIÓN DEL PROBLEMA: }

El seguimiento de movimiento se realiza convencionalmente con costosos
sistemas de captura que varían entre los 150 y 400 millones de pesos
aproximadamente. Este seguimiento del movimiento presenta estos inconvenientes.
\begin{itemize}
\item Usan marcadores en forma de trajes y dispositivos pegados al cuerpo
y sus extremidades, que alteran la naturalidad de los movimientos.
Además, se necesita de expertos para posicionar los marcadores, pues
los marcadores deben estar localizados en puntos antropométricos específicos.
\item Los sistemas estereoscópicos que realizan una reconstrucción tridimensional
desde múltiples puntos de vista manejan grandes volúmenes de datos
correspondientes a la geometría del cuerpo, con lo cual se requiere
maquinas de alto rendimiento. 
\end{itemize}

\section{OBJETIVO GENERAL Y OBJETIVOS ESPECÍFICOS: }

\subsection{Objetivo General: }

Seguimiento del movimiento del cuerpo humano en 3 dimensiones.

\subsection{Objetivos Específicos: }
\begin{enumerate}
\item Capturar mediante video cámaras un cuerpo en movimiento para su análisis.
\item Extraer la silueta del cuerpo desde los videos mediante el método
$\Sigma-\Delta$ Sigma-Delta.
\item Usando los videos, extraer marcadores de las relaciones fundamentales
del cuerpo con lo cual se constituye un esqueleto que representa el
cuerpo. 
\item Realizar el seguimiento del esqueleto en cada cuadro de video y validar
los resultados obtenidos del análisis. 
\item Diseñar un sistema de realidad aumentada que permita visualizar el
movimiento del cuerpo, junto con el esqueleto estimado. 
\end{enumerate}

\section{METODOLOGÍA Y ACTIVIDADES POR OBJETIVOS:}

\subsection{Objetivo 1. Adquisición de Datos: }

Obtener la secuencia de imágenes utilizando 6 cámaras con las siguientes
descripciones: 
\begin{itemize}
\item Cámaras geométricamente localizadas en un arreglo circular alrededor
del centro de la escena.
\item Cámaras con características intrínsecas y extrínsecas calibradas.
\item Cámaras sincronizadas en el tiempo que capturan la escena desde distintos
ángulos.
\item Escenario con condiciones de iluminación controladas. 
\end{itemize}
Actividades: 
\begin{itemize}
\item Ubicar las cámaras en un arreglo circular, alrededor del centro de
la escena. 
\item Iluminar el escenario de acuerdo a parámetros seleccionados. 
\item Calibrar las cámaras. 
\item Capturar de forma sincronizada los videos de un cuerpo articulado
en movimiento. \end{itemize}
\begin{description}
\item [{Entregable:}] Archivos de video digitalizados de cada una de las
cámaras usadas.
\end{description}

\subsection{Objetivo 2. Extracción de la silueta del cuerpo articulado: }

Implementar el método $\Sigma-\triangle$ Sigma-Delta de segmentación
de video, para extraer la silueta del cuerpo articulado.

Actividades
\begin{itemize}
\item Implementar el método de segmentación.
\item Segmentar la silueta del cuerpo desde los videos. \end{itemize}
\begin{description}
\item [{Entregable:}] Archivos de datos con la silueta segmentada para
cada uno de los videos. 
\end{description}

\subsection{Objetivo 3. Extracción del esqueleto:}

Estudio de modelos de atención visual para la extracción de singularidades,
bordes y puntos de cambio en la imagen.

Estudio de modelos fotogramétricos, para la reconstrucción 3D desde
un par estereoscópico.

Estudio de métodos para la reconstrucción de forma desde las siluetas,
también conocido como visual-hull.

Estudio de modelos matemáticos, para la extracción del medial axis.

Actividades: 
\begin{itemize}
\item Selección de una técnica para la detección de puntos característicos.
\item Implementar la técnica de detección.
\item Seleccionar una técnica de reconstrucción estereoscópica.
\item Implementar la técnica de reconstrucción estereoscópica.
\item Seleccionar una técnica de reconstrucción de volumen.
\item Implementar la técnica de reconstrucción de volumen.
\item Desarrollar un método para la extracción del esqueleto.
\item Implementar el método de extracción del esqueleto.\end{itemize}
\begin{description}
\item [{Entregable:}] Archivos de datos con información geométrica tridimensional
del esqueleto extraído.
\end{description}

\subsection{Objetivo 4. Realizar el seguimiento del esqueleto en cada cuadro
de video y validar los resultados obtenidos del análisis: }

Estudio de métodos de seguimiento para determinar el cambio de pose
del esqueleto a través del tiempo.

Calibración de las cámaras.

Se evaluaran los resultados con otros métodos de extracción y seguimiento
del esqueleto, utilizando las mismas secuencias de video.

Actividades: 
\begin{itemize}
\item Desarrollar la técnica de seguimiento.
\item Implementar la técnica de seguimiento.
\item Seleccionar otros métodos de extracción y seguimiento del esqueleto
que usen secuencias de video desde varias cámaras.
\item Obtener los resultados de los otros métodos.
\item Comparar los resultados entre el método desarrollado y los otros métodos
evaluados. \end{itemize}
\begin{description}
\item [{Entregable:}] Archivo con información del cambio de pose del esqueleto
extraído en cada secuencia de video. Tabla con datos de resultados
del método desarrollado, y los otros métodos evaluados.
\end{description}

\subsection{Objetivo 5. Diseñar un sistema de realidad aumentada que permita
visualizar el movimiento del cuerpo, junto con el esqueleto estimado: }

Realizar los pasos necesarios para la construcción de un sistema basándose
en técnicas de ingeniería de software.

Actividades 
\begin{itemize}
\item Realizar un análisis de requerimientos
\item Hacer un diseño del sistema.
\item Implementar el diseño.
\item Documentar el sistema. \end{itemize}
\begin{description}
\item [{Entregable:}] Programa de computadora que permita visualizar el
video junto con el seguimiento del esqueleto. 
\end{description}
\bibliographystyle{plain}
\addcontentsline{toc}{section}{\refname}\bibliography{listado_inicial}

\end{document}

### 2013-01-03 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,annual]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
% for the following cases use the listed document class option:
% [annual] - Technical paper accepted for presentation at the ACM SIGGRAPH 
%   or SIGGRAPH Asia annual conference.
% [sponsored] - Short or full-length technical paper accepted for 
%   presentation at an event sponsored by ACM SIGGRAPH
%   (but not the annual conference Technical Papers program).
% [abstract] - A one-page abstract of your accepted content
%   (Technical Sketches, Posters, Emerging Technologies, etc.). 
%   Content greater than one page in length should use the "[sponsored]"
%   parameter.
% [preprint] - A preprint version of your final content.
% [review] - A technical paper submitted for review. Includes line
%   numbers and anonymization of author and affiliation information.

% When you submit your paper for review, please use the \TOGonlineID''
% command to include the online ID value assigned to your paper by the
% submission management system. Replace '45678' with the value you were
% assigned.
\TOGonlineid{45678}

% If you are preparing a preprint of your accepted paper, and your paper
% will be published in an issue of the ACM "Transactions on Graphics''
% journal, replace the "0'' values in the commands below with the correct
% volume and number values for that issue - you'll get them before your
% final paper is due.
\TOGvolume{0}
\TOGnumber{0}

% The TOGarticleDOI' command accepts the DOI information provided to you
% during production, and which makes up the URLs which identifies the ACM
% article page and direct PDF link in the ACM Digital Library.
% Replace "1111111.2222222'' with the values you are given.
\TOGarticleDOI{1111111.2222222}

% If you would like to include links to personal repositories for auxiliary
% material related your research contribution, you may use one or more of
% these commands to define an appropriate URL. The "\TOGlinkslist'' command
% found just before the first section of your document will add hyperlinked
% icons to your document, in addition to hyperlinked icons which point to
% the ACM Digital Library article page and the ACM Digital Library-held PDF.
\TOGprojectURL{}
\TOGvideoURL{}
\TOGdataURL{}
\TOGcodeURL{}

% Paper title.
\title{Curvature Enhance With Laplacian Operator For Hybrid Quad/Triangle Meshes}

% Author and Affiliation (single author).
%\author{Name \thanks{e-mail: name@unknown.uu}\\ Research Institute}

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

% The ``pdfauthor'' command accepts the authors of the work,
% comma-delimited, and adds this information to the PDF metadata.
\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}

% Keywords that describe your work.
\keywords{laplacian smooth, curvature, sculpting, subdivision surface}

\makeatother

\usepackage{babel}
\begin{document}

\teaser{\includegraphics[width=1\textwidth]{images/teaser_cup} \caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
from coarse model to enhancing the curvature obtained from Catmull-Clark
Subdivision and the use of constraints over coarse model with weight
vertex group in red.}
}

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modelling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for triangles and quads meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modelling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results in a real
production environment with software blender.
\end{abstract}

\begin{CRcatlist}
\CRcat{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling
}{Modeling packages}
\end{CRcatlist}
\keywordlist

\section{Introduction}

%\copyrightspace

Over the last years have been developed novel techniques of modeling
that can generate a variety of shapes to look natural and realistic
\cite{Botsch2006}. Editing techniques have evolved from affine transformations
to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing and creation from sketches \cite{Igarashi1999,Gonen2012},
complex interpolation techniques \cite{Sorkine2004,Zhou2005}, among
others.

Traditional methods for smooth surfaces from coarse geometry like
Catmull-Clark have been widely developed \cite{Catmull1978,Stam1998},
these works generalize uniform B-cubic splines knot insertion to meshes,
some of them add control of the results with the use of creases to
produce sharp edges \cite{DeRose1998}, or the modification of weights
on the vertices that control locally the zone of influence \cite{Biermann2000},
instead our method performs a feature enhancement of the model allowing
parameterize the curvature of the surface creating a family of different
versions of the same object preserving detail and realistic natural
look of the original model.

Many types of brushes have been developed to sculpt meshes, brushes
that perform inflation lose detail when inflating the vertices \cite{Stanculescu2011},
our method allows inflation of the mesh vertices moving in the opposite
direction to the curvature preserving the shape and sharp features
of the model.

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for polygonal meshes composed
of triangles and quads. Also shows some results of curvature enhancement
applications in sculpting, subdivision and modelling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for meshes of arbitrary topology composed for triangles
and quads representing a larger spectrum of mesh that works with today
eliminating the need for preprocessing and allows the preservation
of the original topology. With this operator we proposed a method
to generate family of parameterized shapes, in a robust and predictable
way. Our method enable to customization of smoothness and curvature
obtained during subdivision surfaces process. We proposed a new brush
for enhance silhouette features of mesh in modeling and sculpting.

\section{Related work\label{sub:1.1-Related-work}}

Many tools have been developed for modeling based on Laplacian mesh
processing. Thanks to the kindness of the Laplacian operator these
tools have in common the need for preservation of the geometric details
of the surface for the different processes such as: free-form deformation,
fusion, morphing and other applications \cite{Sorkine2004}.

Methods for offset polygon meshes based on the curvature defined by
the Laplace Beltrami operator have been developed. These methods allow
adjusting shape offset by a constant distance with high enough precision
to minimize Hausdorf error. The problem with these methods is the
loss of detail caused by smoothing, which depends on the size of the
offset \cite{Zhuo2012}. In volumetric approaches on computing the
offset boundary that are based on distance field computation in point-based
representation, this methods the topology of the offset model can
be different from that the original geometry \cite{Chen2011}.

\cite{Gal2009} proposes automatic features detection and shape edition
with feature inter-relationship preservation. In analysis step they
define salient surface features how ridges and valleys with base on
first and second order curvature derivatives \cite{Ohtake2004}, and
angle-based threshold. In feature characterization step the curves
are classified by several properties as planar or non-planar, approximated
by line, circle or ellipse shapes, and so on. In edit step the user
define initial change over several feature and then this edit is propagated
over other features with base in your inter-relationships. This method
works fine with objects that have sharp edges composed of basic geometric
shapes such as lines, circles or ellipses but this method has difficulties
when models are smoother with organic forms and cannot find the features
to edit and preserve.

Digital sculpting is divided into two principal methods: based on
polygonal methods and voxel grids-based methods. Brushes for inflate
operations in polygonal methods only depends on the normal at each
vertex \cite{Stanculescu2011}, in grids-based some operations permit
add or remove voxels and then have that processing isosurfaces from
volume to produce polygonal meshes representation \cite{Galyean1991}.
The problem whit this type of operations is the difficult to maintain
surface details during larger scale deformation.

\section{Laplacian Smooth\label{sec:Laplacian-Smooth}}

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/beltrami}

\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO).}
\end{figure*}

The Laplacian Smooth techniques allows you to reduce noise on a mesh's
surface with minimal changes on its shape. Computer graphics objects
which have been reconstructed from real world, contain undesirable
noise. A Laplacian smoothing removes undesirable noise while still
preserves desirable geometry as well as the shape of the original
model.

The functional used in many Laplacian smoothing approach to constrain
energy minimization is based on a total curvature of a surface $S$.

\begin{equation}
E\left(S\right)=\int_{S}\kappa_{1}^{2}+\kappa_{2}^{2}dS\label{eq:total_cuarvature_integral}
\end{equation}

Where $\kappa_{1}$ and $\kappa_{2}$ are the two principal curvatures
of the surface $S$.

\subsection{Gradient of Voronoi Area}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{images/voronoi_region}

\caption{\label{fig:voronoi_region}Area of Voronoi region around $v_{i}$
in dark blue.\protect \\
 $v_{j}$ 1-ring neighbors around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$
opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
\end{figure}

Consider a surface $S$ compound by a set of triangles around vertex
$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The change in area produced
by move $v_{i}$ is named gradient of \textit{Voronoi region \cite{Pinkall1993,Desbrun1999,Meyer2003}.}

\begin{equation}
\nabla A=\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)\label{eq:eq_gradient_voronoi_area}
\end{equation}

If we normalize this gradient in equation (\ref{eq:eq_gradient_voronoi_area})
by the total area in 1-ring around $v_{i}$, we have the \textit{discrete
mean curvature normal} of a surface $S$ as shown in equation (\ref{eq:discrete_mean_curvature_normal}).

\begin{equation}
2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{eq:discrete_mean_curvature_normal}
\end{equation}

\subsection{Laplace Beltrami Operator}

The \textit{Laplace Beltrami operator} LBO denoted $\triangle_{g}$
is used for measures mean curvature normal of the Surface $S$ \cite{Pinkall1993}.

\begin{equation}
\triangle_{g}S=2\kappa\mathbf{n}\label{eq:def_LBO}
\end{equation}

The LBO has desirable features, one feature of the LBO is in direction
of surface area minimization, allowing us to minimize energy using
it on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).

\section{Proposed Method\label{sec:Proposed-Method}}

Our method allow the editing of geometric features using the curvature
enhancement and smoothing. Generating a parameterized family of shapes
using a set of vertices representing a coarse sketch of the desired
model. Our approach can be mixed with traditional or uniform subdivision
surfaces methods and is iterative and converges towards a continuous
and smooth version of the original model.

Unlike other methods, our method allows to use mixed arbitrary types
of mesh representation as triangles and quads, exploiting the basic
geometrical relationships facilitating and ensuring convergence of
the algorithm and similar shapes consistent with the original shape
against the other methods.

Our method allows the use of soft constraints weighting the effect
of smoothing at each vertex based on a normalized weight, the weights
are assigned to the control vertices of the original mesh or. The
weights of the new vertices resulting from the subdivisions are calculated
by interpolation, allowing to modify the behavior of the method on
exact regions of the original model.

Our approach contain an extension of the Laplace Beltrami operator
for meshes composed by triangles and quads. Using meshes composed
by triangles and quads has been increasing in recent years due to
the flexibility of modeling tools as Blender 3D \cite{blender}. Today
many artists manually connecting vertices such that its edition allows
simplest way to perform animation processes and interpolation \cite{Mullen2007}.
For these reasons it is very important to develop an operator that
allows working with this type of mesh immediately, eliminating the
need to preprocessing the mesh to convert to triangles and losing
the original design made by users.

\subsection{Laplace Beltrami operator over triangular and quadrilateral meshes
TQLBO\label{sub:Laplace-Beltrami-operator}}

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$.

The area of $1$-ring neighborhood ($N_{1}$) with shared face to
vertex $v_{i}$ in $M$ is.

\begin{center}
$A\left(v_{i}\right)=A\left(Q_{N_{1}\left(v_{i}\right)}\right)+A\left(T_{N_{1}\left(v_{i}\right)}\right)$.
\par\end{center}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{images/quad_xiong}

\caption{\label{fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
Triangulations of the quad with common vertex $v_{i}$ proposed by
{[}Xiong 2011{]} to define Mean LBO.}
\end{figure}

Applying the mean average area according to \cite{Xiong2011} of all
possible triangulations for each quad to $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
as show in figure \ref{fig:quad_xiong}.

\begin{center}
$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$
\par\end{center}

Where $q_{1},q_{2},...,q_{i},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.

\begin{equation}
A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{eq:area_1_ring_triangles_quads}
\end{equation}

Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).

\begin{equation}
\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
\end{equation}

According to (\ref{eq:eq_gradient_voronoi_area}), we have.

\begin{center}
$\nabla A\left(t_{j1}^{*}\right)=\frac{\cot\theta_{j3}\left(v_{j}-v_{i}\right)+\cot\theta_{j2}\left(v_{j}^{\prime}-v_{i}\right)}{2}$
\par\end{center}

\begin{center}
$\nabla A\left(t_{j2}^{*}\right)=\frac{\cot\theta_{j5}\left(v_{j}^{\prime}-v_{i}\right)+\cot\theta_{j4}\left(v_{j+1}-v_{i}\right)}{2}$
\par\end{center}

\begin{center}
$\nabla A\left(t_{j3}^{*}\right)=\frac{\cot\theta_{j6}\left(v_{j}-v_{i}\right)+\cot\theta_{j1}\left(v_{j+1}-v_{i}\right)}{2}$
\par\end{center}

\begin{center}
$\nabla A\left(t_{k}\right)=\frac{\cot\alpha_{k}\left(v_{k}-v_{i}\right)+\cot\beta_{k+1}\left(v_{k+1}-v_{i}\right)}{2}$
\par\end{center}

All triangles and quads configurations of the 1-neighborhood faces
adjacent to $v_{i}$ can be simplified in five simple cases how show
in figure \ref{fig:LBO-basic-5-TQ}.

Then according to equation (\ref{eq:discrete_mean_curvature_normal}),
(\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.

\begin{equation}
Acknowledgements\triangle_{g}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
\end{equation}

\begin{equation}
w_{ij}=\begin{cases}
\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
\end{cases}\label{eq:TQLBO_wij}
\end{equation}

We define a Laplacian operator as a matrix equation

\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N\left(v_{i}\right)\\
\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
0 & \mbox{otherwise}
\end{cases}\label{eq:TQLBO_Simple_Matrix}
\end{equation}

Where $L$ is the $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighbors with shared face to
$v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

Normalized version of the TQLBO as a matrix equation

\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
\delta_{ij} & \mbox{otherwise}
\end{cases}\label{eq:TQLBO-Normalized_Matrix}
\end{equation}

Where $\delta_{ij}$ being the Kronecker delta function.

\subsection{Curvature Enhancing\label{sub:Curvature-Enhancing}}

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/spectrum}

\caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
of $-5.0$.}

\end{figure*}

The curvature enhancing use the change produced by Laplacian smoothing
in the inverse direction of the curvature flow for moves the vertices
in the portions of the mesh with most curvature. In this equation
we use a diffusion process:

\begin{center}
$\frac{\partial V}{\partial t}=\lambda L\left(V\right)$ 
\par\end{center}

For solve the equation above we use implicit integration and a normalized
version of TQLBO matrix.

\begin{equation}
\left(I-\left|\lambda dt\right|W_{p}L\right)V^{\prime}=V^{t}\label{eq:Lineal_System_with_wp}
\end{equation}

\begin{center}
$V^{t+1}=V^{t}+\mbox{sign}\left(\lambda\right)\left(V^{\prime}-V^{t}\right)$
\par\end{center}

The vertices $V^{t+1}$are enhance along their inverse curvature normal
directions by solving this simple linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, $\mbox{sign}\left(x\right)$ is the sign function, and $\lambda dt$
is the enhance factor that support negative and positive values, negative
for enhancing positive for smoothing.

At the borders of the meshes that are not closed, you can not calculate
the curvature, for that reason we use the scale-dependent operator
proposed by \cite{Desbrun1999}.

Our method was designed for use with weight vertex groups to specify
the degree of impact on the solution, the weights vary between $0$
and $1$ with a value of $0$ makes no changes and with values 1 applies
the total change. The weights modifying influence zones where the
Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
The weights on each vertex will produce a different solution for that
reason are put before obtaining the solution of the linear system.
Families of shapes that are generated may change substantially with
the weights of specific control points.

The model volume increases as the lambda is most negative, this can
be countered by a simple method of preserving volume. In \cite{Desbrun1999}
present a simple method to resize the mesh but have a problem the
model suffer large displacements with $\lambda<-1.0$ or perform multiple
iterations. We propose the following solution: If we have $v_{i}^{t+1}$
is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration.

\begin{center}
$\overline{v}=\frac{1}{n}\underset{v_{i}\in V}{\sum}v_{i}$, 
\par\end{center}

$\overline{v}$ is the center of the mesh, $vol_{ini}$ is an initial
volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
we have that scale factor for resize the volume is

\begin{center}
$\beta=\left(\frac{vol_{ini}}{vol_{t+1}}\right)^{\frac{1}{3}}$
\par\end{center}

and the new vertices positions are:

\begin{center}
$v_{i\, new}^{t+1}=\beta\left(v_{i}^{t+1}-\overline{v}\right)+\overline{v}$
\par\end{center}

\subsection{Sculpting\label{sub:Sculpting}}

We design a new brush that allows enhancement of the curvatures of
a polygon mesh in real time. Our brush work well with the stroke method
\textsl{Drag Dot} developed in the sculpt mode in Blender \cite{blender}
which allows you to preview the change that occurs in the model until
you release the mouse button or tablet, also enable moves the mouse
over the model to fit exactly where you want to perform the enhancement
of the curvature.

Brushes that perform similar work as inflate can create distortions
in the mesh and can also produce self-intersections of the mesh, as
this brushes only moves the vertices along the normal and does not
take into account the global information. Whereas our method look
for the best way to make inflation while keeping the global curvature
for preserving the shape and sharp features of the model.

Our method simplifies the work required for the enhancement, which
would be to use some different brushes for inflating and some other
to soften and styling. With our enhanced brush can be performed in
one step.

For the real-time work brush is necessary that the matrix is constructed
with the vertices that are within the radius defined by the user involvement,
which dramatically reduces the size of the matrix to be processed,
the center of this sphere depends on the place where the user clicks
on the canvas and three-dimensional mesh place where the click is
projected.

Furthermore special handling is necessary with the vertices are at
the boundary of which have neighbors that are not within the radius
of impact, these vertices must be marked as boundary and not the curvature
calculated for them, but must be present in the matrix to allow the
vertices that have all their neighbors within the selection radius
to calculate correctly the curvature, this change allows the results
to be much smoother on the border. The Laplacian matrix for sculpt
mode as a matrix equation.

\begin{center}
$L\left(i,j\right)=\begin{cases}
-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert <r\\
0 & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert \geq r\\
\delta_{ij} & \mbox{otherwise}
\end{cases}$
\par\end{center}

Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
the radius $r$. Then the matrix should remove rows and columns of
vertices index that are not within the radius.

\subsection{Subdivision surfaces\label{sub:Subdivision-surfaces}}

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/cruz_lambda4}

\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
\end{figure*}

The Catmull-Clark subdivision transformation is used to smooth a surface
as the limit of sequence of subdivision steps\cite{Stam1998}. This
method do a recursive subdivision transformation that refines the
model into a linear interpolation that is a approximate smooth surface.
The process of Catmull-Clark is govern by properties of B-spline curve
from multivariate spline theory\cite{Loop1987}. In many subdivision
surfaces methods Catmull-Clark, Loop so on. The smoothness of the
model is automatically guaranteed\cite{DeRose1998}.

Catmull-Clark subdivision surface method generates smooth and continuous
models from a coarse model and produce results quickly due to the
simplicity of implementation, but with these methods is not easy to
make changes to the global curvature of the model. If we use Catmull-Clark
subdivision surfaces and curvature enhancement for modeling from sketches
with few vertices can generate families of shapes with just a parameter,
which would allow an artist to choose the model of a similar set of
options that best meets your needs without having to change each one
of the control vertices.

Our method allows the use of vertex weight paint over the control
points. The weights can be applied to the coarse model, then to perform
subdivision weights are interpolated, producing weights with smooth
changes in the zones of influence, so the curvature that is obtained
is much softer at those areas. Using vertex group weight and subdivision
surfaces is shown in figure \ref{fig:Subdivision-Cups}.c.

In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
matrix with weights corresponding to each vertex. The weights at each
vertex produce a different solution for this reason the matrix is
placed in the diffusion equation, as families that are generated may
change substantially with weighted of specific control points.

\section{Results\label{sec:Results}}

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for triangles
and quads TQLBO with several example models in figures \ref{fig:Spectrum},\ref{fig:camello_enhanced}.
We test the curvature enhance with TQLBO method on a PC with AMD Quad-Core
Processor @ 2.40 GHz and 8 GB RAM.

\begin{figure}
\includegraphics[width=1\columnwidth]{images/test_triangles_quads}

\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
(c) for triangles, (d) for quads, (e) for triangles and quads random
chosen.}

\end{figure}

Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
smoothing operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

\begin{figure}
\includegraphics[width=1\columnwidth]{images/camello_enhanced2}

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
and neck.}
\end{figure}

Figure \ref{fig:camello_enhanced} show the generation of different
version of camel with the variation of parameter lambda. In the top
row you can see results of do curvature enhance over all model, as
the lambda becomes more negative curvature in this model makes close
in the concave parts and inflates on the convex parts as shown in
figure \ref{fig:Spectrum}. We use negative values to enhance model
silhouette features, among more negative the lambda, the model will
be further enhanced the silhouette features. In the bottom row of
the figure \ref{fig:camello_enhanced} can be observed using weighted
vertex groups, which allows you to specify which areas you want to
model enhancement, on the left is the enhancement of the legs of the
camel produces enhancement of organic aspect, also notes that the
border is not distorted and smooth in the union.

We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
the two produce similar results if the triangles that compose the
mesh are the same size on average , but the normalized version is
more stable and predictable because it is not divided by the area
of the ring which may be zero or very small and cause problems due
to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
bottom row in which the mesh is deformed because the TQLBO is susceptible
to the size of the triangle. The enhancement of curvature of the model
with the normalized Laplacian operator has a more regular behavior.
The model can deform in TQLBO normalized version with large lambdas>
400 intersects self, but produces no peaks observed with the TQLBO.
Figure \ref{fig:(a)Monkey} observed different results because the
area of the triangles in this model is not so regular triangles where
greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
and where the smaller triangles are produced greater enhancement (figure
\ref{fig:(a)Monkey}.c chin).

Our method for enhancement of the silhouette features is predictable
and invariant under isometric transformations as those present in
some animations (see Figure \ref{fig:Animated_Camell}) in this animation
shows some poses of a camel doing a walk. In this animation the legs
and neck are the parts that enhancement is performed as shown in the
bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
produced by methods such as pose interpolation or animation rigging
not significantly affect the result as with camel legs in each sample
pose different flexion of the leg joints enhancement camel keeps flesh-like
shapes in the pattern produced original by the artist. This is due
to the diffusion process which is subjected to the mesh so that small
local changes are treated without significantly affecting global solution.
Our method is invariant of rotation, since depends solely the normal
field of the mesh, wish is invariant under global rotations.

\begin{figure}
\includegraphics[width=1\columnwidth]{images/sculpt_brush}

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Enhance curvature brush for leg into
red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
blue circle, (c) Enhance curvature brush for fingers in red circle.}
\end{figure}

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
locally in real time. One pass was used with the brush as shown in
the figure with the blue and red radius. In the bottom of the figure
\ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process.

Methods using Catmull-Clark subdivision surface and the enhancement
allows to modify the curvature that is obtained with the process of
subdivision as shown in figure \eqref{fig:Subdivision-Cups} this
test used a coarse model of a cup, after the model was performed subdivision
then was performed Laplacian smoothing and enhancement by modifying
the parameters $\lambda$ y $\lambda_{e}$ corresponding to the lambda
for rings and edges respectively. In figure \eqref{fig:Subdivision-Cups}.c,
\eqref{fig:Subdivision-Cups}.d shows also the use weight vertex groups
over coarse models with subdivision surfaces that allowed to generate
the weights for the new interpolated vertices, these new weights were
used for the enhancement obtained the 6 cups that are to the right
of the figure \eqref{fig:Subdivision-Cups}.d.

Laplacian smoothing applied with simple subdivision may produce results
similar to obtained with Catmull-Clark whose models are on average
equal triangles as shown in figure \ref{fig:Catmull_Clark} green
model and that obtained with Laplacian smoothing $\lambda=60.0$,
$\lambda_{e}=12.0$, but also can modify the curvature obtained after
applying Catmull-Clark as shown in the three columns to the right
of the figure \ref{fig:Catmull_Clark}.

\begin{figure}
\includegraphics[width=1\columnwidth]{images/monkey}

\caption{\label{fig:(a)Monkey}(a) Top row: Original model scaled by 4. Bottom
row: Original Model (b) Top and bottom row: enhancing with Normalized-TQLBO
$\lambda=-50$ (c) Top and bottom row: enhancing with TQLBO $\lambda=-50$.}
\end{figure}

\begin{figure*}[t]
\includegraphics[width=1\textwidth]{images/camello_walk2}

\caption{\label{fig:Animated_Camell}Our method is pose insensitive. The enhanced
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Curvature enhancing with weight
vertex group, $\lambda=-400$ and $2$ iterations. }
\end{figure*}

\subsection{Implementation\label{sub:Implementation}}

Our method was implemented how a modifier for modelling and brush
for sculpting on the Blender software \cite{blender} with C and C++.
Working with Blender allowed us to test the method interactively with
others as Catmull-Clark, weight vertex groups and sculpting system
in Blender.

To improve performance, we worked with the Blender mesh struct calculating
all possible data each time visiting each triangle or quad and adding
to its corresponding index in a list that stored the sum of the Laplacian
weights of the ring, in this way only had to visit two times the list
of faces of the mesh list and the two times the list of the edges
if the mesh was not closed. To brush sculpting mode was necessary
to create a list that will map the index of the selected vertices
to a list from 1 to N where N is the number of vertices selected and
the number of rows in the linear system to solve, with this drastically
reduced the calculations should make working with the tool allowing
real-time. In the construction of our Laplacian matrix were blocked
at vertices having faces areas or lengths edges with value zero that
can cause spikes and bad results.

The matrix \ref{eq:TQLBO_Simple_Matrix} is sparse since the number
of neighbors per vertex corresponding to the number of data per row
is small compared to the total number of vertices in the mesh. To
solve the linear system equation \ref{eq:Lineal_System_with_wp} was
used OpenNL which is a a library for solving sparse linear system.

\section{Conclusion and future work\label{sec:Conclusion-and-future}}

We present an extension of the Laplace Beltrami operator for triangles
and quads that can work in production environments without conversion
that provides results similar to those obtained by working only with
triangles or quads.

We introduced a new way to perform enhancement silhouettes in a mesh
for modeling or sculpted in a few steps allows the modification of
the curvature of a model while maintaining its overall shape. We introduce
a new method of modeling and show some of its possible uses. We show
that the method behaves in predictable ways which facilitate the learning
process, it also showed that the method works well with isometric
transformations opening the possibility of introducing it on the stages
of animation.

We demonstrate that this tool serves to work in the early stages in
which are used coarse models to permit modifying the curvature generated
by the Catmull-Clark subdivision surfaces, avoiding the edition of
the vertices to have only to change a few parameters.

As future work we would like to analyze theoretically the relationship
between the Catmull-Clark subdivision surfaces and Laplacian smoothing
because in some cases can produce very similar results. But the subdivision
surface is a fast method thereby reducing computation times for calculate
curvature in the mesh.

\section*{Acknowledgments}

We wold like to thank Eduardo Romero and CIM\&LAB Computer Imaging
\& Medical Applications Laboratory for their support of our research.

This work was supported in part by the Blender Foundation, Google
Summer of code program at 2012.

Livingstone elephant model is provided courtesy of INRIA and ISTI
by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
Technology Ltd, Camel model is provided under a Creative Commons BY
license.

\bibliographystyle{acmsiggraph/acmsiggraph}
\bibliography{template}

\end{document}

### 2013-01-03 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

--- 2013-01-03 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
@@
 % Paper title.
-\title{Curvature Enhance With Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes}
 
@@
 
-\teaser{\includegraphics[width=1\textwidth]{images/teaser_cup} \caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
-from coarse model to enhancing the curvature obtained from Catmull-Clark
-Subdivision and the use of constraints over coarse model with weight
-vertex group in red.}
+\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
+from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
+of $-5.0$.}
 }
@@
 \begin{abstract}
-This paper proposes a novel method for modelling polygonal mesh using
+This paper proposes a novel method for modeling polygonal mesh using
 curvature enhancing. This method use our extension of Laplace Beltrami
-operator for triangles and quads meshes to enhance global curvature
+operator for hybrid quad/triangle meshes to enhance global curvature
 in the model. This work present a novel applications of curvature
-enhancement in sculpting and modelling with subdivision surfaces and
+enhancement in sculpting and modeling with subdivision surfaces and
 weight vertex groups. We show a series of graphics examples that demonstrate
@@
 
+\TOGlinkslist
+
+\copyrightspace
+
 \section{Introduction}
-
-%\copyrightspace
 
@@
 of triangles and quads. Also shows some results of curvature enhancement
-applications in sculpting, subdivision and modelling methods.
+applications in sculpting, subdivision and modeling methods.
 
@@
 \begin{equation}
-Acknowledgements\triangle_{g}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
+\triangle_{g}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
 \end{equation}
@@
 \begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/spectrum}
+\includegraphics[width=1\textwidth]{images/teaser_cup}
 
-\caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
-from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
-of $-5.0$.}
+\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
+from coarse model to enhancing the curvature obtained from Catmull-Clark
+Subdivision and the use of constraints over coarse model with weight
+vertex group in red.}
 
@@
 
+\begin{figure*}[t]
+\includegraphics[width=1\textwidth]{images/cruz_lambda4}
+
+\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
+with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
+$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
+first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
+and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+\end{figure*}
+
 We design a new brush that allows enhancement of the curvatures of
@@
 
-\begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/cruz_lambda4}
-
-\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
-with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
-$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
-first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
-and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
-\end{figure*}
-
 The Catmull-Clark subdivision transformation is used to smooth a surface
@@
 
-\begin{figure}
-\includegraphics[width=1\columnwidth]{images/test_triangles_quads}
-
-\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
-(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
-(c) for triangles, (d) for quads, (e) for triangles and quads random
-chosen.}
-
-\end{figure}
-
 Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/camello_enhanced2}
+\includegraphics[width=1\columnwidth]{images/test_triangles_quads}
 
-\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
-and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
-and neck.}
+\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
+(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
+(c) for triangles, (d) for quads, (e) for triangles and quads random
+chosen.}
 \end{figure}
@@
 
+\begin{figure}
+\includegraphics[width=1\columnwidth]{images/camello_enhanced2}
+
+\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
+Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
+and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
+and neck.}
+\end{figure}
+
 Our method for enhancement of the silhouette features is predictable
@@
 
-\begin{figure}
-\includegraphics[width=1\columnwidth]{images/sculpt_brush}
-
-\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Enhance curvature brush for leg into
-red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
-blue circle, (c) Enhance curvature brush for fingers in red circle.}
-\end{figure}
-
 Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
@@
 With this new method can easily enhance organic features how muscles
-during the sculpting process.
+during the sculpting process. In figure \ref{fig:Performance-sculpt}
+we show the performance of curvature enhancement brush, in this experimet
+we use three models with 12K, 40K and 164K this models were sculpted
+with curvature enhance brush in eache step the brush sphere contain
+a variable number of vertices for processing. The processing time
+for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
+for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
+times are good, because usually an artist sculpts a model for parts,
+and each part is represented by an average of about 3000 vertices
+in the models we use.
 
@@
 \begin{figure}
+\includegraphics[width=1\columnwidth]{images/sculpt_brush}
+
+\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
+for leg into blue circle, (c) Enhance curvature brush for leg into
+red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
+blue circle, (c) Enhance curvature brush for fingers in red circle.}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{images/verts_per_second_sculpt}
+
+\caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
+enhance brush in terms of vertices sculpted per second. Three models
+with 12K, 40K, 164K vertices used for sculpting in real time.}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=1\columnwidth]{images/monkey}
@@
 
-Our method was implemented how a modifier for modelling and brush
-for sculpting on the Blender software \cite{blender} with C and C++.
+Our method was implemented how a modifier for modeling and brush for
+sculpting on the Blender software \cite{blender} with C and C++.
 Working with Blender allowed us to test the method interactively with
@@
 by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
-Technology Ltd, Camel model is provided under a Creative Commons BY
-license.
+Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
+Commons Attribution 3.0 Unported License.
 

### 2013-01-04 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
-%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 subdivision surfaces and sculpting; Lastly some results are shown
-in graphic examples of Laplacian operator for polygonal meshes composed
-of triangles and quads. Also shows some results of curvature enhancement
-applications in sculpting, subdivision and modeling methods.
+in graphic examples of Laplacian operator for hybrid quad/triangle
+meshes. Also shows some results of curvature enhancement applications
+in sculpting, subdivision and modeling methods.
 
 \textbf{Contributions} Our work present an extension of the Laplace
-Beltrami operator for meshes of arbitrary topology composed for triangles
-and quads representing a larger spectrum of mesh that works with today
-eliminating the need for preprocessing and allows the preservation
-of the original topology. With this operator we proposed a method
-to generate family of parameterized shapes, in a robust and predictable
-way. Our method enable to customization of smoothness and curvature
-obtained during subdivision surfaces process. We proposed a new brush
-for enhance silhouette features of mesh in modeling and sculpting.
+Beltrami operator for hybrid quad/triangle meshes representing a larger
+spectrum of mesh that works with today eliminating the need for preprocessing
+and allows the preservation of the original topology. With this operator
+we proposed a method to generate family of parameterized shapes, in
+a robust and predictable way. Our method enable to customization of
+smoothness and curvature obtained during subdivision surfaces process.
+We proposed a new brush for enhance silhouette features of mesh in
+modeling and sculpting.
 
@@
 
-\subsection{Laplace Beltrami operator over triangular and quadrilateral meshes
-TQLBO\label{sub:Laplace-Beltrami-operator}}
+\subsection{Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes TQLBO\label{sub:Laplace-Beltrami-operator}}
 
@@
 
-The area of $1$-ring neighborhood ($N_{1}$) with shared face to
-vertex $v_{i}$ in $M$ is.
+The area of $1$-ring neighborhood ($N_{1}$) with shared face quad
+or triangle to vertex $v_{i}$ in $M$ is.
 
@@
 
-Where $q_{1},q_{2},...,q_{i},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
+Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
 and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.
@@
 
-All triangles and quads configurations of the 1-neighborhood faces
-adjacent to $v_{i}$ can be simplified in five simple cases how show
-in figure \ref{fig:LBO-basic-5-TQ}.
+All triangles and quads configurations of the 1-ring neighborhood
+faces adjacent to $v_{i}$ can be simplified in five simple cases
+how show in figure \ref{fig:LBO-basic-5-TQ}.
 
@@
 of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
-$N\left(v_{i}\right)$ is the 1-ring neighbors with shared face to
-$v_{i}$, $A_{i}$ is the ring area around $v_{i}$.
+$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
+to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.
 
@@
 iterations. We propose the following solution: If we have $v_{i}^{t+1}$
-is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration.
+is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration, we define
+$\overline{v}$ as:
 
@@
 from multivariate spline theory\cite{Loop1987}. In many subdivision
-surfaces methods Catmull-Clark, Loop so on. The smoothness of the
-model is automatically guaranteed\cite{DeRose1998}.
+surfaces methods Catmull-Clark, Loop so on, the smoothness of the
+model is automatically guaranteed \cite{DeRose1998}.
 
@@
 make changes to the global curvature of the model. If we use Catmull-Clark
-subdivision surfaces and curvature enhancement for modeling from sketches
-with few vertices can generate families of shapes with just a parameter,
-which would allow an artist to choose the model of a similar set of
-options that best meets your needs without having to change each one
-of the control vertices.
+subdivision surfaces and curvature enhancement for modeling from coarse
+models with few vertices can generate families of shapes with just
+change a parameter, which would allow an artist to choose the model
+of a similar set of options that best meets your needs without having
+to change each one of the control vertices.
 
@@
 In this section we describe the results of our curvature enhance method
-that used our extension of Laplace Beltrami operator for triangles
-and quads TQLBO with several example models in figures \ref{fig:Spectrum},\ref{fig:camello_enhanced}.
-We test the curvature enhance with TQLBO method on a PC with AMD Quad-Core
-Processor @ 2.40 GHz and 8 GB RAM.
+that used our extension of Laplace Beltrami operator for hybrid quad/triangle
+meshes with several example models in figures \ref{fig:Spectrum},
+\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
+\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
+\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
+enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
+GHz and 8 GB RAM.
 
-Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
-smoothing operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
+Figure \ref{fig:TQLBO_test} show the results when applying Laplace
+Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
 in a model with a simple subdivision. In column (c) Laplacian smoothing
@@
 
+Methods using Catmull-Clark subdivision surface and the enhancement
+allows to modify the curvature that is obtained with the process of
+subdivision as shown in figure \eqref{fig:Subdivision-Cups} this
+test used a coarse model of a cup, after the model was performed subdivision
+then was performed Laplacian smoothing and enhancement by modifying
+the parameters $\lambda$ y $\lambda_{e}$ corresponding to the lambda
+for rings and edges respectively. In figure \eqref{fig:Subdivision-Cups}.c,
+\eqref{fig:Subdivision-Cups}.d shows also the use weight vertex groups
+over coarse models with subdivision surfaces that allowed to generate
+the weights for the new interpolated vertices, these new weights were
+used for the enhancement obtained the 6 cups that are to the right
+of the figure \eqref{fig:Subdivision-Cups}.d.
+
+Laplacian smoothing applied with simple subdivision may produce results
+similar to obtained with Catmull-Clark whose models are on average
+equal triangles as shown in figure \ref{fig:Catmull_Clark} green
+model and that obtained with Laplacian smoothing $\lambda=60.0$,
+$\lambda_{e}=12.0$, but also can modify the curvature obtained after
+applying Catmull-Clark as shown in the three columns to the right
+of the figure \ref{fig:Catmull_Clark}.
+
 Figure \ref{fig:camello_enhanced} show the generation of different
@@
 border is not distorted and smooth in the union.
-
-We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
-and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
-the two produce similar results if the triangles that compose the
-mesh are the same size on average , but the normalized version is
-more stable and predictable because it is not divided by the area
-of the ring which may be zero or very small and cause problems due
-to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
-bottom row in which the mesh is deformed because the TQLBO is susceptible
-to the size of the triangle. The enhancement of curvature of the model
-with the normalized Laplacian operator has a more regular behavior.
-The model can deform in TQLBO normalized version with large lambdas>
-400 intersects self, but produces no peaks observed with the TQLBO.
-Figure \ref{fig:(a)Monkey} observed different results because the
-area of the triangles in this model is not so regular triangles where
-greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
-and where the smaller triangles are produced greater enhancement (figure
-\ref{fig:(a)Monkey}.c chin).
 
@@
 Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
-locally in real time. One pass was used with the brush as shown in
-the figure with the blue and red radius. In the bottom of the figure
-\ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
+brush for sculpting in real time. One pass was used with the brush
+as shown in the figure with the blue and red radius. In the bottom
+of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
 and looks like two bubbles stuck, so do the fingers on the bottom
@@
 we show the performance of curvature enhancement brush, in this experimet
-we use three models with 12K, 40K and 164K this models were sculpted
-with curvature enhance brush in eache step the brush sphere contain
-a variable number of vertices for processing. The processing time
-for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
+we use three models with 12K, 40K and 164K vertices, this models were
+sculpted with curvature enhance brush in eache step the brush sphere
+contain a variable number of vertices for processing. The processing
+time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
 for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
@@
 
-Methods using Catmull-Clark subdivision surface and the enhancement
-allows to modify the curvature that is obtained with the process of
-subdivision as shown in figure \eqref{fig:Subdivision-Cups} this
-test used a coarse model of a cup, after the model was performed subdivision
-then was performed Laplacian smoothing and enhancement by modifying
-the parameters $\lambda$ y $\lambda_{e}$ corresponding to the lambda
-for rings and edges respectively. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use weight vertex groups
-over coarse models with subdivision surfaces that allowed to generate
-the weights for the new interpolated vertices, these new weights were
-used for the enhancement obtained the 6 cups that are to the right
-of the figure \eqref{fig:Subdivision-Cups}.d.
-
-Laplacian smoothing applied with simple subdivision may produce results
-similar to obtained with Catmull-Clark whose models are on average
-equal triangles as shown in figure \ref{fig:Catmull_Clark} green
-model and that obtained with Laplacian smoothing $\lambda=60.0$,
-$\lambda_{e}=12.0$, but also can modify the curvature obtained after
-applying Catmull-Clark as shown in the three columns to the right
-of the figure \ref{fig:Catmull_Clark}.
+We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
+and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
+the two produce similar results if the triangles that compose the
+mesh are the same size on average , but the normalized version is
+more stable and predictable because it is not divided by the area
+of the ring which may be zero or very small and cause problems due
+to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
+bottom row in which the mesh is deformed because the TQLBO is susceptible
+to the size of the triangle. The enhancement of curvature of the model
+with the normalized Laplacian operator has a more regular behavior.
+The model can deform in TQLBO normalized version with large lambdas>
+400 intersects self, but produces no peaks observed with the TQLBO.
+Figure \ref{fig:(a)Monkey} observed different results because the
+area of the triangles in this model is not so regular triangles where
+greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
+and where the smaller triangles are produced greater enhancement (figure
+\ref{fig:(a)Monkey}.c chin).
 

### 2013-01-05 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 % Author and Affiliation (multiple authors).
-\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
-\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
+\author{paper 000X }
+%\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
+%\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
 %\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}
@@
 % comma-delimited, and adds this information to the PDF metadata.
-\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
+%\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
+\pdfauthor{Anonymous}
 
@@
 \begin{abstract}
-This paper proposes a novel method for modelling polygonal mesh using
+This paper proposes a novel method for modeling polygonal mesh using
 curvature enhancing. This method use our extension of Laplace Beltrami
-operator for triangles and quads meshes to enhance global curvature
+operator for hybrid quad/triangle meshes to enhance global curvature
 in the model. This work present a novel applications of curvature
-enhancement in sculpting and modelling with subdivision surfaces and
+enhancement in sculpting and modeling with subdivision surfaces and
 weight vertex groups. We show a series of graphics examples that demonstrate
-the quality, predictability and flexibility of our results in a real
-production environment with software blender.
+the quality, predictability and flexibility of our results.
 \end{abstract}
@@
 
-\section{Introduction}
+\TOGlinkslist
 
 %\copyrightspace
+
+\section{Introduction}
 
@@
 subdivision surfaces and sculpting; Lastly some results are shown
-in graphic examples of Laplacian operator for polygonal meshes composed
-of triangles and quads. Also shows some results of curvature enhancement
-applications in sculpting, subdivision and modelling methods.
+in graphic examples of Laplacian operator for hybrid quad/triangle
+meshes. Also shows some results of curvature enhancement applications
+in sculpting, subdivision and modeling methods.
 
 \textbf{Contributions} Our work present an extension of the Laplace
-Beltrami operator for meshes of arbitrary topology composed for triangles
-and quads representing a larger spectrum of mesh that works with today
-eliminating the need for preprocessing and allows the preservation
-of the original topology. With this operator we proposed a method
-to generate family of parameterized shapes, in a robust and predictable
-way. Our method enable to customization of smoothness and curvature
-obtained during subdivision surfaces process. We proposed a new brush
-for enhance silhouette features of mesh in modeling and sculpting.
+Beltrami operator for hybrid quad/triangle meshes representing a larger
+spectrum of mesh that works with today eliminating the need for preprocessing
+and allows the preservation of the original topology. With this operator
+we proposed a method to generate family of parameterized shapes, in
+a robust and predictable way. Our method enable to customization of
+smoothness and curvature obtained during subdivision surfaces process.
+We proposed a new brush for enhance silhouette features of mesh in
+modeling and sculpting.
 
@@
 
+\begin{figure*}[t]
+\includegraphics[width=1\textwidth]{images/cruz_lambda4}
+
+\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
+with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
+$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
+first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
+and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+\end{figure*}
+
 We design a new brush that allows enhancement of the curvatures of
 a polygon mesh in real time. Our brush work well with the stroke method
-\textsl{Drag Dot} developed in the sculpt mode in Blender \cite{blender}
-which allows you to preview the change that occurs in the model until
-you release the mouse button or tablet, also enable moves the mouse
-over the model to fit exactly where you want to perform the enhancement
-of the curvature.
+named \textsl{Drag Dot}  which allows you to preview the change that
+occurs in the model until you release the mouse button or tablet,
+also enable moves the mouse over the model to fit exactly where you
+want to perform the enhancement of the curvature.
 
@@
 In this section we describe the results of our curvature enhance method
-that used our extension of Laplace Beltrami operator for triangles
-and quads TQLBO with several example models in figures \ref{fig:Spectrum},\ref{fig:camello_enhanced}.
-We test the curvature enhance with TQLBO method on a PC with AMD Quad-Core
-Processor @ 2.40 GHz and 8 GB RAM.
+that used our extension of Laplace Beltrami operator for hybrid quad/triangle
+meshes with several example models in figures \ref{fig:Spectrum},
+\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
+\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
+\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
+enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
+GHz and 8 GB RAM.
+
+Figure \ref{fig:TQLBO_test} show the results when applying Laplace
+Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
+in a model with a simple subdivision. In column (c) Laplacian smoothing
+was applied to the model consists of only quads. In column (d) the
+model was converted to triangles and then Laplacian smoothing was
+applied. In column (e) the model is converted randomly some quads
+into triangles and then Laplacian smoothing was applied, showing similar
+results to those composed only of triangles or squares.
 
@@
 chosen.}
-
 \end{figure}
-
-Figure \ref{fig:TQLBO_test} show the results when applying Laplacian
-smoothing operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
-in a model with a simple subdivision. In column (c) Laplacian smoothing
-was applied to the model consists of only quads. In column (d) the
-model was converted to triangles and then Laplacian smoothing was
-applied. In column (e) the model is converted randomly some quads
-into triangles and then Laplacian smoothing was applied, showing similar
-results to those composed only of triangles or squares.
-
-\begin{figure}
-\includegraphics[width=1\columnwidth]{images/camello_enhanced2}
-
-\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
-and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
-and neck.}
-\end{figure}
-
-Figure \ref{fig:camello_enhanced} show the generation of different
-version of camel with the variation of parameter lambda. In the top
-row you can see results of do curvature enhance over all model, as
-the lambda becomes more negative curvature in this model makes close
-in the concave parts and inflates on the convex parts as shown in
-figure \ref{fig:Spectrum}. We use negative values to enhance model
-silhouette features, among more negative the lambda, the model will
-be further enhanced the silhouette features. In the bottom row of
-the figure \ref{fig:camello_enhanced} can be observed using weighted
-vertex groups, which allows you to specify which areas you want to
-model enhancement, on the left is the enhancement of the legs of the
-camel produces enhancement of organic aspect, also notes that the
-border is not distorted and smooth in the union.
-
-We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
-and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
-the two produce similar results if the triangles that compose the
-mesh are the same size on average , but the normalized version is
-more stable and predictable because it is not divided by the area
-of the ring which may be zero or very small and cause problems due
-to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
-bottom row in which the mesh is deformed because the TQLBO is susceptible
-to the size of the triangle. The enhancement of curvature of the model
-with the normalized Laplacian operator has a more regular behavior.
-The model can deform in TQLBO normalized version with large lambdas>
-400 intersects self, but produces no peaks observed with the TQLBO.
-Figure \ref{fig:(a)Monkey} observed different results because the
-area of the triangles in this model is not so regular triangles where
-greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
-and where the smaller triangles are produced greater enhancement (figure
-\ref{fig:(a)Monkey}.c chin).
-
-Our method for enhancement of the silhouette features is predictable
-and invariant under isometric transformations as those present in
-some animations (see Figure \ref{fig:Animated_Camell}) in this animation
-shows some poses of a camel doing a walk. In this animation the legs
-and neck are the parts that enhancement is performed as shown in the
-bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
-produced by methods such as pose interpolation or animation rigging
-not significantly affect the result as with camel legs in each sample
-pose different flexion of the leg joints enhancement camel keeps flesh-like
-shapes in the pattern produced original by the artist. This is due
-to the diffusion process which is subjected to the mesh so that small
-local changes are treated without significantly affecting global solution.
-Our method is invariant of rotation, since depends solely the normal
-field of the mesh, wish is invariant under global rotations.
-
-\begin{figure}
-\includegraphics[width=1\columnwidth]{images/sculpt_brush}
-
-\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Enhance curvature brush for leg into
-red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
-blue circle, (c) Enhance curvature brush for fingers in red circle.}
-\end{figure}
-
-Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
-locally in real time. One pass was used with the brush as shown in
-the figure with the blue and red radius. In the bottom of the figure
-\ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
-and looks like two bubbles stuck, so do the fingers on the bottom
-of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
-we see better results because not lost the shape of the silhouette
-and kept the details of the fingers and leg. Similar results can be
-obtained by an artist but it would take several steps and the use
-of several brushes with curvatures enhancement only takes one step.
-With this new method can easily enhance organic features how muscles
-during the sculpting process.
 
@@
 
+Figure \ref{fig:camello_enhanced} show the generation of different
+version of camel with the variation of parameter lambda. In the top
+row you can see results of do curvature enhance over all model, as
+the lambda becomes more negative curvature in this model makes close
+in the concave parts and inflates on the convex parts as shown in
+figure \ref{fig:Spectrum}. We use negative values to enhance model
+silhouette features, among more negative the lambda, the model will
+be further enhanced the silhouette features. In the bottom row of
+the figure \ref{fig:camello_enhanced} can be observed using weighted
+vertex groups, which allows you to specify which areas you want to
+model enhancement, on the left is the enhancement of the legs of the
+camel produces enhancement of organic aspect, also notes that the
+border is not distorted and smooth in the union.
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{images/camello_enhanced2}
+
+\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
+Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
+and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
+and neck.}
+\end{figure}
+
+Our method for enhancement of the silhouette features is predictable
+and invariant under isometric transformations as those present in
+some animations (see Figure \ref{fig:Animated_Camell}) in this animation
+shows some poses of a camel doing a walk. In this animation the legs
+and neck are the parts that enhancement is performed as shown in the
+bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
+produced by methods such as pose interpolation or animation rigging
+not significantly affect the result as with camel legs in each sample
+pose different flexion of the leg joints enhancement camel keeps flesh-like
+shapes in the pattern produced original by the artist. This is due
+to the diffusion process which is subjected to the mesh so that small
+local changes are treated without significantly affecting global solution.
+Our method is invariant of rotation, since depends solely the normal
+field of the mesh, wish is invariant under global rotations.
+
+Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
+brush for sculpting in real time. One pass was used with the brush
+as shown in the figure with the blue and red radius. In the bottom
+of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
+and looks like two bubbles stuck, so do the fingers on the bottom
+of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
+we see better results because not lost the shape of the silhouette
+and kept the details of the fingers and leg. Similar results can be
+obtained by an artist but it would take several steps and the use
+of several brushes with curvatures enhancement only takes one step.
+With this new method can easily enhance organic features how muscles
+during the sculpting process. In figure \ref{fig:Performance-sculpt}
+we show the performance of curvature enhancement brush, in this experimet
+we use three models with 12K, 40K and 164K vertices, this models were
+sculpted with curvature enhance brush in eache step the brush sphere
+contain a variable number of vertices for processing. The processing
+time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
+for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
+times are good, because usually an artist sculpts a model for parts,
+and each part is represented by an average of about 3000 vertices
+in the models we use.
+
+We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
+and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
+the two produce similar results if the triangles that compose the
+mesh are the same size on average , but the normalized version is
+more stable and predictable because it is not divided by the area
+of the ring which may be zero or very small and cause problems due
+to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
+bottom row in which the mesh is deformed because the TQLBO is susceptible
+to the size of the triangle. The enhancement of curvature of the model
+with the normalized Laplacian operator has a more regular behavior.
+The model can deform in TQLBO normalized version with large lambdas>
+400 intersects self, but produces no peaks observed with the TQLBO.
+Figure \ref{fig:(a)Monkey} observed different results because the
+area of the triangles in this model is not so regular triangles where
+greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
+and where the smaller triangles are produced greater enhancement (figure
+\ref{fig:(a)Monkey}.c chin).
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{images/sculpt_brush}
+
+\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
+for leg into blue circle, (c) Enhance curvature brush for leg into
+red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
+blue circle, (c) Enhance curvature brush for fingers in red circle.}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\columnwidth]{images/verts_per_second_sculpt}
+
+\caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
+enhance brush in terms of vertices sculpted per second. Three models
+with 12K, 40K, 164K vertices used for sculpting in real time.}
+\end{figure}
+
 \begin{figure}
@@
 
-We wold like to thank Eduardo Romero and CIM\&LAB Computer Imaging
-\& Medical Applications Laboratory for their support of our research.
+We wold like to thank  anonymous friends for their support of our
+research.
 

### 2013-01-05 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 %% Do not edit unless you really know what you are doing.
-\documentclass[english,annual]{acmsiggraph}
+\documentclass[english,review]{acmsiggraph}
 \usepackage[T1]{fontenc}
@@
 % Author and Affiliation (multiple authors).
-\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
-\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
+\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
+\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
+ \\Cimalab Research Group\\National University of Colombia}
 %\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}
@@
 weight vertex groups. We show a series of graphics examples that demonstrate
-the quality, predictability and flexibility of our results in a real
-production environment with software blender.
+the quality, predictability and flexibility of our results.
 \end{abstract}
@@
 
-\copyrightspace
+%\copyrightspace
 
@@
 a polygon mesh in real time. Our brush work well with the stroke method
-\textsl{Drag Dot} developed in the sculpt mode in Blender \cite{blender}
-which allows you to preview the change that occurs in the model until
-you release the mouse button or tablet, also enable moves the mouse
-over the model to fit exactly where you want to perform the enhancement
-of the curvature.
+named \textsl{Drag Dot}  which allows you to preview the change that
+occurs in the model until you release the mouse button or tablet,
+also enable moves the mouse over the model to fit exactly where you
+want to perform the enhancement of the curvature.
 

### 2013-01-08 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
-%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
-\documentclass[english,annual]{acmsiggraph}
+\documentclass[english,review]{acmsiggraph}
 \usepackage[T1]{fontenc}
@@
 % assigned.
-\TOGonlineid{45678}
+\TOGonlineid{XXXXX}
 
@@
 % Paper title.
-\title{Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes}
+\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 % Author and Affiliation (multiple authors).
-\author{paper 000X }
-%\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
-%\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
+\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
+\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
+ \\Cimalab Research Group\\National University of Colombia}
 %\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}
@@
 \begin{abstract}
-This paper proposes a novel method for modeling polygonal mesh using
-curvature enhancing. This method use our extension of Laplace Beltrami
-operator for hybrid quad/triangle meshes to enhance global curvature
-in the model. This work present a novel applications of curvature
-enhancement in sculpting and modeling with subdivision surfaces and
-weight vertex groups. We show a series of graphics examples that demonstrate
-the quality, predictability and flexibility of our results.
+This paper proposes a novel method for modeling a polygonal mesh by
+enhancing the object curvature. This method uses an adapted extension
+of the Laplace Beltrami operator for hybrid quad/triangle meshes,
+to enhance the global curvature. Along with the method, this work
+also presents new applications of curvature enhancement in sculpting
+and modeling with subdivision surfaces and weight vertex groups. A
+series of graphics examples demonstrates the quality, predictability
+and flexibility of the method in a real production environment with
+software blender.
 \end{abstract}
@@
 
-Over the last years have been developed novel techniques of modeling
-that can generate a variety of shapes to look natural and realistic
-\cite{Botsch2006}. Editing techniques have evolved from affine transformations
-to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
+Over the last years several modeling techniques have been developed
+to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
+Editing techniques have evolved from affine transformations to advanced
+tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
 editing and creation from sketches \cite{Igarashi1999,Gonen2012},
-complex interpolation techniques \cite{Sorkine2004,Zhou2005}, among
-others.
+and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
 
-Traditional methods for smooth surfaces from coarse geometry like
-Catmull-Clark have been widely developed \cite{Catmull1978,Stam1998},
-these works generalize uniform B-cubic splines knot insertion to meshes,
-some of them add control of the results with the use of creases to
-produce sharp edges \cite{DeRose1998}, or the modification of weights
-on the vertices that control locally the zone of influence \cite{Biermann2000},
-instead our method performs a feature enhancement of the model allowing
-parameterize the curvature of the surface creating a family of different
-versions of the same object preserving detail and realistic natural
-look of the original model.
+Traditional methods for smoothing surfaces from coarse geometry, like
+the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
+These works generalize the uniform B-cubic splines knot insertion
+to meshes, some of them adding some type of control, for instance
+with the use of creases to produce sharp edges \cite{DeRose1998},
+or the modification of weights on the vertices to locally control
+the zone of influence \cite{Biermann2000}. Instead, the presented
+method performs a feature enhancement of the model by parameterizing
+the surface curvature and thereby creating a family of different versions
+of the same object, preserving therefore the detail of the original
+model and a realistic appearance.
 
-Many types of brushes have been developed to sculpt meshes, brushes
-that perform inflation lose detail when inflating the vertices \cite{Stanculescu2011},
-our method allows inflation of the mesh vertices moving in the opposite
-direction to the curvature preserving the shape and sharp features
+On the other hand, many types of brushes have been developed to sculpt
+meshes. Brushes that perform inflation end up by losing detail when
+inflating the vertices \cite{Stanculescu2011}, in contrast the presented
+method allows inflation of the mesh vertices by moving them towards
+the opposite curvature direction, conserving the shape and sharp features
 of the model.
 
-This work is organized as follows: In the section \ref{sub:1.1-Related-work}
-show works related to the Laplacian mesh processing, digital sculpting,
-and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
-we describe the theoretical framework of the Laplacian operator for
-polygon meshes; In the section \ref{sec:Proposed-Method} we present
-our proposed method for curvature enhancement and applications on
-subdivision surfaces and sculpting; Lastly some results are shown
-in graphic examples of Laplacian operator for hybrid quad/triangle
-meshes. Also shows some results of curvature enhancement applications
-in sculpting, subdivision and modeling methods.
+\textbf{Contributions} This work presents an extension of the Laplace
+Beltrami operator for hybrid quad/triangle meshes representing a larger
+mesh spectrum from what has been presented so far. The method eliminates
+the need of preprocessing and allows preservation of the original
+topology. Likewise, along with this operator, it is proposed a method
+to generate a family of parameterized shapes, in a robust and predictable
+way. This method enables customization of the smoothness and curvature,
+obtained during the subdivision surfaces process. Finally, it is proposed
+a new brush for enhancing silhouette mesh features in modeling and
+sculpting.
 
-\textbf{Contributions} Our work present an extension of the Laplace
-Beltrami operator for hybrid quad/triangle meshes representing a larger
-spectrum of mesh that works with today eliminating the need for preprocessing
-and allows the preservation of the original topology. With this operator
-we proposed a method to generate family of parameterized shapes, in
-a robust and predictable way. Our method enable to customization of
-smoothness and curvature obtained during subdivision surfaces process.
-We proposed a new brush for enhance silhouette features of mesh in
-modeling and sculpting.
+This work is organized as follows: Section \ref{sub:1.1-Related-work}
+presents works related to the Laplacian mesh processing, digital sculpting,
+and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
+, it is described the theoretical framework of the Laplacian operator
+for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
+the method for curvature enhancement and applications of subdivision
+of surfaces and sculpting; finally some Laplacian operator results,
+to hybrid quad/triangle meshes are graphically shown as well as results
+of the curvature enhancement applications in sculpting, subdivision
+and modeling.
 
@@
 
-Many tools have been developed for modeling based on Laplacian mesh
-processing. Thanks to the kindness of the Laplacian operator these
-tools have in common the need for preservation of the geometric details
-of the surface for the different processes such as: free-form deformation,
-fusion, morphing and other applications \cite{Sorkine2004}.
+Many tools have been developed for modeling, based on Laplacian mesh
+processing. Thanks to the advantages of the Laplacian operator, these
+different tools preserve the surface geometric details when using
+them for different processes such as free-form deformation, fusion,
+morphing and other application\cite{Sorkine2004}.
 
-Methods for offset polygon meshes based on the curvature defined by
-the Laplace Beltrami operator have been developed. These methods allow
-adjusting shape offset by a constant distance with high enough precision
-to minimize Hausdorf error. The problem with these methods is the
-loss of detail caused by smoothing, which depends on the size of the
-offset \cite{Zhuo2012}. In volumetric approaches on computing the
-offset boundary that are based on distance field computation in point-based
-representation, this methods the topology of the offset model can
-be different from that the original geometry \cite{Chen2011}.
+Offset polygon mesh methods, based on the curvature defined by the
+Laplace Beltrami operator, have been developed. These methods adjust
+the shape offset by a constant distance, with high precision as to
+minimize the Hausdorf error. Nevertheless, these methods fail to conserve
+enough detail because of the smoothing, a crucial issue which depends
+on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
+representation the computing the offset boundary that are based on
+distance field computation, when performing the offset, the topology
+of the model may be different from the original, changing the original
+design \cite{Chen2011}.
 
 \cite{Gal2009} proposes automatic features detection and shape edition
-with feature inter-relationship preservation. In analysis step they
-define salient surface features how ridges and valleys with base on
-first and second order curvature derivatives \cite{Ohtake2004}, and
-angle-based threshold. In feature characterization step the curves
-are classified by several properties as planar or non-planar, approximated
-by line, circle or ellipse shapes, and so on. In edit step the user
-define initial change over several feature and then this edit is propagated
-over other features with base in your inter-relationships. This method
-works fine with objects that have sharp edges composed of basic geometric
-shapes such as lines, circles or ellipses but this method has difficulties
-when models are smoother with organic forms and cannot find the features
-to edit and preserve.
+with feature inter-relationship preservation. They define salient
+surface features like ridges and valleys with based the first and
+second order curvature derivatives \cite{Ohtake2004}, and angle-based
+threshold. Later the curves are classified by several properties as
+planar or non-planar, approximated by lines, circles, ellipses and
+other complex shapes. In then the user defines an initial change over
+several features and then this change is propagated over other features
+with base in the classified shapes and the inter-relationships between
+these. This method works fine with objects that have sharp edges composed
+of basic geometric shapes such as lines, circles or ellipses but method
+has problems to classify when models are smoother with organic forms
+because it cannot find the features to edit and preserve.
 
-Digital sculpting is divided into two principal methods: based on
-polygonal methods and voxel grids-based methods. Brushes for inflate
+Digital sculpting can be divided into two principal approaches: based
+on polygonal methods and voxel grid-based methods. Brushes for inflate
 operations in polygonal methods only depends on the normal at each
-vertex \cite{Stanculescu2011}, in grids-based some operations permit
-add or remove voxels and then have that processing isosurfaces from
-volume to produce polygonal meshes representation \cite{Galyean1991}.
-The problem whit this type of operations is the difficult to maintain
-surface details during larger scale deformation.
+vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
+allow to add or remove voxels, for produce polygonal meshes require
+processing isosurfaces from volume \cite{Galyean1991}. The problem
+whit this type of operations is the difficult to maintain surface
+details during larger scale deformation.
 
@@
 
-The Laplacian Smooth techniques allows you to reduce noise on a mesh's
-surface with minimal changes on its shape. Computer graphics objects
-which have been reconstructed from real world, contain undesirable
-noise. A Laplacian smoothing removes undesirable noise while still
-preserves desirable geometry as well as the shape of the original
-model.
+Computer graphics objects which have been reconstructed from real
+world, contain undesirable noise. Laplacian Smooth techniques allow
+noise reduction on a mesh's surface with minimal changes on its shape
+while still preserves desirable geometry as well as the shape of the
+original model.
 
-The functional used in many Laplacian smoothing approach to constrain
+The functional used in many Laplacian smoothing approaches to constrain
 energy minimization is based on a total curvature of a surface $S$.
@@
 
-Consider a surface $S$ compound by a set of triangles around vertex
+Consider a surface $S$ composed by a set of triangles around vertex
 $v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
-show in figure \ref{fig:voronoi_region}, The change in area produced
-by move $v_{i}$ is named gradient of \textit{Voronoi region \cite{Pinkall1993,Desbrun1999,Meyer2003}.}
+show in figure \ref{fig:voronoi_region}, The change in the area produced
+by the movement of $v_{i}$ is named gradient of \textit{Voronoi region
+\cite{Pinkall1993,Desbrun1999,Meyer2003}.}
 
@@
 
-The LBO has desirable features, one feature of the LBO is in direction
-of surface area minimization, allowing us to minimize energy using
-it on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).
+The LBO has desirable features: one feature of the LBO is in direction
+of surface area minimization, allowing to minimize energy using it
+on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).
 
@@
 
-Our method allow the editing of geometric features using the curvature
-enhancement and smoothing. Generating a parameterized family of shapes
-using a set of vertices representing a coarse sketch of the desired
+Our method allows the editing of geometric features using the curvature
+enhancement and smoothing, generating a parameterized family of shapes
+from a set of vertices which represent a coarse sketch of the desired
 model. Our approach can be mixed with traditional or uniform subdivision
-surfaces methods and is iterative and converges towards a continuous
+surfaces methods, is iterative and converges towards a continuous
 and smooth version of the original model.
@@
 Our method allows the use of soft constraints weighting the effect
-of smoothing at each vertex based on a normalized weight, the weights
-are assigned to the control vertices of the original mesh or. The
-weights of the new vertices resulting from the subdivisions are calculated
-by interpolation, allowing to modify the behavior of the method on
-exact regions of the original model.
+of smoothing at each vertex based on a normalized weight, which are
+assigned to the control vertices of the original mesh or. The weights
+of the new vertices resulting from the subdivisions are calculated
+by interpolation, allowing modifying the behavior of the method on
+specific regions of the original model.
 
-Our approach contain an extension of the Laplace Beltrami operator
-for meshes composed by triangles and quads. Using meshes composed
-by triangles and quads has been increasing in recent years due to
-the flexibility of modeling tools as Blender 3D \cite{blender}. Today
-many artists manually connecting vertices such that its edition allows
-simplest way to perform animation processes and interpolation \cite{Mullen2007}.
+Our approach is based on an extension of the Laplace Beltrami operator
+for meshes composed by triangles and quads. Interest on meshes composed
+by triangles and quads has increasing in recent years due to the flexibility
+of modeling tools as Blender 3D \cite{blender}. Today many artists
+manually connect vertices such that its edition allows a simple way
+to perform animation processes and interpolation \cite{Mullen2007}.
 For these reasons it is very important to develop an operator that
@@
 
-All triangles and quads configurations of the 1-ring neighborhood
-faces adjacent to $v_{i}$ can be simplified in five simple cases
-how show in figure \ref{fig:LBO-basic-5-TQ}.
+Thus triangles and quads configurations of the 1-ring neighborhood
+faces adjacent to $v_{i}$ can be simplified to five cases shown in
+figure \ref{fig:LBO-basic-5-TQ}.
 
@@
 
-Where $L$ is the $n\times n$ matrix, $n$ is the number of vertices
+Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
 of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
@@
 
-The curvature enhancing use the change produced by Laplacian smoothing
-in the inverse direction of the curvature flow for moves the vertices
-in the portions of the mesh with most curvature. In this equation
-we use a diffusion process:
+The curvature enhancing uses the inverse direction of the curvature
+flow to move the vertices in the portions of the mesh with most curvature.
+In this equation we use a diffusion process:
 
@@
 
-For solve the equation above we use implicit integration and a normalized
+To solve the equation above we use implicit integration and a normalized
 version of TQLBO matrix.
@@
 
-The vertices $V^{t+1}$are enhance along their inverse curvature normal
-directions by solving this simple linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+The vertices $V^{t+1}$are enhanced along their inverse curvature
+normal directions by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
 $L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
@@
 vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, $\mbox{sign}\left(x\right)$ is the sign function, and $\lambda dt$
-is the enhance factor that support negative and positive values, negative
-for enhancing positive for smoothing.
+group, and $\lambda dt$ is the enhance factor that support negative
+and positive values, negative for enhancing positive for smoothing.
 
-At the borders of the meshes that are not closed, you can not calculate
-the curvature, for that reason we use the scale-dependent operator
+The curvature cannot be calculted at the border of the meshes that
+are not closed, for that reason we use the scale-dependent operator
 proposed by \cite{Desbrun1999}.
 
-Our method was designed for use with weight vertex groups to specify
-the degree of impact on the solution, the weights vary between $0$
-and $1$ with a value of $0$ makes no changes and with values 1 applies
-the total change. The weights modifying influence zones where the
-Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
-The weights on each vertex will produce a different solution for that
-reason are put before obtaining the solution of the linear system.
+Our method was designed for use with weighted vertex groups which
+specify the final curvature enhancement on the solution, these weights
+vary between $0$ and $1$ with a value of $0$ makes no changes and
+with values 1 applies a maximal change. The weights modify influence
+zones where the Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
 Families of shapes that are generated may change substantially with
@@
 
-The model volume increases as the lambda is most negative, this can
-be countered by a simple method of preserving volume. In \cite{Desbrun1999}
-present a simple method to resize the mesh but have a problem the
-model suffer large displacements with $\lambda<-1.0$ or perform multiple
-iterations. We propose the following solution: If we have $v_{i}^{t+1}$
-is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration, we define
-$\overline{v}$ as:
+The models volume increases as the lambda is larger and negative,
+this can be go against by a simple method of volume preservation.
+In \cite{Desbrun1999} presents a simple method to resize the mesh
+however the model suffers large displacements when $\lambda<-1.0$
+or after multiple iterations. We propose the following solution: If
+$v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
+we define $\overline{v}$ as:
 
@@
 volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
-we have that scale factor for resize the volume is
+we define a scale factor.
 
@@
 
-and the new vertices positions are:
+The new vertices positions are:
 
@@
 
-We design a new brush that allows enhancement of the curvatures of
-a polygon mesh in real time. Our brush work well with the stroke method
-named \textsl{Drag Dot}  which allows you to preview the change that
-occurs in the model until you release the mouse button or tablet,
-also enable moves the mouse over the model to fit exactly where you
-want to perform the enhancement of the curvature.
+We designed a new brush that allows the enhancement of the curvatures
+of a polygon mesh in real time. Our brush works well with the stroke
+method named \textsl{Drag Dot}  which allows to preview the changes
+in the model before you release the mouse button or pen tablet, also
+allows to move the mouse over the model to fit exactly where you want
+to perform the enhancement of the curvature.
 
 Brushes that perform similar work as inflate can create distortions
-in the mesh and can also produce self-intersections of the mesh, as
-this brushes only moves the vertices along the normal and does not
-take into account the global information. Whereas our method look
-for the best way to make inflation while keeping the global curvature
-for preserving the shape and sharp features of the model.
+in the mesh and can also produce self-intersections in the mesh, as
+these brushes only move the vertices along the normal and do not take
+into account the global information. Whereas our method looks for
+the best way to make inflation while preserving the global curvature
+retaining the several shape and sharp features of the model.
 
@@
 would be to use some different brushes for inflating and some other
-to soften and styling. With our enhanced brush can be performed in
-one step.
+to soften and styling. With our enhanced brush in one step can be
+performed.
 
-For the real-time work brush is necessary that the matrix is constructed
-with the vertices that are within the radius defined by the user involvement,
-which dramatically reduces the size of the matrix to be processed,
+For the real-time brush it necessary that the Laplacian matrix is
+constructed with the vertices that are within the radius  of the sphere
+defined by the user, which reduces the size of the matrix to be processed,
 the center of this sphere depends on the place where the user clicks
@@
 
-Furthermore special handling is necessary with the vertices are at
-the boundary of which have neighbors that are not within the radius
-of impact, these vertices must be marked as boundary and not the curvature
-calculated for them, but must be present in the matrix to allow the
-vertices that have all their neighbors within the selection radius
-to calculate correctly the curvature, this change allows the results
-to be much smoother on the border. The Laplacian matrix for sculpt
-mode as a matrix equation.
+Furthermore special handling is required for the vertices at the boundary
+which have neighbors that are not within the radius of the brush.
+These vertices must be marked as boundary and the curvature will not
+be calculated for them, but must be present in the matrix so that
+every vertex has their neighbors within the selection, this change
+allows the results to be much smoother on the border. The Laplacian
+matrix for sculpt mode as a matrix equation.
 
@@
 Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
-the radius $r$. Then the matrix should remove rows and columns of
-vertices index that are not within the radius.
+of radius $r$. The matrixes should remove rows and columns of vertices
+index that are not within the radius.
 
@@
 The Catmull-Clark subdivision transformation is used to smooth a surface
-as the limit of sequence of subdivision steps\cite{Stam1998}. This
-method do a recursive subdivision transformation that refines the
-model into a linear interpolation that is a approximate smooth surface.
-The process of Catmull-Clark is govern by properties of B-spline curve
-from multivariate spline theory\cite{Loop1987}. In many subdivision
-surfaces methods Catmull-Clark, Loop so on, the smoothness of the
-model is automatically guaranteed \cite{DeRose1998}.
+as the limit of a sequence of subdivision steps\cite{Stam1998}. This
+process is governed by properties of B-splines curve from multivariate
+spline theory\cite{Loop1987}. This method does a recursive subdivision
+transformation that refines the model into a linear interpolation
+that approximates a smooth surface. The smoothness of the model is
+automatically guaranteed \cite{DeRose1998}.
 
-Catmull-Clark subdivision surface method generates smooth and continuous
+Catmull-Clark subdivision surface methods generate smooth and continuous
 models from a coarse model and produce results quickly due to the
@@
 subdivision surfaces and curvature enhancement for modeling from coarse
-models with few vertices can generate families of shapes with just
-change a parameter, which would allow an artist to choose the model
-of a similar set of options that best meets your needs without having
-to change each one of the control vertices.
+models with few vertices can generate families of shapes changing
+a single parameter, this would allow an artist to choose the model
+from a similar set of options that best meets his/her needs without
+having to change each one of the control vertices.
 
 Our method allows the use of vertex weight paint over the control
-points. The weights can be applied to the coarse model, then to perform
-subdivision weights are interpolated, producing weights with smooth
-changes in the zones of influence, so the curvature that is obtained
-is much softer at those areas. Using vertex group weight and subdivision
-surfaces is shown in figure \ref{fig:Subdivision-Cups}.c.
+points. The weights can be applied to a coarse model, then to perform
+a Catmull-Clark subdivision where weights are interpolated, producing
+weights with smooth changes in the zones of influence, so the obtained
+curvature is much softer at those areas as shown in figure \ref{fig:Subdivision-Cups}.c.
 
 In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
-matrix with weights corresponding to each vertex. The weights at each
+matrix with weights corresponding to each vertex. Weights at each
 vertex produce a different solution for this reason the matrix is
@@
 In this section we describe the results of our curvature enhance method
-that used our extension of Laplace Beltrami operator for hybrid quad/triangle
-meshes with several example models in figures \ref{fig:Spectrum},
+with the extension of the Laplace Beltrami operator for hybrid quad/triangle
+meshes with several example models (see figures \ref{fig:Spectrum},
 \ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
 \ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
-\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
+\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). We test the curvature
 enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
@@
 applied. In column (e) the model is converted randomly some quads
-into triangles and then Laplacian smoothing was applied, showing similar
+into triangles and then Laplacian smoothing is applied, showing similar
 results to those composed only of triangles or squares.
@@
 Figure \ref{fig:camello_enhanced} show the generation of different
-version of camel with the variation of parameter lambda. In the top
-row you can see results of do curvature enhance over all model, as
-the lambda becomes more negative curvature in this model makes close
-in the concave parts and inflates on the convex parts as shown in
-figure \ref{fig:Spectrum}. We use negative values to enhance model
-silhouette features, among more negative the lambda, the model will
-be further enhanced the silhouette features. In the bottom row of
+versions of a camel according to parameter lambda. In the top row
+you can see results of do curvature enhance over all model, as the
+lambda becomes larger and negative in this model it inflates the convex
+parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
+the larger enhancements on the model features. In the bottom row of
 the figure \ref{fig:camello_enhanced} can be observed using weighted
@@
 local changes are treated without significantly affecting global solution.
-Our method is invariant of rotation, since depends solely the normal
-field of the mesh, wish is invariant under global rotations.
+Our method is invariant of rotation, this since depends solely the
+normal field of the mesh, wish is invariant under global rotations.
 
@@
 during the sculpting process. In figure \ref{fig:Performance-sculpt}
-we show the performance of curvature enhancement brush, in this experimet
+we show the performance of curvature enhancement brush, in this experiment
 we use three models with 12K, 40K and 164K vertices, this models were
-sculpted with curvature enhance brush in eache step the brush sphere
+sculpted with curvature enhance brush in each step the brush sphere
 contain a variable number of vertices for processing. The processing

### 2013-01-08 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 
-Laplacian smoothing applied with simple subdivision may produce results
-similar to obtained with Catmull-Clark whose models are on average
+Laplacian smoothing applied with simple subdivision may produce similar
+results to those obtained with Catmull-Clark whose models are on average
 equal triangles as shown in figure \ref{fig:Catmull_Clark} green
@@
 parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
-the larger enhancements on the model features. In the bottom row of
-the figure \ref{fig:camello_enhanced} can be observed using weighted
-vertex groups, which allows you to specify which areas you want to
-model enhancement, on the left is the enhancement of the legs of the
-camel produces enhancement of organic aspect, also notes that the
-border is not distorted and smooth in the union.
+the larger enhancements on the model features. The bottom row of figure
+\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
+which allows to specify which areas will be enhanced. On the left
+the enhancement of the legs of the camel is shown which produces enhancement
+of organic aspect, notice that the border is not distorted and smooth
+in the union.
 
@@
 and invariant under isometric transformations as those present in
-some animations (see Figure \ref{fig:Animated_Camell}) in this animation
-shows some poses of a camel doing a walk. In this animation the legs
-and neck are the parts that enhancement is performed as shown in the
-bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
-produced by methods such as pose interpolation or animation rigging
-not significantly affect the result as with camel legs in each sample
-pose different flexion of the leg joints enhancement camel keeps flesh-like
-shapes in the pattern produced original by the artist. This is due
-to the diffusion process which is subjected to the mesh so that small
-local changes are treated without significantly affecting global solution.
-Our method is invariant of rotation, this since depends solely the
-normal field of the mesh, wish is invariant under global rotations.
+some animations (see Figure \ref{fig:Animated_Camell}). This animation
+shows some poses of a camel during a walk, enhancement is performed
+in the neck and legs as shown in the bottom left part of the figure
+\ref{fig:Animated_Camell}. Local modifications produced by pose interpolation
+or animation rigging do not significantly affect the result as with
+camel legs in each sample pose different flexion of the leg joints
+enhancement camel keeps flesh-like shapes in the pattern produced
+original by the artist. This is due to the diffusion process which
+is subjected to the mesh so that small local changes are treated without
+significantly affecting global solution. Our method is invariant of
+rotation, this since depends exclusively on the normal field of the
+mesh, wish is invariant under global rotations.
 
@@
 brush for sculpting in real time. One pass was used with the brush
-as shown in the figure with the blue and red radius. In the bottom
-of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
-and looks like two bubbles stuck, so do the fingers on the bottom
-of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
-we see better results because not lost the shape of the silhouette
-and kept the details of the fingers and leg. Similar results can be
-obtained by an artist but it would take several steps and the use
-of several brushes with curvatures enhancement only takes one step.
-With this new method can easily enhance organic features how muscles
-during the sculpting process. In figure \ref{fig:Performance-sculpt}
-we show the performance of curvature enhancement brush, in this experiment
+as shown in the figure with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
+camel shows how the leg self-intersecting and looks like two bubbles
+stuck, the same happens to the fingers on the bottom of the figure.
+Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
+we get better results sd the are retained shape of the silhouette
+and the details of the fingers and leg. Similar results can be obtained
+by an artist however it would take several steps and require the use
+of several brushes. With curvature enhancement it only takes one step.
+This new method can easily enhance organic features like muscles during
+the sculpting process. In figure \ref{fig:Performance-sculpt} we
+show the performance of curvature enhancement brush, in this experiment
 we use three models with 12K, 40K and 164K vertices, this models were
@@
 
-We did tests with the Laplacian operator to equation (\ref{eq:TQLBO_Simple_Matrix})
+Tests with the Laplacian operator equation (\ref{eq:TQLBO_Simple_Matrix})
 and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
-the two produce similar results if the triangles that compose the
-mesh are the same size on average , but the normalized version is
-more stable and predictable because it is not divided by the area
-of the ring which may be zero or very small and cause problems due
-to floating point calculation errors as shown in figure \ref{fig:(a)Monkey}.c
-bottom row in which the mesh is deformed because the TQLBO is susceptible
-to the size of the triangle. The enhancement of curvature of the model
-with the normalized Laplacian operator has a more regular behavior.
-The model can deform in TQLBO normalized version with large lambdas>
-400 intersects self, but produces no peaks observed with the TQLBO.
-Figure \ref{fig:(a)Monkey} observed different results because the
-area of the triangles in this model is not so regular triangles where
-greater area enhancement is less (figure \ref{fig:(a)Monkey}.c skull),
-and where the smaller triangles are produced greater enhancement (figure
-\ref{fig:(a)Monkey}.c chin).
+produce similar results if the triangles that compose the mesh are
+the same size on average. The normalized version is more stable and
+predictable because it is not divided by the area of the ring which
+may be very small and cause problems during floating point calculations
+as shown in figure \ref{fig:(a)Monkey}.c bottom row. The enhancement
+of curvature of the model with the normalized Laplacian operator has
+a more regular behavior. The model can be deformed in TQLBO normalized
+version with large lambdas ($\lambda>400$) while it intersects itself
+it produces no peaks. Figure \ref{fig:(a)Monkey} shows different
+results due to the area of the triangles in the model. Triangles with
+larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
+skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
+chin).
 
@@
 
-Our method was implemented how a modifier for modeling and brush for
+Our method was implemented as a modifier for modeling and brush for
 sculpting on the Blender software \cite{blender} with C and C++.
-Working with Blender allowed us to test the method interactively with
+Working with Blender allowed us to test the method interactively against
 others as Catmull-Clark, weight vertex groups and sculpting system
@@
 
-To improve performance, we worked with the Blender mesh struct calculating
-all possible data each time visiting each triangle or quad and adding
-to its corresponding index in a list that stored the sum of the Laplacian
-weights of the ring, in this way only had to visit two times the list
-of faces of the mesh list and the two times the list of the edges
-if the mesh was not closed. To brush sculpting mode was necessary
-to create a list that will map the index of the selected vertices
-to a list from 1 to N where N is the number of vertices selected and
-the number of rows in the linear system to solve, with this drastically
-reduced the calculations should make working with the tool allowing
-real-time. In the construction of our Laplacian matrix were blocked
-at vertices having faces areas or lengths edges with value zero that
-can cause spikes and bad results.
+To improve the performance, we worked with Blender mesh struct visiting
+each triangle or quad and adding its corresponding index in a list
+that stores the sum of the Laplacian weights of the ring, in this
+way we only had to visit two times the list of faces of the mesh list
+and two times the list of the edges if the mesh was not closed. The
+brush sculpting mode required to create a list that maps the index
+of the selected vertices to a list from 1 to N where N is the number
+of vertices selected and the number of rows in the linear system to
+solve. This drastically reduced the calculations enabling real-time
+processing. In the construction of our Laplacian matrix several index
+were locked at vertices having faces areas or lengths edges with value
+zero that can cause spikes and bad results.
 
-The matrix \ref{eq:TQLBO_Simple_Matrix} is sparse since the number
-of neighbors per vertex corresponding to the number of data per row
-is small compared to the total number of vertices in the mesh. To
-solve the linear system equation \ref{eq:Lineal_System_with_wp} was
-used OpenNL which is a a library for solving sparse linear system.
+Under this conditions matrix at the equation\ref{eq:TQLBO_Simple_Matrix}
+is sparse since the number of neighbors per vertex corresponding to
+the number of data per row is small compared to the total number of
+vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
+was used OpenNL which is a a library for solving sparse linear system.
 
@@
 
-We present an extension of the Laplace Beltrami operator for triangles
-and quads that can work in production environments without conversion
-that provides results similar to those obtained by working only with
-triangles or quads.
+This work presented an extension of the Laplace Beltrami operator
+for hybrid quad/triangle meshes that can be used in production environments
+without modification that provides results similar to those obtained
+by working only with triangles or quads.
 
-We introduced a new way to perform enhancement silhouettes in a mesh
-for modeling or sculpted in a few steps allows the modification of
-the curvature of a model while maintaining its overall shape. We introduce
-a new method of modeling and show some of its possible uses. We show
-that the method behaves in predictable ways which facilitate the learning
-process, it also showed that the method works well with isometric
-transformations opening the possibility of introducing it on the stages
-of animation.
+We introduced a new way to perform silhouettes enhancement in a mesh
+for modeling or sculpting in a few steps which allows the modification
+of the curvature of a model while preserving its overall shape. We
+introduce a new method of modeling and show some of its possible uses.
+This method behaves in predictable ways which facilitate the learning
+process, and works well with isometric transformations opening the
+possibility of introducing it on the process of animation.
 
-We demonstrate that this tool serves to work in the early stages in
-which are used coarse models to permit modifying the curvature generated
-by the Catmull-Clark subdivision surfaces, avoiding the edition of
-the vertices to have only to change a few parameters.
+We show that this tool could work in the early stages in where coarse
+models are used, allowing to modify the curvature generated by the
+Catmull-Clark subdivision surfaces, avoiding the edition of the vertices
+with the change of a few parameters.
 
-As future work we would like to analyze theoretically the relationship
-between the Catmull-Clark subdivision surfaces and Laplacian smoothing
-because in some cases can produce very similar results. But the subdivision
+As future work we analyze theoretically the relationship between the
+Catmull-Clark subdivision surfaces and Laplacian smoothing because
+in some cases can produce very similar results. But the subdivision
 surface is a fast method thereby reducing computation times for calculate
@@
 Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
-Commons Attribution 3.0 Unported License.
+Commons Attribution 3.0 Unported License. Dinosaur model is under
+public domain, courtesy of Blender Foundation.
 

### 2013-01-09 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
-%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 Figure \ref{fig:camello_enhanced} show the generation of different
-version of camel with the variation of parameter lambda. In the top
-row you can see results of do curvature enhance over all model, as
-the lambda becomes more negative curvature in this model makes close
-in the concave parts and inflates on the convex parts as shown in
-figure \ref{fig:Spectrum}. We use negative values to enhance model
-silhouette features, among more negative the lambda, the model will
-be further enhanced the silhouette features. In the bottom row of
-the figure \ref{fig:camello_enhanced} can be observed using weighted
-vertex groups, which allows you to specify which areas you want to
-model enhancement, on the left is the enhancement of the legs of the
-camel produces enhancement of organic aspect, also notes that the
-border is not distorted and smooth in the union.
+versions of a camel according to parameter lambda. In the top row
+you can see results of do curvature enhance over all model, as the
+lambda becomes larger and negative in this model it inflates the convex
+parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
+the larger enhancements on the model features. The bottom row of figure
+\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
+which allows to specify which areas will be enhanced. On the left
+the enhancement of the legs of the camel is shown which produces enhancement
+of organic aspect, notice that the border is not distorted and smooth
+in the union.
 
@@
 and invariant under isometric transformations as those present in
-some animations (see Figure \ref{fig:Animated_Camell}) in this animation
-shows some poses of a camel doing a walk. In this animation the legs
-and neck are the parts that enhancement is performed as shown in the
-bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
-produced by methods such as pose interpolation or animation rigging
-not significantly affect the result as with camel legs in each sample
-pose different flexion of the leg joints enhancement camel keeps flesh-like
-shapes in the pattern produced original by the artist. This is due
-to the diffusion process which is subjected to the mesh so that small
-local changes are treated without significantly affecting global solution.
-Our method is invariant of rotation, since depends solely the normal
-field of the mesh, wish is invariant under global rotations.
+some animations (see Figure \ref{fig:Animated_Camell}). This animation
+shows some poses of a camel during a walk, enhancement is performed
+in the neck and legs as shown in the bottom left part of the figure
+\ref{fig:Animated_Camell}. Local modifications produced by pose interpolation
+or animation rigging do not significantly affect the result as with
+camel legs in each sample pose different flexion of the leg joints
+enhancement camel keeps flesh-like shapes in the pattern produced
+original by the artist. This is due to the diffusion process which
+is subjected to the mesh so that small local changes are treated without
+significantly affecting global solution. Our method is invariant of
+rotation, this since depends exclusively on the normal field of the
+mesh, wish is invariant under global rotations.
 
@@
 brush for sculpting in real time. One pass was used with the brush
-as shown in the figure with the blue and red radius. In the bottom
-of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
-and looks like two bubbles stuck, so do the fingers on the bottom
-of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
-we see better results because not lost the shape of the silhouette
-and kept the details of the fingers and leg. Similar results can be
-obtained by an artist but it would take several steps and the use
-of several brushes with curvatures enhancement only takes one step.
-With this new method can easily enhance organic features how muscles
-during the sculpting process. In figure \ref{fig:Performance-sculpt}
-we show the performance of curvature enhancement brush, in this experimet
+as shown in the figure with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
+camel shows how the leg self-intersecting and looks like two bubbles
+stuck, the same happens to the fingers on the bottom of the figure.
+Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
+we get better results sd the are retained shape of the silhouette
+and the details of the fingers and leg. Similar results can be obtained
+by an artist however it would take several steps and require the use
+of several brushes. With curvature enhancement it only takes one step.
+This new method can easily enhance organic features like muscles during
+the sculpting process. In figure \ref{fig:Performance-sculpt} we
+show the performance of curvature enhancement brush, in this experiment
 we use three models with 12K, 40K and 164K vertices, this models were
-sculpted with curvature enhance brush in eache step the brush sphere
+sculpted with curvature enhance brush in each step the brush sphere
 contain a variable number of vertices for processing. The processing
@@
 Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
-Commons Attribution 3.0 Unported License.
+Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
+are under public domain, courtesy of Blender Foundation.
 

### 2013-01-10 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

@@
 % Paper title.
-\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 \begin{abstract}
-This paper proposes a novel method for modeling a polygonal mesh by
-enhancing the object curvature. This method uses an adapted extension
-of the Laplace Beltrami operator for hybrid quad/triangle meshes,
-to enhance the global curvature. Along with the method, this work
-also presents new applications of curvature enhancement in sculpting
-and modeling with subdivision surfaces and weight vertex groups. A
+This paper proposes a novel modeling method for a hybrid quad/triangle mesh by
+enhancing the global object curvature. This method uses an adapted extension
+of the Laplace Beltrami operator. Along with the method, this work
+also presents new applications in sculpting
+and modeling, with subdivision of surfaces and weight vertex groups. A
 series of graphics examples demonstrates the quality, predictability
@@
 tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
-editing and creation from sketches \cite{Igarashi1999,Gonen2012},
+editing, creation from sketches \cite{Igarashi1999,Gonen2012},
 and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
@@
 with the use of creases to produce sharp edges \cite{DeRose1998},
-or the modification of weights on the vertices to locally control
+or the modification of the vertex weights to locally control
 the zone of influence \cite{Biermann2000}. Instead, the presented
 method performs a feature enhancement of the model by parameterizing
-the surface curvature and thereby creating a family of different versions
-of the same object, preserving therefore the detail of the original
-model and a realistic appearance.
+the surface curvature, creating a family of different versions
+of the same object and therefore preserving  the detail of the original
+model and a more realistic appearance.
 
@@
 \textbf{Contributions} This work presents an extension of the Laplace
-Beltrami operator for hybrid quad/triangle meshes representing a larger
+Beltrami operator for hybrid quad/triangle meshes, representing a larger
 mesh spectrum from what has been presented so far. The method eliminates
@@
 obtained during the subdivision surfaces process. Finally, it is proposed
-a new brush for enhancing silhouette mesh features in modeling and
+a new brush for enhancing the silhouette mesh features in modeling and
 sculpting.
@@
 presents works related to the Laplacian mesh processing, digital sculpting,
-and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
-, it is described the theoretical framework of the Laplacian operator
+and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}, it is described the theoretical framework of the Laplacian operator
 for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
@@
 
-Many tools have been developed for modeling, based on Laplacian mesh
+Many tools have been developed for modeling, based on the Laplacian mesh
 processing. Thanks to the advantages of the Laplacian operator, these
@@
 
-Offset polygon mesh methods, based on the curvature defined by the
+Offset methods for polygon meshing, based on the curvature defined by the
 Laplace Beltrami operator, have been developed. These methods adjust
-the shape offset by a constant distance, with high precision as to
+the shape offset by a constant distance, with enough precision as to
 minimize the Hausdorf error. Nevertheless, these methods fail to conserve
-enough detail because of the smoothing, a crucial issue which depends
-on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
-representation the computing the offset boundary that are based on
-distance field computation, when performing the offset, the topology
-of the model may be different from the original, changing the original
-design \cite{Chen2011}.
+sufficient detail because of the smoothing, a crucial issue which depends
+on the offset size\cite{Zhuo2012}. In volumetric approaches, in case of point-based
+representations, the offset boundary computation is based on the
+distance field and therefore when calculating such offset, the topology
+of the model may be different to the original  \cite{Chen2011}.
 
-\cite{Gal2009} proposes automatic features detection and shape edition
+\cite{Gal2009} proposes automatic feature detection and shape edition
 with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys with based the first and
+surface features like ridges and valleys, characerized bytheir first and
 second order curvature derivatives \cite{Ohtake2004}, and angle-based
-threshold. Later the curves are classified by several properties as
+threshold.Likewise, curves have been also classified as
 planar or non-planar, approximated by lines, circles, ellipses and
-other complex shapes. In then the user defines an initial change over
-several features and then this change is propagated over other features
-with base in the classified shapes and the inter-relationships between
-these. This method works fine with objects that have sharp edges composed
-of basic geometric shapes such as lines, circles or ellipses but method
-has problems to classify when models are smoother with organic forms
-because it cannot find the features to edit and preserve.
+other complex shapes. In such case, the user defines an initial change over
+several features and this change is propagated towards other features,
+based in the classified shapes and the inter-relationships between
+them. This method works well with objects that have sharp edges, composed
+of basic geometric shapes such as lines, circles or ellipses, but the method
+is very limited at classifying when models are smooth since it cannot find the features to edit and preserve.
 
-Digital sculpting can be divided into two principal approaches: based
-on polygonal methods and voxel grid-based methods. Brushes for inflate
-operations in polygonal methods only depends on the normal at each
-vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
-allow to add or remove voxels, for produce polygonal meshes require
+Digital sculpting have been traditionally approached either under a polygonal representation or a voxel grid-based method.
+Brushes for inflation operations only depend on the normal vertex \cite{Stanculescu2011}, in grid-based sculpting, some other operations have allowed to add or remove voxels, since producing polygonal meshes require
 processing isosurfaces from volume \cite{Galyean1991}. The problem
-whit this type of operations is the difficult to maintain surface
-details during larger scale deformation.
+whit this type of operations is the difficulty of maintaining the surface
+details during larger scale deformations.
 

### 2013-01-11 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 \begin{abstract}
-This paper proposes a novel modeling method for a hybrid quad/triangle mesh by
-enhancing the global object curvature. This method uses an adapted extension
-of the Laplace Beltrami operator. Along with the method, this work
-also presents new applications in sculpting
-and modeling, with subdivision of surfaces and weight vertex groups. A
+This paper proposes a novel modeling method for a hybrid quad/triangle
+mesh by enhancing the global object curvature. This method uses an
+adapted extension of the Laplace Beltrami operator. Along with the
+method, this work also presents new applications in sculpting and
+modeling, with subdivision of surfaces and weight vertex groups. A
 series of graphics examples demonstrates the quality, predictability
@@
 tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
-editing, creation from sketches \cite{Igarashi1999,Gonen2012},
-and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
+editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
+complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
 
@@
 with the use of creases to produce sharp edges \cite{DeRose1998},
-or the modification of the vertex weights to locally control
-the zone of influence \cite{Biermann2000}. Instead, the presented
-method performs a feature enhancement of the model by parameterizing
-the surface curvature, creating a family of different versions
-of the same object and therefore preserving  the detail of the original
-model and a more realistic appearance.
+or the modification of vertex weight to locally control the zone of
+influence \cite{Biermann2000}. Instead, the presented method performs
+a feature enhancement of the model by parameterizing the surface curvature,
+creating a family of different versions of the same object and therefore
+preserving the detail of the original model and a realistic appearance.
 
@@
 \textbf{Contributions} This work presents an extension of the Laplace
-Beltrami operator for hybrid quad/triangle meshes, representing a larger
-mesh spectrum from what has been presented so far. The method eliminates
-the need of preprocessing and allows preservation of the original
-topology. Likewise, along with this operator, it is proposed a method
-to generate a family of parameterized shapes, in a robust and predictable
-way. This method enables customization of the smoothness and curvature,
-obtained during the subdivision surfaces process. Finally, it is proposed
-a new brush for enhancing the silhouette mesh features in modeling and
-sculpting.
+Beltrami operator for hybrid quad/triangle meshes, representing a
+larger mesh spectrum from what has been presented so far. The method
+eliminates the need of preprocessing and allows preservation of the
+original topology. Likewise, along with this operator, it is proposed
+a method to generate a family of parameterized shapes, in a robust
+and predictable way. This method enables customization of the smoothness
+and curvature, obtained during the subdivision surfaces process. Finally,
+it is proposed a new brush for enhancing the silhouette mesh features
+in modeling and sculpting.
 
@@
 presents works related to the Laplacian mesh processing, digital sculpting,
-and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}, it is described the theoretical framework of the Laplacian operator
+and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
+, it is described the theoretical framework of the Laplacian operator
 for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
@@
 
-Many tools have been developed for modeling, based on the Laplacian mesh
-processing. Thanks to the advantages of the Laplacian operator, these
-different tools preserve the surface geometric details when using
-them for different processes such as free-form deformation, fusion,
-morphing and other application\cite{Sorkine2004}.
+Many tools have been developed for modeling, based on the Laplacian
+mesh processing. Thanks to the advantages of the Laplacian operator,
+these different tools preserve the surface geometric details when
+using them for different processes such as free-form deformation,
+fusion, morphing and other application\cite{Sorkine2004}.
 
-Offset methods for polygon meshing, based on the curvature defined by the
-Laplace Beltrami operator, have been developed. These methods adjust
-the shape offset by a constant distance, with enough precision as to
-minimize the Hausdorf error. Nevertheless, these methods fail to conserve
-sufficient detail because of the smoothing, a crucial issue which depends
-on the offset size\cite{Zhuo2012}. In volumetric approaches, in case of point-based
-representations, the offset boundary computation is based on the
-distance field and therefore when calculating such offset, the topology
-of the model may be different to the original  \cite{Chen2011}.
+Offset methods for polygon meshing, based on the curvature defined
+by the Laplace Beltrami operator, have been developed. These methods
+adjust the shape offset by a constant distance, with enough precision
+as to minimize the Hausdorf error. Nevertheless, these methods fail
+to conserve sufficient detail because of the smoothing, a crucial
+issue which depends on the offset size \cite{Zhuo2012}. In volumetric
+approaches, in case of point-based representations, the offset boundary
+computation is based on the distance field and therefore when calculating
+such offset, the topology of the model may be different to the original
+\cite{Chen2011}.
 
@@
 with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys, characerized bytheir first and
-second order curvature derivatives \cite{Ohtake2004}, and angle-based
-threshold.Likewise, curves have been also classified as
-planar or non-planar, approximated by lines, circles, ellipses and
-other complex shapes. In such case, the user defines an initial change over
-several features and this change is propagated towards other features,
-based in the classified shapes and the inter-relationships between
-them. This method works well with objects that have sharp edges, composed
-of basic geometric shapes such as lines, circles or ellipses, but the method
-is very limited at classifying when models are smooth since it cannot find the features to edit and preserve.
+surface features like ridges and valleys, characerized bytheir first
+and second order curvature derivatives \cite{Ohtake2004}, and angle-based
+threshold.Likewise, curves have been also classified as planar or
+non-planar, approximated by lines, circles, ellipses and other complex
+shapes. In such case, the user defines an initial change over several
+features and this change is propagated towards other features, based
+in the classified shapes and the inter-relationships between them.
+This method works well with objects that have sharp edges, composed
+of basic geometric shapes such as lines, circles or ellipses, but
+the method is very limited at classifying when models are smooth since
+it cannot find the features to edit and preserve.
 
-Digital sculpting have been traditionally approached either under a polygonal representation or a voxel grid-based method.
-Brushes for inflation operations only depend on the normal vertex \cite{Stanculescu2011}, in grid-based sculpting, some other operations have allowed to add or remove voxels, since producing polygonal meshes require
-processing isosurfaces from volume \cite{Galyean1991}. The problem
-whit this type of operations is the difficulty of maintaining the surface
-details during larger scale deformations.
+Digital sculpting have been traditionally approached either under
+a polygonal representation or a voxel grid-based method. Brushes for
+inflation operations only depend on the normal vertex \cite{Stanculescu2011},
+in grid-based sculpting, some other operations have allowed to add
+or remove voxels, since producing polygonal meshes require processing
+isosurfaces from volume \cite{Galyean1991}. The problem whit this
+type of operations is the difficulty of maintaining the surface details
+during larger scale deformations.
 

### 2013-01-11 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 
-Over the last years several modeling techniques have been developed
-to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
+Over the last years several, modeling techniques able to generate
+a variety of realistic shapes, have been developed \cite{Botsch2006}.
 Editing techniques have evolved from affine transformations to advanced
@@
 editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
-complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
+complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
+based methods however require to interact with a minimun number of
+control points for any operation to be efficient, or in other words,
+a unicity condition is introduced by demanding a smooth surface after
+any of these shape operations. Hence, traditional modeling methods
+for subdividing surfaces from coarse geometry have become widely popular
+\cite{Catmull1978,Stam1998}. These works have generalized a uniform
+B-cubic spline knot insertion to meshes, some of them adding some
+type of control, for instance with the use of creases to produce sharp
+edges \cite{DeRose1998}, or the modification of some vertex weights
+to locally control the zone of influence \cite{Biermann2000}. Neverteless
+these methods are difficult to deal with since they require a large
+number of parameters and a very tedious customization. Instead, the
+presented method requires a single parameter that controls the global
+curvature, whereby it performs a curvature enhancement and shape exaggeration
+of the model, creating a family of different versions of the same
+object and therefore preserving the detail of the original model and
+a realistic appearance.
 
-Traditional methods for smoothing surfaces from coarse geometry, like
-the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
-These works generalize the uniform B-cubic splines knot insertion
-to meshes, some of them adding some type of control, for instance
-with the use of creases to produce sharp edges \cite{DeRose1998},
-or the modification of vertex weight to locally control the zone of
-influence \cite{Biermann2000}. Instead, the presented method performs
-a feature enhancement of the model by parameterizing the surface curvature,
-creating a family of different versions of the same object and therefore
-preserving the detail of the original model and a realistic appearance.
+The curvature enhancement and shape exaggeration can be used in the
+sculpting proccess when inflating with a brush since current brushes
+that perform inflation end up by losing detail when moving vertices
+\cite{Stanculescu2011}, in contrast the presented method allows inflation
+of the mesh vertices by moving them towards the reverse curvature
+direction, conserving the shape and sharp features of the model.
 
-On the other hand, many types of brushes have been developed to sculpt
-meshes. Brushes that perform inflation end up by losing detail when
-inflating the vertices \cite{Stanculescu2011}, in contrast the presented
-method allows inflation of the mesh vertices by moving them towards
-the opposite curvature direction, conserving the shape and sharp features
-of the model.
+Interest on meshes composed by triangles and quads has increasing
+in recent years due to the flexibility of modeling tools as Blender
+3D \cite{blender}. Today many artists manually connect vertices such
+that its edition allows a simple way to perform animation processes
+and interpolation \cite{Mullen2007}. For these reasons it is very
+important to develop an operator that allows working with this type
+of mesh immediately, eliminating the need to preprocessing the mesh
+to convert to triangles and losing the original design made by users.
 
@@
 
-Unlike other methods, our method allows to use mixed arbitrary types
-of mesh representation as triangles and quads, exploiting the basic
-geometrical relationships facilitating and ensuring convergence of
-the algorithm and similar shapes consistent with the original shape
-against the other methods.
-
 Our method allows the use of soft constraints weighting the effect
@@
 
-Our approach is based on an extension of the Laplace Beltrami operator
-for meshes composed by triangles and quads. Interest on meshes composed
-by triangles and quads has increasing in recent years due to the flexibility
-of modeling tools as Blender 3D \cite{blender}. Today many artists
-manually connect vertices such that its edition allows a simple way
-to perform animation processes and interpolation \cite{Mullen2007}.
-For these reasons it is very important to develop an operator that
-allows working with this type of mesh immediately, eliminating the
-need to preprocessing the mesh to convert to triangles and losing
-the original design made by users.
+Our work presents an extension of the Laplace Beltrami operator for
+hybrid quad/triangle meshes, allows using mixed arbitrary types of
+mesh representation, exploiting the basic geometrical relationships
+facilitating and ensuring convergence of the algorithm and similar
+shapes consistent with the original shape against the other methods.
 

### 2013-01-12 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

@@
 % Paper title.
-\title{Curvature Enhancement With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 
-\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
+\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhanced shapes,
 from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
@@
 \begin{abstract}
-This paper proposes a novel modeling method for a hybrid quad/triangle
+This paper proposes a novel modeling method for modeling a hybrid quad/triangle
 mesh by enhancing the global object curvature. This method uses an
 adapted extension of the Laplace Beltrami operator. Along with the
-method, this work also presents new applications in sculpting and
+method, this work presents new applications in sculpting and
 modeling, with subdivision of surfaces and weight vertex groups. A
@@
 edges \cite{DeRose1998}, or the modification of some vertex weights
-to locally control the zone of influence \cite{Biermann2000}. Neverteless
+to locally control the zone of influence \cite{Biermann2000}. Nevertheless,
 these methods are difficult to deal with since they require a large
@@
 
-The curvature enhancement and shape exaggeration can be used in the
-sculpting proccess when inflating with a brush since current brushes
-that perform inflation end up by losing detail when moving vertices
-\cite{Stanculescu2011}, in contrast the presented method allows inflation
-of the mesh vertices by moving them towards the reverse curvature
-direction, conserving the shape and sharp features of the model.
-
-Interest on meshes composed by triangles and quads has increasing
-in recent years due to the flexibility of modeling tools as Blender
-3D \cite{blender}. Today many artists manually connect vertices such
-that its edition allows a simple way to perform animation processes
-and interpolation \cite{Mullen2007}. For these reasons it is very
-important to develop an operator that allows working with this type
-of mesh immediately, eliminating the need to preprocessing the mesh
-to convert to triangles and losing the original design made by users.
+Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
+Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}.
+It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles.
+The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when brush inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
+In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.
 

### 2013-01-14 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

@@
 % Paper title.
-\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 \begin{abstract}
-This paper proposes a novel method for modeling a polygonal mesh by
-enhancing the object curvature. This method uses an adapted extension
-of the Laplace Beltrami operator for hybrid quad/triangle meshes,
-to enhance the global curvature. Along with the method, this work
-also presents new applications of curvature enhancement in sculpting
-and modeling with subdivision surfaces and weight vertex groups. A
+This paper proposes a novel modeling method for constructing a hybrid quad/triangle
+mesh by enhancing the global object curvature. This method uses an
+adapted extension of the Laplace Beltrami operator, resulting in a large variety of meshes. Along with the
+method, this work presents new applications in sculpting and
+modeling, with subdivision of surfaces and weight vertex groups. A
 series of graphics examples demonstrates the quality, predictability
@@
 
-Over the last years several modeling techniques have been developed
-to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
+Over the last years several, modeling techniques able to generate
+a variety of realistic shapes, have been developed \cite{Botsch2006}.
 Editing techniques have evolved from affine transformations to advanced
 tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
-editing and creation from sketches \cite{Igarashi1999,Gonen2012},
-and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.
-
-Traditional methods for smoothing surfaces from coarse geometry, like
-the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
-These works generalize the uniform B-cubic splines knot insertion
-to meshes, some of them adding some type of control, for instance
-with the use of creases to produce sharp edges \cite{DeRose1998},
-or the modification of weights on the vertices to locally control
-the zone of influence \cite{Biermann2000}. Instead, the presented
-method performs a feature enhancement of the model by parameterizing
-the surface curvature and thereby creating a family of different versions
-of the same object, preserving therefore the detail of the original
-model and a realistic appearance.
-
-On the other hand, many types of brushes have been developed to sculpt
-meshes. Brushes that perform inflation end up by losing detail when
-inflating the vertices \cite{Stanculescu2011}, in contrast the presented
-method allows inflation of the mesh vertices by moving them towards
-the opposite curvature direction, conserving the shape and sharp features
-of the model.
+editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
+complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
+based methods however require to interact with a minimun number of
+control points for any operation to be efficient, or in other words,
+a unicity condition is introduced by demanding a smooth surface after
+any of these shape operations. Hence, traditional modeling methods
+for subdividing surfaces from coarse geometry have become widely popular
+\cite{Catmull1978,Stam1998}. These works have generalized a uniform
+B-cubic spline knot insertion to meshes, some of them adding some
+type of control, for instance with the use of creases to produce sharp
+edges \cite{DeRose1998}, or the modification of some vertex weights
+to locally control the zone of influence \cite{Biermann2000}. Nevertheless,
+these methods are difficult to deal with since they require a large
+number of parameters and a very tedious customization. Instead, the
+presented method requires a single parameter that controls the global
+curvature, which is used to maintain realistic shapes, creating a family of different versions of the same
+object and therefore preserving the detail of the original model and
+a realistic appearance.
+Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
+Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}.
+It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles.
+The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
+In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.
 
 \textbf{Contributions} This work presents an extension of the Laplace
-Beltrami operator for hybrid quad/triangle meshes representing a larger
-mesh spectrum from what has been presented so far. The method eliminates
-the need of preprocessing and allows preservation of the original
-topology. Likewise, along with this operator, it is proposed a method
-to generate a family of parameterized shapes, in a robust and predictable
-way. This method enables customization of the smoothness and curvature,
-obtained during the subdivision surfaces process. Finally, it is proposed
-a new brush for enhancing silhouette mesh features in modeling and
-sculpting.
+Beltrami operator for hybrid quad/triangle meshes, representing a
+larger mesh spectrum from what has been presented so far. The method
+eliminates the need of preprocessing and allows preservation of the
+original topology. Likewise, along with this operator, it is proposed
+a method to generate a family of parameterized shapes, in a robust
+and predictable way. This method enables customization of the smoothness
+and curvature, obtained during the subdivision surfaces process. Finally,
+it is proposed a new brush for enhancing the silhouette mesh features
+in modeling and sculpting.
 
@@
 
-Many tools have been developed for modeling, based on Laplacian mesh
-processing. Thanks to the advantages of the Laplacian operator, these
-different tools preserve the surface geometric details when using
-them for different processes such as free-form deformation, fusion,
-morphing and other application\cite{Sorkine2004}.
+Many tools have been developed for modeling, based on the Laplacian
+mesh processing. Thanks to the advantages of the Laplacian operator,
+these different tools preserve the surface geometric details when
+using them for different processes such as free-form deformation,
+fusion, morphing and other application\cite{Sorkine2004}.
 
-Offset polygon mesh methods, based on the curvature defined by the
-Laplace Beltrami operator, have been developed. These methods adjust
-the shape offset by a constant distance, with high precision as to
-minimize the Hausdorf error. Nevertheless, these methods fail to conserve
-enough detail because of the smoothing, a crucial issue which depends
-on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
-representation the computing the offset boundary that are based on
-distance field computation, when performing the offset, the topology
-of the model may be different from the original, changing the original
-design \cite{Chen2011}.
+Offset methods for polygon meshing, based on the curvature defined
+by the Laplace Beltrami operator, have been developed. These methods
+adjust the shape offset by a constant distance, with enough precision
+as to minimize the Hausdorff error. Nevertheless, these methods fail
+to conserve sufficient detail because of the smoothing, a crucial
+issue which depends on the offset size \cite{Zhuo2012}. In volumetric
+approaches, in case of point-based representations, the offset boundary
+computation is based on the distance field and therefore when calculating
+such offset, the topology of the model may be different to the original
+\cite{Chen2011}.
 
-\cite{Gal2009} proposes automatic features detection and shape edition
+Gai et al. \cite{Gal2009} propose automatic feature detection and shape edition
 with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys with based the first and
-second order curvature derivatives \cite{Ohtake2004}, and angle-based
-threshold. Later the curves are classified by several properties as
-planar or non-planar, approximated by lines, circles, ellipses and
-other complex shapes. In then the user defines an initial change over
-several features and then this change is propagated over other features
-with base in the classified shapes and the inter-relationships between
-these. This method works fine with objects that have sharp edges composed
-of basic geometric shapes such as lines, circles or ellipses but method
-has problems to classify when models are smoother with organic forms
-because it cannot find the features to edit and preserve.
+surface features like ridges and valleys, characerized by their first
+and second order curvature derivatives \cite{Ohtake2004}, and angle-based
+threshold. Likewise, curves have been also classified as planar or
+non-planar, approximated by lines, circles, ellipses and other complex
+shapes. In such case, the user defines an initial change over several
+features which is propagated towards other features, based
+on the classified shapes and the inter-relationships between them.
+This method works well with objects that have sharp edges, composed
+of basic geometric shapes such as lines, circles or ellipses. However,
+the method is very limited when models are smooth since
+it cannot find the proper features to edit.
 
-Digital sculpting can be divided into two principal approaches: based
-on polygonal methods and voxel grid-based methods. Brushes for inflate
-operations in polygonal methods only depends on the normal at each
-vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
-allow to add or remove voxels, for produce polygonal meshes require
-processing isosurfaces from volume \cite{Galyean1991}. The problem
-whit this type of operations is the difficult to maintain surface
-details during larger scale deformation.
+Digital sculpting have been traditionally approached either under
+a polygonal representation or a voxel grid-based method. Brushes for
+inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
+In grid-based sculpting, some other operations have allowed to add
+or remove voxels since production of polygonal meshes require a processing of
+isosurfaces from a volume \cite{Galyean1991}. The drawback comes from the difficulty of maintaining the surface details
+during larger scale deformations.
 
@@
 
-Computer graphics objects which have been reconstructed from real
-world, contain undesirable noise. Laplacian Smooth techniques allow
-noise reduction on a mesh's surface with minimal changes on its shape
-while still preserves desirable geometry as well as the shape of the
-original model.
+Computer objects, reconstructed from the real
+world, are usually noisy. Laplacian Smooth techniques allow a proper
+noise reduction on the mesh surface with minimal shape changes,
+while still preserving a desirable geometry as well as the original shape.
 
-The functional used in many Laplacian smoothing approaches to constrain
-energy minimization is based on a total curvature of a surface $S$.
+Many smoothing Laplacian functionals regularize the surface energy by controling the total surface curvature $S$.
 
@@
 
-\caption{\label{fig:voronoi_region}Area of Voronoi region around $v_{i}$
+\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
 in dark blue.\protect \\
- $v_{j}$ 1-ring neighbors around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$
-opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
+ $v_{j}$ belong to the first neighborhood around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$ are the
+opposite angles to the edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
 \end{figure}
 
-Consider a surface $S$ composed by a set of triangles around vertex
-$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
-show in figure \ref{fig:voronoi_region}, The change in the area produced
-by the movement of $v_{i}$ is named gradient of \textit{Voronoi region
+Consider a surface $S$, composed of a set of triangles, around the vertex
+$v_{i}$. Let us define the \textit{Voronoi region} of $v_{i}$, as
+show in figure \ref{fig:voronoi_region}, The area change produced
+by the movement of $v_{i}$ is called the gradient of the \textit{Voronoi region
 \cite{Pinkall1993,Desbrun1999,Meyer2003}.}
@@
 
-If we normalize this gradient in equation (\ref{eq:eq_gradient_voronoi_area})
-by the total area in 1-ring around $v_{i}$, we have the \textit{discrete
-mean curvature normal} of a surface $S$ as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
+If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is normalized 
+by the total area of the first neighborhood around $v_{i}$, the \textit{discrete
+mean curvature normal} of a surface $S$  is obtained, as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
 
@@
 
-The \textit{Laplace Beltrami operator} LBO denoted $\triangle_{g}$
-is used for measures mean curvature normal of the Surface $S$ \cite{Pinkall1993}.
+The \textit{Laplace Beltrami operator} LBO, noted as $\triangle_{g}$,
+is used for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.
 
@@
 
-The LBO has desirable features: one feature of the LBO is in direction
-of surface area minimization, allowing to minimize energy using it
-on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).
+The LBO has desirable properties: the LBO points out to the direction
+of the minimal surface area, minimizing the energy of the total surface curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).
 
@@
 
-Our method allows the editing of geometric features using the curvature
+The method allows edition of geometric features using the curvature
 enhancement and smoothing, generating a parameterized family of shapes
@@
 and smooth version of the original model.
-
-Unlike other methods, our method allows to use mixed arbitrary types
-of mesh representation as triangles and quads, exploiting the basic
-geometrical relationships facilitating and ensuring convergence of
-the algorithm and similar shapes consistent with the original shape
-against the other methods.
 
@@
 Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
-Commons Attribution 3.0 Unported License. Dinosaur model is under
-public domain, courtesy of Blender Foundation.
+Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
+are under public domain, courtesy of Blender Foundation.
 

### 2013-01-14 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 
-\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhanced shapes,
+\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
 from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
@@
 \begin{abstract}
-This paper proposes a novel modeling method for modeling a hybrid quad/triangle
-mesh by enhancing the global object curvature. This method uses an
+This paper proposes a novel modeling method for a hybrid quad/triangle
+mesh by enhancing the global object curvature. This method uses our
 adapted extension of the Laplace Beltrami operator. Along with the
-method, this work presents new applications in sculpting and
-modeling, with subdivision of surfaces and weight vertex groups. A
-series of graphics examples demonstrates the quality, predictability
-and flexibility of the method in a real production environment with
-software blender.
+method, this work presents new applications in sculpting and modeling,
+with subdivision of surfaces and weight vertex groups. A series of
+graphics examples demonstrates the quality, predictability and flexibility
+of the method in a real production environment with software blender.
 \end{abstract}
@@
 edges \cite{DeRose1998}, or the modification of some vertex weights
-to locally control the zone of influence \cite{Biermann2000}. Nevertheless,
+to locally control the zone of influence \cite{Biermann2000}. Neverteless
 these methods are difficult to deal with since they require a large
@@
 presented method requires a single parameter that controls the global
-curvature, whereby it performs a curvature enhancement and shape exaggeration
-of the model, creating a family of different versions of the same
-object and therefore preserving the detail of the original model and
-a realistic appearance.
+curvature, which is used to maintain realistic shapes, creating a
+family of different versions of the same object and therefore preserving
+the detail of the original model and a realistic appearance.
 
-Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
-Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}.
-It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles.
-The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when brush inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
-In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.
+Interest in meshes composed of triangles and quads has lately increased
+because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
+Nowadays, many artists use a manual connection of a couple of vertices
+to perform animation processes and interpolation \cite{Mullen2007}.
+It is then of paramount importance to develop operators that easily
+interact with such meshes, eliminating the need of preprocessing the
+mesh to convert it to triangles. The curvature enhancement and shape
+exaggeration can thus be used as such operator in the sculpting process,
+when inflating a shape since current brushes end up by losing detail
+when moving vertices \cite{Stanculescu2011}. In contrast, the presented
+method inflates a mesh by moving the vertices towards the reverse
+curvature direction, conserving the shape and sharp features of the
+model.
 
@@
 adjust the shape offset by a constant distance, with enough precision
-as to minimize the Hausdorf error. Nevertheless, these methods fail
+as to minimize the Hausdorff error. Nevertheless, these methods fail
 to conserve sufficient detail because of the smoothing, a crucial
@@
 
-\cite{Gal2009} proposes automatic feature detection and shape edition
-with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys, characerized bytheir first
-and second order curvature derivatives \cite{Ohtake2004}, and angle-based
-threshold.Likewise, curves have been also classified as planar or
-non-planar, approximated by lines, circles, ellipses and other complex
-shapes. In such case, the user defines an initial change over several
-features and this change is propagated towards other features, based
-in the classified shapes and the inter-relationships between them.
-This method works well with objects that have sharp edges, composed
-of basic geometric shapes such as lines, circles or ellipses, but
-the method is very limited at classifying when models are smooth since
-it cannot find the features to edit and preserve.
+Gal et al. \cite{Gal2009} propose automatic feature detection and
+shape edition with feature inter-relationship preservation. They define
+salient surface features like ridges and valleys, characerized by
+their first and second order curvature derivatives \cite{Ohtake2004},
+and angle-based threshold. Likewise, curves have been also classified
+as planar or non-planar, approximated by lines, circles, ellipses
+and other complex shapes. In such case, the user defines an initial
+change over several features which is propagated towards other features,
+based on the classified shapes and the inter-relationships between
+them. This method works well with objects that have sharp edges, composed
+of basic geometric shapes such as lines, circles or ellipses. However,
+the method is very limited when models are smooth since it cannot
+find the proper features to edit.
 
@@
 a polygonal representation or a voxel grid-based method. Brushes for
-inflation operations only depend on the normal vertex \cite{Stanculescu2011},
-in grid-based sculpting, some other operations have allowed to add
-or remove voxels, since producing polygonal meshes require processing
-isosurfaces from volume \cite{Galyean1991}. The problem whit this
-type of operations is the difficulty of maintaining the surface details
-during larger scale deformations.
+inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
+In grid-based sculpting, some other operations have allowed to add
+or remove voxels since production of polygonal meshes require a processing
+of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
+from the difficulty of maintaining the surface details during larger
+scale deformations.
 
@@
 
-Computer graphics objects which have been reconstructed from real
-world, contain undesirable noise. Laplacian Smooth techniques allow
-noise reduction on a mesh's surface with minimal changes on its shape
-while still preserves desirable geometry as well as the shape of the
-original model.
+Computer objects, reconstructed from the real world, are usually noisy.
+Laplacian Smooth techniques allow a proper noise reduction on the
+mesh surface with minimal shape changes, while still preserving a
+desirable geometry as well as the original shape.
 
-The functional used in many Laplacian smoothing approaches to constrain
-energy minimization is based on a total curvature of a surface $S$.
+Many smoothing Laplacian functionals regularize the surface energy
+by controling the total surface curvature$S$.
 
@@
 
-\caption{\label{fig:voronoi_region}Area of Voronoi region around $v_{i}$
+\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
 in dark blue.\protect \\
- $v_{j}$ 1-ring neighbors around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$
-opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
+ $v_{j}$ belong to the first neighborhood around $v_{i}$. $\alpha_{j}$
+and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
 \end{figure}
 
-Consider a surface $S$ composed by a set of triangles around vertex
-$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
-show in figure \ref{fig:voronoi_region}, The change in the area produced
-by the movement of $v_{i}$ is named gradient of \textit{Voronoi region
-\cite{Pinkall1993,Desbrun1999,Meyer2003}.}
+Consider a surface $S$ composed of a set of triangles around vertex
+$v_{i}$. Let us define the \textit{Voronoi region} of $v_{i}$ as
+show in figure \ref{fig:voronoi_region}, The area change produced
+by the movement of $v_{i}$ is called the gradient of \textit{Voronoi
+region \cite{Pinkall1993,Desbrun1999,Meyer2003}.}
 
@@
 
-If we normalize this gradient in equation (\ref{eq:eq_gradient_voronoi_area})
-by the total area in 1-ring around $v_{i}$, we have the \textit{discrete
-mean curvature normal} of a surface $S$ as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
+If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is
+normalized by the total area of the first neighborhood around $v_{i}$,
+the \textit{discrete mean curvature normal} of a surface $S$ is obtained,
+as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
 
@@
 
-The \textit{Laplace Beltrami operator} LBO denoted $\triangle_{g}$
-is used for measures mean curvature normal of the Surface $S$ \cite{Pinkall1993}.
+The \textit{Laplace Beltrami operator} LBO noted as $\triangle_{g}$
+is used for measuring the mean curvature normal to the Surface $S$
+\cite{Pinkall1993}.
 
@@
 
-The LBO has desirable features: one feature of the LBO is in direction
-of surface area minimization, allowing to minimize energy using it
-on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).
+The LBO has desirable properties: the LBO points out to the direction
+of the minimal surface area, minimizing the energy of the total surface
+curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).
 
@@
 
-Our method allows the editing of geometric features using the curvature
-enhancement and smoothing, generating a parameterized family of shapes
-from a set of vertices which represent a coarse sketch of the desired
-model. Our approach can be mixed with traditional or uniform subdivision
-surfaces methods, is iterative and converges towards a continuous
-and smooth version of the original model.
+The method allows shape magnification and exaggeration using the laplacian
+smoothing operator in the reverse direction, generating a parameterized
+family of shapes from a set of vertices which represent a coarse sketch
+of the desired model. Our approach can be mixed with traditional or
+uniform subdivision surfaces methods, is iterative and converges towards
+a continuous and smooth version of the original model.
 

### 2013-01-14 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

@@
 
+%i.e.= id est (esto es)
 The LBO has desirable properties: the LBO points out to the direction
@@
 
-The method allows shape magnification and exaggeration using the laplacian
-smoothing operator in the reverse direction, generating a parameterized
-family of shapes from a set of vertices which represent a coarse sketch
-of the desired model. Our approach can be mixed with traditional or
-uniform subdivision surfaces methods, is iterative and converges towards
-a continuous and smooth version of the original model.
-
-Our method allows the use of soft constraints weighting the effect
-of smoothing at each vertex based on a normalized weight, which are
-assigned to the control vertices of the original mesh or. The weights
-of the new vertices resulting from the subdivisions are calculated
-by interpolation, allowing modifying the behavior of the method on
-specific regions of the original model.
-
-Our work presents an extension of the Laplace Beltrami operator for
-hybrid quad/triangle meshes, allows using mixed arbitrary types of
-mesh representation, exploiting the basic geometrical relationships
-facilitating and ensuring convergence of the algorithm and similar
-shapes consistent with the original shape against the other methods.
+This method exaggerates a shape using a Laplacian smoothing operator in the reverse direction, i.e., the new shape is a modified version in which those areas with larger curvature are magnified.
+The operator amounts to a generator of a set of models which conserves the basic silhouette of the original shape.
+In addition, the presented approach can be easily mixed with traditional or uniform subdivision of surfaces.
+This method is based on an original extension of the Laplace Beltrami operator for hybrid quad/triangle meshes, mixing arbitrary types of meshes, exploiting the basic geometrical relationships and ensuring algorithm convergence.
 
@@
 Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
-triangles $T$.
-
-The area of $1$-ring neighborhood ($N_{1}$) with shared face quad
-or triangle to vertex $v_{i}$ in $M$ is.
+triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$ with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
+or triangle $A\left(T_{N_{1}\left(v_{i}\right)}\right)$ to vertex $v_{i}$ in $M$   is.
 
@@
 
-Applying the mean average area according to \cite{Xiong2011} of all
-possible triangulations for each quad to $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
-as show in figure \ref{fig:quad_xiong}.
+Applying the mean average area, according to \cite{Xiong2011}, from all
+possible triangulations, as show in figure \ref{fig:quad_xiong}, the area for each quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$ is
 
@@
 
-Thus triangles and quads configurations of the 1-ring neighborhood
-faces adjacent to $v_{i}$ can be simplified to five cases shown in
+Triangle and quad configurations of the 1-ring neighborhood
+faces, adjacent to $v_{i}$, can be simplified to five cases, as shown in
 figure \ref{fig:LBO-basic-5-TQ}.
 
-Then according to equation (\ref{eq:discrete_mean_curvature_normal}),
+According to equation (\ref{eq:discrete_mean_curvature_normal}),
 (\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
@@
 
-\subsection{Curvature Enhancing\label{sub:Curvature-Enhancing}}
+\subsection{The Curvature Enhancement\label{sub:Curvature-Enhancing}}
 
@@
 
-\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
-from coarse model to enhancing the curvature obtained from Catmull-Clark
-Subdivision and the use of constraints over coarse model with weight
-vertex group in red.}
+\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
+from a coarse model: the curvature, obtained from the Catmull-Clark
+Subdivision, is enhanced. Soft constraints, over the coarse model, is drawn in red.}
 
@@
 
-The curvature enhancing uses the inverse direction of the curvature
-flow to move the vertices in the portions of the mesh with most curvature.
-In this equation we use a diffusion process:
+The curvature is enhanced by using the reverse direction of the curvature
+flow, moving the vertices towards those mesh portions with larger curvature.
+A standard diffusion process is applied:
 
@@
 
-To solve the equation above we use implicit integration and a normalized
+To solve this equation, implicit integration is used as well as a normalized
 version of TQLBO matrix.
@@
 
-The vertices $V^{t+1}$are enhanced along their inverse curvature
-normal directions by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+The vertices $V^{t+1}$ are enhanced, along their reverse curvature direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
 $L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
@@
 vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, and $\lambda dt$ is the enhance factor that support negative
-and positive values, negative for enhancing positive for smoothing.
+group, and $\lambda dt$ is the enhancement factor that supports negative
+and positive values: negative for enhancement and positive for smoothing.
 
-The curvature cannot be calculted at the border of the meshes that
-are not closed, for that reason we use the scale-dependent operator
-proposed by \cite{Desbrun1999}.
-
-Our method was designed for use with weighted vertex groups which
-specify the final curvature enhancement on the solution, these weights
-vary between $0$ and $1$ with a value of $0$ makes no changes and
-with values 1 applies a maximal change. The weights modify influence
-zones where the Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
-Families of shapes that are generated may change substantially with
+The method was devised to use with weighted vertex groups, which
+specify the final curvature enhancement of the solution, meaning $0$ as no changes and 1 when a maximal change is applied. The weights modify the influence
+zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}. Interestingly, the generated family of shapes may change substantially with
 the weights of specific control points.
 
-The models volume increases as the lambda is larger and negative,
-this can be go against by a simple method of volume preservation.
-In \cite{Desbrun1999} presents a simple method to resize the mesh
-however the model suffers large displacements when $\lambda<-1.0$
-or after multiple iterations. We propose the following solution: If
+The model volume increases as the lambda is larger and negative,
+this can be counteracted with a simple volume preservation. 
+However, the mesh may suffer large displacements when $\lambda<-1.0$
+or after multiple iterations. A simple volume conservation algorithm is: If
 $v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
@@
 
-$\overline{v}$ is the center of the mesh, $vol_{ini}$ is an initial
+$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial
 volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
-we define a scale factor.
+the scale factor.
 
@@
 
-The new vertices positions are:
+allows to move the new vertices to:
 
@@
 
-\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
-with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
-$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
-first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
+\caption{\label{fig:Catmull_Clark}Left: Original Model,  color model
+with Catmull-Clark Subdivision in green. Models with Laplacian smoothing: $\lambda=60.0$,
+$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applying curvature enhancement: $\lambda=-200.0$, $\lambda_{e}=12.0$
 and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
@@
 
-We designed a new brush that allows the enhancement of the curvatures
-of a polygon mesh in real time. Our brush works well with the stroke
-method named \textsl{Drag Dot}  which allows to preview the changes
-in the model before you release the mouse button or pen tablet, also
-allows to move the mouse over the model to fit exactly where you want
-to perform the enhancement of the curvature.
+A new sculpting brush is herein proposed and aims to inflate the shape, magnifying the shape curvatures
+of a polygon mesh in real time. This brush works properly with the stroke
+method  \textsl{Drag Dot}, allowing to pre-visualize the model changes before the mouse is released. Also,
+it allows to move the mouse along the model to match the curvature zone which is supposed to be enhanced.
 
-Brushes that perform similar work as inflate can create distortions
-in the mesh and can also produce self-intersections in the mesh, as
-these brushes only move the vertices along the normal and do not take
-into account the global information. Whereas our method looks for
-the best way to make inflation while preserving the global curvature
-retaining the several shape and sharp features of the model.
-
-Our method simplifies the work required for the enhancement, which
-would be to use some different brushes for inflating and some other
-to soften and styling. With our enhanced brush in one step can be
-performed.
-
-For the real-time brush it necessary that the Laplacian matrix is
-constructed with the vertices that are within the radius  of the sphere
-defined by the user, which reduces the size of the matrix to be processed,
-the center of this sphere depends on the place where the user clicks
-on the canvas and three-dimensional mesh place where the click is
+Brushes that perform a similar inflation can introduce mesh distortions or produce mesh self-intersections, provided these brushes only move the vertices along the normal without any global information.
+In contrast, the present method searches for a proper inflation while preserving the global curvature, retaining the original shape and main model features.
+In addition, this method simplifies the work required for the enhancement since it needs not different brushes for inflating, softening or styling.
+The enhanced brush can make all these operation in a single step.
+Real-time brushes require the Laplacian matrix is constructed with the vertices that are within the sphere radius defined by the user, reducing the matrix to be processed,
+the center of this sphere depending on the place where the user clicks on the canvas and the three-dimensional mesh placed where the click is
 projected.
-
-Furthermore special handling is required for the vertices at the boundary
-which have neighbors that are not within the radius of the brush.
-These vertices must be marked as boundary and the curvature will not
-be calculated for them, but must be present in the matrix so that
-every vertex has their neighbors within the selection, this change
-allows the results to be much smoother on the border. The Laplacian
-matrix for sculpt mode as a matrix equation.
+Special handling is required for the boundary vertices with neighbors that are not within the brush radius: these vertices are marked as boundary and the curvature is not there calculated, but they must be included in the matrix so that every vertex has their corresponding neighbors within the selection.
+The sculpting Laplacian matrix reads as.
 
@@
 
-Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
-of radius $r$. The matrixes should remove rows and columns of vertices
-index that are not within the radius.
+Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center
+of radius $r$. The matrices should remove rows and columns of vertices that are not within the radius.
 
@@
 
-The Catmull-Clark subdivision transformation is used to smooth a surface
+The Catmull-Clark subdivision transformation is used to smooth a surface,
 as the limit of a sequence of subdivision steps\cite{Stam1998}. This
-process is governed by properties of B-splines curve from multivariate
-spline theory\cite{Loop1987}. This method does a recursive subdivision
-transformation that refines the model into a linear interpolation
-that approximates a smooth surface. The smoothness of the model is
+process is governed by a B-spline curve \cite{Loop1987}, performing a recursive subdivision transformation that refines the model into a linear interpolation
+that approximates a smooth surface. The model smoothness is
 automatically guaranteed \cite{DeRose1998}.
@@
 Catmull-Clark subdivision surface methods generate smooth and continuous
-models from a coarse model and produce results quickly due to the
-simplicity of implementation, but with these methods is not easy to
-make changes to the global curvature of the model. If we use Catmull-Clark
-subdivision surfaces and curvature enhancement for modeling from coarse
-models with few vertices can generate families of shapes changing
-a single parameter, this would allow an artist to choose the model
-from a similar set of options that best meets his/her needs without
-having to change each one of the control vertices.
+models from a coarse model and produce quick results because of the
+simplicity of implementation. Nevertheless, changes to the global curvature are hardly implantable. The Catmull-Clark
+subdivision surfaces together with curvature enhancement can easily generate families of shapes by changing
+a single parameter, allowing to handle a model with very few vertices. In practice, this would allow an artist to choose a model
+from a similar set of options that  would meet his/her needs without having to change each of the control vertices.
+Likewise, the presented method allows the use of vertex weight paint over the control points.
+The weights can be applied to a coarse model, followed by  a Catmull-Clark subdivision where weights are interpolated, producing
+weights with smooth changes in the influence zones,  as shown in figure \ref{fig:Subdivision-Cups}.c.
 
-Our method allows the use of vertex weight paint over the control
-points. The weights can be applied to a coarse model, then to perform
-a Catmull-Clark subdivision where weights are interpolated, producing
-weights with smooth changes in the zones of influence, so the obtained
-curvature is much softer at those areas as shown in figure \ref{fig:Subdivision-Cups}.c.
-
-In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
+In equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
 matrix with weights corresponding to each vertex. Weights at each
-vertex produce a different solution for this reason the matrix is
-placed in the diffusion equation, as families that are generated may
+vertex produce a different solution so that the matrix must be
+placed in the diffusion equation since families that are generated may
 change substantially with weighted of specific control points.
@@
 
-In this section we describe the results of our curvature enhance method
+The results of the curvature enhancement method
 with the extension of the Laplace Beltrami operator for hybrid quad/triangle
@@
 \ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
-\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). We test the curvature
-enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
+\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). The curvature
+enhancement was assessed with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
 GHz and 8 GB RAM.
 
-Figure \ref{fig:TQLBO_test} show the results when applying Laplace
+Figure \ref{fig:TQLBO_test} shows the results when applying the Laplace
 Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
-in a model with a simple subdivision. In column (c) Laplacian smoothing
-was applied to the model consists of only quads. In column (d) the
-model was converted to triangles and then Laplacian smoothing was
-applied. In column (e) the model is converted randomly some quads
-into triangles and then Laplacian smoothing is applied, showing similar
-results to those composed only of triangles or squares.
+in a model with a simple subdivision. In column (c) the Laplacian smoothing
+was applied to a model consisting of only quads. In column (d) the
+model was converted to triangles and then the Laplacian smoothing was
+applied. In column (e) the model was randomly converted  from some quads
+into triangles and then the Laplacian smoothing is applied, showing similar
+results to those meshes composed only of triangles or quads.
 
@@
 
-Methods using Catmull-Clark subdivision surface and the enhancement
+Methods using the Catmull-Clark subdivision surface and the enhancement
 allows to modify the curvature that is obtained with the process of
-subdivision as shown in figure \eqref{fig:Subdivision-Cups} this
-test used a coarse model of a cup, after the model was performed subdivision
-then was performed Laplacian smoothing and enhancement by modifying
-the parameters $\lambda$ y $\lambda_{e}$ corresponding to the lambda
-for rings and edges respectively. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use weight vertex groups
-over coarse models with subdivision surfaces that allowed to generate
-the weights for the new interpolated vertices, these new weights were
-used for the enhancement obtained the 6 cups that are to the right
+subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
+test used a coarse cup model, in which the subdivision was performed, followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
+\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex groups over coarse models, with subdivision surfaces that allowed to generate
+the weights for the new interpolated vertices. These new weights were
+used for the enhancement obtained on the 6 cups that are at the right
 of the figure \eqref{fig:Subdivision-Cups}.d.
 
-Laplacian smoothing applied with simple subdivision may produce similar
-results to those obtained with Catmull-Clark whose models are on average
-equal triangles as shown in figure \ref{fig:Catmull_Clark} green
-model and that obtained with Laplacian smoothing $\lambda=60.0$,
-$\lambda_{e}=12.0$, but also can modify the curvature obtained after
-applying Catmull-Clark as shown in the three columns to the right
-of the figure \ref{fig:Catmull_Clark}.
-
-Figure \ref{fig:camello_enhanced} show the generation of different
-versions of a camel according to parameter lambda. In the top row
-you can see results of do curvature enhance over all model, as the
-lambda becomes larger and negative in this model it inflates the convex
-parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
-the larger enhancements on the model features. The bottom row of figure
-\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
-which allows to specify which areas will be enhanced. On the left
-the enhancement of the legs of the camel is shown which produces enhancement
-of organic aspect, notice that the border is not distorted and smooth
-in the union.
+Laplacian smoothing applied with simple subdivision may produce similar results to those obtained with Catmull-Clark, whose models are in average equal triangles, as shown in figure \ref{fig:Catmull_Clark}, green model.
+The one obtained with the Laplacian smoothing is shown in panel (c), (d)  and those curvature modified versions are in (d) and (f).
+As can be observed, different versions of the original sketch can be obtained by parameterizing a single model value, a great advantage of the presented method.
+Figure \ref{fig:camello_enhanced} shows the generation of different versions of a camel according to the $\lambda$ parameter.
+In the top row,  it is shown the curvature enhancement results, as $\lambda$ becomes larger and negative, the resultant shape is observed as if the model would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
+The larger the $\lambda$ parameter the larger the model feature enhancements.
+The bottom row of figure \ref{fig:camello_enhanced} shows the use of weighted vertex groups, specifying which areas will be enhanced.
+On the left, the enhancement of the camel legs produces an organic aspect, notice that the border is not distorted and smooth.
 
@@
 
-\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
-and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
+\caption{\label{fig:camello_enhanced}Top row: Original camel model at left.
+Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
+and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for the head
 and neck.}
@@
 
-Our method for enhancement of the silhouette features is predictable
-and invariant under isometric transformations as those present in
-some animations (see Figure \ref{fig:Animated_Camell}). This animation
-shows some poses of a camel during a walk, enhancement is performed
-in the neck and legs as shown in the bottom left part of the figure
-\ref{fig:Animated_Camell}. Local modifications produced by pose interpolation
-or animation rigging do not significantly affect the result as with
-camel legs in each sample pose different flexion of the leg joints
-enhancement camel keeps flesh-like shapes in the pattern produced
-original by the artist. This is due to the diffusion process which
-is subjected to the mesh so that small local changes are treated without
-significantly affecting global solution. Our method is invariant of
-rotation, this since depends exclusively on the normal field of the
-mesh, wish is invariant under global rotations.
+The enhancement of the silhouette features is predictable
+and invariant under isometric transformations, as those classically used in
+some animations (see Figure \ref{fig:Animated_Camell}). In this figure, the animation
+shows some camel poses during a walk, the enhancement is performed
+at the neck and legs, as shown in the bottom left camel in figure
+\ref{fig:Animated_Camell}. Local modifications produced by the pose interpolation
+or animation rigging practically do not affect the result.
+In spite of at any pose of the camel legs there is a clear difference, the enhancement method allows a  flesh-like shape in the original pattern produced by the artist.
+This is due to the mesh restricted diffusion process so that small local changes are treated without affecting the global solution.
+The method therefore is rotation invariant since it depends exclusively on the normal mesh field, which is rotation invariant.
 
-Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
-brush for sculpting in real time. One pass was used with the brush
-as shown in the figure with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
-camel shows how the leg self-intersecting and looks like two bubbles
-stuck, the same happens to the fingers on the bottom of the figure.
-Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
-we get better results sd the are retained shape of the silhouette
-and the details of the fingers and leg. Similar results can be obtained
-by an artist however it would take several steps and require the use
-of several brushes. With curvature enhancement it only takes one step.
-This new method can easily enhance organic features like muscles during
-the sculpting process. In figure \ref{fig:Performance-sculpt} we
-show the performance of curvature enhancement brush, in this experiment
-we use three models with 12K, 40K and 164K vertices, this models were
-sculpted with curvature enhance brush in each step the brush sphere
-contain a variable number of vertices for processing. The processing
-time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
-for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
-times are good, because usually an artist sculpts a model for parts,
-and each part is represented by an average of about 3000 vertices
-in the models we use.
+Figure \ref{fig:Sculpt_Brush} shows the use of a curvature enhancement
+brush for sculpting in real time. One pass was used with the brush,
+as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
+the camel foot shows the inflation intersection that looks like two bubbles, a similar pattern to what is observed to the fingers on the bottom of the same figure.
+The silhouette enhancement is observed in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained together with its finger and leg details.
+Similar results can be obtained by a user, however it would take several steps and require the use
+of several brushes, while the curvature enhancement took a single step.
+Likewise, this new method can easily enhance organic features like muscles during the sculpting process.
+In figure \ref{fig:Performance-sculpt} the curvature enhancement brush performance is illustrated, in this experiment three models with 12K, 40K and 164K vertices, were used.
+These models were
+sculpted with the curvature enhance brush, at each step the brush sphere
+containing a variable number of vertices for processing. The processing
+time for 800 vertices in the camel paw (40k model) only took 0.1 seconds,
+for 2600 vertices in the leg and neck (model 40k) took 0.5 seconds, these
+times are suitable in real applications since an artist sculpts a model for parts,
+and each part is represented by an average of about 3000 vertices.
 
-Tests with the Laplacian operator equation (\ref{eq:TQLBO_Simple_Matrix})
-and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
-produce similar results if the triangles that compose the mesh are
-the same size on average. The normalized version is more stable and
+Tests with the Laplacian operator  (equation \ref{eq:TQLBO_Simple_Matrix})
+and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
+produce similar results if the triangles that compose the mesh are about
+the same size. The normalized version is more stable and
 predictable because it is not divided by the area of the ring which
-may be very small and cause problems during floating point calculations
-as shown in figure \ref{fig:(a)Monkey}.c bottom row. The enhancement
-of curvature of the model with the normalized Laplacian operator has
-a more regular behavior. The model can be deformed in TQLBO normalized
-version with large lambdas ($\lambda>400$) while it intersects itself
-it produces no peaks. Figure \ref{fig:(a)Monkey} shows different
-results due to the area of the triangles in the model. Triangles with
+may be very small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c bottom row.
+The curvature enhancement of the model with the normalized Laplacian operator results in a more regular pattern.
+The model can be deformed with a TQLBO normalized
+version with large $\lambda$ ($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey} shows different
+results due to the triangle areas in the model. Triangles with
 larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
@@
 red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
-blue circle, (c) Enhance curvature brush for fingers in red circle.}
+blue circle, (c) Curvature enhancement brush for fingers in red circle.}
 \end{figure}
@@
 \caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
-enhance brush in terms of vertices sculpted per second. Three models
+enhancement brush in terms of the sculpted vertices per second. Three models
 with 12K, 40K, 164K vertices used for sculpting in real time.}
@@
 
-\caption{\label{fig:Animated_Camell}Our method is pose insensitive. The enhanced
+\caption{\label{fig:Animated_Camell}The method is pose insensitive. The enhancement
 for the different poses are similar in terms of shape. Top row: Original
-walk cycle camel model. Bottom row: Curvature enhancing with weight
+walk cycle camel model. Bottom row: Curvature enhancement with weight
 vertex group, $\lambda=-400$ and $2$ iterations. }
@@
 
-Our method was implemented as a modifier for modeling and brush for
-sculpting on the Blender software \cite{blender} with C and C++.
-Working with Blender allowed us to test the method interactively against
-others as Catmull-Clark, weight vertex groups and sculpting system
+The method was implemented as a modifier for modeling and brush for
+sculpting, on the Blender software \cite{blender} in C and C++.
+Working with the Blender allowed to test the method interactively against
+others, as Catmull-Clark, weight vertex groups and sculpting system
 in Blender.
 
-To improve the performance, we worked with Blender mesh struct visiting
-each triangle or quad and adding its corresponding index in a list
-that stores the sum of the Laplacian weights of the ring, in this
-way we only had to visit two times the list of faces of the mesh list
-and two times the list of the edges if the mesh was not closed. The
-brush sculpting mode required to create a list that maps the index
-of the selected vertices to a list from 1 to N where N is the number
-of vertices selected and the number of rows in the linear system to
-solve. This drastically reduced the calculations enabling real-time
-processing. In the construction of our Laplacian matrix several index
-were locked at vertices having faces areas or lengths edges with value
-zero that can cause spikes and bad results.
+To improve the performance, it was worked with the Blender mesh struct, visiting
+each triangle or quad and storing its corresponding index and the sum of the Laplacian weights of the ring in a list so that only two visits were required for the list of mesh faces and two times the edge list, if the mesh was not closed.
+This drastically reduced calculations, enabling real-time
+processing. In the construction of the Laplacian matrix, several index were locked at vertices having face areas or edge lengths with null value that could cause spikes and bad results.
 
-Under this conditions matrix at the equation\ref{eq:TQLBO_Simple_Matrix}
-is sparse since the number of neighbors per vertex corresponding to
-the number of data per row is small compared to the total number of
+Under these conditions, the matrix at equation\ref{eq:TQLBO_Simple_Matrix}
+is sparse since the number of neighbors per vertex, corresponding to
+the number of data per row, is smaller compared to the total number of
 vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
@@
 for hybrid quad/triangle meshes that can be used in production environments
-without modification that provides results similar to those obtained
+and provides results similar to those obtained
 by working only with triangles or quads.
-
-We introduced a new way to perform silhouettes enhancement in a mesh
-for modeling or sculpting in a few steps which allows the modification
-of the curvature of a model while preserving its overall shape. We
-introduce a new method of modeling and show some of its possible uses.
-This method behaves in predictable ways which facilitate the learning
-process, and works well with isometric transformations opening the
+This paper has introduced a new way to change silhouettes in a mesh for modeling or sculpting in a few steps by means of the curvature model modification while preserving its overall shape.
+In addition,  a new modeling method has also been presented some possible applications have been illustrated.
+The method works properly with isometric transformations, opening the
 possibility of introducing it on the process of animation.
 
-We show that this tool could work in the early stages in where coarse
+We show that this tool may work in early modeling stages, case in which coarse
 models are used, allowing to modify the curvature generated by the
-Catmull-Clark subdivision surfaces, avoiding the edition of the vertices
-with the change of a few parameters.
+Catmull-Clark subdivision surfaces, and thereby avoiding edition of the vertices
+with change of a single parameters.
 
-As future work we analyze theoretically the relationship between the
-Catmull-Clark subdivision surfaces and Laplacian smoothing because
-in some cases can produce very similar results. But the subdivision
-surface is a fast method thereby reducing computation times for calculate
-curvature in the mesh.
+Future work includes the analysis of theoretical relationships between the
+Catmull-Clark subdivision surfaces and the Laplacian smoothing since they can produce very similar results.
 

### 2013-01-15 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 This paper proposes a novel modeling method for a hybrid quad/triangle
-mesh by enhancing the global object curvature. This method uses our
-adapted extension of the Laplace Beltrami operator. Along with the
+mesh by enhancing the global object curvature. This method uses a
+original extension of the Laplace Beltrami operator. Along with the
 method, this work presents new applications in sculpting and modeling,
@@
 
-%i.e.= id est (esto es)
 The LBO has desirable properties: the LBO points out to the direction
@@
 
-This method exaggerates a shape using a Laplacian smoothing operator in the reverse direction, i.e., the new shape is a modified version in which those areas with larger curvature are magnified.
-The operator amounts to a generator of a set of models which conserves the basic silhouette of the original shape.
-In addition, the presented approach can be easily mixed with traditional or uniform subdivision of surfaces.
-This method is based on an original extension of the Laplace Beltrami operator for hybrid quad/triangle meshes, mixing arbitrary types of meshes, exploiting the basic geometrical relationships and ensuring algorithm convergence.
+This method exaggerates a shape using a Laplacian smoothing operator
+in the reverse direction, i.e., the new shape is a modified version
+in which those areas with larger curvature are magnified. The operator
+amounts to a generator of a set of models which conserves the basic
+silhouette of the original shape. In addition, the presented approach
+can be easily mixed with traditional or uniform subdivision of surfaces.
+This method is based on an original extension of the Laplace Beltrami
+operator for hybrid quad/triangle meshes, mixing arbitrary types of
+meshes, exploiting the basic geometrical relationships and ensuring
+algorithm convergence.
 
@@
 Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
-triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$ with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
-or triangle $A\left(T_{N_{1}\left(v_{i}\right)}\right)$ to vertex $v_{i}$ in $M$   is.
+triangles $T$.
+
+Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
+triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
+with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
+or triangle $\ensuremath{A\left(T_{N_{1}\left(v_{i}\right)}\right)}$
+to vertex $\ensuremath{v_{i}}$ in $M$ is.
 
@@
 
-Applying the mean average area, according to \cite{Xiong2011}, from all
-possible triangulations, as show in figure \ref{fig:quad_xiong}, the area for each quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$ is
+Applying the mean average area, according to \cite{Xiong2011}, from
+all possible triangulations, as show in figure \ref{fig:quad_xiong},
+the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
+is
 
@@
 
-Triangle and quad configurations of the 1-ring neighborhood
-faces, adjacent to $v_{i}$, can be simplified to five cases, as shown in
+Triangle and quad configurations of the 1-ring neighborhood faces,
+adjacent to $v_{i}$, can be simplified to five cases, as shown in
 figure \ref{fig:LBO-basic-5-TQ}.
@@
 from a coarse model: the curvature, obtained from the Catmull-Clark
-Subdivision, is enhanced. Soft constraints, over the coarse model, is drawn in red.}
+Subdivision, is enhanced. Soft constraints, over the coarse model,
+is drawn in red.}
 
@@
 The curvature is enhanced by using the reverse direction of the curvature
-flow, moving the vertices towards those mesh portions with larger curvature.
-A standard diffusion process is applied:
+flow, moving the vertices towards those mesh portions with larger
+curvature. A standard diffusion process is applied:
 
@@
 
-To solve this equation, implicit integration is used as well as a normalized
-version of TQLBO matrix.
+To solve this equation, implicit integration is used as well as a
+normalized version of TQLBO matrix.
 
@@
 
-The vertices $V^{t+1}$ are enhanced, along their reverse curvature direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+The vertices $V^{t+1}$ are enhanced, along their reverse curvature
+direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
 $L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
@@
 vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, and $\lambda dt$ is the enhancement factor that supports negative
-and positive values: negative for enhancement and positive for smoothing.
+group, and $\lambda dt$
 
-The method was devised to use with weighted vertex groups, which
-specify the final curvature enhancement of the solution, meaning $0$ as no changes and 1 when a maximal change is applied. The weights modify the influence
-zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}. Interestingly, the generated family of shapes may change substantially with
-the weights of specific control points.
+is the enhancement factor that supports negative and positive values:
+negative for enhancement and positive for smoothing.
 
-The model volume increases as the lambda is larger and negative,
-this can be counteracted with a simple volume preservation. 
-However, the mesh may suffer large displacements when $\lambda<-1.0$
-or after multiple iterations. A simple volume conservation algorithm is: If
+The method was devised to use with weighted vertex groups, which specify
+the final curvature enhancement of the solution, meaning $0$ as no
+changes and 1 when a maximal change is applied. The weights modify
+the influence zones, where the Laplacian is applied, as shown in equation
+\ref{eq:Lineal_System_with_wp}. Interestingly, the generated family
+of shapes may change substantially with the weights of specific control
+points.
+
+The model volume increases as the lambda is larger and negative, this
+can be counteracted with a simple volume preservation. However, the
+mesh may suffer large displacements when $\lambda<-1.0$ or after
+multiple iterations. A simple volume conservation algorithm is: If
 $v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
@@
 
-$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial
-volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
-the scale factor.
+$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
+and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
+factor.
 
@@
 
-\caption{\label{fig:Catmull_Clark}Left: Original Model,  color model
-with Catmull-Clark Subdivision in green. Models with Laplacian smoothing: $\lambda=60.0$,
-$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying curvature enhancement: $\lambda=-200.0$, $\lambda_{e}=12.0$
-and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
+Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
+$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
+Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applying curvature enhancement: (e) $\lambda=-200.0$,
+$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
 \end{figure*}
 
-A new sculpting brush is herein proposed and aims to inflate the shape, magnifying the shape curvatures
-of a polygon mesh in real time. This brush works properly with the stroke
-method  \textsl{Drag Dot}, allowing to pre-visualize the model changes before the mouse is released. Also,
-it allows to move the mouse along the model to match the curvature zone which is supposed to be enhanced.
+A new sculpting brush is herein proposed and aims to inflate the shape,
+magnifying the shape curvatures of a polygon mesh in real time. This
+brush works properly with the stroke method \textsl{Drag Dot}, allowing
+to pre-visualize the model changes before the mouse is released. Also,
+it allows to move the mouse along the model to match the curvature
+zone which is supposed to be enhanced.
 
-Brushes that perform a similar inflation can introduce mesh distortions or produce mesh self-intersections, provided these brushes only move the vertices along the normal without any global information.
-In contrast, the present method searches for a proper inflation while preserving the global curvature, retaining the original shape and main model features.
-In addition, this method simplifies the work required for the enhancement since it needs not different brushes for inflating, softening or styling.
-The enhanced brush can make all these operation in a single step.
-Real-time brushes require the Laplacian matrix is constructed with the vertices that are within the sphere radius defined by the user, reducing the matrix to be processed,
-the center of this sphere depending on the place where the user clicks on the canvas and the three-dimensional mesh placed where the click is
-projected.
-Special handling is required for the boundary vertices with neighbors that are not within the brush radius: these vertices are marked as boundary and the curvature is not there calculated, but they must be included in the matrix so that every vertex has their corresponding neighbors within the selection.
-The sculpting Laplacian matrix reads as.
+Brushes that perform a similar inflation can introduce mesh distortions
+or produce mesh self-intersections, provided these brushes only move
+the vertices along the normal without any global information. In contrast,
+the present method searches for a proper inflation while preserving
+the global curvature, retaining the original shape and main model
+features. In addition, this method simplifies the work required for
+the enhancement since it needs not different brushes for inflating,
+softening or styling. The enhanced brush can make all these operation
+in a single step. Real-time brushes require the Laplacian matrix is
+constructed with the vertices that are within the sphere radius defined
+by the user, reducing the matrix to be processed, the center of this
+sphere depending on the place where the user clicks on the canvas
+and the three-dimensional mesh placed where the click is projected.
+Special handling is required for the boundary vertices with neighbors
+that are not within the brush radius: these vertices are marked as
+boundary and the curvature is not there calculated, but they must
+be included in the matrix so that every vertex has their corresponding
+neighbors within the selection. The sculpting Laplacian matrix reads
+as.
 
@@
 
-Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center
-of radius $r$. The matrices should remove rows and columns of vertices that are not within the radius.
+Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center of
+radius $r$. The matrices should remove rows and columns of vertices
+that are not within the radius.
 
@@
 The Catmull-Clark subdivision transformation is used to smooth a surface,
-as the limit of a sequence of subdivision steps\cite{Stam1998}. This
-process is governed by a B-spline curve \cite{Loop1987}, performing a recursive subdivision transformation that refines the model into a linear interpolation
-that approximates a smooth surface. The model smoothness is
-automatically guaranteed \cite{DeRose1998}.
+as the limit of a sequence of subdivision steps \cite{Stam1998}.
+This process is governed by a B-spline curve \cite{Loop1987}, performing
+a recursive subdivision transformation that refines the model into
+a linear interpolation that approximates a smooth surface. The model
+smoothness is automatically guaranteed \cite{DeRose1998}.
 
@@
 models from a coarse model and produce quick results because of the
-simplicity of implementation. Nevertheless, changes to the global curvature are hardly implantable. The Catmull-Clark
-subdivision surfaces together with curvature enhancement can easily generate families of shapes by changing
-a single parameter, allowing to handle a model with very few vertices. In practice, this would allow an artist to choose a model
-from a similar set of options that  would meet his/her needs without having to change each of the control vertices.
-Likewise, the presented method allows the use of vertex weight paint over the control points.
-The weights can be applied to a coarse model, followed by  a Catmull-Clark subdivision where weights are interpolated, producing
-weights with smooth changes in the influence zones,  as shown in figure \ref{fig:Subdivision-Cups}.c.
+simplicity of implementation. Nevertheless, changes to the global
+curvature are hardly implantable. The Catmull-Clark subdivision surfaces
+together with curvature enhancement can easily generate families of
+shapes by changing a single parameter, allowing to handle a model
+with very few vertices. In practice, this would allow an artist to
+choose a model from a similar set of options that would meet his/her
+needs without having to change each of the control vertices. Likewise,
+the presented method allows the use of vertex weight paint over the
+control points. The weights can be applied to a coarse model, followed
+by a Catmull-Clark subdivision where weights are interpolated, producing
+weights with smooth changes in the influence zones, as shown in figure
+\ref{fig:Subdivision-Cups}.c.
 
@@
 matrix with weights corresponding to each vertex. Weights at each
-vertex produce a different solution so that the matrix must be
-placed in the diffusion equation since families that are generated may
-change substantially with weighted of specific control points.
+vertex produce a different solution so that the matrix must be placed
+in the diffusion equation since families that are generated may change
+substantially with weighted of specific control points.
 
@@
 
-The results of the curvature enhancement method
-with the extension of the Laplace Beltrami operator for hybrid quad/triangle
-meshes with several example models (see figures \ref{fig:Spectrum},
-\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
-\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
-\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). The curvature
-enhancement was assessed with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
-GHz and 8 GB RAM.
+The results of the curvature enhancement method with the extension
+of the Laplace Beltrami operator for hybrid quad/triangle meshes with
+several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
+\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
+\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
+\ref{fig:Animated_Camell}). The curvature enhancement was assessed
+with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz
+and 8 GB RAM.
 
@@
 Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
-in a model with a simple subdivision. In column (c) the Laplacian smoothing
-was applied to a model consisting of only quads. In column (d) the
-model was converted to triangles and then the Laplacian smoothing was
-applied. In column (e) the model was randomly converted  from some quads
-into triangles and then the Laplacian smoothing is applied, showing similar
-results to those meshes composed only of triangles or quads.
+in a model with a simple subdivision. In column (c) the Laplacian
+smoothing was applied to a model consisting of only quads. In column
+(d) the model was converted to triangles and then the Laplacian smoothing
+was applied. In column (e) the model was randomly converted from some
+quads into triangles and then the Laplacian smoothing is applied,
+showing similar results to those meshes composed only of triangles
+or quads.
 
@@
 subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
-test used a coarse cup model, in which the subdivision was performed, followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex groups over coarse models, with subdivision surfaces that allowed to generate
-the weights for the new interpolated vertices. These new weights were
-used for the enhancement obtained on the 6 cups that are at the right
-of the figure \eqref{fig:Subdivision-Cups}.d.
+test used a coarse cup model, in which the subdivision was performed,
+followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
+\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
+groups over coarse models, with subdivision surfaces that allowed
+to generate the weights for the new interpolated vertices. These new
+weights were used for the enhancement obtained on the 6 cups that
+are at the right of the figure \eqref{fig:Subdivision-Cups}.d.
 
-Laplacian smoothing applied with simple subdivision may produce similar results to those obtained with Catmull-Clark, whose models are in average equal triangles, as shown in figure \ref{fig:Catmull_Clark}, green model.
-The one obtained with the Laplacian smoothing is shown in panel (c), (d)  and those curvature modified versions are in (d) and (f).
-As can be observed, different versions of the original sketch can be obtained by parameterizing a single model value, a great advantage of the presented method.
-Figure \ref{fig:camello_enhanced} shows the generation of different versions of a camel according to the $\lambda$ parameter.
-In the top row,  it is shown the curvature enhancement results, as $\lambda$ becomes larger and negative, the resultant shape is observed as if the model would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
+Laplacian smoothing applied with simple subdivision may produce similar
+results to those obtained with Catmull-Clark, whose models are in
+average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
+(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
+the Laplacian smoothing is shown in panel (c), (d) and those curvature
+modified versions are in (e) and (f). As can be observed, different
+versions of the original sketch can be obtained by parameterizing
+a single model value, a great advantage of the presented method. Figure
+\ref{fig:camello_enhanced} shows the generation of different versions
+of a camel according to the $\lambda$ parameter. In the top row,
+it is shown the curvature enhancement results, as $\lambda$ becomes
+larger and negative, the resultant shape is observed as if the model
+would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
 The larger the $\lambda$ parameter the larger the model feature enhancements.
-The bottom row of figure \ref{fig:camello_enhanced} shows the use of weighted vertex groups, specifying which areas will be enhanced.
-On the left, the enhancement of the camel legs produces an organic aspect, notice that the border is not distorted and smooth.
+The bottom row of figure \ref{fig:camello_enhanced} shows the use
+of weighted vertex groups, specifying which areas will be enhanced.
+On the left, the enhancement of the camel legs produces an organic
+aspect, notice that the border is not distorted and smooth.
 
@@
 
-\caption{\label{fig:camello_enhanced}Top row: Original camel model at left.
+\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
 Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
 Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
-and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for the head
-and neck.}
+and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
+the head and neck.}
 \end{figure}
 
-The enhancement of the silhouette features is predictable
-and invariant under isometric transformations, as those classically used in
-some animations (see Figure \ref{fig:Animated_Camell}). In this figure, the animation
-shows some camel poses during a walk, the enhancement is performed
-at the neck and legs, as shown in the bottom left camel in figure
-\ref{fig:Animated_Camell}. Local modifications produced by the pose interpolation
-or animation rigging practically do not affect the result.
-In spite of at any pose of the camel legs there is a clear difference, the enhancement method allows a  flesh-like shape in the original pattern produced by the artist.
-This is due to the mesh restricted diffusion process so that small local changes are treated without affecting the global solution.
-The method therefore is rotation invariant since it depends exclusively on the normal mesh field, which is rotation invariant.
+The enhancement of the silhouette features is predictable and invariant
+under isometric transformations, as those classically used in some
+animations (see Figure \ref{fig:Animated_Camell}). In this figure,
+the animation shows some camel poses during a walk, the enhancement
+is performed at the neck and legs, as shown in the bottom left camel
+in figure \ref{fig:Animated_Camell}. Local modifications produced
+by the pose interpolation or animation rigging practically do not
+affect the result. In spite of at any pose of the camel legs there
+is a clear difference, the enhancement method allows a flesh-like
+shape in the original pattern produced by the artist. This is due
+to the mesh restricted diffusion process so that small local changes
+are treated without affecting the global solution. The method therefore
+is rotation invariant since it depends exclusively on the normal mesh
+field, which is rotation invariant.
 
@@
 as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
-the camel foot shows the inflation intersection that looks like two bubbles, a similar pattern to what is observed to the fingers on the bottom of the same figure.
-The silhouette enhancement is observed in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained together with its finger and leg details.
-Similar results can be obtained by a user, however it would take several steps and require the use
-of several brushes, while the curvature enhancement took a single step.
-Likewise, this new method can easily enhance organic features like muscles during the sculpting process.
-In figure \ref{fig:Performance-sculpt} the curvature enhancement brush performance is illustrated, in this experiment three models with 12K, 40K and 164K vertices, were used.
-These models were
-sculpted with the curvature enhance brush, at each step the brush sphere
-containing a variable number of vertices for processing. The processing
-time for 800 vertices in the camel paw (40k model) only took 0.1 seconds,
-for 2600 vertices in the leg and neck (model 40k) took 0.5 seconds, these
-times are suitable in real applications since an artist sculpts a model for parts,
-and each part is represented by an average of about 3000 vertices.
+the camel foot shows the inflation intersection that looks like two
+bubbles, a similar pattern to what is observed to the fingers on the
+bottom of the same figure. The silhouette enhancement is observed
+in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
+together with its finger and leg details. Similar results can be obtained
+by a user, however it would take several steps and require the use
+of several brushes, while the curvature enhancement took a single
+step. Likewise, this new method can easily enhance organic features
+like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
+the curvature enhancement brush performance is illustrated, in this
+experiment three models with 12K, 40K and 164K vertices, were used.
+These models were sculpted with the curvature enhance brush, at each
+step the brush sphere containing a variable number of vertices for
+processing. The processing time for 800 vertices in the camel paw
+(40k model) only took 0.1 seconds, for 2600 vertices in the leg and
+neck (model 40k) took 0.5 seconds, these times are suitable in real
+applications since an artist sculpts a model for parts, and each part
+is represented by an average of about 3000 vertices.
 
@@
 and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
-produce similar results if the triangles that compose the mesh are about
-the same size. The normalized version is more stable and
-predictable because it is not divided by the area of the ring which
-may be very small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c bottom row.
-The curvature enhancement of the model with the normalized Laplacian operator results in a more regular pattern.
-The model can be deformed with a TQLBO normalized
-version with large $\lambda$ ($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey} shows different
-results due to the triangle areas in the model. Triangles with
-larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
+produce similar results if the triangles that compose the mesh are
+about the same size. The normalized version is more stable and predictable
+because it is not divided by the area of the ring which may be very
+small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
+bottom row. The curvature enhancement of the model with the normalized
+Laplacian operator results in a more regular pattern. The model can
+be deformed with a TQLBO normalized version with large $\lambda$
+($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}
+shows different results due to the triangle areas in the model. Triangles
+with larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
 skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
@@
 \caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
-enhancement brush in terms of the sculpted vertices per second. Three models
-with 12K, 40K, 164K vertices used for sculpting in real time.}
+enhancement brush in terms of the sculpted vertices per second. Three
+models with 12K, 40K, 164K vertices used for sculpting in real time.}
 \end{figure}
@@
 The method was implemented as a modifier for modeling and brush for
-sculpting, on the Blender software \cite{blender} in C and C++.
-Working with the Blender allowed to test the method interactively against
+sculpting, on the Blender software \cite{blender} in C and C++. Working
+with the Blender allowed to test the method interactively against
 others, as Catmull-Clark, weight vertex groups and sculpting system
@@
 
-To improve the performance, it was worked with the Blender mesh struct, visiting
-each triangle or quad and storing its corresponding index and the sum of the Laplacian weights of the ring in a list so that only two visits were required for the list of mesh faces and two times the edge list, if the mesh was not closed.
-This drastically reduced calculations, enabling real-time
-processing. In the construction of the Laplacian matrix, several index were locked at vertices having face areas or edge lengths with null value that could cause spikes and bad results.
+To improve the performance, it was worked with the Blender mesh struct,
+visiting each triangle or quad and storing its corresponding index
+and the sum of the Laplacian weights of the ring in a list so that
+only two visits were required for the list of mesh faces and two times
+the edge list, if the mesh was not closed. This drastically reduced
+calculations, enabling real-time processing. In the construction of
+the Laplacian matrix, several index were locked at vertices having
+face areas or edge lengths with null value that could cause spikes
+and bad results.
 
-Under these conditions, the matrix at equation\ref{eq:TQLBO_Simple_Matrix}
-is sparse since the number of neighbors per vertex, corresponding to
-the number of data per row, is smaller compared to the total number of
-vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
+Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
+is sparse since the number of neighbors per vertex, corresponding
+to the number of data per row, is smaller compared to the total number
+of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
 was used OpenNL which is a a library for solving sparse linear system.
+
+The curvature cannot be calculted at the border of the meshes that
+are not closed, for that reason we use the scale-dependent operator
+proposed by
+
+Desbrun et al. \cite{Desbrun1999}.
 
@@
 for hybrid quad/triangle meshes that can be used in production environments
-and provides results similar to those obtained
-by working only with triangles or quads.
-This paper has introduced a new way to change silhouettes in a mesh for modeling or sculpting in a few steps by means of the curvature model modification while preserving its overall shape.
-In addition,  a new modeling method has also been presented some possible applications have been illustrated.
-The method works properly with isometric transformations, opening the
-possibility of introducing it on the process of animation.
+and provides results similar to those obtained by working only with
+triangles or quads. This paper has introduced a new way to change
+silhouettes in a mesh for modeling or sculpting in a few steps by
+means of the curvature model modification while preserving its overall
+shape. In addition, a new modeling method has also been presented
+some possible applications have been illustrated. The method works
+properly with isometric transformations, opening the possibility of
+introducing it on the process of animation.
 
-We show that this tool may work in early modeling stages, case in which coarse
-models are used, allowing to modify the curvature generated by the
-Catmull-Clark subdivision surfaces, and thereby avoiding edition of the vertices
-with change of a single parameters.
+We show that this tool may work in early modeling stages, case in
+which coarse models are used, allowing to modify the curvature generated
+by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
+of the vertices with change of a single parameters.
 
-Future work includes the analysis of theoretical relationships between the
-Catmull-Clark subdivision surfaces and the Laplacian smoothing since they can produce very similar results.
+Future work includes the analysis of theoretical relationships between
+the Catmull-Clark subdivision surfaces and the Laplacian smoothing
+since they can produce very similar results.
 

### 2013-01-15 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
msg

@@
 \begin{abstract}
-This paper proposes a novel modeling method for constructing a hybrid quad/triangle
-mesh by enhancing the global object curvature. This method uses an
-adapted extension of the Laplace Beltrami operator, resulting in a large variety of meshes. Along with the
-method, this work presents new applications in sculpting and
-modeling, with subdivision of surfaces and weight vertex groups. A
-series of graphics examples demonstrates the quality, predictability
-and flexibility of the method in a real production environment with
-software blender.
+This paper proposes a novel modeling method for a hybrid quad/triangle
+mesh that allows to set a family of possible shapes by controlling a single parameter, the global curvature. The method uses an
+original extension of the Laplace Beltrami operator that efficiently estimates a curvature parameter which is used to define an enhanced shape after a particular operation performed in certain mesh points.
+Along with the
+method, this work presents new applications in sculpting and modeling,
+with subdivision of surfaces and weight vertex groups. A series of
+graphics examples demonstrates the quality, predictability and flexibility
+of the method in a real production environment with software blender.
 \end{abstract}
@@
 presented method requires a single parameter that controls the global
-curvature, which is used to maintain realistic shapes, creating a family of different versions of the same
-object and therefore preserving the detail of the original model and
-a realistic appearance.
-Interest in meshes composed of triangles and quads has lately increased because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
-Nowadays, many artists use a manual connection of a couple of vertices to perform animation processes and interpolation \cite{Mullen2007}.
-It is then of paramount importance to develop operators that easily interact with such meshes, eliminating the need of preprocessing the mesh to convert it to triangles.
-The curvature enhancement and shape exaggeration can thus be used as such operator in the sculpting process, when inflating a shape since current brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
-In contrast, the presented method inflates a mesh by moving the vertices towards the reverse curvature direction, conserving the shape and sharp features of the model.
+curvature, which is used to maintain realistic shapes, creating a
+family of different versions of the same object and therefore preserving
+the detail of the original model and a realistic appearance.
+
+Interest in meshes composed of triangles and quads has lately increased
+because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
+Nowadays, many artists use a manual connection of a couple of vertices
+to perform animation processes and interpolation \cite{Mullen2007}.
+It is then of paramount importance to develop operators that easily
+interact with such meshes, eliminating the need of preprocessing the
+mesh to convert it to triangles. The curvature enhancement and shape
+exaggeration can thus be used as such operator in the sculpting process,
+when inflating a shape since current brushes end up by losing detail
+when moving vertices \cite{Stanculescu2011}. In contrast, the presented
+method inflates a mesh by moving the vertices towards the reverse
+curvature direction, conserving the shape and sharp features of the
+model.
 
@@
 
-Gai et al. \cite{Gal2009} propose automatic feature detection and shape edition
-with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys, characerized by their first
-and second order curvature derivatives \cite{Ohtake2004}, and angle-based
-threshold. Likewise, curves have been also classified as planar or
-non-planar, approximated by lines, circles, ellipses and other complex
-shapes. In such case, the user defines an initial change over several
-features which is propagated towards other features, based
-on the classified shapes and the inter-relationships between them.
-This method works well with objects that have sharp edges, composed
+Gal et al. \cite{Gal2009} propose automatic feature detection and
+shape edition with feature inter-relationship preservation. They define
+salient surface features like ridges and valleys, characerized by
+their first and second order curvature derivatives \cite{Ohtake2004},
+and angle-based threshold. Likewise, curves have been also classified
+as planar or non-planar, approximated by lines, circles, ellipses
+and other complex shapes. In such case, the user defines an initial
+change over several features which is propagated towards other features,
+based on the classified shapes and the inter-relationships between
+them. This method works well with objects that have sharp edges, composed
 of basic geometric shapes such as lines, circles or ellipses. However,
-the method is very limited when models are smooth since
-it cannot find the proper features to edit.
+the method is very limited when models are smooth since it cannot
+find the proper features to edit.
 
@@
 In grid-based sculpting, some other operations have allowed to add
-or remove voxels since production of polygonal meshes require a processing of
-isosurfaces from a volume \cite{Galyean1991}. The drawback comes from the difficulty of maintaining the surface details
-during larger scale deformations.
+or remove voxels since production of polygonal meshes require a processing
+of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
+from the difficulty of maintaining the surface details during larger
+scale deformations.
 
@@
 
-Computer objects, reconstructed from the real
-world, are usually noisy. Laplacian Smooth techniques allow a proper
-noise reduction on the mesh surface with minimal shape changes,
-while still preserving a desirable geometry as well as the original shape.
+Computer objects, reconstructed from the real world, are usually noisy.
+Laplacian Smooth techniques allow a proper noise reduction on the
+mesh surface with minimal shape changes, while still preserving a
+desirable geometry as well as the original shape.
 
-Many smoothing Laplacian functionals regularize the surface energy by controling the total surface curvature $S$.
+Many smoothing Laplacian functionals regularize the surface energy
+by controling the total surface curvature$S$.
 
@@
 in dark blue.\protect \\
- $v_{j}$ belong to the first neighborhood around $v_{i}$. $\alpha_{j}$ and $\beta_{j}$ are the
-opposite angles to the edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
+ $v_{j}$ belong to the first neighborhood around $v_{i}$. $\alpha_{j}$
+and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
 \end{figure}
 
-Consider a surface $S$, composed of a set of triangles, around the vertex
-$v_{i}$. Let us define the \textit{Voronoi region} of $v_{i}$, as
+Consider a surface $S$ composed of a set of triangles around vertex
+$v_{i}$. Let us define the \textit{Voronoi region} of $v_{i}$ as
 show in figure \ref{fig:voronoi_region}, The area change produced
-by the movement of $v_{i}$ is called the gradient of the \textit{Voronoi region
-\cite{Pinkall1993,Desbrun1999,Meyer2003}.}
+by the movement of $v_{i}$ is called the gradient of \textit{Voronoi
+region \cite{Pinkall1993,Desbrun1999,Meyer2003}.}
 
@@
 
-If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is normalized 
-by the total area of the first neighborhood around $v_{i}$, the \textit{discrete
-mean curvature normal} of a surface $S$  is obtained, as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
+If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is
+normalized by the total area of the first neighborhood around $v_{i}$,
+the \textit{discrete mean curvature normal} of a surface $S$ is obtained,
+as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
 
@@
 
-The \textit{Laplace Beltrami operator} LBO, noted as $\triangle_{g}$,
-is used for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.
+The \textit{Laplace Beltrami operator} LBO noted as $\triangle_{g}$
+is used for measuring the mean curvature normal to the Surface $S$
+\cite{Pinkall1993}.
 
@@
 The LBO has desirable properties: the LBO points out to the direction
-of the minimal surface area, minimizing the energy of the total surface curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).
+of the minimal surface area, minimizing the energy of the total surface
+curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).
 
@@
 
-The method allows edition of geometric features using the curvature
-enhancement and smoothing, generating a parameterized family of shapes
-from a set of vertices which represent a coarse sketch of the desired
-model. Our approach can be mixed with traditional or uniform subdivision
-surfaces methods, is iterative and converges towards a continuous
-and smooth version of the original model.
-
-Our method allows the use of soft constraints weighting the effect
-of smoothing at each vertex based on a normalized weight, which are
-assigned to the control vertices of the original mesh or. The weights
-of the new vertices resulting from the subdivisions are calculated
-by interpolation, allowing modifying the behavior of the method on
-specific regions of the original model.
-
-Our work presents an extension of the Laplace Beltrami operator for
-hybrid quad/triangle meshes, allows using mixed arbitrary types of
-mesh representation, exploiting the basic geometrical relationships
-facilitating and ensuring convergence of the algorithm and similar
-shapes consistent with the original shape against the other methods.
+This method exaggerates a shape using a Laplacian smoothing operator
+in the reverse direction, i.e., the new shape is a modified version
+in which those areas with larger curvature are magnified. The operator
+amounts to a generator of a set of models which conserves the basic
+silhouette of the original shape. In addition, the presented approach
+can be easily mixed with traditional or uniform subdivision of surfaces.
+This method is based on an original extension of the Laplace Beltrami
+operator for hybrid quad/triangle meshes, mixing arbitrary types of
+meshes, exploiting the basic geometrical relationships and ensuring
+algorithm convergence.
 
@@
 
-The area of $1$-ring neighborhood ($N_{1}$) with shared face quad
-or triangle to vertex $v_{i}$ in $M$ is.
+Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
+triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
+with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
+or triangle $\ensuremath{A\left(T_{N_{1}\left(v_{i}\right)}\right)}$
+to vertex $\ensuremath{v_{i}}$ in $M$ is.
 
@@
 
-Applying the mean average area according to \cite{Xiong2011} of all
-possible triangulations for each quad to $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
-as show in figure \ref{fig:quad_xiong}.
+Applying the mean average area, according to \cite{Xiong2011}, from
+all possible triangulations, as show in figure \ref{fig:quad_xiong},
+the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
+is
 
@@
 
-Thus triangles and quads configurations of the 1-ring neighborhood
-faces adjacent to $v_{i}$ can be simplified to five cases shown in
+Triangle and quad configurations of the 1-ring neighborhood faces,
+adjacent to $v_{i}$, can be simplified to five cases, as shown in
 figure \ref{fig:LBO-basic-5-TQ}.
 
-Then according to equation (\ref{eq:discrete_mean_curvature_normal}),
+According to equation (\ref{eq:discrete_mean_curvature_normal}),
 (\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
@@
 
-\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method
-from coarse model to enhancing the curvature obtained from Catmull-Clark
-Subdivision and the use of constraints over coarse model with weight
-vertex group in red.}
+\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
+from a coarse model: the curvature, obtained from the Catmull-Clark
+Subdivision, is enhanced. Soft constraints, over the coarse model,
+is drawn in red.}
 
@@
 
-The curvature enhancing uses the inverse direction of the curvature
-flow to move the vertices in the portions of the mesh with most curvature.
-In this equation we use a diffusion process:
+The curvature is enhanced by using the reverse direction of the curvature
+flow, moving the vertices towards those mesh portions with larger
+curvature. A standard diffusion process is applied:
 
@@
 
-To solve the equation above we use implicit integration and a normalized
-version of TQLBO matrix.
+To solve this equation, implicit integration is used as well as a
+normalized version of TQLBO matrix.
 
@@
 
-The vertices $V^{t+1}$are enhanced along their inverse curvature
-normal directions by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+The vertices $V^{t+1}$ are enhanced, along their reverse curvature
+direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
 $L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
@@
 vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, and $\lambda dt$ is the enhance factor that support negative
-and positive values, negative for enhancing positive for smoothing.
+group, and $\lambda dt$
 
-The curvature cannot be calculted at the border of the meshes that
-are not closed, for that reason we use the scale-dependent operator
-proposed by \cite{Desbrun1999}.
+is the enhancement factor that supports negative and positive values:
+negative for enhancement and positive for smoothing.
 
-Our method was designed for use with weighted vertex groups which
-specify the final curvature enhancement on the solution, these weights
-vary between $0$ and $1$ with a value of $0$ makes no changes and
-with values 1 applies a maximal change. The weights modify influence
-zones where the Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
-Families of shapes that are generated may change substantially with
-the weights of specific control points.
+The method was devised to use with weighted vertex groups, which specify
+the final curvature enhancement of the solution, meaning $0$ as no
+changes and 1 when a maximal change is applied. The weights modify
+the influence zones, where the Laplacian is applied, as shown in equation
+\ref{eq:Lineal_System_with_wp}. Interestingly, the generated family
+of shapes may change substantially with the weights of specific control
+points.
 
-The models volume increases as the lambda is larger and negative,
-this can be go against by a simple method of volume preservation.
-In \cite{Desbrun1999} presents a simple method to resize the mesh
-however the model suffers large displacements when $\lambda<-1.0$
-or after multiple iterations. We propose the following solution: If
+The model volume increases as the lambda is larger and negative, this
+can be counteracted with a simple volume preservation. However, the
+mesh may suffer large displacements when $\lambda<-1.0$ or after
+multiple iterations. A simple volume conservation algorithm is: If
 $v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
@@
 
-$\overline{v}$ is the center of the mesh, $vol_{ini}$ is an initial
-volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
-we define a scale factor.
+$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
+and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
+factor.
 
@@
 
-\caption{\label{fig:Catmull_Clark}Left: Original Model, in green color model
-with Catmull-Clark Subdivision. Models with Laplacian smoothing: $\lambda=60.0$,
-$\lambda_{e}=12.0$ and $\lambda=90.0$, $\lambda_{e}=80.0$. Models
-first filter with Laplacian smoothing $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applied curvature enhancing: $\lambda=-200.0$, $\lambda_{e}=12.0$
-and $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
+Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
+$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
+Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applying curvature enhancement: (e) $\lambda=-200.0$,
+$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
 \end{figure*}
 
-We designed a new brush that allows the enhancement of the curvatures
-of a polygon mesh in real time. Our brush works well with the stroke
-method named \textsl{Drag Dot}  which allows to preview the changes
-in the model before you release the mouse button or pen tablet, also
-allows to move the mouse over the model to fit exactly where you want
-to perform the enhancement of the curvature.
+A new sculpting brush is herein proposed and aims to inflate the shape,
+magnifying the shape curvatures of a polygon mesh in real time. This
+brush works properly with the stroke method \textsl{Drag Dot}, allowing
+to pre-visualize the model changes before the mouse is released. Also,
+it allows to move the mouse along the model to match the curvature
+zone which is supposed to be enhanced.
 
-Brushes that perform similar work as inflate can create distortions
-in the mesh and can also produce self-intersections in the mesh, as
-these brushes only move the vertices along the normal and do not take
-into account the global information. Whereas our method looks for
-the best way to make inflation while preserving the global curvature
-retaining the several shape and sharp features of the model.
-
-Our method simplifies the work required for the enhancement, which
-would be to use some different brushes for inflating and some other
-to soften and styling. With our enhanced brush in one step can be
-performed.
-
-For the real-time brush it necessary that the Laplacian matrix is
-constructed with the vertices that are within the radius  of the sphere
-defined by the user, which reduces the size of the matrix to be processed,
-the center of this sphere depends on the place where the user clicks
-on the canvas and three-dimensional mesh place where the click is
-projected.
-
-Furthermore special handling is required for the vertices at the boundary
-which have neighbors that are not within the radius of the brush.
-These vertices must be marked as boundary and the curvature will not
-be calculated for them, but must be present in the matrix so that
-every vertex has their neighbors within the selection, this change
-allows the results to be much smoother on the border. The Laplacian
-matrix for sculpt mode as a matrix equation.
+Brushes that perform a similar inflation can introduce mesh distortions
+or produce mesh self-intersections, provided these brushes only move
+the vertices along the normal without any global information. In contrast,
+the present method searches for a proper inflation while preserving
+the global curvature, retaining the original shape and main model
+features. In addition, this method simplifies the work required for
+the enhancement since it needs not different brushes for inflating,
+softening or styling. The enhanced brush can make all these operation
+in a single step. Real-time brushes require the Laplacian matrix is
+constructed with the vertices that are within the sphere radius defined
+by the user, reducing the matrix to be processed, the center of this
+sphere depending on the place where the user clicks on the canvas
+and the three-dimensional mesh placed where the click is projected.
+Special handling is required for the boundary vertices with neighbors
+that are not within the brush radius: these vertices are marked as
+boundary and the curvature is not there calculated, but they must
+be included in the matrix so that every vertex has their corresponding
+neighbors within the selection. The sculpting Laplacian matrix reads
+as.
 
@@
 
-Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
-of radius $r$. The matrixes should remove rows and columns of vertices
-index that are not within the radius.
+Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center of
+radius $r$. The matrices should remove rows and columns of vertices
+that are not within the radius.
 
@@
 
-The Catmull-Clark subdivision transformation is used to smooth a surface
-as the limit of a sequence of subdivision steps\cite{Stam1998}. This
-process is governed by properties of B-splines curve from multivariate
-spline theory\cite{Loop1987}. This method does a recursive subdivision
-transformation that refines the model into a linear interpolation
-that approximates a smooth surface. The smoothness of the model is
-automatically guaranteed \cite{DeRose1998}.
+The Catmull-Clark subdivision transformation is used to smooth a surface,
+as the limit of a sequence of subdivision steps \cite{Stam1998}.
+This process is governed by a B-spline curve \cite{Loop1987}, performing
+a recursive subdivision transformation that refines the model into
+a linear interpolation that approximates a smooth surface. The model
+smoothness is automatically guaranteed \cite{DeRose1998}.
 
 Catmull-Clark subdivision surface methods generate smooth and continuous
-models from a coarse model and produce results quickly due to the
-simplicity of implementation, but with these methods is not easy to
-make changes to the global curvature of the model. If we use Catmull-Clark
-subdivision surfaces and curvature enhancement for modeling from coarse
-models with few vertices can generate families of shapes changing
-a single parameter, this would allow an artist to choose the model
-from a similar set of options that best meets his/her needs without
-having to change each one of the control vertices.
+models from a coarse model and produce quick results because of the
+simplicity of implementation. Nevertheless, changes to the global
+curvature are hardly implantable. The Catmull-Clark subdivision surfaces
+together with curvature enhancement can easily generate families of
+shapes by changing a single parameter, allowing to handle a model
+with very few vertices. In practice, this would allow an artist to
+choose a model from a similar set of options that would meet his/her
+needs without having to change each of the control vertices. Likewise,
+the presented method allows the use of vertex weight paint over the
+control points. The weights can be applied to a coarse model, followed
+by a Catmull-Clark subdivision where weights are interpolated, producing
+weights with smooth changes in the influence zones, as shown in figure
+\ref{fig:Subdivision-Cups}.c.
 
-Our method allows the use of vertex weight paint over the control
-points. The weights can be applied to a coarse model, then to perform
-a Catmull-Clark subdivision where weights are interpolated, producing
-weights with smooth changes in the zones of influence, so the obtained
-curvature is much softer at those areas as shown in figure \ref{fig:Subdivision-Cups}.c.
-
-In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
+In equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
 matrix with weights corresponding to each vertex. Weights at each
-vertex produce a different solution for this reason the matrix is
-placed in the diffusion equation, as families that are generated may
-change substantially with weighted of specific control points.
+vertex produce a different solution so that the matrix must be placed
+in the diffusion equation since families that are generated may change
+substantially with weighted of specific control points.
 
@@
 
-In this section we describe the results of our curvature enhance method
-with the extension of the Laplace Beltrami operator for hybrid quad/triangle
-meshes with several example models (see figures \ref{fig:Spectrum},
-\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
-\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
-\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). We test the curvature
-enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
-GHz and 8 GB RAM.
+The results of the curvature enhancement method with the extension
+of the Laplace Beltrami operator for hybrid quad/triangle meshes with
+several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
+\ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
+\ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
+\ref{fig:Animated_Camell}). The curvature enhancement was assessed
+with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz
+and 8 GB RAM.
 
-Figure \ref{fig:TQLBO_test} show the results when applying Laplace
+Figure \ref{fig:TQLBO_test} shows the results when applying the Laplace
 Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
-in a model with a simple subdivision. In column (c) Laplacian smoothing
-was applied to the model consists of only quads. In column (d) the
-model was converted to triangles and then Laplacian smoothing was
-applied. In column (e) the model is converted randomly some quads
-into triangles and then Laplacian smoothing is applied, showing similar
-results to those composed only of triangles or squares.
+in a model with a simple subdivision. In column (c) the Laplacian
+smoothing was applied to a model consisting of only quads. In column
+(d) the model was converted to triangles and then the Laplacian smoothing
+was applied. In column (e) the model was randomly converted from some
+quads into triangles and then the Laplacian smoothing is applied,
+showing similar results to those meshes composed only of triangles
+or quads.
 
@@
 
-Methods using Catmull-Clark subdivision surface and the enhancement
+Methods using the Catmull-Clark subdivision surface and the enhancement
 allows to modify the curvature that is obtained with the process of
-subdivision as shown in figure \eqref{fig:Subdivision-Cups} this
-test used a coarse model of a cup, after the model was performed subdivision
-then was performed Laplacian smoothing and enhancement by modifying
-the parameters $\lambda$ y $\lambda_{e}$ corresponding to the lambda
-for rings and edges respectively. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use weight vertex groups
-over coarse models with subdivision surfaces that allowed to generate
-the weights for the new interpolated vertices, these new weights were
-used for the enhancement obtained the 6 cups that are to the right
-of the figure \eqref{fig:Subdivision-Cups}.d.
+subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
+test used a coarse cup model, in which the subdivision was performed,
+followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
+\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
+groups over coarse models, with subdivision surfaces that allowed
+to generate the weights for the new interpolated vertices. These new
+weights were used for the enhancement obtained on the 6 cups that
+are at the right of the figure \eqref{fig:Subdivision-Cups}.d.
 
 Laplacian smoothing applied with simple subdivision may produce similar
-results to those obtained with Catmull-Clark whose models are on average
-equal triangles as shown in figure \ref{fig:Catmull_Clark} green
-model and that obtained with Laplacian smoothing $\lambda=60.0$,
-$\lambda_{e}=12.0$, but also can modify the curvature obtained after
-applying Catmull-Clark as shown in the three columns to the right
-of the figure \ref{fig:Catmull_Clark}.
-
-Figure \ref{fig:camello_enhanced} show the generation of different
-versions of a camel according to parameter lambda. In the top row
-you can see results of do curvature enhance over all model, as the
-lambda becomes larger and negative in this model it inflates the convex
-parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
-the larger enhancements on the model features. The bottom row of figure
-\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
-which allows to specify which areas will be enhanced. On the left
-the enhancement of the legs of the camel is shown which produces enhancement
-of organic aspect, notice that the border is not distorted and smooth
-in the union.
+results to those obtained with Catmull-Clark, whose models are in
+average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
+(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
+the Laplacian smoothing is shown in panel (c), (d) and those curvature
+modified versions are in (e) and (f). As can be observed, different
+versions of the original sketch can be obtained by parameterizing
+a single model value, a great advantage of the presented method. Figure
+\ref{fig:camello_enhanced} shows the generation of different versions
+of a camel according to the $\lambda$ parameter. In the top row,
+it is shown the curvature enhancement results, as $\lambda$ becomes
+larger and negative, the resultant shape is observed as if the model
+would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
+The larger the $\lambda$ parameter the larger the model feature enhancements.
+The bottom row of figure \ref{fig:camello_enhanced} shows the use
+of weighted vertex groups, specifying which areas will be enhanced.
+On the left, the enhancement of the camel legs produces an organic
+aspect, notice that the border is not distorted and smooth.
 
@@
 \caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Curvature enhancing with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Curvature enhancing with weight vertex group, $\lambda=-50.0$
-and 2 iterations at legs, $\lambda=-200.0$ and 1 iteration in head
-and neck.}
+Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
+and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
+the head and neck.}
 \end{figure}
 
-Our method for enhancement of the silhouette features is predictable
-and invariant under isometric transformations as those present in
-some animations (see Figure \ref{fig:Animated_Camell}). This animation
-shows some poses of a camel during a walk, enhancement is performed
-in the neck and legs as shown in the bottom left part of the figure
-\ref{fig:Animated_Camell}. Local modifications produced by pose interpolation
-or animation rigging do not significantly affect the result as with
-camel legs in each sample pose different flexion of the leg joints
-enhancement camel keeps flesh-like shapes in the pattern produced
-original by the artist. This is due to the diffusion process which
-is subjected to the mesh so that small local changes are treated without
-significantly affecting global solution. Our method is invariant of
-rotation, this since depends exclusively on the normal field of the
-mesh, wish is invariant under global rotations.
+The enhancement of the silhouette features is predictable and invariant
+under isometric transformations, as those classically used in some
+animations (see Figure \ref{fig:Animated_Camell}). In this figure,
+the animation shows some camel poses during a walk, the enhancement
+is performed at the neck and legs, as shown in the bottom left camel
+in figure \ref{fig:Animated_Camell}. Local modifications produced
+by the pose interpolation or animation rigging practically do not
+affect the result. In spite of at any pose of the camel legs there
+is a clear difference, the enhancement method allows a flesh-like
+shape in the original pattern produced by the artist. This is due
+to the mesh restricted diffusion process so that small local changes
+are treated without affecting the global solution. The method therefore
+is rotation invariant since it depends exclusively on the normal mesh
+field, which is rotation invariant.
 
-Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
-brush for sculpting in real time. One pass was used with the brush
-as shown in the figure with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
-camel shows how the leg self-intersecting and looks like two bubbles
-stuck, the same happens to the fingers on the bottom of the figure.
-Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
-we get better results sd the are retained shape of the silhouette
-and the details of the fingers and leg. Similar results can be obtained
-by an artist however it would take several steps and require the use
-of several brushes. With curvature enhancement it only takes one step.
-This new method can easily enhance organic features like muscles during
-the sculpting process. In figure \ref{fig:Performance-sculpt} we
-show the performance of curvature enhancement brush, in this experiment
-we use three models with 12K, 40K and 164K vertices, this models were
-sculpted with curvature enhance brush in each step the brush sphere
-contain a variable number of vertices for processing. The processing
-time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
-for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
-times are good, because usually an artist sculpts a model for parts,
-and each part is represented by an average of about 3000 vertices
-in the models we use.
+Figure \ref{fig:Sculpt_Brush} shows the use of a curvature enhancement
+brush for sculpting in real time. One pass was used with the brush,
+as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
+the camel foot shows the inflation intersection that looks like two
+bubbles, a similar pattern to what is observed to the fingers on the
+bottom of the same figure. The silhouette enhancement is observed
+in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
+together with its finger and leg details. Similar results can be obtained
+by a user, however it would take several steps and require the use
+of several brushes, while the curvature enhancement took a single
+step. Likewise, this new method can easily enhance organic features
+like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
+the curvature enhancement brush performance is illustrated, in this
+experiment three models with 12K, 40K and 164K vertices, were used.
+These models were sculpted with the curvature enhance brush, at each
+step the brush sphere containing a variable number of vertices for
+processing. The processing time for 800 vertices in the camel paw
+(40k model) only took 0.1 seconds, for 2600 vertices in the leg and
+neck (model 40k) took 0.5 seconds, these times are suitable in real
+applications since an artist sculpts a model for parts, and each part
+is represented by an average of about 3000 vertices.
 
-Tests with the Laplacian operator equation (\ref{eq:TQLBO_Simple_Matrix})
-and its normalized version equation (\ref{eq:TQLBO-Normalized_Matrix}),
+Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
+and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
 produce similar results if the triangles that compose the mesh are
-the same size on average. The normalized version is more stable and
-predictable because it is not divided by the area of the ring which
-may be very small and cause problems during floating point calculations
-as shown in figure \ref{fig:(a)Monkey}.c bottom row. The enhancement
-of curvature of the model with the normalized Laplacian operator has
-a more regular behavior. The model can be deformed in TQLBO normalized
-version with large lambdas ($\lambda>400$) while it intersects itself
-it produces no peaks. Figure \ref{fig:(a)Monkey} shows different
-results due to the area of the triangles in the model. Triangles with
-larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
+about the same size. The normalized version is more stable and predictable
+because it is not divided by the area of the ring which may be very
+small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
+bottom row. The curvature enhancement of the model with the normalized
+Laplacian operator results in a more regular pattern. The model can
+be deformed with a TQLBO normalized version with large $\lambda$
+($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}
+shows different results due to the triangle areas in the model. Triangles
+with larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
 skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
@@
 \caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
-enhance brush in terms of vertices sculpted per second. Three models
-with 12K, 40K, 164K vertices used for sculpting in real time.}
+enhancement brush in terms of the sculpted vertices per second. Three
+models with 12K, 40K, 164K vertices used for sculpting in real time.}
 \end{figure}
@@
 
-Our method was implemented as a modifier for modeling and brush for
-sculpting on the Blender software \cite{blender} with C and C++.
-Working with Blender allowed us to test the method interactively against
-others as Catmull-Clark, weight vertex groups and sculpting system
+The method was implemented as a modifier for modeling and brush for
+sculpting, on the Blender software \cite{blender} in C and C++. Working
+with the Blender allowed to test the method interactively against
+others, as Catmull-Clark, weight vertex groups and sculpting system
 in Blender.
 
-To improve the performance, we worked with Blender mesh struct visiting
-each triangle or quad and adding its corresponding index in a list
-that stores the sum of the Laplacian weights of the ring, in this
-way we only had to visit two times the list of faces of the mesh list
-and two times the list of the edges if the mesh was not closed. The
-brush sculpting mode required to create a list that maps the index
-of the selected vertices to a list from 1 to N where N is the number
-of vertices selected and the number of rows in the linear system to
-solve. This drastically reduced the calculations enabling real-time
-processing. In the construction of our Laplacian matrix several index
-were locked at vertices having faces areas or lengths edges with value
-zero that can cause spikes and bad results.
+To improve the performance, it was worked with the Blender mesh struct,
+visiting each triangle or quad and storing its corresponding index
+and the sum of the Laplacian weights of the ring in a list so that
+only two visits were required for the list of mesh faces and two times
+the edge list, if the mesh was not closed. This drastically reduced
+calculations, enabling real-time processing. In the construction of
+the Laplacian matrix, several index were locked at vertices having
+face areas or edge lengths with null value that could cause spikes
+and bad results.
 
-Under this conditions matrix at the equation\ref{eq:TQLBO_Simple_Matrix}
-is sparse since the number of neighbors per vertex corresponding to
-the number of data per row is small compared to the total number of
-vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
+Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
+is sparse since the number of neighbors per vertex, corresponding
+to the number of data per row, is smaller compared to the total number
+of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
 was used OpenNL which is a a library for solving sparse linear system.
+
+The curvature cannot be calculted at the border of the meshes that
+are not closed, for that reason we use the scale-dependent operator
+proposed by
+
+Desbrun et al. \cite{Desbrun1999}.
 
@@
 for hybrid quad/triangle meshes that can be used in production environments
-without modification that provides results similar to those obtained
-by working only with triangles or quads.
+and provides results similar to those obtained by working only with
+triangles or quads. This paper has introduced a new way to change
+silhouettes in a mesh for modeling or sculpting in a few steps by
+means of the curvature model modification while preserving its overall
+shape. In addition, a new modeling method has also been presented
+some possible applications have been illustrated. The method works
+properly with isometric transformations, opening the possibility of
+introducing it on the process of animation.
 
-We introduced a new way to perform silhouettes enhancement in a mesh
-for modeling or sculpting in a few steps which allows the modification
-of the curvature of a model while preserving its overall shape. We
-introduce a new method of modeling and show some of its possible uses.
-This method behaves in predictable ways which facilitate the learning
-process, and works well with isometric transformations opening the
-possibility of introducing it on the process of animation.
+We show that this tool may work in early modeling stages, case in
+which coarse models are used, allowing to modify the curvature generated
+by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
+of the vertices with change of a single parameters.
 
-We show that this tool could work in the early stages in where coarse
-models are used, allowing to modify the curvature generated by the
-Catmull-Clark subdivision surfaces, avoiding the edition of the vertices
-with the change of a few parameters.
-
-As future work we analyze theoretically the relationship between the
-Catmull-Clark subdivision surfaces and Laplacian smoothing because
-in some cases can produce very similar results. But the subdivision
-surface is a fast method thereby reducing computation times for calculate
-curvature in the mesh.
+Future work includes the analysis of theoretical relationships between
+the Catmull-Clark subdivision surfaces and the Laplacian smoothing
+since they can produce very similar results.
 

### 2013-01-15 trunk/documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 % Paper title.
-\title{Curvature Enhanced Shape With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Shape Enhanced With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 
-\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive curvature enhance shapes,
-from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
-of $-5.0$.}
+\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
+$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
+$-5.0$.}
 }
@@
 This paper proposes a novel modeling method for a hybrid quad/triangle
-mesh by enhancing the global object curvature. This method uses a
-original extension of the Laplace Beltrami operator. Along with the
-method, this work presents new applications in sculpting and modeling,
+mesh that allows to set a family of possible shapes by controlling
+a single parameter, the global curvature. The method uses an original
+extension of the Laplace Beltrami operator that efficiently estimates
+a curvature parameter which is used to define an enhanced shape after
+a particular operation performed in certain mesh points. Along with
+the method, this work presents new applications in sculpting and modeling,
 with subdivision of surfaces and weight vertex groups. A series of
 graphics examples demonstrates the quality, predictability and flexibility
-of the method in a real production environment with software blender.
+of the method in a real production environment with software Blender.
 \end{abstract}
@@
 interact with such meshes, eliminating the need of preprocessing the
-mesh to convert it to triangles. The curvature enhancement and shape
-exaggeration can thus be used as such operator in the sculpting process,
-when inflating a shape since current brushes end up by losing detail
-when moving vertices \cite{Stanculescu2011}. In contrast, the presented
-method inflates a mesh by moving the vertices towards the reverse
-curvature direction, conserving the shape and sharp features of the
-model.
+mesh to convert it to triangles. The shape enhancement and shape exaggeration
+can thus be used as such brush in the sculpting process, when inflating
+a shape since current brushes end up by losing detail when moving
+vertices \cite{Stanculescu2011}. In contrast, the presented method
+inflates a mesh by moving the vertices towards the reverse curvature
+direction, conserving the shape and sharp features of the model.
 
@@
 for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
-the method for curvature enhancement and applications of subdivision
-of surfaces and sculpting; finally some Laplacian operator results,
-to hybrid quad/triangle meshes are graphically shown as well as results
-of the curvature enhancement applications in sculpting, subdivision
-and modeling.
+the method for shape enhancement and applications of subdivision of
+surfaces and sculpting; finally some Laplacian operator results, to
+hybrid quad/triangle meshes are graphically shown as well as results
+of the shape enhancement applications in sculpting, subdivision and
+modeling.
 
@@
 If the gradient in equation (\ref{eq:eq_gradient_voronoi_area}) is
-normalized by the total area of the first neighborhood around $v_{i}$,
-the \textit{discrete mean curvature normal} of a surface $S$ is obtained,
-as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
+normalized by the total area of the $1$-ring neighborhood around
+$v_{i}$, the \textit{discrete mean curvature normal} of a surface
+$S$ is obtained, as shown in equation (\ref{eq:discrete_mean_curvature_normal}).
 
@@
 Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
-triangles $T$.
-
-Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
 triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
-with shared face quad $A\left(Q_{N_{1}\left(v_{i}\right)}\right)$
-or triangle $\ensuremath{A\left(T_{N_{1}\left(v_{i}\right)}\right)}$
-to vertex $\ensuremath{v_{i}}$ in $M$ is.
+corresponds to a sum of the quad faces $A\left(Q_{v_{i}}\right)$
+and the areas of the triangular faces $\ensuremath{A\left(T_{v_{i}}\right)}$
+adjacent to vertex $\ensuremath{v_{i}}$.
 
 \begin{center}
-$A\left(v_{i}\right)=A\left(Q_{N_{1}\left(v_{i}\right)}\right)+A\left(T_{N_{1}\left(v_{i}\right)}\right)$.
+$A\left(v_{i}\right)=A\left(Q_{v_{i}}\right)+A\left(T_{v_{i}}\right)$.
 \par\end{center}
@@
 all possible triangulations, as show in figure \ref{fig:quad_xiong},
-the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
-is
+the area for each quad $\ensuremath{A\left(Q_{v_{i}}\right)}$ is
 
@@
 
-Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{N_{1}\left(v_{i}\right)}$
-and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{N_{1}\left(v_{i}\right)}$.
+Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{v_{i}}$ and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{v_{i}}$.
 
@@
 
+{\small 
 \begin{equation}
@@
 \end{equation}
+}{\small \par}
 
@@
 
-\subsection{The Curvature Enhancement\label{sub:Curvature-Enhancing}}
+\subsection{The Shape Enhancement\label{sub:Curvature-Enhancing}}
 
@@
 \caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
-from a coarse model: the curvature, obtained from the Catmull-Clark
-Subdivision, is enhanced. Soft constraints, over the coarse model,
-is drawn in red.}
+from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
+Subdivision (b), (d), is enhanced. Soft constraints, over the coarse
+model, is drawn in red and blue (c).}
 
@@
 
-The curvature is enhanced by using the reverse direction of the curvature
+The shape is enhanced by using the reverse direction of the curvature
 flow, moving the vertices towards those mesh portions with larger
@@
 The vertices $V^{t+1}$ are enhanced, along their reverse curvature
-direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
 $L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
@@
 vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, and $\lambda dt$
-
-is the enhancement factor that supports negative and positive values:
-negative for enhancement and positive for smoothing.
+group, and $\lambda dt$ is the enhancement factor that supports negative
+and positive values: negative for enhancement and positive for smoothing.
 
 The method was devised to use with weighted vertex groups, which specify
-the final curvature enhancement of the solution, meaning $0$ as no
-changes and 1 when a maximal change is applied. The weights modify
-the influence zones, where the Laplacian is applied, as shown in equation
-\ref{eq:Lineal_System_with_wp}. Interestingly, the generated family
-of shapes may change substantially with the weights of specific control
-points.
+the final shape enhancement of the solution, meaning $0$ as no changes
+and 1 when a maximal change is applied. The weights modify the influence
+zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
+Interestingly, the generated family of shapes may change substantially
+with the weights of specific control points.
+
+The curvature cannot be calculted at the boundary of the meshes that
+are not closed, for that reason we use the scale-dependent operator
+proposed by Desbrun et al. \cite{Desbrun1999}, the enhancement factor
+for boundary is represented by $\lambda_{e}$.
 
@@
 Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying curvature enhancement: (e) $\lambda=-200.0$,
-$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+and before applying shape enhancement: (e) $\lambda=-200.0$, $\lambda_{e}=12.0$
+and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
 \end{figure*}
@@
 to pre-visualize the model changes before the mouse is released. Also,
-it allows to move the mouse along the model to match the curvature
-zone which is supposed to be enhanced.
+it allows to move the mouse along the model to match the shape zone
+which is supposed to be enhanced.
 
@@
 curvature are hardly implantable. The Catmull-Clark subdivision surfaces
-together with curvature enhancement can easily generate families of
-shapes by changing a single parameter, allowing to handle a model
-with very few vertices. In practice, this would allow an artist to
-choose a model from a similar set of options that would meet his/her
-needs without having to change each of the control vertices. Likewise,
-the presented method allows the use of vertex weight paint over the
-control points. The weights can be applied to a coarse model, followed
-by a Catmull-Clark subdivision where weights are interpolated, producing
+together with shape enhancement can easily generate families of shapes
+by changing a single parameter, allowing to handle a model with very
+few vertices. In practice, this would allow an artist to choose a
+model from a similar set of options that would meet his/her needs
+without having to change each of the control vertices. Likewise, the
+presented method allows the use of vertex weight paint over the control
+points. The weights can be applied to a coarse model, followed by
+a Catmull-Clark subdivision where weights are interpolated, producing
 weights with smooth changes in the influence zones, as shown in figure
@@
 
-The results of the curvature enhancement method with the extension
-of the Laplace Beltrami operator for hybrid quad/triangle meshes with
+The results of the shape enhancement method with the extension of
+the Laplace Beltrami operator for hybrid quad/triangle meshes with
 several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
@@
 \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
-\ref{fig:Animated_Camell}). The curvature enhancement was assessed
-with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz
-and 8 GB RAM.
+\ref{fig:Animated_Camell}). The shape enhancement was assessed with
+TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
+GB RAM.
 
@@
 results to those obtained with Catmull-Clark, whose models are in
-average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
-(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
-the Laplacian smoothing is shown in panel (c), (d) and those curvature
-modified versions are in (e) and (f). As can be observed, different
-versions of the original sketch can be obtained by parameterizing
-a single model value, a great advantage of the presented method. Figure
-\ref{fig:camello_enhanced} shows the generation of different versions
-of a camel according to the $\lambda$ parameter. In the top row,
-it is shown the curvature enhancement results, as $\lambda$ becomes
-larger and negative, the resultant shape is observed as if the model
-would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
-The larger the $\lambda$ parameter the larger the model feature enhancements.
-The bottom row of figure \ref{fig:camello_enhanced} shows the use
-of weighted vertex groups, specifying which areas will be enhanced.
-On the left, the enhancement of the camel legs produces an organic
-aspect, notice that the border is not distorted and smooth.
+average equal triangles. Figure \ref{fig:Catmull_Clark}.b. shows
+Catmull-Clark subdivision , \ref{fig:Catmull_Clark}.c. shows Laplacian
+smoothing. The one obtained with the Laplacian smoothing is shown
+in panel (c), (d) and those curvature modified versions are in (e)
+and (f). As can be observed, different versions of the original sketch
+can be obtained by parameterizing a single model value, a great advantage
+of the presented method. Figure \ref{fig:camello_enhanced} shows
+the generation of different versions of a camel according to the $\lambda$
+parameter. In the top row, it is shown the shape enhancement results,
+as $\lambda$ becomes larger and negative, the resultant shape is
+observed as if the model would inflate the more convex parts, as shown
+in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
+the larger the model feature enhancements. The bottom row of figure
+\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
+specifying which areas will be enhanced. On the left, the enhancement
+of the camel legs produces an organic aspect, notice that the border
+is not distorted and smooth.
 
@@
 \caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Curvature enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Curvature enhancement with weight vertex group, $\lambda=-50.0$
+Shape enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Shape enhancement with weight vertex group, $\lambda=-50.0$
 and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
@@
 
-Figure \ref{fig:Sculpt_Brush} shows the use of a curvature enhancement
+Figure \ref{fig:Sculpt_Brush} shows the use of a shape enhancement
 brush for sculpting in real time. One pass was used with the brush,
@@
 in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
-together with its finger and leg details. Similar results can be obtained
-by a user, however it would take several steps and require the use
-of several brushes, while the curvature enhancement took a single
+together with its finger and foot details. Similar results can be
+obtained by a user, however it would take several steps and require
+the use of several brushes, while the shape enhancement took a single
 step. Likewise, this new method can easily enhance organic features
 like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
-the curvature enhancement brush performance is illustrated, in this
-experiment three models with 12K, 40K and 164K vertices, were used.
-These models were sculpted with the curvature enhance brush, at each
-step the brush sphere containing a variable number of vertices for
-processing. The processing time for 800 vertices in the camel paw
-(40k model) only took 0.1 seconds, for 2600 vertices in the leg and
-neck (model 40k) took 0.5 seconds, these times are suitable in real
-applications since an artist sculpts a model for parts, and each part
-is represented by an average of about 3000 vertices.
+the shape enhancement brush performance is illustrated, in this experiment
+three models with 12K, 40K and 164K vertices, were used. These models
+were sculpted with the shape enhance brush, at each step the brush
+sphere containing a variable number of vertices for processing. The
+processing time for 800 vertices in the camel paw (40k model) only
+took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
+took 0.5 seconds, these times are suitable in real applications since
+an artist sculpts a model for parts, and each part is represented
+by an average of about 1800 vertices.
 
@@
 small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
-bottom row. The curvature enhancement of the model with the normalized
+bottom row. The shape enhancement of the model with the normalized
 Laplacian operator results in a more regular pattern. The model can
 be deformed with a TQLBO normalized version with large $\lambda$
-($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}
+($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}.c
 shows different results due to the triangle areas in the model. Triangles
@@
 \caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Enhance curvature brush for leg into
-red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
-blue circle, (c) Curvature enhancement brush for fingers in red circle.}
+for leg into blue circle, (c) Enhance shape brush for leg into red
+circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
+circle, (c) Shape enhancement brush for fingers in red circle.}
 \end{figure}
@@
 
-\caption{\label{fig:Performance-sculpt}Performance of our dynamic curvature
-enhancement brush in terms of the sculpted vertices per second. Three
-models with 12K, 40K, 164K vertices used for sculpting in real time.}
+\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape enhancement
+brush in terms of the sculpted vertices per second. Three models with
+12K, 40K, 164K vertices used for sculpting in real time.}
 \end{figure}
@@
 for the different poses are similar in terms of shape. Top row: Original
-walk cycle camel model. Bottom row: Curvature enhancement with weight
+walk cycle camel model. Bottom row: Shape enhancement with weight
 vertex group, $\lambda=-400$ and $2$ iterations. }
@@
 
-The curvature cannot be calculted at the border of the meshes that
-are not closed, for that reason we use the scale-dependent operator
-proposed by
-
-Desbrun et al. \cite{Desbrun1999}.
-
 \section{Conclusion and future work\label{sec:Conclusion-and-future}}
@@
 We show that this tool may work in early modeling stages, case in
-which coarse models are used, allowing to modify the curvature generated
+which coarse models are used, allowing to modify the shape generated
 by the Catmull-Clark subdivision surfaces, and thereby avoiding edition

### 2013-01-15 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

@@
 This paper proposes a novel modeling method for a hybrid quad/triangle
-mesh that allows to set a family of possible shapes by controlling a single parameter, the global curvature. The method uses an
-original extension of the Laplace Beltrami operator that efficiently estimates a curvature parameter which is used to define an enhanced shape after a particular operation performed in certain mesh points.
-Along with the
-method, this work presents new applications in sculpting and modeling,
+mesh that allows to set a family of possible shapes by controlling
+a single parameter, the global curvature. The method uses an original
+extension of the Laplace Beltrami operator that efficiently estimates
+a curvature parameter which is used to define an enhanced shape after
+a particular operation performed in certain mesh points. Along with
+the method, this work presents new applications in sculpting and modeling,
 with subdivision of surfaces and weight vertex groups. A series of
 graphics examples demonstrates the quality, predictability and flexibility
-of the method in a real production environment with software blender.
+of the method in a real production environment with software Blender.
 \end{abstract}
@@
 using them for different processes such as free-form deformation,
-fusion, morphing and other application\cite{Sorkine2004}.
+fusion, morphing and other applications \cite{Sorkine2004}.
 
@@
 
-Gal et al. \cite{Gal2009} propose automatic feature detection and
-shape edition with feature inter-relationship preservation. They define
-salient surface features like ridges and valleys, characerized by
-their first and second order curvature derivatives \cite{Ohtake2004},
-and angle-based threshold. Likewise, curves have been also classified
-as planar or non-planar, approximated by lines, circles, ellipses
-and other complex shapes. In such case, the user defines an initial
-change over several features which is propagated towards other features,
-based on the classified shapes and the inter-relationships between
-them. This method works well with objects that have sharp edges, composed
-of basic geometric shapes such as lines, circles or ellipses. However,
-the method is very limited when models are smooth since it cannot
-find the proper features to edit.
+\cite{Gal2009} propose automatic feature detection and shape edition
+with feature inter-relationship preservation. They define salient
+surface features like ridges and valleys, characerized by their first
+and second order curvature derivatives \cite{Ohtake2004}, and angle-based
+threshold. Likewise, curves have been also classified as planar or
+non-planar, approximated by lines, circles, ellipses and other complex
+shapes. In such case, the user defines an initial change over several
+features which is propagated towards other features, based on the
+classified shapes and the inter-relationships between them. This method
+works well with objects that have sharp edges, composed of basic geometric
+shapes such as lines, circles or ellipses. However, the method is
+very limited when models are smooth since it cannot find the proper
+features to edit.
 
@@
 Many smoothing Laplacian functionals regularize the surface energy
-by controling the total surface curvature$S$.
+by controling the total surface curvature $S$.
 
@@
 all possible triangulations, as show in figure \ref{fig:quad_xiong},
-the area for each quad $\ensuremath{A\left(Q_{N_{1}\left(v_{i}\right)}\right)}$
-is
+the area for quads $\ensuremath{A\left(Q_{v_{i}}\right)}$ and triangles
+$A\left(T_{v_{i}}\right)$ is.
 
@@
 
-allows to move the new vertices to:
+allows to scale the vertices to:
 
@@
 \caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
-Subdivision. Models with Laplacian smoothing: (c) $\lambda=60.0$,
-$\lambda_{e}=12.0$ and (d) $\lambda=90.0$, $\lambda_{e}=80.0$.
-Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying curvature enhancement: (e) $\lambda=-200.0$,
-$\lambda_{e}=12.0$ and (f) $\lambda=-40.0$, $\lambda_{e}=-100.0$.}
+Subdivision. Models with Laplacian smoothing: (c) and (d). Models
+with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applying shape enhancement: (e) and (f).}
 \end{figure*}
@@
 
-Laplacian smoothing applied with simple subdivision may produce similar
-results to those obtained with Catmull-Clark, whose models are in
-average equal triangles, as shown in figure \ref{fig:Catmull_Clark},
-(b) Catmull-Clark, (c) Laplacian smoothing. The one obtained with
-the Laplacian smoothing is shown in panel (c), (d) and those curvature
-modified versions are in (e) and (f). As can be observed, different
-versions of the original sketch can be obtained by parameterizing
-a single model value, a great advantage of the presented method. Figure
-\ref{fig:camello_enhanced} shows the generation of different versions
-of a camel according to the $\lambda$ parameter. In the top row,
-it is shown the curvature enhancement results, as $\lambda$ becomes
-larger and negative, the resultant shape is observed as if the model
-would inflate the more convex parts, as shown in figure \ref{fig:Spectrum}.
-The larger the $\lambda$ parameter the larger the model feature enhancements.
-The bottom row of figure \ref{fig:camello_enhanced} shows the use
-of weighted vertex groups, specifying which areas will be enhanced.
-On the left, the enhancement of the camel legs produces an organic
-aspect, notice that the border is not distorted and smooth.
+Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
+may produce similar results to those obtained with Catmull-Clark (see
+figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
+triangles. The one obtained with the Laplacian smoothing is shown
+in panel (c), (d) and those curvature modified versions are in (e)
+and (f). As can be observed, different versions of the original sketch
+can be obtained by parameterizing a single model value, a great advantage
+of the presented method. Figure \ref{fig:camello_enhanced} shows
+the generation of different versions of a camel according to the $\lambda$
+parameter. In the top row, it is shown the shape enhancement results,
+as $\lambda$ becomes larger and negative, the resultant shape is
+observed as if the model would inflate the more convex parts, as shown
+in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
+the larger the model feature enhancements. The bottom row of figure
+\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
+specifying which areas will be enhanced. On the left, the enhancement
+of the camel legs produces an organic aspect, notice that the border
+is not distorted and smooth.
 
@@
 and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
-produce similar results if the triangles that compose the mesh are
-about the same size. The normalized version is more stable and predictable
-because it is not divided by the area of the ring which may be very
-small and causes numeric problems, as shown in figure \ref{fig:(a)Monkey}.c
-bottom row. The curvature enhancement of the model with the normalized
-Laplacian operator results in a more regular pattern. The model can
-be deformed with a TQLBO normalized version with large $\lambda$
-($\lambda>400$) while intersecting itself with no peaks. Figure \ref{fig:(a)Monkey}
-shows different results due to the triangle areas in the model. Triangles
-with larger area have smaller enhancement (figure \ref{fig:(a)Monkey}.c
-skull), and smaller triangles have larger enhancements (figure \ref{fig:(a)Monkey}.c
-chin).
+produce similar results if the triangles or quads that compose the
+mesh are about the same size. The normalized version is more stable
+and predictable because it is not divided by the area of the ring
+which may be very small and causes numeric problems, as shown in figure
+\ref{fig:(a)Monkey}.c bottom row. The shape enhancement of the model
+with the normalized Laplacian operator results in a more regular pattern.
+The model can be deformed with a TQLBO normalized version with large
+$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
+Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
+areas in the model. Quadss with larger area have smaller enhancement
+(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
+enhancements (figure \ref{fig:(a)Monkey}.c chin).
 
@@
 
-\caption{\label{fig:(a)Monkey}(a) Top row: Original model scaled by 4. Bottom
-row: Original Model (b) Top and bottom row: enhancing with Normalized-TQLBO
+\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
+model scaled by 4. (b) Top and bottom row: enhancing with Normalized-TQLBO
 $\lambda=-50$ (c) Top and bottom row: enhancing with TQLBO $\lambda=-50$.}
@@
 the Laplacian matrix, several index were locked at vertices having
-face areas or edge lengths with null value that could cause spikes
+face areas or edge lengths with zero value that could cause spikes
 and bad results.
@@
 was used OpenNL which is a a library for solving sparse linear system.
-
-The curvature cannot be calculted at the border of the meshes that
-are not closed, for that reason we use the scale-dependent operator
-proposed by
-
-Desbrun et al. \cite{Desbrun1999}.
 

### 2013-04-26 documents/thesis/SIBGRAPI2013/TQLBO.tex

--- 2013-01-15 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex
@@
-%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
-%% Do not edit unless you really know what you are doing.
-\documentclass[english,review]{acmsiggraph}
-\usepackage[T1]{fontenc}
-\usepackage[latin9]{inputenc}
+\documentclass[10pt, conference]{IEEEtran}
+\usepackage{subimages}
+\setfigdir{figs}
+\usepackage[cmex10]{amsmath}
+\interdisplaylinepenalty=2500
+\usepackage{amsthm}
 \usepackage{amssymb}
 \usepackage{graphicx}
+\newtheorem{definition}{Definition}
+%\usepackage{hyperref}
 
-\makeatletter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-% for the following cases use the listed document class option:
-% [annual] - Technical paper accepted for presentation at the ACM SIGGRAPH 
-%   or SIGGRAPH Asia annual conference.
-% [sponsored] - Short or full-length technical paper accepted for 
-%   presentation at an event sponsored by ACM SIGGRAPH
-%   (but not the annual conference Technical Papers program).
-% [abstract] - A one-page abstract of your accepted content
-%   (Technical Sketches, Posters, Emerging Technologies, etc.). 
-%   Content greater than one page in length should use the "[sponsored]"
-%   parameter.
-% [preprint] - A preprint version of your final content.
-% [review] - A technical paper submitted for review. Includes line
-%   numbers and anonymization of author and affiliation information.
+\hyphenation{op-tical net-works semi-conduc-tor}
 
-% When you submit your paper for review, please use the \TOGonlineID''
-% command to include the online ID value assigned to your paper by the
-% submission management system. Replace '45678' with the value you were
-% assigned.
-\TOGonlineid{XXXXX}
+\begin{document}
+\title{Shape Inflation With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
-% If you are preparing a preprint of your accepted paper, and your paper
-% will be published in an issue of the ACM "Transactions on Graphics''
-% journal, replace the "0'' values in the commands below with the correct
-% volume and number values for that issue - you'll get them before your
-% final paper is due.
-\TOGvolume{0}
-\TOGnumber{0}
+%------------------------------------------------------------------------- 
+% change the % on next lines to produce the final camera-ready version 
+\newif\iffinal
+%\finalfalse
+\finaltrue
+\newcommand{\jemsid}{99999}
+%-------------------------------------------------------------------------
 
-% The TOGarticleDOI' command accepts the DOI information provided to you
-% during production, and which makes up the URLs which identifies the ACM
-% article page and direct PDF link in the ACM Digital Library.
-% Replace "1111111.2222222'' with the values you are given.
-\TOGarticleDOI{1111111.2222222}
+\iffinal
+  \author{%
+    \IEEEauthorblockN{Alexander Pinzon, Eduardo Romero}
+    \IEEEauthorblockA{%
+      Cimalab Research Group\\
+      Universidad Nacional de Colombia\\
+      Bogota-Colombia\\
+      %Email: \href{mailto:apinzonf@unal.edu.co}{apinzonf@unal.edu.co}, \href{mailto:edromero@unal.edu.co}{edromero@unal.edu.co}
+      Email: apinzonf@unal.edu.co, edromero@unal.edu.co }
+  }
+\else
+  \author{Sibgrapi paper ID: \jemsid \\ }
+\fi
 
-% If you would like to include links to personal repositories for auxiliary
-% material related your research contribution, you may use one or more of
-% these commands to define an appropriate URL. The "\TOGlinkslist'' command
-% found just before the first section of your document will add hyperlinked
-% icons to your document, in addition to hyperlinked icons which point to
-% the ACM Digital Library article page and the ACM Digital Library-held PDF.
-\TOGprojectURL{}
-\TOGvideoURL{}
-\TOGdataURL{}
-\TOGcodeURL{}
-
-% Paper title.
-\title{Shape Enhanced With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
-
-% Author and Affiliation (single author).
-%\author{Name \thanks{e-mail: name@unknown.uu}\\ Research Institute}
-
-% Author and Affiliation (multiple authors).
-\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
-\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
- \\Cimalab Research Group\\National University of Colombia}
-%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}
-
-% The ``pdfauthor'' command accepts the authors of the work,
-% comma-delimited, and adds this information to the PDF metadata.
-%\pdfauthor{Alexander Pinzon, Eduardo Romero, Ton Roosendaal}
-\pdfauthor{Anonymous}
-
-% Keywords that describe your work.
-\keywords{laplacian smooth, curvature, sculpting, subdivision surface}
-
-\makeatother
-
-\usepackage{babel}
-\begin{document}
-
-\teaser{\includegraphics[width=1\textwidth]{images/spectrum} \caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
+\teaser{%
+  \oneimage{\label{fig:Spectrum} A set of 48 successive shapes enhanced, from
 $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
-$-5.0$.}
+$-5.0$.}{.99}{spectrum}
 }
@@
 \maketitle
-\maketitle 
+
 \begin{abstract}
@@
 extension of the Laplace Beltrami operator that efficiently estimates
-a curvature parameter which is used to define an enhanced shape after
+a curvature parameter which is used to define an inflated shape after
 a particular operation performed in certain mesh points. Along with
@@
 of the method in a real production environment with software Blender.
+
 \end{abstract}
 
-\begin{CRcatlist}
-\CRcat{I.3.5}{Computer Graphics}{Computational Geometry and Object Modeling
-}{Modeling packages}
-\end{CRcatlist}
-\keywordlist
+\begin{IEEEkeywords}
+laplacian smooth; curvature; sculpting; subdivision surface
 
-\TOGlinkslist
+\end{IEEEkeywords}
 
-%\copyrightspace
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-
+%
 Over the last years several, modeling techniques able to generate
@@
 
-\textbf{Contributions} This work presents an extension of the Laplace
+%------------------------------------------------------------------------- 
+\paragraph*{Contributions}
+%
+This work presents an extension of the Laplace
 Beltrami operator for hybrid quad/triangle meshes, representing a
@@
 
-\section{Related work\label{sub:1.1-Related-work}}
-
+%------------------------------------------------------------------------- 
+\subsection{Related work\label{sub:1.1-Related-work}}
+%
 Many tools have been developed for modeling, based on the Laplacian
@@
 
+%==========================================
 \section{Laplacian Smooth\label{sec:Laplacian-Smooth}}
-
+%
 \begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/beltrami}
+\includegraphics[width=1\textwidth]{figs/beltrami}
 
@@
 \begin{figure}[h]
-\includegraphics[width=1\columnwidth]{images/voronoi_region}
+\includegraphics[width=1\columnwidth]{figs/voronoi_region}
 
@@
 \begin{figure}[h]
-\includegraphics[width=1\columnwidth]{images/quad_xiong}
+\includegraphics[width=1\columnwidth]{figs/quad_xiong}
 
@@
 \begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/teaser_cup}
+\includegraphics[width=1\textwidth]{figs/teaser_cup}
 
@@
 \begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/cruz_lambda4}
+\includegraphics[width=1\textwidth]{figs/cruz_lambda4}
 
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/test_triangles_quads}
+\includegraphics[width=1\columnwidth]{figs/test_triangles_quads}
 
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/camello_enhanced2}
+\includegraphics[width=1\columnwidth]{figs/camello_enhanced2}
 
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/sculpt_brush}
+\includegraphics[width=1\columnwidth]{figs/sculpt_brush}
 
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/verts_per_second_sculpt}
+\includegraphics[width=1\columnwidth]{figs/verts_per_second_sculpt}
 
@@
 \begin{figure}
-\includegraphics[width=1\columnwidth]{images/monkey}
+\includegraphics[width=1\columnwidth]{figs/monkey}
 
@@
 \begin{figure*}[t]
-\includegraphics[width=1\textwidth]{images/camello_walk2}
+\includegraphics[width=1\textwidth]{figs/camello_walk2}
 
@@
 
-\section*{Acknowledgments}
-
+%==========================================
+\iffinal
+% use section* for acknowledgement
+\section*{Acknowledgment}
+%
 We wold like to thank  anonymous friends for their support of our
@@
 are under public domain, courtesy of Blender Foundation.
+\fi
 
-\bibliographystyle{acmsiggraph/acmsiggraph}
+%==========================================
+
+\bibliographystyle{IEEEtran}
 \bibliography{template}
@@
 \end{document}
+
+%==========================================

### 2013-04-26 documents/thesis/SIBGRAPI2013/TQLBO.tex

@@
 \newif\iffinal
-%\finalfalse
-\finaltrue
+\finalfalse
+%\finaltrue
 \newcommand{\jemsid}{99999}
@@
 interact with such meshes, eliminating the need of preprocessing the
-mesh to convert it to triangles. The shape enhancement and shape exaggeration
+mesh to convert it to triangles. The shape inflation and shape exaggeration
 can thus be used as such brush in the sculpting process, when inflating
@@
 and curvature, obtained during the subdivision surfaces process. Finally,
-it is proposed a new brush for enhancing the silhouette mesh features
+it is proposed a new brush for inflating the silhouette mesh features
 in modeling and sculpting.
@@
 for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
-the method for shape enhancement and applications of subdivision of
+the method for shape inflation and applications of subdivision of
 surfaces and sculpting; finally some Laplacian operator results, to
 hybrid quad/triangle meshes are graphically shown as well as results
-of the shape enhancement applications in sculpting, subdivision and
+of the shape inflation applications in sculpting, subdivision and
 modeling.
@@
 by the Laplace Beltrami operator, have been developed. These methods
-adjust the shape offset by a constant distance, with enough precision
-as to minimize the Hausdorff error. Nevertheless, these methods fail
+adjust the shape offset by a constant distance, with enough precision. Nevertheless, these methods fail
 to conserve sufficient detail because of the smoothing, a crucial
@@
 surface features like ridges and valleys, characerized by their first
-and second order curvature derivatives \cite{Ohtake2004}, and angle-based
+and second order curvature derivatives, see \cite{Ohtake2004}, and angle-based
 threshold. Likewise, curves have been also classified as planar or
@@
 
-The \textit{Laplace Beltrami operator} LBO noted as $\triangle_{g}$
+The \textit{Laplace Beltrami operator} LBO noted as $\triangle$
 is used for measuring the mean curvature normal to the Surface $S$
@@
 \begin{equation}
-\triangle_{g}S=2\kappa\mathbf{n}\label{eq:def_LBO}
+%\triangle_{g}S=2\kappa\mathbf{n}\label{eq:def_LBO}
+\triangle S=2\kappa\mathbf{n}\label{eq:def_LBO}
 \end{equation}
@@
 The LBO has desirable properties: the LBO points out to the direction
-of the minimal surface area, minimizing the energy of the total surface
-curvature $S$ at equation (\ref{eq:total_cuarvature_integral}).
+of the minimal surface area.
 
@@
 \begin{equation}
-\triangle_{g}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
+\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
 \end{equation}
@@
 
-\subsection{The Shape Enhancement\label{sub:Curvature-Enhancing}}
+\subsection{The Shape Inflation\label{sub:Curvature-Enhancing}}
 
@@
 from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
-Subdivision (b), (d), is enhanced. Soft constraints, over the coarse
+Subdivision (b), (d), is inflated. Soft constraints, over the coarse
 model, is drawn in red and blue (c).}
@@
 
-The shape is enhanced by using the reverse direction of the curvature
+The shape is inflated by using the reverse direction of the curvature
 flow, moving the vertices towards those mesh portions with larger
@@
 
-The vertices $V^{t+1}$ are enhanced, along their reverse curvature
+The vertices $V^{t+1}$ are inflated, along their reverse curvature
 direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
@@
 $x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
-vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
-group, and $\lambda dt$ is the enhancement factor that supports negative
-and positive values: negative for enhancement and positive for smoothing.
+vertices positions, $W_{p}$ is a diagonal matrix with vertex weights,
+ and $\lambda dt$ is the inflate factor that supports negative
+and positive values: negative for inflation and positive for smoothing.
 
 The method was devised to use with weighted vertex groups, which specify
-the final shape enhancement of the solution, meaning $0$ as no changes
+the final shape inflation of the solution, meaning $0$ as no changes
 and 1 when a maximal change is applied. The weights modify the influence
@@
 are not closed, for that reason we use the scale-dependent operator
-proposed by Desbrun et al. \cite{Desbrun1999}, the enhancement factor
+proposed by Desbrun et al. \cite{Desbrun1999}, the inflation factor
 for boundary is represented by $\lambda_{e}$.
@@
 
+The shape inflation use a negative curvature flow that is an unstable process 
+when performing many iterations, however, our method uses less than 3 
+iterations to get good results, and with 3 iterations or less the method behaves stable.
+
 \subsection{Sculpting\label{sub:Sculpting}}
@@
 with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying shape enhancement: (e) and (f).}
+and before applying shape inflation: (e) and (f).}
 \end{figure*}
@@
 it allows to move the mouse along the model to match the shape zone
-which is supposed to be enhanced.
+which is supposed to be inflated.
 
@@
 features. In addition, this method simplifies the work required for
-the enhancement since it needs not different brushes for inflating,
-softening or styling. The enhanced brush can make all these operation
+the inflation since it needs not different brushes for inflating,
+softening or styling. The inflated brush can make all these operation
 in a single step. Real-time brushes require the Laplacian matrix is
@@
 curvature are hardly implantable. The Catmull-Clark subdivision surfaces
-together with shape enhancement can easily generate families of shapes
+together with shape inflation can easily generate families of shapes
 by changing a single parameter, allowing to handle a model with very
@@
 
-The results of the shape enhancement method with the extension of
+The results of the shape inflation method with the extension of
 the Laplace Beltrami operator for hybrid quad/triangle meshes with
@@
 \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
-\ref{fig:Animated_Camell}). The shape enhancement was assessed with
+\ref{fig:Animated_Camell}). The shape inflation was assessed with
 TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
@@
 
-Methods using the Catmull-Clark subdivision surface and the enhancement
+Methods using the Catmull-Clark subdivision surface and the inflation
 allows to modify the curvature that is obtained with the process of
@@
 test used a coarse cup model, in which the subdivision was performed,
-followed by a Laplacian smoothing and enhancement. In figure \eqref{fig:Subdivision-Cups}.c,
+followed by a Laplacian smoothing and inflation. In figure \eqref{fig:Subdivision-Cups}.c,
 \eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
@@
 to generate the weights for the new interpolated vertices. These new
-weights were used for the enhancement obtained on the 6 cups that
+weights were used for the inflation obtained on the 6 cups that
 are at the right of the figure \eqref{fig:Subdivision-Cups}.d.
@@
 the generation of different versions of a camel according to the $\lambda$
-parameter. In the top row, it is shown the shape enhancement results,
+parameter. In the top row, it is shown the shape inflation results,
 as $\lambda$ becomes larger and negative, the resultant shape is
@@
 in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
-the larger the model feature enhancements. The bottom row of figure
+the larger the model feature inflations. The bottom row of figure
 \ref{fig:camello_enhanced} shows the use of weighted vertex groups,
-specifying which areas will be enhanced. On the left, the enhancement
+specifying which areas will be inflated. On the left, the inflation
 of the camel legs produces an organic aspect, notice that the border
@@
 \caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Shape enhancement with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Shape enhancement with weight vertex group, $\lambda=-50.0$
+Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+Bottom row: Shape inflation with weight vertex group, $\lambda=-50.0$
 and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
@@
 
-The enhancement of the silhouette features is predictable and invariant
+The inflation of the silhouette features is predictable and invariant
 under isometric transformations, as those classically used in some
 animations (see Figure \ref{fig:Animated_Camell}). In this figure,
-the animation shows some camel poses during a walk, the enhancement
+the animation shows some camel poses during a walk, the inflation
 is performed at the neck and legs, as shown in the bottom left camel
@@
 affect the result. In spite of at any pose of the camel legs there
-is a clear difference, the enhancement method allows a flesh-like
+is a clear difference, the inflation method allows a flesh-like
 shape in the original pattern produced by the artist. This is due
@@
 
-Figure \ref{fig:Sculpt_Brush} shows the use of a shape enhancement
+Figure \ref{fig:Sculpt_Brush} shows the use of a shape inflation
 brush for sculpting in real time. One pass was used with the brush,
@@
 bubbles, a similar pattern to what is observed to the fingers on the
-bottom of the same figure. The silhouette enhancement is observed
+bottom of the same figure. The silhouette inflation is observed
 in figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
@@
 obtained by a user, however it would take several steps and require
-the use of several brushes, while the shape enhancement took a single
-step. Likewise, this new method can easily enhance organic features
+the use of several brushes, while the shape inflation took a single
+step. Likewise, this new method can easily inflate organic features
 like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
-the shape enhancement brush performance is illustrated, in this experiment
+the shape inflation brush performance is illustrated, in this experiment
 three models with 12K, 40K and 164K vertices, were used. These models
-were sculpted with the shape enhance brush, at each step the brush
+were sculpted with the shape inflate brush, at each step the brush
 sphere containing a variable number of vertices for processing. The
@@
 took 0.5 seconds, these times are suitable in real applications since
-an artist sculpts a model for parts, and each part is represented
-by an average of about 1800 vertices.
+an artist sculpts a model for parts.
+%, and each part is represented by an average of about 1800 vertices.
 
@@
 which may be very small and causes numeric problems, as shown in figure
-\ref{fig:(a)Monkey}.c bottom row. The shape enhancement of the model
+\ref{fig:(a)Monkey}.c bottom row. The shape inflation of the model
 with the normalized Laplacian operator results in a more regular pattern.
@@
 Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
-areas in the model. Quadss with larger area have smaller enhancement
+areas in the model. Quadss with larger area have smaller inflation
 (figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
-enhancements (figure \ref{fig:(a)Monkey}.c chin).
+inflations (figure \ref{fig:(a)Monkey}.c chin).
 
@@
 \caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Enhance shape brush for leg into red
+for leg into blue circle, (c) Inflate shape brush for leg into red
 circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
-circle, (c) Shape enhancement brush for fingers in red circle.}
+circle, (c) Shape inflation brush for fingers in red circle.}
 \end{figure}
@@
 
-\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape enhancement
+\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape inflation
 brush in terms of the sculpted vertices per second. Three models with
@@
 \caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
-model scaled by 4. (b) Top and bottom row: enhancing with Normalized-TQLBO
-$\lambda=-50$ (c) Top and bottom row: enhancing with TQLBO $\lambda=-50$.}
+model scaled by 4. (b) Top and bottom row: inflating with Normalized-TQLBO
+$\lambda=-50$ (c) Top and bottom row: inflating with TQLBO $\lambda=-50$.}
 \end{figure}
@@
 
-\caption{\label{fig:Animated_Camell}The method is pose insensitive. The enhancement
+\caption{\label{fig:Animated_Camell}The method is pose insensitive. The inflation
 for the different poses are similar in terms of shape. Top row: Original
-walk cycle camel model. Bottom row: Shape enhancement with weight
+walk cycle camel model. Bottom row: Shape inflation with weight
 vertex group, $\lambda=-400$ and $2$ iterations. }

### 2013-05-21 trunk/software/laplace_operator/skeletonizer.m

@@ -1,0 +1,150 @@
+function  [M, F]  = skeletonizer( iter );
+
+addpath('E:\personal\maestria\tesis\Jeronimo\trunk\software\Laplacian_test');
+addpath('E:\personal\maestria\tesis\Jeronimo\trunk\software\Laplacian_test\toolbox_graph');
+addpath('E:\personal\maestria\tesis\Jeronimo\trunk\software\Laplacian_test\toolbox_graph\toolbox');
+
+
+[FileName,PathName,FilterIndex] = uigetfile('*.off','Select the off-file');
+%UNTITLED Summary of this function goes here
+%   Detailed explanation goes here
+
+[V, F] = read_off(strcat(PathName, FileName));
+
+options.name = 'skeleton'; % useful for displaying
+options.symmetrize = 1;
+options.normalize = 0;
+L =  compute_mesh_laplacian(V,F,'conformal',options);
+
+nv = length(V);
+nf = length(F);
+
+A0 = zeros(1,nf);
+
+for i=1:nf 
+   A0(i) = arealf(F, V, i);
+end
+A_avg_0 = mean(A0);
+
+At_0 = arearing(F,V);
+
+%WL = sqrt(A_avg_0) / 1000;
+WL = 10;
+SL = 2;
+WH = speye(nv);
+
+M_A = [WL*L; WH];
+%M_A = [speye(nv, nv) + 0.2*L; WH];
+whv = WH*V';
+M_B = [zeros(nv, 3);  whv];
+%M_B = [V  whv'];
+
+tol = 1.e-6;
+maxit = 1000;
+[smbx, smby] = size(M_B);
+fprintf(1, 'size %d, %d\n', smbx, smby);
+[smbx, smby] = size(M_B(1,:)');
+fprintf(1, 'size %d, %d', smbx, smby);
+
+
+M_XYZ = (M_A'*M_A)\(M_A'*M_B); 
+%[Lu_0,U_0,P_0] = lu(M_A);
+%M_XYZ = U_0\(Lu_0\M_B);
+%(A'*A)\(A'*B);
+%U = cgs(L, C', tol, maxit);
+%U = linsolve(L, C');
+
+
+%M_XYZ(1,:) = lsqr(M_A, M_B(1,:)', tol, maxit);
+%M_XYZ(2,:) = lsqr(M_A, M_B(2,:)', tol, maxit);
+%M_XYZ(3,:) = lsqr(M_A, M_B(3,:)', tol, maxit);
+
[…]

### 2013-05-21 software/laplace_operator/toolbox_graph/compute_mesh_weight.m

@@ -1,0 +1,106 @@
+function W = compute_mesh_weight(vertex,face,type,options)
+
+% compute_mesh_weight - compute a weight matrix
+%
+%   W = compute_mesh_weight(vertex,face,type,options);
+%
+%   W is sparse weight matrix and W(i,j)=0 is vertex i and vertex j are not
+%   connected in the mesh.
+%
+%   type is either 
+%       'combinatorial': W(i,j)=1 is vertex i is conntected to vertex j.
+%       'distance': W(i,j) = 1/d_ij^2 where d_ij is distance between vertex
+%           i and j.
+%       'conformal': W(i,j) = cot(alpha_ij)+cot(beta_ij) where alpha_ij and
+%           beta_ij are the adjacent angle to edge (i,j)
+%
+%   If options.normalize=1, the the rows of W are normalize to sum to 1.
+%
+%   Copyright (c) 2007 Gabriel Peyre
+
+options.null = 0;
+[vertex,face] = check_face_vertex(vertex,face);
+
+nface = size(face,1);
+n = max(max(face));
+
+verb = getoptions(options, 'verb', n>5000);
+
+if nargin<3
+    type = 'conformal';
+end
+
+switch lower(type)
+    case 'combinatorial'
+        W = triangulation2adjacency(face);
+    case 'distance'
+        W = my_euclidean_distance(triangulation2adjacency(face),vertex);
+        W(W>0) = 1./W(W>0);
+        W = (W+W')/2; 
+    case 'conformal'
+        % conformal laplacian
+        W = sparse(n,n);
+        ring = compute_vertex_face_ring(face);
+        for i = 1:n
+            if verb
+                progressbar(i,n);
+            end
+            for b = ring{i}
+                % b is a face adjacent to a
+                bf = face(:,b);
+                % compute complementary vertices
+                if bf(1)==i
+                    v = bf(2:3);
+                elseif bf(2)==i
+                    v = bf([1 3]);
+                elseif bf(3)==i
+                    v = bf(1:2);
+                else
+                    error('Problem in face ring.');
+                end
+                j = v(1); k = v(2);
+                vi = vertex(:,i);
+                vj = vertex(:,j);
+                vk = vertex(:,k);
+                % angles
[…]

### 2013-05-21 software/sjSkeletonizer/source/plugin/sjMeshContractionAu2008.cpp

@@ -127,12 +127,15 @@ bool IterateLaplacianSmoothingSeparate::evolve(sjStateContext * ssc){
 	LinearSolver *solver;
 	SystemSolverParameters params ;
 	std::string  * mipo = new std::string("SUPERLU");
+	//std::string  * mipo = new std::string("ACE");
+	
 	params.set_arg_value("method", *mipo) ; 
 		
 	solver = new LinearSolver(n) ;
 	solver->set_system_solver(params) ;
 	solver->set_least_squares(true) ;
 	solver->set_invert_matrix(true) ;
+	solver->set_symmetric(true);
 
 	cout<<"\nIterate system: No = "<<this->m_context->iteration+1<<"|\t";
 	cout<<"Volume Ini= "<<calcVolume(STATE_MESH)<<"|\t";

### 2013-05-21 documents/thesis/SIPAIM2010/FASIPAIM2010.tex

%% LyX 1.6.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,spanish]{elsarticle2}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{placeins}

\usepackage{babel}
\addto\shorthandsspanish{\spanishdeactivate{~<>}}

\begin{document}

\title{Análisis Experimental de la Extracción del Esqueleto por Contracción con Suavizado Laplaciano}

%\title{Análisis Experimental para la Extracción del Esqueleto por Contracción con Suavizado Laplaciano}

\author[rvt]{Alexander Pinzón Fernández}
\author[rvt]{Fabio Martínez Carrillo}

\author[rvt]{Eduardo Romero Castro\fnref{fn2}}

\cortext[fn2]{Autor Correspondiente: Eduardo Romero. Carrera 30 45-03, Ed. 471
Facultad de Medicina, +57 1 3165491, \textbf{edromero@.unal.edu.co}}

\address[rvt]{Grupo de Investigación Bioingenium, Universidad Nacional de Colombia}
\begin{abstract}

Este articulo presenta un análisis sistematico del método de extracción del esqueleto por medio de la contracción de un volumen con suavizado Laplaciano. El trabajo realiza una aproximación experimental al problema de la extracción del esqueleto, para encontrar el rendimiento
del método evaluado frente a cambios isometricos, y durante la fase de simplificación. Esta evaluación utilizo el modelo tridimensional
animado de una persona que realizaba una caminata, a este modelo se le extrajo el esqueleto y se compararon las diferencias en distintos instantes de la animación, y distintas configuraciones del proceso de simplificación. Los resultados muestran un óptimo rendimiento del método frente a las transformaciones isométricas, y múltiples problemas en la fase de simplificación de mallas.\end{abstract}

\begin{keyword}
extracción del esqueleto, suavizado laplaciano
\end{keyword}
\maketitle

\section{Introducción}

En los últimos años se ha incrementado la demanda de sistemas para la captura de movimiento basados en sensores ópticos \citet{Au2008}. Estos sistemas permiten obtener una representacion de cada una de las articulaciones de una persona que realiza movimientos. En el modelamiento de objetos articulados, la cinematica del movimiento esta dado por la posicion de las articulaciones en el tiempo, y estas posiciones a su vez dan una representacion de la interaccion entre cada uno de los componentes del sistema locomotor (las fuerzas de accion -reaccion, los comandos neuro motores, sistema osteo-musculo-esqueletico). La información recolectada mediante estos sistemas permite la realización de una análisis cuantitativo del movimiento permitiendo estimar de forma precisa datos como velocidad, aceleración, entre otras, estas medidas se utilizan en áreas como la medicina para el diagnostico de patologías asociadas a la marcha, o en el cine para la animacion de personajes, o en los deportes para analizar las posturas de un gimnasta.

En computacion grafica, el registro del movimiento de un esqueleto se realiza  dado una secuencia logica de actividades, que son: la captura de vídeo de una persona en movimiento, la reconstrucción 3D a partir de los datos de la captura, y la extracción del esqueleto del objeto tridimensional reconstruido. Uno de los puntos criticos, en este proceso es la extracción del esqueleto dado que no existe una definición formal para la representacion de esta estructura\citet{Cornea2007}. Una aproximacion tipica, consiste en considerar los ejes medios de un objeto 3, definido como el lugar donde se encuentran los centros de todas las esferas de máximo radio inscritas en el cuerpo como se observa en la figura \ref{fig:Medial-axis-and}.	
\begin{center}
%
\begin{figure}[tbh]
\begin{centering}
\includegraphics[scale=0.3]{img/IMG4}
\par\end{centering}
\caption{\label{fig:Medial-axis-and}Medial axis and medial surface}
\end{figure}
\par\end{center}

En la literatura se han descrito diversos metodos de extraccion del esqueleto  y diferentes metricas que permiten identificar los metodos apropiados dada una aplicacion especifica\citet{Attali2007}. Uno de los mejores metodos reportados en la literatura, para la extracción del esqueleto,  es el método de suavizado Laplaciano \citet{Au2008} por sus ventajas de representación homotopica y las conexiones jerárquicas entre sus partes.

En este articulo se desarrolla un análisis experimental de la extracción del esqueleto usando suavizado laplaciano, que pretende ser un nuevo enfoque para el calculo de patrones cinemáticos que permitan ser usados en la clínica para identificar movimientos normales y patológicos. El articulo esta organizado como sigue: el capitulo 1 se presenta de forma general un resumen sobre trabajos relacionados en el área de la extracción del esqueleto que pueden ser tenidos en cuenta para una aplicación clínica (presición, conservación de puntos anatómicos de interes). En el capitulo 2 se hace una descripción detallada de la técnica de extracción del esqueleto por contracción con suavizado Laplaciano. En el capitulo 3 se muesran los resultados obtenidos dada un conjunto de experimentos realizados sobre el modelo. En el capitulo 4 se hace una discusion alrededor de los resultados obtenidos y su usabilidad en el area clínica. Finalmente en el capitulo 5 se describen algunas conclusiones y lineamientos para el trabajo futuro.

\section{Trabajo Relacionado}

En computación grafica se definen los esqueletos (estructuras 1D) como versiones simplificadas de la geometría y topología de un objeto 3D que permiten reducir  la dimensionalidad  de los objetos y  capturar las relaciones dinámicas esenciales para describir la dinamica de un objeto, por ejemplo, en el análisis de marcha los movimientos normales y patologicos estan definifos por un conjunto de relaciones de sus articuaciones\citet{Svensson2002, Starck2005}. Habitualmente, la extracción del esqueleto se realiza con técnicas que reducen la dimensionalidad de un objeto, teniendo en cuenta ciertas restricciones de contracción y minimización de energía hasta encontrar un esqueleto irreducible ó encontrar sus ejes medios\citet{Au2008}. Sin embargo estas representaciones simplistas generalmente pierden informacion de posiciones anatomicas importante para una apliación clínica. Por otra parte, las  representaciones topológicas de un objeto tridimensional, permiten hacer simplificaciones mediante grafos y relaciones  dadas por un esqueleto apriori que permite minimizar el error entre el esqueleto y el grafo \citet{Aguiar2008,HernandezEsteban2002,4178157,Bradley2008}, lo cual conlleva a restricciones para la estimación de diferentes modelos.

Otras aproximaciones permiten hacer una estimación en 2D, para luego utilizar información a priori que permita estimar como fue transformado el esqueleto tridimensional real \citet{Remondino2003,AitAider2006,Cheng2006} el problema radica en utilizar modelos a priori ademas de esqueletos de entrenamiento. Finamelnte los modelos probabilísticos permiten resolver incorporar las dependencias espaciales entre los vértices en el proceso de agrupamiento, y proveer una solución globalmente óptima. En particular, basados en Campos Aleatorios de Markov Gibbs (MRF) \citet{Lavoue2008,Caillette2008,Hou2007} en estos modelos el problema radica en el uso de modelos a priori.

\section{Método De Contracción Con Suavizado Laplaciano}

 Este metodo contrae iterativamente la malla por medio del suavizado laplaciano hasta tener un volumen de cero luego se simplifica la malla por medio de un algoritmo de colapso de bordes que permite obtener un esqueleto 1D del volumen.
Este proceso se puede observar de forma simplificada en la figura \ref{fig:Proceso-de-extraccion}. Este método busca la minimización de energía teniendo en cuenta los siguientes componentes.

\begin{itemize}
\item Un operador Lapaciano que pemite remover las frecuencias altas, es decir suavizar los detalles de la geometría 
\item Una fuerza de atracción que usa los vértices, para mantener información clave de la geometría durante la contracción.
\item Un fuerza de contracción que hace que la forma tridimensional pierda volumen.
\end{itemize}
 .

\begin{center}
%
\begin{figure*}[tbh]
\begin{centering}
\includegraphics[scale=0.3]{img/contraccion}
\par\end{centering}

\centering{}\caption{\label{fig:Proceso-de-extraccion}Proceso de extracción del esqueleto}

\end{figure*}

\par\end{center}

A continuación se describe en detalle cada uno de los componentes que conforman este método. 
\subsection{Suavizado de Laplace}

Una nueva posición en la malla esta dada por sus vecinos como se representa a continuación:

	\[
	x_{i}=\frac{1}{N}\sum_{j=0}^{N}x_{j}
\]

\noindent donde $N$ es el numero de vértice vecinos de $x_{i}$. Esta aproximación en general se restringe por una función de peso que pemite ponderar ciertas caracteristicas y esta definida como:

	\[x_{i}=\frac{1}{N}\sum_{j=0}^{N}w_{j}x_{j}\]
\noindent donde existe una  función de peso $w_{j}$, para ponderar el vértice $x_{j}$.

\subsection{Extracción del Esqueleto}

A partir de  una malla de polígonos $G=\left(V,E\right)$, con vértices $V$ y aristas $E$, el problema de extracción de un esqueleto $S=\left(U,B\right)$ donde $U$ ($U=\left[u_{1}^{T},u_{2}^{T},...,u_{m}^{T}\right]$) son los nodos definido por sus posiciones  y $B$ las aristas puede ser desarrollado basado un proceso de contracción de la geometría que iterativamente suaviza y colapsa la geometría de la malla en una manera restringida. Este proceso es aplicado en el espacio de objeto, directamente en la representación de la malla, sin cualquier proceso de voxelización. Con las fuerzas de contracción cuidadosamente ponderadas y las fuerzas de atracción, el proceso de contracción produce una forma mínima delgada con empalmes y las ramas correspondientes a las particiones del objeto \citet{Au2008}.

\subsection{Contracción de la Geometría}

El vértice de la posición $V'$ es suavizado y contraído a lo largo de dirección de su normal, como resultado de la solución de la ecuación
discreta de Laplace $LV'=0$, donde $L$ es la curvatura del flujo del campo del operador de Laplace de $n\times n$, con los elementos.

$L_{ij}=\left\{ \begin{array}{cc}
w_{ij}=cot\alpha_{ij}+cot\beta_{ij} & si\left(i,j\right)\in E\\
\sum_{\left(i,k\right)\in E}^{k}-w_{ij} & si\, i=j\\
0 & en\, otro\, caso\end{array}\right\} $

Donde $\alpha_{ij}$ y $\beta_{ij}$ son los ángulos opuestos correspondiente al borde $\left(i,j\right)$, como se observa en la figura \ref{fig:a)-El-borde}.

%
\begin{figure}[tbh]
\includegraphics[scale=0.2]{img/alpha_Beta}

\caption{\label{fig:a)-El-borde}a) El borde entre $x_{i}$, $x_{j}$. b) Los
ángulos opuestos $\alpha_{ij}$ y $\beta_{ij}$. Imagen Tomada de
\citet{Desbrun1999}.}

\end{figure}

Dada la ponderación cotangente, las coordenadas de Laplace $\delta=LV=\left[\delta_{1}^{T},\delta_{2}^{T},...,\delta_{n}^{T}\right]^{T}$
aproximan hacia adentro de la normal de la curvatura del flujo.

$\delta_{i}=-4A_{i}\kappa_{i}\mathbf{n}_{i}$, donde \foreignlanguage{english}{$4A_{i},\,\kappa_{i}$}
y $\mathbf{n_{\mathbf{i}}}$ son el área de un anillo local, con esto
se aproximan la curvatura media local, y se aproxima la normal hacia
afuera del vértice $i$.

Entonces resolviendo $LV'=0$, significa remover el componente de la normal y contraer la geometría de la malla.

Las restricciones de atracción, son fuerzas que atraen los vértices
hacia la geometría.

La solución del siguiente sistema, proporciona las nuevas posiciones
de los vértice $V'$

$\left[\begin{array}{c}
W_{L}L\\
W_{H}\end{array}\right]V'=\left[\begin{array}{c}
0\\
W_{H}V\end{array}\right]$

donde $W_{H}$ son las restricciones de atracción y $W_{L}$ las restricciones
de contracción.\\

La solución se logra mediante mínimos cuadrados así.

$\left\Vert W_{L}LV'\right\Vert ^{2}+\sum_{j}W_{H,i}\left\Vert v_{j}^{'}-v_{i}\right\Vert ^{2}$

El proceso iterativo de contracción es el siguiente, donde $t$ representa
cada iteración.
\begin{enumerate}
\item Resolver \foreignlanguage{english}{$\left[\begin{array}{c}
W_{L}^{t}L^{t}\\
W_{H}^{t}\end{array}\right]V^{t+1}=\left[\begin{array}{c}
0\\
W_{H}^{t}V^{t}\end{array}\right]\, para\, V^{t+1}$}
\item Actualizar $W_{L}^{t+1}=S_{L}W_{L}^{t}$ y $W_{H,i}^{t+1}=W_{H,i}^{0}\sqrt{\frac{A_{i}^{0}}{A_{i}^{t}}}$,
donde $A_{i}^{t}$ y $A_{i}^{0}$son los actuales y originales áreas
de un anillo, respectivamente.
\item Computar el nuevo operador de Laplace $L^{t+1}$ con las actuales
posiciones de los vértice $V^{t+1}$ usando la definición de $L_{i,j}$
\end{enumerate}

\section{Experimentación}

Se uso la implementación hecha en \citet{Au2008} por los autores,
para realizar la extracción del esqueleto de un modelo tridimensional
que fue obtenido mediante el método de recuperación de forma desde
las siluetas realizado por \citet{Vlasic2008}, como se observa en
la figura \ref{fig:Caracter-creado-1}. De este modelo se registro
una caminata durante 240 cuadros.

\begin{center}
%
\begin{figure}[tbh]
\begin{centering}
\includegraphics[scale=0.1]{img/vlasic2008}
\par\end{centering}

\caption{\label{fig:Caracter-creado-1}Modelo tridimensional obtenido con el
método de \citet{Vlasic2008}.}

\end{figure}

\par\end{center}

El modelo fue proporcionado por los autores de \citet{Vlasic2008}
en el sitio web \textbf{http://www.mit.edu/\textasciitilde{}ibaran}.
En este sitio web existe un repositorio de diez datasets.

Cada dataset contiene:
\begin{itemize}
\item Los parámetros de calibración de las ocho cámaras de la escena.
\item Ocho imágenes correspondientes al fondo de la escena sin la persona
presente.
\item Ocho vídeos tomados desde distintos ángulos de la persona grabada
durante 240 cuadros.
\item Las siluetas de la persona en cada uno de los cuadros de cada cámara.
\item Los modelos tridimensionales de los 240 cuadros obtenidos mediante
el método propuesto en \citet{Vlasic2008}.
\item Un esqueleto modelo.
\end{itemize}
Para evaluar el proceso de simplificación se variaron el numero de
nodos usados para describir uniones en el esqueleto, luego se analizaba
cada nodo y se clasificaba como \textbf{Valido} si este se encontraba
en la posición correcta respecto al esqueleto modelo, \textbf{Erróneo}
si no se encontraba en una posición donde existiera un nodo en el
esqueleto modelo, y por ultimo por cada nodo que no se recupero en
el esqueleto extraído se contaba como un nodo \textbf{Faltante}, en la
imagen \ref{fig:nodoesss} se observa cada tipo de nodo.

\begin{center}
%
\begin{figure*}[tbh]
\begin{centering}
\includegraphics[scale=0.3]{img/nodos_es}
\par\end{centering}

\centering{}\caption{\label{fig:nodoesss}Descripción del tipo de nodos}

\end{figure*}

\par\end{center}

Durante esta fase se utilizo el modelo tridimensional del primer cuadro de
la animación del dataset llamado \textbf{I\_march}, a este modelo
3D se le realizo el proceso de contracción con un numero de 13 iteraciones
para contraer el volumen hasta un umbral cercano a cero, luego en
el proceso de simplificación se variaron el numero de nodos a extraer
desde 32 hasta 16 como se observa en la figura \ref{fig:Variacion-del-numero},
en esta figura se muestran de izquierda a derecha los resultados con
32 , 28, 24, 20, y 16 nodos . El esqueleto modelo contaba con un numero
de 21 nodos

\begin{center}
%
\begin{figure*}[tbh]
\begin{centering}
\includegraphics[scale=0.3]{img/simplificacion}
\par\end{centering}

\centering{}\caption{\label{fig:Variacion-del-numero}Variación del numero de nodos}

\end{figure*}

\par\end{center}

Los resultados de este análisis se pueden observar en la tabla \ref{tab:Variacion-del-numero}
donde se muestran 5 columnas que representan la siguiente información,
en la columna \textbf{Nodos} se muestra el numero de vértices que
se desean obtener después del proceso de simplificación, en la columna
\textbf{Validos} se muestra el numero de nodos que están correctamente
localizados y que representaban uniones en el esqueleto, en la columna
\textbf{Erróneos} se muestra el numero de nodos que están ocupando
espacios que no corresponden a uniones en la jerarquía, o que están
sobre una linea entre dos uniones reales del esqueleto, por ultimo
en la columna \textbf{Faltantes} se muestra el numero de nodos que
hicieron falta para la correcta reconstrucción de un esqueleto valido
para este modelo.

\begin{center}
%
\begin{table}[htbp]
\caption{\label{tab:Variacion-del-numero}Variación del numero de nodos en
el proceso de simplificación.}

\centering{}\begin{tabular}{|c|c|c|c|}
\hline 
Nodos & Validos & Erroneos & Faltantes \tabularnewline
\hline
\hline 
16 & 13 & 3 & 8\tabularnewline
\hline 
20 & 17 & 3 & 4\tabularnewline
\hline 
24 & 21 & 3 & 0\tabularnewline
\hline 
28 & 21 & 7 & 0\tabularnewline
\hline 
32 & 21 & 11 & 0\tabularnewline
\hline
\end{tabular}
\end{table}

\par\end{center}

La segunda etapa del experimento consistía en la realización de extracciones
del esqueleto en distintas momentos de la animación y observar la
correspondencia topológica entre los esqueletos obtenidos para así
observar como se comporta el método frente a transformaciones isométricas
de la geometría de un cuerpo.En esta etapa se realizaron 13 iteraciones
durante el proceso de contracción y se usaron 24 nodos en el proceso
de simplificación. Se utilizo el mismo modelo del experimento anterior,
se utilizaron distintas poses de este modelo tomadas cada 40 cuadros
para un total de 6 poses, Cada pose representa una posición distinta
de la persona durante la caminata, como se observa en la figura \ref{fig:Distintas-posiciones-del}.

\begin{center}
%
\begin{figure*}[tbh]
\begin{centering}
\includegraphics[scale=0.3]{img/poses}
\par\end{centering}

\centering{}\caption{\label{fig:Distintas-posiciones-del}Distintas posiciones del mismo
cuerpo.}

\end{figure*}

\par\end{center}

En la tabla \ref{tab:Cambios-isometricos} se observan los resultados
obtenidos al realizar cambios isométricas sobre la geometría del personaje
estos cambios representan las distintas poses que tomaba la geometría
del personaje en distintos momentos de la caminata. En la tabla \ref{tab:Cambios-isometricos}
la columna \textbf{Cuadro} representa el momento en el tiempo en el
cual se realizo la captura de la geometría, las demás columnas representan
la misma información que en la tabla \ref{tab:Variacion-del-numero}.

%
\begin{table}[htbp]
\caption{\label{tab:Cambios-isometricos}Cambios isométricas sobre la geometría.}

\centering{}\begin{tabular}{|c|c|c|c|}
\hline 
Cuadro & Validos & Erroneos & Faltantes \tabularnewline
\hline
\hline 
40 & 18 & 6 & 3\tabularnewline
\hline 
80 & 19 & 5 & 2\tabularnewline
\hline 
120 & 20 & 4 & 1\tabularnewline
\hline 
160 & 21 & 3 & 0\tabularnewline
\hline 
200 & 17 & 7 & 4\tabularnewline
\hline 
240 & 20 & 4 & 1\tabularnewline
\hline
\end{tabular}
\end{table}

\section{Resultados Experimentales}

El método de extracción del esqueleto por contracción con suavizado
Laplaciano recupera de forma óptima el esqueleto de un cuerpo bajo
transformaciones isométricas, según se observa en la tabla \ref{tab:Resultados-isometric},
donde se recuperaron en promedio 19.71 nodos de los 21 necesarios
para reconstruir el esqueleto en diferentes momentos del tiempo. Se
observa también que el método posiciona mal 4.83 nodos en promedio,
provocando que se usen mas nodos de los necesario para reconstruir
el esqueleto. Por ultimo en esta tabla observamos que el método no
pudo recuperar 1.86 nodos de los necesarios para la reconstrucción
del esqueleto siendo necesario la intervención manual del usuario
para recuperar el esqueleto en su totalidad.

\begin{center}
%
\begin{table}[tbh]
\begin{centering}
\begin{tabular}{|l|r|r|r|}
\hline 
 & Validos & Erroneos & Faltantes\tabularnewline
\hline
\hline 
Media & 19.71 & 4.83 & 1.86\tabularnewline
\hline 
Desviación Estándar & 1.47 & 1.47 & 1.47\tabularnewline
\hline 
Mínimo & 17 & 3 & 0\tabularnewline
\hline 
Máximo & 21 & 7 & 4\tabularnewline
\hline
\end{tabular}
\par\end{centering}

\centering{}\caption{\label{tab:Resultados-isometric}Resultados obtenidos al realizar
transformaciones isométricas}

\end{table}

\par\end{center}

Durante la fase de simplificación el método presenta un comportamiento
claro como se puede observar en la gráfica \ref{fig:Grafico-simplificacion},
en donde los nodos validos, luego de hacer la recuperación total de
los 21 nodos del esqueleto no sufren perdida ni son sensibles al usar
mas de 24 nodos (blue line). El método una vez alcanza su numero óptimo
de nodos para realizar la recuperación, los demás nodos que se añadan
serán puestos en localizaciones erróneas, además el método parece
siempre tener un numero mínimo de 3 nodos recuperados erróneamente
como se observa el la linea rojo del gráfico \ref{fig:Grafico-simplificacion}.
La linea verde en el gráfico \ref{fig:Grafico-simplificacion} describe
el numero de nodos que hacen falta para recuperar el modelo, se observa
que 24 es el numero de nodos requeridos para recuperar por completo
el esqueleto, y que el uso de mas nodos no implica perdida en la recuperación
del esqueleto.

\begin{center}
%
\begin{figure}[tbh]
\begin{centering}
\includegraphics[scale=0.4]{img/graficoSimplificacion2}
\par\end{centering}

\centering{}\caption{\label{fig:Grafico-simplificacion}Gráfico de la variación de nodos
validos, erróneos y faltantes durante la fase de simplificación}

\end{figure}

\par\end{center}

\section{Conclusiones}

El método de extracción mostró ser robusto y tener baja sensibilidad
frente a cambios isométricos de la geometría, requiere de supervisión
únicamente en la primera fase de simplificación para obtener el numero
óptimo de nodos, luego el método puede trabajar de forma automática
a o largo de todos los cuadros.

El método recupera de forma eficiente el esqueleto sin hacer uso de
un modelo, eliminando la necesidad de estimar la pose minimizando
el calculo necesario para ajustar el esqueleto encontrado con el modelo,
y así mismo poder realizar de forma sencilla y automática el seguimiento
del esqueleto a lo largo del vídeo,

\section{Trabajo Futuro}

Como trabajo futuro se puede mejorar la recuperación de información
haciendo uso de la coherencia espacio temporal no presente en la técnica
de extracción, para superar la perdida de información entre cuadros
de vídeo.

Es posible crear un método para automatizar el proceso de simplificación
para encontrar el numero óptimo de nodos con el cual puede ser representado
el esqueleto de forma correcta, haciendo uso de algoritmos de partición
de mallas.

\subsubsection*{Agradecimientos}

The captured performance data were provided courtesy of the Computer
Graphics Group of the MIT CSAIL Vision Research (Cambirdge, USA).

\bibliographystyle{plain}
\bibliography{listado_inicial}

\end{document}

### 2013-05-23 documents/thesis/resources/HojaTituloMSc.tex

%\newpage
%\setcounter{page}{1}
\begin{center}
\begin{figure}
\centering%
\includegraphics[width=0.4\columnwidth]{resources/logo_un.png}
\end{figure}
\thispagestyle{empty} \vspace*{2.0cm} \textbf{\huge
T\'{\i}tulo de la tesis  o trabajo de investigaci\'{o}n}\\[6.0cm]
\Large\textbf{Nombres y apellidos completos del autor}\\[6.0cm]
\small Universidad Nacional de Colombia\\
Facultad, Departamento (Escuela, etc.)\\
Ciudad, Colombia\\
A\~{n}o\\
\end{center}

\newpage{\pagestyle{empty}\cleardoublepage}

\newpage
\begin{center}
\thispagestyle{empty} \vspace*{0cm} \textbf{\huge
T\'{\i}tulo de la tesis  o trabajo de investigaci\'{o}n}\\[3.0cm]
\Large\textbf{Nombres y apellidos completos del autor}\\[3.0cm]
\small Tesis o trabajo de grado presentada(o) como requisito parcial para optar al
t\'{\i}tulo de:\\
\textbf{Indicar el t\'{\i}tulo que se obtendr\'{a}. Por ejemplo, Magister en Ingenier\'{\i}a Qu\'{\i}mica}\\[2.5cm]
Director(a):\\
T\'{\i}tulo (Ph.D., Doctor, Qu\'{\i}mico, etc.) y nombre del director(a)\\[2.0cm]
L\'{\i}nea de Investigaci\'{o}n:\\
Nombrar la l\'{\i}nea de investigaci\'{o}n en la que enmarca la tesis  o trabajo de investigaci\'{o}n\\
Grupo de Investigaci\'{o}n:\\
Nombrar el grupo en caso que sea posible\\[2.5cm]
Universidad Nacional de Colombia\\
Facultad, Departamento (Escuela, etc.)\\
Ciudad, Colombia\\
A\~{n}o\\
\end{center}

\newpage{\pagestyle{empty}\cleardoublepage}

\newpage
\thispagestyle{empty} \textbf{}\normalsize
\\\\\\%
\textbf{(Dedicatoria o un lema)}\\[4.0cm]

\begin{flushright}
\begin{minipage}{8cm}
    \noindent
        \small
        Su uso es opcional y cada autor podr\'{a} determinar la distribuci\'{o}n del texto en la p\'{a}gina, se sugiere esta presentaci\'{o}n. En ella el autor dedica su trabajo en forma especial a personas y/o entidades.\\[1.0cm]\\
        Por ejemplo:\\[1.0cm]
        A mis padres\\[1.0cm]\\
        o\\[1.0cm]
        La preocupaci\'{o}n por el hombre y su destino siempre debe ser el
        inter\'{e}s primordial de todo esfuerzo t\'{e}cnico. Nunca olvides esto
        entre tus diagramas y ecuaciones.\\\\
        Albert Einstein\\
\end{minipage}
\end{flushright}

\newpage{\pagestyle{empty}\cleardoublepage}

\newpage
\thispagestyle{empty} \textbf{}\normalsize
\\\\\\%
\textbf{\LARGE Agradecimientos}
\addcontentsline{toc}{chapter}{\numberline{}Agradecimientos}\\\\
Esta secci\'{o}n es opcional, en ella el autor agradece a las personas o instituciones que colaboraron en la realizaci\'{o}n de la tesis  o trabajo de investigaci\'{o}n. Si se incluye esta secci\'{o}n, deben aparecer los nombres completos, los cargos y su aporte al documento.\\

\newpage{\pagestyle{empty}\cleardoublepage}

\newpage
\textbf{\LARGE Resumen}
\addcontentsline{toc}{chapter}{\numberline{}Resumen}\\\\
El resumen es una presentaci\'{o}n abreviada y precisa (la NTC 1486 de 2008 recomienda revisar la norma ISO 214 de 1976). Se debe usar una extensi\'{o}n m\'{a}xima de 12 renglones. Se recomienda que este resumen sea anal\'{\i}tico, es decir, que sea completo, con informaci\'{o}n cuantitativa y cualitativa, generalmente incluyendo los siguientes aspectos: objetivos, dise\~{n}o, lugar y circunstancias, pacientes (u objetivo del estudio), intervenci\'{o}n, mediciones y principales resultados, y conclusiones. Al final del resumen se deben usar palabras claves tomadas del texto (m\'{\i}nimo 3 y m\'{a}ximo 7 palabras), las cuales permiten la recuperaci\'{o}n de la informaci\'{o}n.\\

\textbf{\small Palabras clave: (m\'{a}ximo 10 palabras, preferiblemente seleccionadas de las listas internacionales que permitan el indizado cruzado)}.\\

A continuaci\'{o}n se presentan algunos ejemplos de tesauros que se pueden consultar para asignar las palabras clave, seg\'{u}n el \'{a}rea tem\'{a}tica:\\

\textbf{Artes}: AAT: Art y Architecture Thesaurus.

\textbf{Ciencias agropecuarias}: 1) Agrovoc: Multilingual Agricultural Thesaurus - F.A.O. y 2)GEMET: General Multilingual Environmental Thesaurus.

\textbf{Ciencias sociales y humanas}: 1) Tesauro de la UNESCO y 2) Population Multilingual Thesaurus.

\textbf{Ciencia y tecnolog\'{\i}a}: 1) Astronomy Thesaurus Index. 2) Life Sciences Thesaurus, 3) Subject Vocabulary, Chemical Abstracts Service y 4) InterWATER: Tesauro de IRC - Centro Internacional de Agua Potable y Saneamiento.

\textbf{Tecnolog\'{\i}as y ciencias m\'{e}dicas}: 1) MeSH: Medical Subject Headings (National Library of Medicine's USA) y 2) DECS: Descriptores en ciencias de la Salud (Biblioteca Regional de Medicina BIREME-OPS).

\textbf{Multidisciplinarias}: 1) LEMB - Listas de Encabezamientos de Materia y 2) LCSH- Library of Congress Subject Headings.\\

Tambi\'{e}n se pueden encontrar listas de temas y palabras claves, consultando las distintas bases de datos disponibles a trav\'{e}s del Portal del Sistema Nacional de Bibliotecas\footnote{ver: www.sinab.unal.edu.co}, en la secci\'{o}n "Recursos bibliogr\'{a}ficos" opci\'{o}n "Bases de datos".\\

\textbf{\LARGE Abstract}\\\\
Es el mismo resumen pero traducido al ingl\'{e}s. Se debe usar una extensi\'{o}n m\'{a}xima de 12 renglones. Al final del Abstract se deben traducir las anteriores palabras claves tomadas del texto (m\'{\i}nimo 3 y m\'{a}ximo 7 palabras), llamadas keywords. Es posible incluir el resumen en otro idioma diferente al espa\~{n}ol o al ingl\'{e}s, si se considera como importante dentro del tema tratado en la investigaci\'{o}n, por ejemplo: un trabajo dedicado a problemas ling\"{u}\'{\i}sticos del mandar\'{\i}n seguramente estar\'{\i}a mejor con un resumen en mandar\'{\i}n.\\[2.0cm]
\textbf{\small Keywords: palabras clave en ingl\'{e}s(m\'{a}ximo 10 palabras, preferiblemente seleccionadas de las listas internacionales que permitan el indizado cruzado)}\\

### 2013-07-06 documents/thesis/SIBGRAPI2013/Final_TQLBO.tex

--- 2013-04-26 documents/thesis/SIBGRAPI2013/TQLBO.tex
@@
 \begin{document}
-\title{Shape Inflation With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
+\title{Shape Inflation With an Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}
 
@@
 \newif\iffinal
-\finalfalse
-%\finaltrue
-\newcommand{\jemsid}{99999}
+%\finalfalse
+\finaltrue
+\newcommand{\jemsid}{114677}
 %-------------------------------------------------------------------------
@@
 complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
-based methods however require to interact with a minimun number of
+based methods however require to interact with a small number of
 control points for any operation to be efficient, or in other words,
@@
 edges \cite{DeRose1998}, or the modification of some vertex weights
-to locally control the zone of influence \cite{Biermann2000}. Neverteless
+to locally control the zone of influence \cite{Biermann2000}. Nevertheless
 these methods are difficult to deal with since they require a large
@@
 original topology. Likewise, along with this operator, it is proposed
-a method to generate a family of parameterized shapes, in a robust
+a method to generate a family of parametrized shapes, in a robust
 and predictable way. This method enables customization of the smoothness
@@
 \section{Laplacian Smooth\label{sec:Laplacian-Smooth}}
-%
-\begin{figure*}[t]
-\includegraphics[width=1\textwidth]{figs/beltrami}
-
-\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
-vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
-(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
-{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO).}
-\end{figure*}
 
@@
 Many smoothing Laplacian functionals regularize the surface energy
-by controling the total surface curvature $S$.
+by controlling the total surface curvature $S$.
 
-\begin{equation}
-E\left(S\right)=\int_{S}\kappa_{1}^{2}+\kappa_{2}^{2}dS\label{eq:total_cuarvature_integral}
-\end{equation}
+\begin{center}
+$E\left(S\right)=\int_{S}\kappa_{1}^{2}+\kappa_{2}^{2}dS$
+\par\end{center}
+%\end{equation}
 
@@
 \end{figure}
+
+\begin{figure*}[t]
+\includegraphics[width=1\textwidth]{figs/beltrami}
+
+\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
+vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
+(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
+{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO).}
+\end{figure*}
 
@@
 operator for hybrid quad/triangle meshes, mixing arbitrary types of
-meshes, exploiting the basic geometrical relationships and ensuring
-algorithm convergence.
+meshes, exploiting the basic geometrical relationships and ensuring good results with few algorithm iterations.
 
@@
 and the areas of the triangular faces $\ensuremath{A\left(T_{v_{i}}\right)}$
-adjacent to vertex $\ensuremath{v_{i}}$.
+adjacent to vertex $\ensuremath{v_{i}}$
 
@@
 the area for quads $\ensuremath{A\left(Q_{v_{i}}\right)}$ and triangles
-$A\left(T_{v_{i}}\right)$ is.
+$A\left(T_{v_{i}}\right)$ is
 
 \begin{center}
-$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$
+$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$, 
 \par\end{center}
 
-Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{v_{i}}$ and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{v_{i}}$.
+Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{v_{i}}$ and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{v_{i}}$
 
@@
 
-Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).
+Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads})
 
@@
 
-According to (\ref{eq:eq_gradient_voronoi_area}), we have.
+According to (\ref{eq:eq_gradient_voronoi_area}), we have
 
@@
 (\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
-the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.
+the TQLBO (Triangle-Quad LBO) of $v_{i}$ is
 
@@
 
-We define a Laplacian operator as a matrix equation
+We define a TQLBO as a matrix equation
 
@@
 -\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N\left(v_{i}\right)\\
-\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
+%\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
+\frac{1}{2A_{i}}\underset{k\in N\left(v_{i}\right)}{\sum}w_{ik} & \mbox{if }i=j\\
 0 & \mbox{otherwise}
@@
 
-Normalized version of the TQLBO as a matrix equation
+Normalized equation of the TQLBO
 
@@
 L\left(i,j\right)=\begin{cases}
--\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
+%-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
+-\frac{w_{ij}}{\underset{k\in N\left(v_{i}\right)}{\sum}w_{ik}} & \mbox{if }j\in N\left(v_{i}\right)\\
 \delta_{ij} & \mbox{otherwise}
@@
 To solve this equation, implicit integration is used as well as a
-normalized version of TQLBO matrix.
+normalized version of TQLBO matrix
 
@@
 
-The curvature cannot be calculted at the boundary of the meshes that
+The curvature cannot be calculated at the boundary of the meshes that
 are not closed, for that reason we use the scale-dependent operator
@@
 $\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
-and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
-factor.
+and $vol_{t+1}$ is the volume at the iteration $t+1$, $n$ is the number of vertices, then the scale
+factor
 
@@
 the Laplace Beltrami operator for hybrid quad/triangle meshes with
-several example models (see figures \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
+several example models shown in figures  \ref{fig:Spectrum}, \ref{fig:Subdivision-Cups},
 \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test}, \ref{fig:camello_enhanced},
 \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey},
-\ref{fig:Animated_Camell}). The shape inflation was assessed with
+\ref{fig:Animated_Camell}. The shape inflation was assessed with
 TQLBO method on a PC with AMD Quad-Core Processor @ 2.40 GHz and 8
@@
 (c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
-(c) for triangles, (d) for quads, (e) for triangles and quads random
+(c) for quads, (d) for triangles, (e) for triangles and quads random
 chosen.}
@@
 
-Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
+Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.c.)
 may produce similar results to those obtained with Catmull-Clark (see
-figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
+figure \ref{fig:Catmull_Clark}.b.), whose models are in average equal
 triangles. The one obtained with the Laplacian smoothing is shown
@@
 Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
-areas in the model. Quadss with larger area have smaller inflation
+areas in the model. Quads with larger area have smaller inflation
 (figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
@@
 
-\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Inflate shape brush for leg into red
-circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
+\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Traditional inflate brush
+for leg into blue circle, (c) Shape inflation brush for leg into red
+circle. Bottom row: (a) Hand, (b) Traditional inflate brush for fingers into blue
 circle, (c) Shape inflation brush for fingers in red circle.}
@@
 of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
-was used OpenNL which is a a library for solving sparse linear system.
+was used OpenNL \cite{Buatois2007}  which is a a library for solving sparse linear system.
 

### 2013-07-06 software/laplace_operator/test_edit3d.m

@@ -1,0 +1,81 @@
+function test_edit3d()
+    addpath(genpath('E:\personal\maestria\tesis\Jeronimo\trunk\software\laplace_operator'));
+    %cactus
+%     static_anchors = [17 31 32 35 47 77 86 87 120 242 248 251 253 305 308 492 629 1040 1047 1095 1263 1266 1336 1337 1351 1356 1359 1363 1449 1452];
+%     handle_anchors = [722 798 170 800 790 797 1201 1207 173 1203 58 1202 3 200];
+%     [V,F] = read_off('E:/media3D/cactus.off');
+%     [V2,F2] = read_off('E:/media3D/cactus2.off');
+
+    static_anchors = [1];
+    handle_anchors = [2];
+    [V,F] = read_off('E:/media3D/cube.off');
+    [V2,F2] = read_off('E:/media3D/cube.off');
+
+    
+    
+    %tubo 
+%     handle_anchors = [209 210 211 212 213 215 216 217 218 219 220 221 222 223 224 225 226 227 228 229 230 231 232 233 234 235 236 237 238 239 240];
+%     static_anchors = [1:64];
+%     [V,F] = read_off('J:/OBJ/tubo.off');
+%     [V2,F2] = read_off('J:/OBJ/tubo6.off');
+    
+    
+    %verbl
+    %leg
+    %handle_anchors = [641, 655, 657, 659, 661, 669, 683, 685, 693, 577, 579, 581, 583, 585, 587, 589, 591, 593, 595, 597, 599, 601, 605, 607, 609, 611, 613, 615, 617, 619, 621, 623, 625, 627, 629, 633, 637, 639];
+    %static_anchors = [1:300 449, 451, 485, 441, 423, 489, 471, 431, 435, 437, 425, 473, 439, 447, 477, 453];
+    
+    %head
[…]

### 2013-07-06 trunk/software/laplace_operator/LaplacianEditing3D.m

@@ -1,40 +1,258 @@
-function LaplacianEditing3D(xyz,F, Fixed_Points, Edited_Points);
-    n = length(V);
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Sorkine, O.; Cohen-Or, D.; Lipman, Y.; Alexa, M.; Rossl, C. & Seidel, H.-P. Laplacian surface editing Proceedings of the 2004 EurographicsACM SIGGRAPH symposium on Geometry processing, ACM, 2004, 175-184
+%
+% Lipman, Y.; Sorkine, O.; Levin, D. & Cohen-Or, D. Linear rotation-invariant coordinates for meshes ACM Trans. Graph., ACM, 2005, 24, 479-487
+%
+% Perez, Alvaro. OBJECT DEFORMATION USING LAPLACIAN COORDINATES. Master Thesis. 2010.
+% 
+% http://igl.ethz.ch/projects/Laplacian-mesh-processing/Laplacian-mesh-editing/laplacian-editing-2D-MATLAB.zip
+%
+% Matlab Mesh Toolkit http://www.dgp.toronto.edu/~rms/software/matlabmesh/
+%
+% Toolbox Graph https://www.ceremade.dauphine.fr/~peyre/matlab/graph/content.html
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% Author: Alexander Pinzon Fernandez apinzonf@gmail.com 2013
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function Vf = LaplacianEditing3D(xyz,F, static_anchors, handle_anchors, anchors_pos);
+    n = length(xyz);
     name = 'gsoc';
     options.name = name; % useful for displaying
     options.symmetrize = 1;
     options.normalize = 0;
-    L = compute_mesh_laplacian(V,F,'conformal',options); 
-    xyz = xyz';
+    L = compute_mesh_laplacian(xyz,F,'conformal',options); 
+    [normal,normalf] = compute_normal(xyz,F);
+    
     delta = L*xyz;
+    %xyz = xyz';
     L_prime = [   L       zeros(n)   zeros(n)% the x-part
-                zeros(n)    L        zeros(n)
-                zeros(n)  zeros(n)     L]; % the y-part
[…]

### 2014-05-13 trunk/documents/thesis/thesis_LO_QT.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{esint}
\onehalfspacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\pdfpageheight\paperheight
\pdfpagewidth\paperwidth

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[12pt,spanish,fleqn,openany,letterpaper,pagesize]{scrbook}

%\usepackage[ansinew]{inputenc}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{eepic}
\usepackage{amsmath}
\usepackage{threeparttable}
\usepackage{amscd}
\usepackage{here}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{longtable}

\usepackage{rotating} %Para rotar texto, objetos y tablas seite. No se ve en DVI solo en PS. Seite 328 Hundebuch
                        %se usa junto con \rotate, \sidewidestable ....

\renewcommand{\theequation}{\thechapter-\arabic{equation}}
\renewcommand{\thefigure}{\textbf{\thechapter-\arabic{figure}}}
\renewcommand{\thetable}{\textbf{\thechapter-\arabic{table}}}

\pagestyle{fancyplain}%\addtolength{\headwidth}{\marginparwidth}
\textheight22.5cm \topmargin0cm \textwidth16.5cm
\oddsidemargin0.5cm \evensidemargin-0.5cm%
\renewcommand{\chaptermark}[1]{\markboth{\thechapter\; #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\; #1}}
\lhead[\fancyplain{}{\thepage}]{\fancyplain{}{\rightmark}}
\rhead[\fancyplain{}{\leftmark}]{\fancyplain{}{\thepage}}
\fancyfoot{}
\thispagestyle{fancy}%

\addtolength{\headwidth}{0cm}
\unitlength1mm %Define la unidad LE para Figuras
%\mathindent0cm %Define la distancia de las formulas al texto,  fleqn las descentra
\marginparwidth0cm
\parindent0cm %Define la distancia de la primera linea de un parrafo a la margen

%Para tablas,  redefine el backschlash en tablas donde se define la posici\'{o}n del texto en las
%casillas (con \centering \raggedright o \raggedleft)
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

%Espacio entre lineas
\renewcommand{\baselinestretch}{1.1}

%Neuer Befehl f\"{u}r die Tabelle Eigenschaften der Aktivkohlen
\newcommand{\arr}[1]{\raisebox{1.5ex}[0cm][0cm]{#1}}

%Neue Kommandos
\usepackage{resources/Befehle}

%Trennungsliste
\hyphenation {Reaktor-ab-me-ssun-gen Gas-zu-sa-mmen-set-zung
Raum-gesch-win-dig-keit Durch-fluss Stick-stoff-gemisch
Ad-sorp-tions-tem-pe-ra-tur Klein-schmidt
Kohlen-stoff-Mole-kular-siebe Py-rolysat-aus-beu-te
Trans-port-vor-gan-ge}

%\pagenumbering{roman}
%\let\myTOC\tableofcontents
%\renewcommand\tableofcontents{%
%\myTOC
%\clearpage
%\pagenumbering{arabic}
%}

\makeatother

\usepackage{babel}
\begin{document}
\pagenumbering{roman}
\begin{center}
\begin{figure}
\centering%
%\includegraphics[width=0.4\columnwidth]{resources/logo_un.png}
%\includegraphics[width=0.4]{logo_un.png}
\end{figure}
\thispagestyle{empty}

\vspace{2cm}

\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

\vspace{6cm}

\textbf{\large Alexander Pinzón Fernández}{\large \par}

\vspace{6cm}

Universidad Nacional de Colombia

Facultad de Ingenieria, Departamento de Sistemas e Industrial

{\small Grupo de Investigación CIM@LAB}{\small \par}

Bogotá, Colombia

2014

\end{center}

\newpage{}

\begin{center}
\thispagestyle{empty} 
\vspace*{0cm}

\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
Meshes}{\huge \par}

\vspace{2.5cm}

\textbf{\large Alexander Pinzón Fernández}{\large \par}

\vspace{2.5cm}

{\small A thesis submitted in partial fulfillment of the requirements
for the degree of:}{\small \par}

\textbf{Master in Systems Engineering and Computer Science}

\vspace{2cm}

{\small Advisor:}\\
{\small Eduardo Romero Castro , Ph.D.}{\small \par}

{\small \vspace{1.5cm}
}{\small \par}

{\small Research Area:}\\
{\small Computer Graphics}{\small \par}

{\small \vspace{2cm}
}{\small \par}

{\small Universidad Nacional de Colombia}\\
{\small Facultad de Ingenieria, Departamento de Sistemas e Industrial}\\
{\small Grupo de Investigación CIM@LAB}\\
{\small Bogotá, Colombia}\\
{\small 2014}{\small \par}

\end{center}
\newpage 
\thispagestyle{empty}

\textbf{Dedicación}

{\small \vspace{4cm}
}{\small \par}

\noindent \begin{flushright}
\begin{minipage}[t]{8cm}%
{\small A Beatriz y Campo Elias mis padres que siempre me dieron la
libertad de escoger, con su comprensión y apoyo me permitieron dedicar
mi tiempo a la ciencia.}{\small \par}

{\small \vspace{1cm}
}{\small \par}

{\small A mis padres}{\small \par}

{\small \vspace{1cm}
}{\small \par}

Beatriz Fernandez Vargas

Campo Elias Pinzon Rojas%
\end{minipage}
\par\end{flushright}

\newpage
\thispagestyle{empty}

\textbf{\LARGE Acknowledgement}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}

\vspace{2cm}

I wold like to thank my advisor professor Eduardo Romero and CIM\&LAB
research group for his support in this thesis.

{\small \vspace{1cm}
}{\small \par}

I would like to thank all the workers in Colombia who fund the public
education with their work.

{\small \vspace{1cm}
}{\small \par}

This work was supported in part by the Blender Foundation, Google
Summer of code program at 2012 - 2013.

\newpage{}

\textbf{\LARGE Abstract}{\LARGE \par}

\addcontentsline{toc}{chapter}{\numberline{}Abstract}

In the last two decades three-dimensional modeling methods have been
evolving and developing rapidly, thanks in part to the use of vector
operators of differential geometry. The Laplacian operator has been
one of the most widely studied and used thanks to the properties exhibited
by their eigenvectors in novel applications such as noise reduction,
enhancement, remeshing, UV mapping, posed, skeletonization, among
other. The differential operator is defined in a continuous and smooth
domain named manifold, manifolds are often approximated by discrete
polygon meshes composed by triangles and quadrangles which represent
the real world three-dimensional objects. In these meshes spectral
structure is calculated using a discrete Laplacian operator, the discrete
version of the Laplacian operator given by Pinkall in 1993 works only
with meshes of triangles, and Xiong in 2011 working exclusively with
quads. This thesis proposes an original extension of the Laplacian
operator that allows to work with hybrid meshes composed by triangles
and quadrangles.

Along with the operator, this work presents new sculpting and modeling
applications with base on the enhancement, applications on subdivision
surfaces using smoothing, mesh posing using differential coordinates
and skeletonization using iterative contraction. This series of applications
demonstrates the quality, predictability and flexibility of the proposed
operator.

The proposed operator was successfully used in real production environments
within software Blender how new tools. Currently these tools are available
as open source software.

\textbf{\LARGE Resumen}{\LARGE \par}

En las dos últimas décadas los métodos de modelado tridimensional
han ido evolucionando y desarrollándose rápidamente, en parte gracias
al uso de operadores vectoriales de geometría diferencial. El operador
Laplaciano ha sido uno de los más ampliamente estudiado y usado gracias
a las propiedades exhibidas por sus vectores propios en novedosas
aplicaciones como: reducción de ruido, realce, remallado, mapeo UV,
posado, esqueletonización, entre otras. Este operador diferencial
es definido en un dominio continuo y suave llamado variedad, las variedades
son a menudo aproximadas por mallas discretas de polígonos compuestas
por triángulos y cuadrángulos que a su vez representan objetos tridimensionales
del mundo real. En estas mallas se calcula la estructura espectral
con el uso de algún operador Laplaciano discreto, la versión discreta
del operador Laplaciano propuesta por Pinkall en el 1993 trabaja únicamente
con mallas compuestas por triángulos, y la de Xiong en el 2011 trabaja
exclusivamente con cuadrángulos. Esta tesis propone una extensión
original del Operador Laplaciano que permite trabajar con mallas híbridas
compuestas por triángulos y cuadrángulos.

Junto con el operador, este trabajo presenta nuevas aplicaciones en
esculpido y modelamiento con base en el realce, aplicaciones en subdivisión
de superficies con el uso de suavizado, posado de mallas con el uso
de coordenadas diferenciales y esqueletonización usando contracción
iterativa. Esta serie de aplicaciones demuestra la calidad, predictibilidad
y flexibilidad del operador propuesto.

El operador propuesto fue usado de forma exitosa en ambientes reales
de producción dentro del software Blender como nuevas herramientas.
Actualmente estas herramientas están disponibles como programas de
código abierto.

{\small \vspace{1cm}
}{\small \par}

\textbf{\small Keywords: laplacian operator; smooth; enhance; sculpting;
subdivision surface}{\small \par}

\tableofcontents{}

\listoffigures

\listoftables

\pagenumbering{arabic}

\chapter{Introduction}

The discrete versions of Laplace Beltrami Operator have been used
in the last years for the develop of new geometric modeling tools.
In the work of Pinkall \cite{Pinkall1993} was introduced the cotangent
version of Laplace operator, that allow to find the minimal surface
when compute a discete harmonic map with the Laplacian operator, this
version has been widely studied and applied in various problems of
computer geometric modeling. The manifolds that are continuous domains
homeomorphic to $\mathbb{R}^{n}$ are represented in computers by
polygon meshes. These polygons are generally composed of triangles
and quadrangles, while work with laplacian operator in this hybrid
composition are not a mathematical challenge, most research uses only
meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006},
in other recent studies \cite{Liu2008,Xiong2011} the Laplacian operator
is working exclusively with quadrangles. But in the artistic scope
topology and the way the edges are distributed, the triangle and quadrangles,
directly affects the processes of animation, interpolation, textured,
etc. As discussed by \cite{Mullen2007} who use a manual connection
of a couple of vertices to perform animation processes and interpolation.
It is then of paramount importance to develop operators that easily
interact with such meshes, eliminating the need of preprocessing the
mesh to convert it to triangles and change the original topology.

Modeling techniques able to generate a variety of realistic shapes,
have been developed \cite{Botsch2006}. Editing techniques have evolved
from affine transformations to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
based methods however require to interact with a minimun number of
control points for any operation to be efficient, or in other words,
a unicity condition is introduced by demanding a smooth surface after
any of these shape operations. Hence, traditional modeling methods
for subdividing surfaces from coarse geometry have become widely popular
\cite{Catmull1978,Stam1998}. These works have generalized a uniform
B-cubic spline knot insertion to meshes, some of them adding some
type of control, for instance with the use of creases to produce sharp
edges \cite{DeRose1998}, or the modification of some vertex weights
to locally control the zone of influence \cite{Biermann2000}. Neverteless
these methods are difficult to deal with since they require a large
number of parameters and a very tedious customization. Instead, the
presented applications requires a single parameter that controls the
global curvature, which is used to maintain realistic shapes, creating
a family of different versions of the same object and therefore preserving
the detail of the original model and a realistic appearance.

The shape inflation and shape exaggeration can thus be used as such
brush in the sculpting process, when inflating a shape since current
brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
In contrast, the presented enhance method inflates a mesh by moving
the vertices towards the reverse curvature direction, conserving the
shape and sharp features of the model.

\paragraph{Contributions}

This work presents an extension of the Laplace Beltrami Operator for
hybrid quad/triangle meshes, representing a larger mesh spectrum from
what has been presented so far. The method eliminates the need of
preprocessing and allows preservation of the original topology. Likewise,
along with this operator, it is proposed a method to generate a family
of parameterized shapes, in a robust and predictable way. This method
enables customization of the smoothness and curvature, obtained during
the subdivision surfaces process. Finally, it is proposed a new brush
for inflating the silhouette mesh features in modeling and sculpting.

This work is organized as follows: Chapter \ref{sub:1.1-Related-work}
presents works related to the Laplacian operator, applications in
digital sculpting, deformation, and offsetting methods for polygonal
meshes; In chapter \ref{chap:Mathematical-foundation}, it is described
the theoretical framework of the Laplacian operator for polygon meshes;
In chapter \ref{sec:Proposed-Method}, it is presented the extension
of the Laplacian Operator for hybrid meshes and applications of shape
inflation ,subdivision of surfaces , deformation, skelenotization
and sculpting; finally some Laplacian Operator results, to hybrid
quad/triangle meshes are graphically shown as well as results of the
shape inflation applications in sculpting, subdivision, deformation,
skelenotization and modeling.

\chapter{Related work\label{sub:1.1-Related-work}}

Many tools have been developed for modeling, based on the Laplacian
mesh processing. These different tools preserve the surface geometric
details when using laplacian operators for different processes such
as smoothing, enhancing, free-form deformation, fusion, morphing and
other applications \cite{Ranjan2012}.

The most used discretization of Laplace Beltrami operator $\Delta_{\mbox{\ensuremath{\Omega}}}$
over a triangulated mesh $\Omega$ was proposed by Pinkall \cite{Pinkall1993}.

\noindent \begin{center}
$\Delta_{\mbox{\ensuremath{\Omega}}}\left(u\right)=\frac{1}{2}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(x_{i}-x_{j}\right)$
\par\end{center}

Where $N_{1}$is the 1-ring neighboorhood, $\alpha$ and $\beta$
are the opposite angles to edge between vertex $i$ and vertex $j$.
In this work the discretize laplacian operator was used to find the
minimal surface based on minimization energy strategy using the Dirichlet's
energy of the function $u$ over a manifold represented by triangulated
mesh $\Omega$.

\noindent \begin{center}
$E_{D}\left(u\right)=\frac{1}{2}\int_{\Omega}\bigl|\nabla u\bigr|^{2}$
\par\end{center}

Then Taubin works \cite{Taubin1995} for first time treat the problem
of noise reduction in digital poligonal meshes from signal proccessing
point of view. Taubin extends Fourier analysis to signals defined
on polygonal meshes, Taubin observe that Fourier transform is a decomposition
of the signal into an eigenvectors of the Laplacian operator, and
reconstruct the signal with a linear combination of these eigenvectors.
Desbrun works \cite{Desbrun1999} consider the same approach of Taubin,
but Desbrun use a curvature normal ($\bar{\kappa}\mathbf{n}$) based
on cotangen Laplace operator version for noise reduction over a difussion
process. This it's the most important and popular Laplace Beltrami
opertator discretization \cite{Liu2008}, many works for mesh smoothing
and fairing have been developed based on this LBO discretization \cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}.

\noindent \begin{center}
$\frac{\partial x_{i}}{\partial t}=-\bar{\kappa_{i}}\mathbf{n_{i}}$
\par\end{center}

\noindent \begin{center}
$-\bar{\kappa_{i}}\mathbf{n_{i}}=\frac{1}{A}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)$
\par\end{center}

Where $A$ is the area surrounding vertex $i$. This laplacian operator
$L$ was used for reduce the noise in a mesh $X$ over a difussion
process.

The convergence of the Laplace Beltrami operator has been very important
in fields how numerical analysis, given that implications in the simulation
process and geometric partial differentials equations. In the works
of \cite{Xu2004} is established the convergence of several discrete
Laplace Beltrami operators over triangulated meshes with numerical
results that support the theoretical analysis. Over quadrilateral
meshes Liu \cite{Liu2008} presents a discrete Laplace Beltrami Operator
based on a bilinear interpolation and its convergence over this type
of meshes composed only by quads.

In the work of Sorkine \cite{Sorkine2006} the laplacian operator
was used to repose a meshes while preserving geometry details of the
surface. The details was stored in differential coordinates $\delta_{i}$
for every vertex $v_{i}$.

\noindent \begin{center}
$\delta_{i}=\sum_{j\in N_{1}\left(i\right)}\frac{1}{2}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)$
\par\end{center}

The differential coordinates represents the difference between the
absolut coordinate of $v_{i}$and the center of mass of its immediate
neighboors.

Offset methods for polygon meshing, based on the curvature defined
by the Laplace Beltrami operator, have been developed. These methods
adjust the shape offset by a constant distance, with enough precision.
Nevertheless, these methods fail to conserve sufficient detail because
of the smoothing, a crucial issue which depends on the offset size
\cite{Zhuo2012}. In volumetric approaches, in case of point-based
representations, the offset boundary computation is based on the distance
field and therefore when calculating such offset, the topology of
the model may be different to the original \cite{Chen2011}.

\cite{Gal2009} propose automatic feature detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys, characerized by their first
and second order curvature derivatives, see \cite{Ohtake2004}, and
angle-based threshold. Likewise, curves have been also classified
as planar or non-planar, approximated by lines, circles, ellipses
and other complex shapes. In such case, the user defines an initial
change over several features which is propagated towards other features,
based on the classified shapes and the inter-relationships between
them. This method works well with objects that have sharp edges, composed
of basic geometric shapes such as lines, circles or ellipses. However,
the method is very limited when models are smooth since it cannot
find the proper features to edit.

Digital sculpting have been traditionally approached either under
a polygonal representation or a voxel grid-based method. Brushes for
inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
In grid-based sculpting, some other operations have allowed to add
or remove voxels since production of polygonal meshes require a processing
of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
from the difficulty of maintaining the surface details during larger
scale deformations.

In the literature, several studies have described the skeleton extraction
systems and different metrics that identify appropriate methods given
an application specific \cite{Attali2007}. One of the best methods
reported in the literature for the extraction of the skeleton is the
Laplacian smoothing method for its advantages of homotopy representation
and hierarchical connections between parts. The Skeleton extraction
methods permits simplify the dimension of the object preserving the
topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
present a skeleton extraction method based on iterative smooothing-contraction,
in this method the several constraints are used to waranty that the
process converge to skeleton formed by branchs and joins, the constraints
based on laplacian operator, the low frequencies of the mesh are preserving
with the use of attractor to original mesh, while the iterative smoothin
process remove high frecuencies.

\chapter{Mathematical foundation\label{chap:Mathematical-foundation}}

This chapter studies basic mathematical foundation on differential
geometry to understand the differential operators and the Laplace
beltrami operator.

The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
The differential operators show a deep relationships betwen the geoemetry
(curvatures, geodesics) and topology of the manifold. This differential
operators are very used in applications on computer geometric modelling
over the last years \cite{Rosenberg1997,Alexa2011}.

\section{Manifolds}

A manifold is a topological space $M$ with the following properties:

If $x\in M$, then there is some neighborhood $N\left(x\right)$ and
some integer $n\geq0$ such that $N(x)$ is homeomorphic to $\mathbb{R}^{n}$
\cite{Spivak1-1999}.

This work is related to manifolds that represent a surface in an three-dimensional
Eucliddean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.

The manifols are represented by polygonal meshes with points connected
by triangles and quads.

\section{Laplace Operator}

In computer graphics a manifold is often approximated by a discrete
mesh \cite{Ranjan2012}, then is necessary to define a discrete laplacian
operator that act on functions defined on such meshes.

Consider a smooth compact manifold $M$ of dimension $m$ isometrically
embedded in a Euclidean space $\mathbb{R}^{d}$.

Given a twice continuously differentiable function $f\in C^{2}\left(M\right)$,
let $\nabla_{\mbox{M}}f$ denote the gradient vector field of $f$
on $M$.

The Laplace-Beltrami operator $\Delta_{\mbox{M}}$ of $f$ is defined
as the divergence of the gradient; that is \cite{Spivak1-1999},

\noindent \begin{center}
$\frac{\partial^{2}f}{\partial x^{2}}+\frac{\partial^{2}f}{\partial y^{2}}+\frac{\partial^{2}f}{\partial z^{2}}=0$
\par\end{center}

\noindent \begin{center}
$\nabla_{\mbox{M}}^{2}f=\Delta_{\mbox{M}}f=0$
\par\end{center}

\noindent 
\begin{equation}
\Delta_{\mbox{M}}f=div\left(\nabla_{\mbox{M}}f\right)
\end{equation}

\subsection{Discrete Laplace Operator Setting}

Discrete Laplacian operators are linear operators that act on functions
defines on meshes. These functions are specified by their values at
the vertices.

Thus, if a mesh $M$ has $n$ vertices, then functions on $M$ will
be represented by vectors with $n$ components and a mesh Laplacian
will be described by an $n\times n$ matrix \cite{Ranjan2012}.

The Laplacian operator locally takes the difference between the value
of a function at a vertex and a weighted average of its values at
the first-order or one-ring neighbor vertices, then a Laplacian matrix
$L$ has a local form given by

\noindent \begin{center}
$L\left(f\right)_{i}=b_{i}^{-1}\underset{j\in N\left(i\right)}{\sum}w_{ij}\left(f_{i}-f_{j}\right)$
\par\end{center}

Where $w_{ij}$are the weights between the vertex $i$ and the vertex
$j$. $b_{i}^{-1}$ are the factors depending of the boundary region
over vertex $i$. $N\left(i\right)$ are the neighbors that share
a edge with vertex $i$.

\subsection{Gradient of Voronoi Area}

Consider a surface $S$ composed of a set of triangles around vertex
$v_{i}$. Let us define the \textsl{Voronoi Region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The area change produced
by the movement of $v_{i}$ is called the gradient of \textsl{Voronoi
region} \cite{Pinkall1993,Desbrun1999,Meyer2003}.

\noindent 
\begin{align}
\nabla A & =\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)\label{eq:eq_gradient_voronoi_area}
\end{align}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/voronoi_region}

\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
in dark blue.$v_{j}$ belong to the first neighborhood around $v_{i}$.
$\alpha_{j}$ and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
\end{figure}

If the gradient in equation \ref{eq:eq_gradient_voronoi_area} is
normalized by the total area of the 1-ring neighborhood around $v_{i}$,
the \textsl{discrete mean curvature normal} of a surface $S$ is obtained,
as shown in equation \ref{eq:discrete_mean_curvature_normal}.

\noindent 
\begin{equation}
2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{eq:discrete_mean_curvature_normal}
\end{equation}

\section{Laplace Beltrami Operator}

The \textit{Laplace Beltrami operator} LBO noted as $\Delta$ is used
for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.

\noindent 
\begin{equation}
\Delta_{\mbox{S}}=2\kappa\mathbf{n}\label{eq:def_LBO}
\end{equation}

\chapter{Proposed Laplacian Operator\label{sec:Proposed-Method}}

This thesis propose an original extension of the Laplace Beltrami
operator for hybrid quad/triangle meshes, mixing arbitrary types of
meshes, exploiting the basic geometrical relationships and ensuring
algorithm convergence.

With the use of the proposed Laplacian Operator this work show succesful
uses in: Smoothing, Enhancing, Smooth Subdivision, Deformation, Sculpting,
and Skeletonization.

\section{Proposed Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes
TQLBO\label{sub:Laplace-Beltrami-operator}}

Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
corresponds to a sum of the areas of the quad faces $A\left(Q_{i}\right)$
and the areas of the triangular faces $\ensuremath{A\left(T_{i}\right)}$
adjacent to vertex $\ensuremath{v_{i}}$.

\noindent \begin{center}
$A\left(v_{i}\right)=A\left(Q_{i}\right)+A\left(T_{i}\right)$ 
\par\end{center}

\begin{figure}[H]
\includegraphics[width=1\columnwidth]{resources/figs/quad_xiong}

\caption{\label{fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
Triangulations of the quad with common vertex $v_{i}$ proposed by
{[}Xiong 2011{]} to define Mean LBO.}
\end{figure}

Applying the mean average area, according to Xiong et. al. \cite{Xiong2011},
from all possible triangulations, as show in figure \ref{fig:quad_xiong},
the area for quads $\ensuremath{A\left(Q_{i}\right)}$ and triangles
$A\left(T_{i}\right)$ is.

\noindent \begin{center}
$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$ 
\par\end{center}

Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{i}$ are quads adjacent
to $v_{i}$, and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{i}$ are triangles
adjacent to $v_{i}$.

Applying triangulations of the quad with common vertex $v_{i}$ proposed
by \cite{Xiong2011}.

\noindent 
\begin{equation}
A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{eq:area_1_ring_triangles_quads}
\end{equation}

Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).

\noindent {\small 
\begin{equation}
\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
\end{equation}
}{\small \par}

According to (\ref{eq:eq_gradient_voronoi_area}), we have.

\noindent \begin{center}
$\nabla A\left(t_{j1}^{*}\right)=\frac{\cot\theta_{j3}\left(v_{j}-v_{i}\right)+\cot\theta_{j2}\left(v_{j}^{\prime}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{j2}^{*}\right)=\frac{\cot\theta_{j5}\left(v_{j}^{\prime}-v_{i}\right)+\cot\theta_{j4}\left(v_{j+1}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{j3}^{*}\right)=\frac{\cot\theta_{j6}\left(v_{j}-v_{i}\right)+\cot\theta_{j1}\left(v_{j+1}-v_{i}\right)}{2}$ 
\par\end{center}

\noindent \begin{center}
$\nabla A\left(t_{k}\right)=\frac{\cot\alpha_{k}\left(v_{k}-v_{i}\right)+\cot\beta_{k+1}\left(v_{k+1}-v_{i}\right)}{2}$ 
\par\end{center}

Triangle and quad configurations of the 1-ring neighborhood faces,
adjacent to $v_{i}$, can be simplified to five cases, as shown in
figure \ref{fig:LBO-basic-5-TQ}.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/beltrami}

\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO) our contribution.}

\end{figure}

According to equation (\ref{eq:discrete_mean_curvature_normal}),
(\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.

\noindent 
\begin{equation}
\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
\end{equation}

\noindent {\small where
\begin{equation}
w_{ij}=\begin{cases}
\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
\end{cases}\label{eq:TQLBO_wij}
\end{equation}
}{\small \par}

We define a Laplacian operator as a matrix equation

\noindent 
\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N\left(v_{i}\right)\\
\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
0 & \mbox{otherwise}
\end{cases}\label{eq:TQLBO_Simple_Matrix}
\end{equation}

Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

Normalized version of the TQLBO as a matrix equation

\noindent 
\begin{equation}
L\left(i,j\right)=\begin{cases}
-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
\delta_{ij} & \mbox{otherwise}
\end{cases}\label{eq:TQLBO-Normalized_Matrix}
\end{equation}

Where $\delta_{ij}$ being the Kronecker delta function.

\section{Mesh Smoothing\label{sub:Laplacian-Smooth}}

Computer objects, reconstructed from the real world, are usually noisy.
A common way to attenueate noise in a polygonal mesh is through a
diffusion process \cite{Taubin1995,Desbrun1999}. Laplacian smooth
techniques over a diffusion process allow a proper noise reduction
on the mesh surface with minimal shape changes, while still preserving
a desirable geometry as well as the original shape. The simple idea
is that the vertices are moved in the direction of the Laplacian when
we use the contangent version the vertices are moved in the direction
of the curvature flow. The complexity of Laplacian smoothing can be
linear in time and space with a fast convergence and the diffussion
proccess can attenuate noise with only one iteration due the sparseness
of the laplacian operator.

\noindent 
\begin{equation}
\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
\end{equation}

Where L is the Laplacian matrix defined in equation \ref{eq:TQLBO-Normalized_Matrix}
for meshes with regular sampling, and equation \ref{eq:TQLBO_Simple_Matrix}
for meshes composed by triangles or quads with differents size or
irregular sampling. $\lambda$ is a scalar that control the diffussion
proccess, and smoothing factor.

The equation \ref{eq:diffusion_process} can be linearly approximated
using implicit integration with a Laplacian Operator version of TQLBO,
the use of implicit integration permit the system to be more stability.

\begin{equation}
\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
\end{equation}

\section{The Shape Inflation\label{sub:Curvature-Enhancing}}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/teaser_cup}

\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
Subdivision (b), (d), is inflated. Soft constraints, over the coarse
model, is drawn in red and blue (c).}
\end{figure}

This method exaggerates a shape using a Laplacian smoothing operator
in the reverse direction, i.e., the new shape is a modified version
in which those areas with larger curvature are magnified. The operator
amounts to a generator of a set of models which conserves the basic
silhouette of the original shape. In addition, the presented approach
can be easily mixed with traditional or uniform subdivision of surfaces.

The shape is inflated by using the reverse direction of the curvature
flow, moving the vertices towards those mesh portions with larger
curvature. A standard diffusion process is applied:

\noindent \begin{center}
$\frac{\partial V}{\partial t}=\lambda L\left(V\right)$ 
\par\end{center}

To solve this equation, implicit integration is used as well as a
normalized version of TQLBO matrix.

\noindent 
\begin{equation}
\left(I-\left|\lambda dt\right|W_{p}L\right)V^{\prime}=V^{t}\label{eq:Lineal_System_with_wp}
\end{equation}

\noindent \begin{center}
$V^{t+1}=V^{t}+\mbox{sign}\left(\lambda\right)\left(V^{\prime}-V^{t}\right)$ 
\par\end{center}

The vertices $V^{t+1}$ are inflated, along their reverse curvature
direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with vertex weights,
and $\lambda dt$ is the inflate factor that supports negative and
positive values: negative for inflation and positive for smoothing.

The method was devised to use with weighted vertex groups, which specify
the final shape inflation of the solution, meaning $0$ as no changes
and 1 when a maximal change is applied. The weights modify the influence
zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
Interestingly, the generated family of shapes may change substantially
with the weights of specific control points.

The curvature cannot be calculted at the boundary of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by Desbrun et al. \cite{Desbrun1999}, the inflation factor
for boundary is represented by $\lambda_{e}$.

The model volume increases as the lambda is larger and negative, this
can be counteracted with a simple volume preservation. However, the
mesh may suffer large displacements when $\lambda<-1.0$ or after
multiple iterations. A simple volume conservation algorithm is: If
$v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
we define $\overline{v}$ as:

\noindent \begin{center}
$\overline{v}=\frac{1}{n}\underset{v_{i}\in V}{\sum}v_{i}$, 
\par\end{center}

$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
factor.

\noindent \begin{center}
$\beta=\left(\frac{vol_{ini}}{vol_{t+1}}\right)^{\frac{1}{3}}$ 
\par\end{center}

allows to scale the vertices to:

\noindent \begin{center}
$v_{i\, new}^{t+1}=\beta\left(v_{i}^{t+1}-\overline{v}\right)+\overline{v}$ 
\par\end{center}

The shape inflation use a negative curvature flow that is an unstable
process when performing many iterations, however, our method uses
less than 3 iterations to get good results, and with 3 iterations
or less the method behaves stable.

\section{Sculpting\label{sub:Sculpting}}

A new sculpting brush is herein proposed and aims to inflate the shape,
magnifying the shape curvatures of a polygon mesh in real time. This
brush works properly with the stroke method \textsl{Drag Dot}, allowing
to pre-visualize the model changes before the mouse is released. Also,
it allows to move the mouse along the model to match the shape zone
which is supposed to be inflated.

Brushes that perform a similar inflation can introduce mesh distortions
or produce mesh self-intersections, provided these brushes only move
the vertices along the normal without any global information. In contrast,
the present method searches for a proper inflation while preserving
the global curvature, retaining the original shape and main model
features. In addition, this method simplifies the work required for
the inflation since it needs not different brushes for inflating,
softening or styling. The inflated brush can make all these operation
in a single step. Real-time brushes require the Laplacian matrix is
constructed with the vertices that are within the sphere radius defined
by the user, reducing the matrix to be processed, the center of this
sphere depending on the place where the user clicks on the canvas
and the three-dimensional mesh placed where the click is projected.
Special handling is required for the boundary vertices with neighbors
that are not within the brush radius: these vertices are marked as
boundary and the curvature is not there calculated, but they must
be included in the matrix so that every vertex has their corresponding
neighbors within the selection. The sculpting Laplacian matrix reads
as.

\noindent \begin{center}
$L\left(i,j\right)=\begin{cases}
-\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert <r\\
0 & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert \geq r\\
\delta_{ij} & \mbox{otherwise}
\end{cases}$ 
\par\end{center}

Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center of
radius $r$. The matrices should remove rows and columns of vertices
that are not within the radius.

\section{Laplacian Deform\label{sub:Laplacian-Deform}}

The Laplacian deform allows to pose a mesh while preserving geometric
details of the surface. This method allows to defines a set of anchor
vertices, and then moves some of them around. The system keeps the
rest of the anchor vertices in fixed positions, and calculates the
best possible locations of all the remaining vertices to preserve
the original geometric details.

This thesis adapt the method proposed by Sorkine \cite{Sorkine2004}
for mesh deformations, delete the use of static vertices and allow
application of this system in hybrid meshes composes by triangles
and quads with the TQLBO proposed.

This method captures the geometric details using a differential coordinates
representations. The differential coordinates captures the local geometric
information (curvature and direction) of the vertex based on its neighbors
how show in figure \ref{fig:DifferentialCoor}.

\begin{figure}
\noindent \begin{centering}
\includegraphics[width=0.7\columnwidth]{resources/figs/DifferentialCoordinates}
\par\end{centering}

\caption{\label{fig:DifferentialCoor} Difference between $v_{i}$ and the
center of mass of its neighboors $v_{1},...,v$.}
\end{figure}

\begin{equation}
\delta_{i}=\overset{m}{\underset{j=1}{\sum}}w_{ij}\left(v_{i}-v_{j}\right)\label{eq:DifferentialCoordinate}
\end{equation}

Where $\delta_{i}$ is the differential coordinate for vertex $v_{i}$.
The $v_{j}$ are the inmediate neighoors of $v_{i}$, and $w_{ij}$
is the weigth betwen vertex $v_{i}$ and $v_{j}$ defined in equation
\ref{eq:TQLBO_wij} that is TQLBO.

Then the linear systems for find the new pose of a mesh is.

\begin{equation}
\begin{bmatrix}w_{l}L\\
W_{c}
\end{bmatrix}X=\begin{bmatrix}\delta\\
W_{c}C
\end{bmatrix}\label{eq:LaplacianDefomSystem}
\end{equation}

Where $w_{l}$ is the weigth for Laplacian Matrix $L$, the Laplacian
matrix $L$ was defined in equation \ref{eq:TQLBO_Simple_Matrix}
. $Wc$ is a matrix that containts ones int the indexes of anchors
vertices. $C$ is a vector with coordinates of anchors vertices after
several transformatios. $\delta$ are the differential coordinates
defined in equation \ref{eq:DifferentialCoordinate}.

\section{Subdivision surfaces\label{sub:Subdivision-surfaces}}

The Catmull-Clark subdivision transformation is used to smooth a surface,
as the limit of a sequence of subdivision steps \cite{Stam1998}.
This process is governed by a B-spline curve \cite{Loop1987}, performing
a recursive subdivision transformation that refines the model into
a linear interpolation that approximates a smooth surface. The model
smoothness is automatically guaranteed \cite{DeRose1998}.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/cruz_lambda4}

\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
Subdivision. Models with Laplacian smoothing: (c) and (d). Models
with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
and before applying shape inflation: (e) and (f).}
\end{figure}

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce quick results because of the
simplicity of implementation. Nevertheless, changes to the global
curvature are hardly implantable. The Catmull-Clark subdivision surfaces
together with shape inflation can easily generate families of shapes
by changing a single parameter, allowing to handle a model with very
few vertices. In practice, this would allow an artist to choose a
model from a similar set of options that would meet his/her needs
without having to change each of the control vertices. Likewise, the
presented method allows the use of vertex weight paint over the control
points. The weights can be applied to a coarse model, followed by
a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the influence zones, as shown in figure
\ref{fig:Subdivision-Cups}.c.

In equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
matrix with weights corresponding to each vertex. Weights at each
vertex produce a different solution so that the matrix must be placed
in the diffusion equation since families that are generated may change
substantially with weighted of specific control points.

\section{Skeleton Extraction}

Skelton extraction reduces the dimensionality and represents a three-dimensional
object as a uni-dimensional structure \cite{Cornea2007}.

The skeleton extraction use the natural shrink produced by the laplacian
smoothing \cite{Meyer2003}, to contratc iteratively the mesh until
the volume inside the surface is near to zero (see figure \ref{fig:MeshContracted}).
The method stretch the shrink mesh to warranty that object preservers
the best at posibble the original topology with the use of attraction
constraint \cite{Au2008}.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/contraccion}

\caption{\label{fig:MeshContracted}From left to right iterative mesh contraction.}
\end{figure}

The laplacian smooth proccess move the vertices in the direction of
the Laplacian, if cotangent laplacian operator is used, the vertices
move in the direction of minimal surface \cite{Pinkall1993} following
the curvature flow of the mesh surface.

In the work of Au \cite{Au2008} is proposed the next system of equation
to iteratively contratc the mesh until a skeleton.

\begin{equation}
\left[\begin{array}{c}
W_{L}L\\
W_{H}
\end{array}\right]X_{t+1}=\left[\begin{array}{c}
0\\
W_{H}X_{t}
\end{array}\right]\label{eq:SkeletonExtraction}
\end{equation}

where $L$ is the Laplacian matrix describe in equation \ref{eq:TQLBO_Simple_Matrix},
$W_{L}$ is the factor for smoothing, $W_{H}$ is the factor for attraction
constraint.

$W_{L}$ and $W_{H}$ are changing in every iteration. The contraction
and smoothing constraint $W_{L}^{t+1}=S_{L}W_{L}^{t}$ with $S_{L}=2.0$.
The attraction constraint $W_{H,i}^{t+1}=W_{H,i}^{0}\sqrt{\frac{A_{i}^{0}}{A_{i}^{t}}}$.

$A_{i}^{t}$ y $A_{i}^{0}$ are the current area and initial aerea
of the ring surrounding $x_{i}$.

In this thesis an additional constraint is proposed which seeks the
vertices and the skeleton does not shrink, to eliminate the need to
adjust the final skeleton taking each skeleton node and move to the
center of your local mesh region.

The basic idea is move the vertices along of the normal line estimated
on every vertex based on the avergage of the faces normals.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/LineConstraintSkeleton}

\caption{\label{fig:LineConstraint}Left: The vertex $x_{i}$ move along line
constraint. Right: the distance of vertex $x_{i}$ to plane 1 and
plane 2 when change the position in every iteration.}
\end{figure}

This line can be see as intersection of two planes (see figure \ref{fig:LineConstraint})
created with the information of the vertex $x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$
and neighboors $x_{j}$ of $x_{i}$.

The equation of the plane.

\noindent \begin{center}
$a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}=0$
\par\end{center}

There is varios methods to build a equation of the plane based on
three non-collinear points, we choose this three points based on vertex
$x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$ and neighboors
$x_{j}$ of $x_{i}$.

$P_{1}=x_{i}$, $P_{2}=x_{j}$ when $x_{j}\in Neighboors\left(x_{i}\right)$
and $P_{3}=P_{1}-\overrightarrow{\mathbf{n}_{i}}$.

To build a equation plane only need three non-collinear points $\left\{ P_{1},P_{2},P_{3}\right\} $
and solve the next systems of equations for variables $a,b,c$.

\noindent \begin{center}
$\begin{array}{c}
ax_{1}+by_{1}+cz_{1}+d=0\\
ax_{2}+by_{2}+cz_{2}+d=0\\
ax_{3}+by_{3}+cz_{3}+d=0
\end{array}$
\par\end{center}

The distance of point $P_{0}=\{x_{0},y_{0},z_{0}\}$ to a plane $\Pi=a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}$.

\noindent \begin{center}
$\left|\Pi-P_{0}\right|=\frac{\left|ax_{0}+by_{0}+cz_{0}+d\right|}{\sqrt{a^{2}+b^{2}+c^{2}}}$
\par\end{center}

In the equation above, every point $P_{0}=\{x_{0},y_{0},z_{0}\}$
that belong to plane made the equation zero. If the point $P_{0}$
is not in the plane the value of the equation of the plane change,
and the absolute value is increased if $P_{0}$ is more distant of
the plane. Let us use this simple relation to build a valid constraint
that can be put in the form of linear equation $Ax=B$. Where $A$
is the matrix with values $\begin{vmatrix}a & b & c\end{vmatrix}$
the $x$ value correspond to every vertex in mesh $\{x_{0},y_{0},z_{0}\}$
and $B$ correspond to $d$ value of the plane equation. How the linear
system presented in equation \ref{eq:SkeletonExtraction} don't has
a unique solution, the system solve it in the least-squares sense.
With the new constraint the system then try to minimize the distance
betwen the new vertex positions and the two planes.

The new system of equations proposed

\begin{equation}
\left[\begin{array}{c}
W_{L}L\\
W_{H}\\
W_{D}\Pi_{1}\\
W_{D}\Pi_{2}
\end{array}\right]X_{t+1}=\left[\begin{array}{c}
0\\
W_{H}X_{t}\\
-D_{1}\\
-D_{2}
\end{array}\right]\label{eq:SkeletonExtractionDistance}
\end{equation}

where $W_{D}$ is the weigth to new constraints, that forced the vertices
to move along of the normal line of every vertex. $\Pi_{1}$ and $\Pi_{2}$
are matrix that contains $a,b,c$ values of the equation of the plane
for every vertex. $D_{1}$ and $D_{2}$ are the vector with $d$ values
of the equations of the planes for every vertex.

\chapter{Results\label{sec:Results}}

This chapter show the results of the Laplace Beltrami operator for
hybrid quad/triangle meshes with several example models (see figures
\ref{fig:Spectrum}, \ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark},
\ref{fig:TQLBO_test}, \ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush},
\ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}).
It first show a comparisson of the Laplacian Operator in meshes composed
by triangles, by quads and hybrid meshes composed by triangles/quads.
Section \ref{sec:Customizing-Curvature-by} show the use of TQLBO
in applications of Shape Inflation and Subdivision Surfaces on normal
meshes and meshes change with isometric transformations. It Section
\ref{sec:Shape-Inflation-Brush} show a novel shape inflation brush
for sculpting systems that works in real time. It Section \ref{sec:Posing-Meshes-with}
show mesh deformations and posing applications using differential
coordinates defined with the TQLBO. It Section \ref{sec:Laplace-Operator-and}
discusses the differences betwen common version and normalized version
of the TQLBO. It Section \ref{sec:Performance-Testing-of} describe
a performance comparison of differents numericals solvers used to
solve a Laplacian linear equation system. Finally discusses some especific
technical aspect about the implementation of the TQLBO on several
computer systems at Section \ref{sec:Conclusion-and-future}.

Figure \ref{fig:TQLBO_test} shows the results when applying the Laplace
Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) the Laplacian
smoothing was applied to a model consisting of only quads. In column
(d) the model was converted to triangles and then the Laplacian smoothing
was applied. In column (e) the model was randomly converted from some
quads into triangles and then the Laplacian smoothing is applied,
showing similar results to those meshes composed only of triangles
or quads.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[height=0.5\textheight]{resources/figs/test_triangles_quads}
\par\end{centering}

\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
(c) for triangles, (d) for quads, (e) for triangles and quads random
chosen.}
\end{figure}

\section{Customizing Curvature by Shape Inflation.\label{sec:Customizing-Curvature-by}}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/spectrum}

\caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
$-5.0$.}
\end{figure}

The shape inflation was assessed with TQLBO method on a PC with AMD
Quad-Core Processor @ 2.40 GHz and 8 GB RAM.

Methods using the Catmull-Clark subdivision surface and the inflation
allows to modify the curvature that is obtained with the process of
subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
test used a coarse cup model, in which the subdivision was performed,
followed by a Laplacian smoothing and inflation. In figure \eqref{fig:Subdivision-Cups}.c,
\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
groups over coarse models, with subdivision surfaces that allowed
to generate the weights for the new interpolated vertices. These new
weights were used for the inflation obtained on the 6 cups that are
at the right of the figure \eqref{fig:Subdivision-Cups}.d.

Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
may produce similar results to those obtained with Catmull-Clark (see
figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
triangles. The one obtained with the Laplacian smoothing is shown
in panel (c), (d) and those curvature modified versions are in (e)
and (f). As can be observed, different versions of the original sketch
can be obtained by parameterizing a single model value, a great advantage
of the presented method. Figure \ref{fig:camello_enhanced} shows
the generation of different versions of a camel according to the $\lambda$
parameter. In the top row, it is shown the shape inflation results,
as $\lambda$ becomes larger and negative, the resultant shape is
observed as if the model would inflate the more convex parts, as shown
in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
the larger the model feature inflations. The bottom row of figure
\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
specifying which areas will be inflated. On the left, the inflation
of the camel legs produces an organic aspect, notice that the border
is not distorted and smooth.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[height=0.5\textheight]{resources/figs/camello_enhanced2}
\par\end{centering}

\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
Bottom row: Shape inflation with weight vertex group, $\lambda=-50.0$
and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
the head and neck.}
\end{figure}

The inflation of the silhouette features is predictable and invariant
under isometric transformations, as those classically used in some
animations (see Figure \ref{fig:Animated_Camell}). In this figure,
the animation shows some camel poses during a walk, the inflation
is performed at the neck and legs, as shown in the bottom left camel
in figure \ref{fig:Animated_Camell}. Local modifications produced
by the pose interpolation or animation rigging practically do not
affect the result. In spite of at any pose of the camel legs there
is a clear difference, the inflation method allows a flesh-like shape
in the original pattern produced by the artist. This is due to the
mesh restricted diffusion process so that small local changes are
treated without affecting the global solution. The method therefore
is rotation invariant since it depends exclusively on the normal mesh
field, which is rotation invariant.

\begin{figure}[H]
\includegraphics[width=1\textwidth]{resources/figs/camello_walk2}

\caption{\label{fig:Animated_Camell}The method is pose insensitive. The inflation
for the different poses are similar in terms of shape. Top row: Original
walk cycle camel model. Bottom row: Shape inflation with weight vertex
group, $\lambda=-400$ and $2$ iterations. }
\end{figure}

\section{Shape Inflation Brush in Real Time\label{sec:Shape-Inflation-Brush}}

Figure \ref{fig:Sculpt_Brush} shows the use of a shape inflation
brush for sculpting in real time. One pass was used with the brush,
as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
the camel foot shows the inflation intersection that looks like two
bubbles, a similar pattern to what is observed to the fingers on the
bottom of the same figure. The silhouette inflation is observed in
figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
together with its finger and foot details. Similar results can be
obtained by a user, however it would take several steps and require
the use of several brushes, while the shape inflation took a single
step. Likewise, this new method can easily inflate organic features
like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
the shape inflation brush performance is illustrated, in this experiment
three models with 12K, 40K and 164K vertices, were used. These models
were sculpted with the shape inflate brush, at each step the brush
sphere containing a variable number of vertices for processing. The
processing time for 800 vertices in the camel paw (40k model) only
took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
took 0.5 seconds, these times are suitable in real applications since
an artist sculpts a model for parts.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[height=0.3\textheight]{resources/figs/sculpt_brush}
\par\end{centering}

\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
for leg into blue circle, (c) Inflate shape brush for leg into red
circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
circle, (c) Shape inflation brush for fingers in red circle.}
\end{figure}

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[width=1\columnwidth]{resources/figs/verts_per_second_sculpt}
\par\end{centering}

\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape inflation
brush in terms of the sculpted vertices per second. Three models with
12K, 40K, 164K vertices used for sculpting in real time.}
\end{figure}

\section{Posing Meshes with Laplacian Deform\label{sec:Posing-Meshes-with}}

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{resources/figs/Armadillo}
\par\end{centering}

\caption{\label{fig:Armadillo}Anchor vertices in blue color. (a) Original
Model, (b,c,d) new poses change only anchor vertices, system find
positions for vertices in yellow color.}
\end{figure}

Figure \eqref{fig:Armadillo} shows the Laplacian Deform applied in
a model with 173K vertices, only anchor vertices was used and are
represented in blue color, when the user apply several transformation
(location, rotation, scale) over this anchors vertices, the system
find a solution and estimate the position of the vetices in yellow
color. This method work in real time, to achieve this the matrix $\begin{bmatrix}w_{l}L\\
W_{c}
\end{bmatrix}$ in the equation \eqref{eq:LaplacianDefomSystem} is decomposed in
matrix $LU$ with LU factorization only one time when the system init.
Once the matrix is factorized the system can solve the unknowns in
a fast way in term of miliseconds. For get better results the method
permits solve several times the system of equations, and not need
factorize matriz LU could be that at every iteration, only the differential
coordinates are adjust since the differential coordinates can be rotated
at every iteration and get bettter results. In the figure only four
iterations were used, but the system find good solutions with only
one iteration when the angle of rotations are less that $\pi$.

\section{Laplace Operator and Normalized Version \label{sec:Laplace-Operator-and}}

Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
produce similar results if the triangles or quads that compose the
mesh are about the same size. The normalized version is more stable
and predictable because it is not divided by the area of the ring
which may be very small and causes numeric problems, as shown in figure
\ref{fig:(a)Monkey}.c bottom row. The shape inflation of the model
with the normalized Laplacian operator results in a more regular pattern.
The model can be deformed with a TQLBO normalized version with large
$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
areas in the model. Quadss with larger area have smaller inflation
(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
inflations (figure \ref{fig:(a)Monkey}.c chin).

\begin{figure}[H]
\includegraphics[width=1\columnwidth]{resources/figs/monkey}

\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
model scaled by 4. (b) Top and bottom row: inflating with Normalized-TQLBO
$\lambda=-50$ (c) Top and bottom row: inflating with TQLBO $\lambda=-50$.}
\end{figure}

\section{Skeletonizer}

Skeletonizer is a product of software that permits the proccessing,
visualization and extraction of the skeleton from polygonal meshes.
The software was designed with base in a plugin system and pipe-filters
paradigm. This software implement the method for skeleton extraction
describe in equation \ref{eq:SkeletonExtractionDistance}.

The software is called sjSkeletonizer and use the following computacional
frameworks and libraries.
\begin{description}
\item [{CGAL}] Computational Geometry Algorithms Library \cite{cgal}.
\item [{Graphite}] is a research platform for computer graphics, 3D modeling
and numerical geometry \cite{graphite}.
\item [{QT}] is a cross-platform application and UI framework \cite{qt}.
\end{description}
\begin{figure}
\includegraphics[width=1\textwidth]{resources/figs/poses}

\caption{\label{fig:Skeleton-extraction-poses} Model with different poses
and skeleton obtained with our skeleton extraction software.}

\end{figure}

\section{Performance Testing of Solvers \label{sec:Performance-Testing-of}}

Performance evaluation of some numerical solvers for compute Laplacian
Smooth system.

Linear equation system to solve

$\frac{\partial V}{\partial t}=\lambda L\left(V\right)$

Integrating the diffusion equation with a explicit Euler scheme

$\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}$

Where $V^{n+1}$ is the actual position of vertices, and $V^{t+1}$
are the vertices after Laplacian Smoothing. $\lambda\partial t$ is
the smoothing factor. L is the Laplacian Matrix defined in equation
\ref{eq:TQLBO_Simple_Matrix}.

Solving the sparse linear system

$Ax=b$

Where:

$A=\left(I-\lambda\partial tL\right)$

$x=V^{n+1}$

$b=V^{n}$

\subsection{Hardware Specification }
\begin{itemize}
\item Processor: AMD Quad-Core 2.40 GHz 
\item RAM: 8.0 GB 
\item OS: Windows 7 Professional 
\item Graphics controller: NVIDIA Quadro FX 570
\end{itemize}

\subsection{Software Specification }
\begin{description}
\item [{CGAL}] Computational Geometry Algorithms Library 
\item [{Graphite}] Research platform for computer graphics
\end{description}

\subsection{Numeric Solvers Used }
\begin{description}
\item [{CG:}] Conjugate gradient method. 
\item [{BICGSTAB:}] Biconjugate gradient stabilized method. 
\item [{GMRES:}] Generalized minimal residual method. 
\item [{SUPERLU:}] Sparse Direct Solver, LU decomposition with partial
pivoting. 
\item [{TAUCS\_LDLT:}] A library of sparse linear solvers with LDLT factorization. 
\item [{CHOLMOD:}] Supernodal sparse Cholesky factorization. 
\end{description}
LU factorization is a numerical method that works with large, sparse,
nonsymmetric systems of linear equations \cite{Levy2005}. We choose
the implementacion of LU factorizacion in a OpenNL-SuperLU library,
because this method show the better performance for the computacion
of a solution for a Laplacian Smoothing linear system of equations
presented in equation \ref{eq:LaplacianSmoothLinearEquationSystem}
how see in the table \ref{tab:TimeVsSolvers}. OpenNLSuper allow works
with the Graphics Unit Proccesor GPU, for exploit the capacity of
GPU to work with parallel structures, more fast that traditional CPU.

\begin{table}[H]
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline 
Model & Vertices & CG & BICGSTAB & GMRES & SUPERLU & TAUCS & CHOLMOD\tabularnewline
\hline 
\hline 
Cross & 24 & 0.05 & 0.05 & 0.04 & 0.04 & 0.05 & 0.05\tabularnewline
\hline 
King & 538 & 0.83 & 0.63 & 0.71 & 0.61 & 0.68 & 0.79\tabularnewline
\hline 
YModel & 4770 & 19.60 & 16.44 & 16.93 & 16.06 & 16.88 & 17.95\tabularnewline
\hline 
Man & 10002 & 33.43 & 27.76 & 29.91 & 28.54 & 29.53 & 30.80\tabularnewline
\hline 
Neptune & 28052 & 133.97 & 136.46 & 136.39 & 133.21 & 142.87 & 142.76\tabularnewline
\hline 
Armadillo & 34594 & 194.48 & 174.88 & 175.80 & 169.92 & 181.70 & 183.49\tabularnewline
\hline 
\end{tabular}

\caption{\label{tab:TimeVsSolvers}Vertices Vs Seconds, Laplacian Smoothing
performance.}
\end{table}

\begin{figure}[H]
\includegraphics[width=1\textwidth]{Data/Benchmark}

\caption{asdas}

\end{figure}

\section{Implementation\label{sec:Implementation}}

The method was implemented as a modifier for modeling and brush for
sculpting, on the Blender software \cite{blender} in C and C++. Working
with the Blender allowed to test the method interactively against
others, as Catmull-Clark, weight vertex groups and sculpting system
in Blender.

To improve the performance, it was worked with the Blender mesh struct,
visiting each triangle or quad and storing its corresponding index
and the sum of the Laplacian weights of the ring in a list so that
only two visits were required for the list of mesh faces and two times
the edge list, if the mesh was not closed. This drastically reduced
calculations, enabling real-time processing. In the construction of
the Laplacian matrix, several index were locked at vertices having
face areas or edge lengths with zero value that could cause spikes
and bad results.

Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
is sparse since the number of neighbors per vertex, corresponding
to the number of data per row, is smaller compared to the total number
of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
was used OpenNL which is a a library for solving sparse linear system.

\chapter{Conclusion and future work\label{sec:Conclusion-and-future}}

This work presented an extension of the Laplace Beltrami operator
for hybrid quad/triangle meshes that can be used in production environments
and provides results similar to those obtained by working only with
triangles or quads. This paper has introduced a new way to change
silhouettes in a mesh for modeling or sculpting in a few steps by
means of the curvature model modification while preserving its overall
shape. In addition, a new modeling method has also been presented
some possible applications have been illustrated. The method works
properly with isometric transformations, opening the possibility of
introducing it on the process of animation.

We show that this tool may work in early modeling stages, case in
which coarse models are used, allowing to modify the shape generated
by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
of the vertices with change of a single parameters.

Future work includes the analysis of theoretical relationships between
the Catmull-Clark subdivision surfaces and the Laplacian smoothing
since they can produce very similar results.

\bibliographystyle{plain}
\addcontentsline{toc}{chapter}{\bibname}\bibliography{bibliografia/listado_inicial,TQLBO-paper/template,D:/src/blender/GSoC/GSOC2013/bibliography_mesh_editing,SIBGRAPI2013/template}

\end{document}

### 2014-06-11 documents/thesis/Capitulo_4.tex

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[12pt,letterpaper,english,12pt,english,openany,letterpaper,pagesize]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{float}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{setspace}
\onehalfspacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\pdfpageheight\paperheight
\pdfpagewidth\paperwidth

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\documentclass[12pt,spanish,fleqn,openany,letterpaper,pagesize]{scrbook}

%\usepackage[ansinew]{inputenc}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{eepic}
\usepackage{amsmath}
\usepackage{threeparttable}
\usepackage{amscd}
\usepackage{here}
\usepackage{graphicx}
\usepackage{lscape}
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{longtable}

\usepackage{rotating} %Para rotar texto, objetos y tablas seite. No se ve en DVI solo en PS. Seite 328 Hundebuch
                        %se usa junto con \rotate, \sidewidestable ....

\renewcommand{\theequation}{\thechapter-\arabic{equation}}
\renewcommand{\thefigure}{\textbf{\thechapter-\arabic{figure}}}
\renewcommand{\thetable}{\textbf{\thechapter-\arabic{table}}}

\pagestyle{fancyplain}%\addtolength{\headwidth}{\marginparwidth}
\textheight22.5cm \topmargin0cm \textwidth16.5cm
\oddsidemargin0.5cm \evensidemargin-0.5cm%
\renewcommand{\chaptermark}[1]{\markboth{\thechapter\; #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\; #1}}
\lhead[\fancyplain{}{\thepage}]{\fancyplain{}{\rightmark}}
\rhead[\fancyplain{}{\leftmark}]{\fancyplain{}{\thepage}}
\fancyfoot{}
\thispagestyle{fancy}%

\addtolength{\headwidth}{0cm}
\unitlength1mm %Define la unidad LE para Figuras
%\mathindent0cm %Define la distancia de las formulas al texto,  fleqn las descentra
\marginparwidth0cm
\parindent0cm %Define la distancia de la primera linea de un parrafo a la margen

%Para tablas,  redefine el backschlash en tablas donde se define la posici\'{o}n del texto en las
%casillas (con \centering \raggedright o \raggedleft)
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

%Espacio entre lineas
\renewcommand{\baselinestretch}{1.1}

%Neuer Befehl f\"{u}r die Tabelle Eigenschaften der Aktivkohlen
\newcommand{\arr}[1]{\raisebox{1.5ex}[0cm][0cm]{#1}}

%Neue Kommandos
\usepackage{resources/Befehle}

%Trennungsliste
\hyphenation {Reaktor-ab-me-ssun-gen Gas-zu-sa-mmen-set-zung
Raum-gesch-win-dig-keit Durch-fluss Stick-stoff-gemisch
Ad-sorp-tions-tem-pe-ra-tur Klein-schmidt
Kohlen-stoff-Mole-kular-siebe Py-rolysat-aus-beu-te
Trans-port-vor-gan-ge}

%\pagenumbering{roman}
%\let\myTOC\tableofcontents
%\renewcommand\tableofcontents{%
%\myTOC
%\clearpage
%\pagenumbering{arabic}
%}

\makeatother

\usepackage{babel}
\begin{document}

\chapter{Mesh smoothing based on curvature flow operator in a diffusion equation\label{sub:Laplacian-Smooth}}

This work was accepted as part of the software Blender \cite{blender},
an open source 3D application for modeling, animation, rendering,
compositing, video editing and game creation. The work was supported
by an awarded internship of the Google Summer of Code 2012 program,
administered for Google Inc.

\section{Synopsis}

Computer graphics objects reconstructed from real world contain undesirable
noise. A Mesh smoothing removes undesirable noise while still preserving
desirable geometric and shape of the original model.

This project improving the mesh smoothing tools in blender, based
on curvature flow operator in a diffusion equation.

This project allows working with hybrid meshes composed by triangles
and quads based on Laplacian operator proposed by Pinzón and Romero
\cite{Pinzon2013}.

\section{Benefits to Blender}

This project proposes a new and robust mesh smoothing tool for blender
user that require improves the appearance of surfaces models.

New methods to scan computer graphics objects using the Kinect ZCam
within Blender, need to remove the noise present at the time of capture.

This mesh smoothing method produce higher quality results without
shrinkage. The smoothing tool current collapses the mesh after several
iterations.

This mesh smoothing method permit uses a hard and soft constraints
on the positions of the points in the mesh to maintain control over
the shape.

This mesh smoothing method can help to remove noise generated during
the sculpting, without removal the desired details of the model.

\section{Deliverables }

A new and robust mesh smoothing tool for Blender.

Some pages of documentation to be included in the manual.

A technical document for developers to improve the method in the future.

A tutorial explaining the use of the tool.

\section{Project Details }

The project would divide into four parts:

To implement mesh smoothing algorithm based on curvature flow operator
in a diffusion equation for blender geometric structures.
\begin{enumerate}
\item Initialize data and necessary structures. 
\item Compute the Laplacian Matrix. 
\item Define the sparse linear system.
\item Solving the sparse linear system, we can use a preconditioned bi-conjugated
gradient numerical library. 
\end{enumerate}
Integrate or use numerical library present in Blender to solve sparse
linear system

Generation of the documentation and tutorials.

\section{Project Schedule}
\begin{itemize}
\item 3 weeks: Understanding the Blender source code and identify the key
points for the project.
\item 1 week: Define the data structures necessary to work with the architecture
of blender.
\item 1 week: Implement methods for the initial configuration needed for
the smoothing algorithm. Implement the method that calculates the
Laplacian matrix.
\item 2 week: Integrate or use numerical library.
\item 2 week: Define the sparse linear system and implement the method to
solve sparse linear system.
\item 3 weeks: Define and implement graphical user integration.
\item 2 weeks: Testing the tool.
\item 3 weeks: Generation of the documentation and tutorials
\end{itemize}

\section{Mesh Smoothing}

A common way to attenuate noise in a polygonal mesh is through a diffusion
process \cite{Taubin1995,Desbrun1999}. Laplacian smooth techniques
over a diffusion process allow a proper noise reduction on the mesh
surface with minimal shape changes, while still preserving a desirable
geometry as well as the original shape. The simple idea is that the
vertices are moved in the direction of the Laplacian when we use the
cotangent version the vertices are moved in the direction of the curvature
flow. The complexity of Laplacian smoothing can be linear in time
and space with a fast convergence and the diffusion process can attenuate
noise with only one iteration due the sparseness of the laplacian
operator.

\noindent 
\begin{equation}
\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
\end{equation}

Where L is the Laplacian matrix defined in equation \ref{eq:LaplacianMatrixForSmoothing}
for meshes composed by triangles or quads with different size or irregular
sampling. $\lambda$ is a scalar that control the diffusion process,
and smoothing factor.

The equation \ref{eq:diffusion_process} can be linearly approximated
using implicit integration with a Laplacian Operator version of TQLBO,
the use of implicit integration permit the system to be more stability.

\begin{equation}
\left(I-\lambda dtL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
\end{equation}

To permit the user to define the region of interest where the laplacian
smooth to be applied, we add a diagonal matrix $W_{p}$ to equation
\ref{eq:LaplacianSmoothLinearEquationSystem} where the every element
in the diagonal correspond to the weight for every vertex.

\noindent \begin{center}
$\left(I-\lambda dtW_{p}L\right)V^{n+1}=V^{n}$
\par\end{center}

For non-close meshes or meshes with holes is not possible to compute
the curvature flow. For this reason the system smooth the edges differently
within the diffusion process. The boundaries are treated as a one-dimensional
curve. In a curve the Laplacian is defined as the weighted difference
between the vertex and the two immediate neighbors, thus ensures the
curve maintained its original form as much as possible. We define
a Laplacian for mesh smoothing as a matrix equation.

\noindent \begin{center}
\begin{equation}
L(i,j)=\begin{cases}
-\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N(v_{i})\wedge v_{i}\notin\mbox{Boundary}\\
\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\wedge v_{i}\notin\mbox{Boundary}\\
-e_{ij} & \mbox{if }j\in N(v_{i})\wedge\left\{ v_{i},v_{j}\right\} \in\mbox{Boundary}\\
\frac{2}{E_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}e_{ij} & \mbox{if }i=j\wedge\left\{ v_{i},v_{j}\right\} \in\mbox{Boundary}\\
0 & \mbox{otherwise}
\end{cases}\label{eq:LaplacianMatrixForSmoothing}
\end{equation}

\par\end{center}

Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{PAPER:eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $e_{ij}=\frac{1}{\left\Vert v_{i}-v_{j}\right\Vert }$
is the inverse length of the edge between vertices $\left\{ v_{i},v_{j}\right\} $,
$E_{i}=\underset{j\in N\left(v_{i}\right)}{\sum}e_{ij}$. $A_{i}$
is the ring area around $v_{i}$.

\section{Results and Conclusions}

The user interface developed to this tool for the software Blender
can be seen in figure \ref{fig:Interface-LaplacianSmoothing}. This
tool allows to set the parameters of $\lambda$ for interior points
and boundaries. Allows to configure soft constraints using weights
defined by vertices in ``Vertex Group'', and allows you to set strong
constraints applying the algorithm independently of axis X, Y or Z.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics{resources/figs/Apinzonf_Diagram_Modifier_Panel}
\par\end{centering}

\caption{\label{fig:Interface-LaplacianSmoothing}Panel inside blender user
interface of the Laplacian Smooth modifier tool.}
\end{figure}

The tool developed can set the parameter $\lambda dt$ of equation
\ref{eq:LaplacianSmoothLinearEquationSystem}. Using a small Lambda
factor ($\lambda<1.0$), you can remove noise from the shape without
affecting desirable geometry (see figure \ref{fig:Factor-LaplacianSmoothing}.b).
Using a large Lambda factor ($\lambda>1.0$) you get smoothed versions
of the shape at the cost of losing fine geometry details (see figure
\ref{fig:Factor-LaplacianSmoothing}.c and \ref{fig:Factor-LaplacianSmoothing}.d).

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingFactor}
\par\end{centering}

\caption{\label{fig:Factor-LaplacianSmoothing}Noise attenuation in face model
with Laplacian smoothing tool using only one iteration and changing
$\lambda$. (a) Original Model. (b) Smoothing $\lambda=0.5$. (c)
Smoothing $\lambda=2.5$ (d) Smoothing with $\lambda=5.0$. }
\end{figure}

The user can smooth the boundaries configuring the parameter ``\textsl{Border}\textquotedbl{},
seen in figure \ref{fig:Interface-LaplacianSmoothing}. Boundaries
are treated differently. There is no way to calculate the curvature
flow on them. For this reason the Lambda factor ``$Border$'' just
smooths them. The change of this parameter and the results seen in
figure \ref{fig:Border-LaplacianSmoothing}, in the figure you can
see how the boundary inside the red circle is smoothing.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingBoundary}
\par\end{centering}

\caption{\label{fig:Border-LaplacianSmoothing} Smoothing boundary changing
$\lambda_{Border}$ factor. (a) Original Model. (b) Smoothing $\lambda_{Border}=1.0$.
(c) Smoothing $\lambda_{Border}=2.5$ (d) Smoothing with $\lambda_{Border}=10.0$. }
\end{figure}

The tool allows the user to add soft constraints using weights for
each vertex, this allows to define regions of interest where you want
to apply the algorithm in the figure \ref{fig:VertexGroup-LaplacianSmoothing}.c
defined in red region where you want it applied the algorithm the
results are shown in figure \ref{fig:VertexGroup-LaplacianSmoothing}.d
where only were smoothed vertices in the red region.

\begin{figure}[H]
\noindent \begin{centering}
\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingVertecGroup}
\par\end{centering}

\caption{\label{fig:VertexGroup-LaplacianSmoothing}Use of weights per vertex
to constrain the effect of mesh smoothing. (a) Original Model. (b)
Smoothing with $\lambda=1.5$ (c) red vertices $weight=1.0$, blue
vertices $weight=0.0$. (d) Smoothing with $\lambda=2.5$. Red vertices
were only smoothing. }
\end{figure}

Module was developed as a tool for Blender software to remove noise
in the most efficient way as they had been doing.

The methods proposed in the art to remove noise, they could only be
applied if the mesh was composed only by triangles, with the developed
tool artists can now remove the noise of their models composed of
triangles and quadrangles.
\end{document}

### 2014-07-08 trunk/documents/thesis/Capitulo_5.tex

--- 2014-05-13 trunk/documents/thesis/thesis_LO_QT.tex
@@
-%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
+%% LyX 2.1.0 created this file.  For more info, see http://www.lyx.org/.
 %% Do not edit unless you really know what you are doing.
@@
 \usepackage{float}
+\usepackage{textcomp}
 \usepackage{amsthm}
 \usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{setspace}
-\usepackage{esint}
 \onehalfspacing
@@
 \pdfpagewidth\paperwidth
+
+\newcommand{\lyxmathsym}[1]{\ifmmode\begingroup\def\b@ld{bold}
+  \text{\ifx\math@version\b@ld\bfseries\fi#1}\endgroup\else#1\fi}
 
@@
 \begin{document}
-\pagenumbering{roman}
-\begin{center}
-\begin{figure}
-\centering%
-%\includegraphics[width=0.4\columnwidth]{resources/logo_un.png}
-%\includegraphics[width=0.4]{logo_un.png}
-\end{figure}
-\thispagestyle{empty}
 
-\vspace{2cm}
+\chapter{Mesh Editing with Laplacian Deform\label{sub:Laplacian-Deform}}
 
-\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
-Meshes}{\huge \par}
+This work was accepted and completed for the software Blender \cite{blender}
+that is an open source 3D application for modeling, animation, rendering,
+compositing, video editing and game creation. In the Google Summer
+of Code 2013 program which was administered for Google Inc.
 
-\vspace{6cm}
+\section{Synopsis}
 
-\textbf{\large Alexander Pinzón Fernández}{\large \par}
+The mesh editing is generally done with affine transformations, Blender3D
+offers some tools to transform the vertices as \textquotedblleft proportional
+editing object mode\textquotedblright{} with which the transformation
+of some vertices is interpolated to the other vertices connected with
+the use of simple distance functions.
 
-\vspace{6cm}
+This project proposes to implement a method for mesh editing based
+on sketching lines defines by user and preserving the geometric details
+of the surface.
 
-Universidad Nacional de Colombia
+This method captures the geometric details using a differential coordinates
+representations. The differential coordinates captures the local geometric
+information (curvature and direction) of the vertex based on its neighbors.
+This method allows you to retrieve the best possible original model
+after changing the positions of some vertices using the differential
+coordinates of the original model.
 
-Facultad de Ingenieria, Departamento de Sistemas e Industrial
+\section{Benefits to Blender}
 
-{\small Grupo de Investigación CIM@LAB}{\small \par}
+This project proposes a new tool for blender user that requires preserve
+the geometric details of the surface during a modeling, transformation,
+definition of the shape keys of the mesh vertices.
 
-Bogotá, Colombia
+The method will allow novice users to edit any polygon mesh preserving
+the surface details.
 
-2014
+This method allows the user to define new shape keys in a most fast
+and intuitive way.
 
-\end{center}
+\section{Deliverables}
+\begin{itemize}
+\item A new mesh editing tool for Blender. 
+\item Some pages of documentation to be included in the manual 
+\item A technical document for developers to improve the method in the future. 
+\item A tutorial explaining the use of the tool.
+\end{itemize}
 
-\newpage{}
+\section{Project Details}
 
-\begin{center}
-\thispagestyle{empty} 
-\vspace*{0cm}
+The project would divide into several parts:
+\begin{enumerate}
+\item Calculate the differential coordinates. 
+\item Store the fixed vertices (Hard constraints). 
+\item Store positions of the edited vertices. 
+\item Store the more representative vertex for retrieve rotation of every
+differential coordinate.
+\item Solve the initial solution \textendash{} in least-squares sense. 
+\item Rotate the differential coordinates with base on initial solution
+and more representative vertex.
+\item Reconstruct the surface \textendash{} in least-squares sense. 
+\item Generation of the documentation and tutorials.
+\end{enumerate}
 
-\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
-Meshes}{\huge \par}
+\section{Project Schedule}
+\begin{itemize}
+\item 2 Weeks: Calculate the differential coordinates.
+\item 2 Weeks: Store the fixed vertexes (Hard constraints).
+\item 2 Weeks: Store positions of the edited vertexes.
+\item 2 Weeks: Compute initial solution.
+\item 2 Weeks: Rotate differential coordinates.
+\item 2 Weeks: Reconstruct the surface \textendash{} in least-squares sense. 
+\item 1 Weeks: Testing the tool and Define and implement graphical user
+integration.
+\item 2 Weeks: Generation of the documentation and tutorials.
+\end{itemize}
 
-\vspace{2.5cm}
-
-\textbf{\large Alexander Pinzón Fernández}{\large \par}
-
-\vspace{2.5cm}
-
-{\small A thesis submitted in partial fulfillment of the requirements
-for the degree of:}{\small \par}
-
-\textbf{Master in Systems Engineering and Computer Science}
-
-\vspace{2cm}
-
-{\small Advisor:}\\
-{\small Eduardo Romero Castro , Ph.D.}{\small \par}
-
-{\small \vspace{1.5cm}
-}{\small \par}
-
-{\small Research Area:}\\
-{\small Computer Graphics}{\small \par}
-
-{\small \vspace{2cm}
-}{\small \par}
-
-{\small Universidad Nacional de Colombia}\\
-{\small Facultad de Ingenieria, Departamento de Sistemas e Industrial}\\
-{\small Grupo de Investigación CIM@LAB}\\
-{\small Bogotá, Colombia}\\
-{\small 2014}{\small \par}
-
-\end{center}
-\newpage 
-\thispagestyle{empty}
-
-\textbf{Dedicación}
-
-{\small \vspace{4cm}
-}{\small \par}
-
-\noindent \begin{flushright}
-\begin{minipage}[t]{8cm}%
-{\small A Beatriz y Campo Elias mis padres que siempre me dieron la
-libertad de escoger, con su comprensión y apoyo me permitieron dedicar
-mi tiempo a la ciencia.}{\small \par}
-
-{\small \vspace{1cm}
-}{\small \par}
-
-{\small A mis padres}{\small \par}
-
-{\small \vspace{1cm}
-}{\small \par}
-
-Beatriz Fernandez Vargas
-
-Campo Elias Pinzon Rojas%
-\end{minipage}
-\par\end{flushright}
-
-\newpage
-\thispagestyle{empty}
-
-\textbf{\LARGE Acknowledgement}{\LARGE \par}
-
-\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}
-
-\vspace{2cm}
-
-I wold like to thank my advisor professor Eduardo Romero and CIM\&LAB
-research group for his support in this thesis.
-
-{\small \vspace{1cm}
-}{\small \par}
-
-I would like to thank all the workers in Colombia who fund the public
-education with their work.
-
-{\small \vspace{1cm}
-}{\small \par}
-
-This work was supported in part by the Blender Foundation, Google
-Summer of code program at 2012 - 2013.
-
-\newpage{}
-
-\textbf{\LARGE Abstract}{\LARGE \par}
-
-\addcontentsline{toc}{chapter}{\numberline{}Abstract}
-
-In the last two decades three-dimensional modeling methods have been
-evolving and developing rapidly, thanks in part to the use of vector
-operators of differential geometry. The Laplacian operator has been
-one of the most widely studied and used thanks to the properties exhibited
-by their eigenvectors in novel applications such as noise reduction,
-enhancement, remeshing, UV mapping, posed, skeletonization, among
-other. The differential operator is defined in a continuous and smooth
-domain named manifold, manifolds are often approximated by discrete
-polygon meshes composed by triangles and quadrangles which represent
-the real world three-dimensional objects. In these meshes spectral
-structure is calculated using a discrete Laplacian operator, the discrete
-version of the Laplacian operator given by Pinkall in 1993 works only
-with meshes of triangles, and Xiong in 2011 working exclusively with
-quads. This thesis proposes an original extension of the Laplacian
-operator that allows to work with hybrid meshes composed by triangles
-and quadrangles.
-
-Along with the operator, this work presents new sculpting and modeling
-applications with base on the enhancement, applications on subdivision
-surfaces using smoothing, mesh posing using differential coordinates
-and skeletonization using iterative contraction. This series of applications
-demonstrates the quality, predictability and flexibility of the proposed
-operator.
-
-The proposed operator was successfully used in real production environments
-within software Blender how new tools. Currently these tools are available
-as open source software.
-
-\textbf{\LARGE Resumen}{\LARGE \par}
-
-En las dos últimas décadas los métodos de modelado tridimensional
-han ido evolucionando y desarrollándose rápidamente, en parte gracias
-al uso de operadores vectoriales de geometría diferencial. El operador
-Laplaciano ha sido uno de los más ampliamente estudiado y usado gracias
-a las propiedades exhibidas por sus vectores propios en novedosas
-aplicaciones como: reducción de ruido, realce, remallado, mapeo UV,
-posado, esqueletonización, entre otras. Este operador diferencial
-es definido en un dominio continuo y suave llamado variedad, las variedades
-son a menudo aproximadas por mallas discretas de polígonos compuestas
-por triángulos y cuadrángulos que a su vez representan objetos tridimensionales
-del mundo real. En estas mallas se calcula la estructura espectral
-con el uso de algún operador Laplaciano discreto, la versión discreta
-del operador Laplaciano propuesta por Pinkall en el 1993 trabaja únicamente
-con mallas compuestas por triángulos, y la de Xiong en el 2011 trabaja
-exclusivamente con cuadrángulos. Esta tesis propone una extensión
-original del Operador Laplaciano que permite trabajar con mallas híbridas
-compuestas por triángulos y cuadrángulos.
-
-Junto con el operador, este trabajo presenta nuevas aplicaciones en
-esculpido y modelamiento con base en el realce, aplicaciones en subdivisión
-de superficies con el uso de suavizado, posado de mallas con el uso
-de coordenadas diferenciales y esqueletonización usando contracción
-iterativa. Esta serie de aplicaciones demuestra la calidad, predictibilidad
-y flexibilidad del operador propuesto.
-
-El operador propuesto fue usado de forma exitosa en ambientes reales
-de producción dentro del software Blender como nuevas herramientas.
-Actualmente estas herramientas están disponibles como programas de
-código abierto.
-
-{\small \vspace{1cm}
-}{\small \par}
-
-\textbf{\small Keywords: laplacian operator; smooth; enhance; sculpting;
-subdivision surface}{\small \par}
-
-\tableofcontents{}
-
-\listoffigures
-
-\listoftables
-
-\pagenumbering{arabic}
-
-\chapter{Introduction}
-
-The discrete versions of Laplace Beltrami Operator have been used
-in the last years for the develop of new geometric modeling tools.
-In the work of Pinkall \cite{Pinkall1993} was introduced the cotangent
-version of Laplace operator, that allow to find the minimal surface
-when compute a discete harmonic map with the Laplacian operator, this
-version has been widely studied and applied in various problems of
-computer geometric modeling. The manifolds that are continuous domains
-homeomorphic to $\mathbb{R}^{n}$ are represented in computers by
-polygon meshes. These polygons are generally composed of triangles
-and quadrangles, while work with laplacian operator in this hybrid
-composition are not a mathematical challenge, most research uses only
-meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006},
-in other recent studies \cite{Liu2008,Xiong2011} the Laplacian operator
-is working exclusively with quadrangles. But in the artistic scope
-topology and the way the edges are distributed, the triangle and quadrangles,
-directly affects the processes of animation, interpolation, textured,
-etc. As discussed by \cite{Mullen2007} who use a manual connection
-of a couple of vertices to perform animation processes and interpolation.
-It is then of paramount importance to develop operators that easily
-interact with such meshes, eliminating the need of preprocessing the
-mesh to convert it to triangles and change the original topology.
-
-Modeling techniques able to generate a variety of realistic shapes,
-have been developed \cite{Botsch2006}. Editing techniques have evolved
-from affine transformations to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
-editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
-complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
-based methods however require to interact with a minimun number of
-control points for any operation to be efficient, or in other words,
-a unicity condition is introduced by demanding a smooth surface after
-any of these shape operations. Hence, traditional modeling methods
-for subdividing surfaces from coarse geometry have become widely popular
-\cite{Catmull1978,Stam1998}. These works have generalized a uniform
-B-cubic spline knot insertion to meshes, some of them adding some
-type of control, for instance with the use of creases to produce sharp
-edges \cite{DeRose1998}, or the modification of some vertex weights
-to locally control the zone of influence \cite{Biermann2000}. Neverteless
-these methods are difficult to deal with since they require a large
-number of parameters and a very tedious customization. Instead, the
-presented applications requires a single parameter that controls the
-global curvature, which is used to maintain realistic shapes, creating
-a family of different versions of the same object and therefore preserving
-the detail of the original model and a realistic appearance.
-
-The shape inflation and shape exaggeration can thus be used as such
-brush in the sculpting process, when inflating a shape since current
-brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
-In contrast, the presented enhance method inflates a mesh by moving
-the vertices towards the reverse curvature direction, conserving the
-shape and sharp features of the model.
-
-\paragraph{Contributions}
-
-This work presents an extension of the Laplace Beltrami Operator for
-hybrid quad/triangle meshes, representing a larger mesh spectrum from
-what has been presented so far. The method eliminates the need of
-preprocessing and allows preservation of the original topology. Likewise,
-along with this operator, it is proposed a method to generate a family
-of parameterized shapes, in a robust and predictable way. This method
-enables customization of the smoothness and curvature, obtained during
-the subdivision surfaces process. Finally, it is proposed a new brush
-for inflating the silhouette mesh features in modeling and sculpting.
-
-This work is organized as follows: Chapter \ref{sub:1.1-Related-work}
-presents works related to the Laplacian operator, applications in
-digital sculpting, deformation, and offsetting methods for polygonal
-meshes; In chapter \ref{chap:Mathematical-foundation}, it is described
-the theoretical framework of the Laplacian operator for polygon meshes;
-In chapter \ref{sec:Proposed-Method}, it is presented the extension
-of the Laplacian Operator for hybrid meshes and applications of shape
-inflation ,subdivision of surfaces , deformation, skelenotization
-and sculpting; finally some Laplacian Operator results, to hybrid
-quad/triangle meshes are graphically shown as well as results of the
-shape inflation applications in sculpting, subdivision, deformation,
-skelenotization and modeling.
-
-\chapter{Related work\label{sub:1.1-Related-work}}
-
-Many tools have been developed for modeling, based on the Laplacian
-mesh processing. These different tools preserve the surface geometric
-details when using laplacian operators for different processes such
-as smoothing, enhancing, free-form deformation, fusion, morphing and
-other applications \cite{Ranjan2012}.
-
-The most used discretization of Laplace Beltrami operator $\Delta_{\mbox{\ensuremath{\Omega}}}$
-over a triangulated mesh $\Omega$ was proposed by Pinkall \cite{Pinkall1993}.
-
-\noindent \begin{center}
-$\Delta_{\mbox{\ensuremath{\Omega}}}\left(u\right)=\frac{1}{2}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(x_{i}-x_{j}\right)$
-\par\end{center}
-
-Where $N_{1}$is the 1-ring neighboorhood, $\alpha$ and $\beta$
-are the opposite angles to edge between vertex $i$ and vertex $j$.
-In this work the discretize laplacian operator was used to find the
-minimal surface based on minimization energy strategy using the Dirichlet's
-energy of the function $u$ over a manifold represented by triangulated
-mesh $\Omega$.
-
-\noindent \begin{center}
-$E_{D}\left(u\right)=\frac{1}{2}\int_{\Omega}\bigl|\nabla u\bigr|^{2}$
-\par\end{center}
-
-Then Taubin works \cite{Taubin1995} for first time treat the problem
-of noise reduction in digital poligonal meshes from signal proccessing
-point of view. Taubin extends Fourier analysis to signals defined
-on polygonal meshes, Taubin observe that Fourier transform is a decomposition
-of the signal into an eigenvectors of the Laplacian operator, and
-reconstruct the signal with a linear combination of these eigenvectors.
-Desbrun works \cite{Desbrun1999} consider the same approach of Taubin,
-but Desbrun use a curvature normal ($\bar{\kappa}\mathbf{n}$) based
-on cotangen Laplace operator version for noise reduction over a difussion
-process. This it's the most important and popular Laplace Beltrami
-opertator discretization \cite{Liu2008}, many works for mesh smoothing
-and fairing have been developed based on this LBO discretization \cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}.
-
-\noindent \begin{center}
-$\frac{\partial x_{i}}{\partial t}=-\bar{\kappa_{i}}\mathbf{n_{i}}$
-\par\end{center}
-
-\noindent \begin{center}
-$-\bar{\kappa_{i}}\mathbf{n_{i}}=\frac{1}{A}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)$
-\par\end{center}
-
-Where $A$ is the area surrounding vertex $i$. This laplacian operator
-$L$ was used for reduce the noise in a mesh $X$ over a difussion
-process.
-
-The convergence of the Laplace Beltrami operator has been very important
-in fields how numerical analysis, given that implications in the simulation
-process and geometric partial differentials equations. In the works
-of \cite{Xu2004} is established the convergence of several discrete
-Laplace Beltrami operators over triangulated meshes with numerical
-results that support the theoretical analysis. Over quadrilateral
-meshes Liu \cite{Liu2008} presents a discrete Laplace Beltrami Operator
-based on a bilinear interpolation and its convergence over this type
-of meshes composed only by quads.
-
-In the work of Sorkine \cite{Sorkine2006} the laplacian operator
-was used to repose a meshes while preserving geometry details of the
-surface. The details was stored in differential coordinates $\delta_{i}$
-for every vertex $v_{i}$.
-
-\noindent \begin{center}
-$\delta_{i}=\sum_{j\in N_{1}\left(i\right)}\frac{1}{2}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)$
-\par\end{center}
-
-The differential coordinates represents the difference between the
-absolut coordinate of $v_{i}$and the center of mass of its immediate
-neighboors.
-
-Offset methods for polygon meshing, based on the curvature defined
-by the Laplace Beltrami operator, have been developed. These methods
-adjust the shape offset by a constant distance, with enough precision.
-Nevertheless, these methods fail to conserve sufficient detail because
-of the smoothing, a crucial issue which depends on the offset size
-\cite{Zhuo2012}. In volumetric approaches, in case of point-based
-representations, the offset boundary computation is based on the distance
-field and therefore when calculating such offset, the topology of
-the model may be different to the original \cite{Chen2011}.
-
-\cite{Gal2009} propose automatic feature detection and shape edition
-with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys, characerized by their first
-and second order curvature derivatives, see \cite{Ohtake2004}, and
-angle-based threshold. Likewise, curves have been also classified
-as planar or non-planar, approximated by lines, circles, ellipses
-and other complex shapes. In such case, the user defines an initial
-change over several features which is propagated towards other features,
-based on the classified shapes and the inter-relationships between
-them. This method works well with objects that have sharp edges, composed
-of basic geometric shapes such as lines, circles or ellipses. However,
-the method is very limited when models are smooth since it cannot
-find the proper features to edit.
-
-Digital sculpting have been traditionally approached either under
-a polygonal representation or a voxel grid-based method. Brushes for
-inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
-In grid-based sculpting, some other operations have allowed to add
-or remove voxels since production of polygonal meshes require a processing
-of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
-from the difficulty of maintaining the surface details during larger
-scale deformations.
-
-In the literature, several studies have described the skeleton extraction
-systems and different metrics that identify appropriate methods given
-an application specific \cite{Attali2007}. One of the best methods
-reported in the literature for the extraction of the skeleton is the
-Laplacian smoothing method for its advantages of homotopy representation
-and hierarchical connections between parts. The Skeleton extraction
-methods permits simplify the dimension of the object preserving the
-topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
-present a skeleton extraction method based on iterative smooothing-contraction,
-in this method the several constraints are used to waranty that the
-process converge to skeleton formed by branchs and joins, the constraints
-based on laplacian operator, the low frequencies of the mesh are preserving
-with the use of attractor to original mesh, while the iterative smoothin
-process remove high frecuencies.
-
-\chapter{Mathematical foundation\label{chap:Mathematical-foundation}}
-
-This chapter studies basic mathematical foundation on differential
-geometry to understand the differential operators and the Laplace
-beltrami operator.
-
-The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
-The differential operators show a deep relationships betwen the geoemetry
-(curvatures, geodesics) and topology of the manifold. This differential
-operators are very used in applications on computer geometric modelling
-over the last years \cite{Rosenberg1997,Alexa2011}.
-
-\section{Manifolds}
-
-A manifold is a topological space $M$ with the following properties:
-
-If $x\in M$, then there is some neighborhood $N\left(x\right)$ and
-some integer $n\geq0$ such that $N(x)$ is homeomorphic to $\mathbb{R}^{n}$
-\cite{Spivak1-1999}.
-
-This work is related to manifolds that represent a surface in an three-dimensional
-Eucliddean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.
-
-The manifols are represented by polygonal meshes with points connected
-by triangles and quads.
-
-\section{Laplace Operator}
-
-In computer graphics a manifold is often approximated by a discrete
-mesh \cite{Ranjan2012}, then is necessary to define a discrete laplacian
-operator that act on functions defined on such meshes.
-
-Consider a smooth compact manifold $M$ of dimension $m$ isometrically
-embedded in a Euclidean space $\mathbb{R}^{d}$.
-
-Given a twice continuously differentiable function $f\in C^{2}\left(M\right)$,
-let $\nabla_{\mbox{M}}f$ denote the gradient vector field of $f$
-on $M$.
-
-The Laplace-Beltrami operator $\Delta_{\mbox{M}}$ of $f$ is defined
-as the divergence of the gradient; that is \cite{Spivak1-1999},
-
-\noindent \begin{center}
-$\frac{\partial^{2}f}{\partial x^{2}}+\frac{\partial^{2}f}{\partial y^{2}}+\frac{\partial^{2}f}{\partial z^{2}}=0$
-\par\end{center}
-
-\noindent \begin{center}
-$\nabla_{\mbox{M}}^{2}f=\Delta_{\mbox{M}}f=0$
-\par\end{center}
-
-\noindent 
-\begin{equation}
-\Delta_{\mbox{M}}f=div\left(\nabla_{\mbox{M}}f\right)
-\end{equation}
-
-\subsection{Discrete Laplace Operator Setting}
-
-Discrete Laplacian operators are linear operators that act on functions
-defines on meshes. These functions are specified by their values at
-the vertices.
-
-Thus, if a mesh $M$ has $n$ vertices, then functions on $M$ will
-be represented by vectors with $n$ components and a mesh Laplacian
-will be described by an $n\times n$ matrix \cite{Ranjan2012}.
-
-The Laplacian operator locally takes the difference between the value
-of a function at a vertex and a weighted average of its values at
-the first-order or one-ring neighbor vertices, then a Laplacian matrix
-$L$ has a local form given by
-
-\noindent \begin{center}
-$L\left(f\right)_{i}=b_{i}^{-1}\underset{j\in N\left(i\right)}{\sum}w_{ij}\left(f_{i}-f_{j}\right)$
-\par\end{center}
-
-Where $w_{ij}$are the weights between the vertex $i$ and the vertex
-$j$. $b_{i}^{-1}$ are the factors depending of the boundary region
-over vertex $i$. $N\left(i\right)$ are the neighbors that share
-a edge with vertex $i$.
-
-\subsection{Gradient of Voronoi Area}
-
-Consider a surface $S$ composed of a set of triangles around vertex
-$v_{i}$. Let us define the \textsl{Voronoi Region} of $v_{i}$ as
-show in figure \ref{fig:voronoi_region}, The area change produced
-by the movement of $v_{i}$ is called the gradient of \textsl{Voronoi
-region} \cite{Pinkall1993,Desbrun1999,Meyer2003}.
-
-\noindent 
-\begin{align}
-\nabla A & =\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)\label{eq:eq_gradient_voronoi_area}
-\end{align}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/voronoi_region}
-
-\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
-in dark blue.$v_{j}$ belong to the first neighborhood around $v_{i}$.
-$\alpha_{j}$ and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
-\end{figure}
-
-If the gradient in equation \ref{eq:eq_gradient_voronoi_area} is
-normalized by the total area of the 1-ring neighborhood around $v_{i}$,
-the \textsl{discrete mean curvature normal} of a surface $S$ is obtained,
-as shown in equation \ref{eq:discrete_mean_curvature_normal}.
-
-\noindent 
-\begin{equation}
-2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{eq:discrete_mean_curvature_normal}
-\end{equation}
-
-\section{Laplace Beltrami Operator}
-
-The \textit{Laplace Beltrami operator} LBO noted as $\Delta$ is used
-for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.
-
-\noindent 
-\begin{equation}
-\Delta_{\mbox{S}}=2\kappa\mathbf{n}\label{eq:def_LBO}
-\end{equation}
-
-\chapter{Proposed Laplacian Operator\label{sec:Proposed-Method}}
-
-This thesis propose an original extension of the Laplace Beltrami
-operator for hybrid quad/triangle meshes, mixing arbitrary types of
-meshes, exploiting the basic geometrical relationships and ensuring
-algorithm convergence.
-
-With the use of the proposed Laplacian Operator this work show succesful
-uses in: Smoothing, Enhancing, Smooth Subdivision, Deformation, Sculpting,
-and Skeletonization.
-
-\section{Proposed Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes
-TQLBO\label{sub:Laplace-Beltrami-operator}}
-
-Given a mesh $M=\left(V,Q,T\right)$, with vertices $V$, quads $Q$,
-triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
-corresponds to a sum of the areas of the quad faces $A\left(Q_{i}\right)$
-and the areas of the triangular faces $\ensuremath{A\left(T_{i}\right)}$
-adjacent to vertex $\ensuremath{v_{i}}$.
-
-\noindent \begin{center}
-$A\left(v_{i}\right)=A\left(Q_{i}\right)+A\left(T_{i}\right)$ 
-\par\end{center}
-
-\begin{figure}[H]
-\includegraphics[width=1\columnwidth]{resources/figs/quad_xiong}
-
-\caption{\label{fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
-Triangulations of the quad with common vertex $v_{i}$ proposed by
-{[}Xiong 2011{]} to define Mean LBO.}
-\end{figure}
-
-Applying the mean average area, according to Xiong et. al. \cite{Xiong2011},
-from all possible triangulations, as show in figure \ref{fig:quad_xiong},
-the area for quads $\ensuremath{A\left(Q_{i}\right)}$ and triangles
-$A\left(T_{i}\right)$ is.
-
-\noindent \begin{center}
-$A\left(v_{i}\right)=\frac{1}{2^{m}}\overset{m}{\underset{j=1}{\sum}}2^{m-1}A\left(q_{j}\right)+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)$ 
-\par\end{center}
-
-Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{i}$ are quads adjacent
-to $v_{i}$, and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{i}$ are triangles
-adjacent to $v_{i}$.
-
-Applying triangulations of the quad with common vertex $v_{i}$ proposed
-by \cite{Xiong2011}.
-
-\noindent 
-\begin{equation}
-A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{eq:area_1_ring_triangles_quads}
-\end{equation}
-
-Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).
-
-\noindent {\small 
-\begin{equation}
-\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
-\end{equation}
-}{\small \par}
-
-According to (\ref{eq:eq_gradient_voronoi_area}), we have.
-
-\noindent \begin{center}
-$\nabla A\left(t_{j1}^{*}\right)=\frac{\cot\theta_{j3}\left(v_{j}-v_{i}\right)+\cot\theta_{j2}\left(v_{j}^{\prime}-v_{i}\right)}{2}$ 
-\par\end{center}
-
-\noindent \begin{center}
-$\nabla A\left(t_{j2}^{*}\right)=\frac{\cot\theta_{j5}\left(v_{j}^{\prime}-v_{i}\right)+\cot\theta_{j4}\left(v_{j+1}-v_{i}\right)}{2}$ 
-\par\end{center}
-
-\noindent \begin{center}
-$\nabla A\left(t_{j3}^{*}\right)=\frac{\cot\theta_{j6}\left(v_{j}-v_{i}\right)+\cot\theta_{j1}\left(v_{j+1}-v_{i}\right)}{2}$ 
-\par\end{center}
-
-\noindent \begin{center}
-$\nabla A\left(t_{k}\right)=\frac{\cot\alpha_{k}\left(v_{k}-v_{i}\right)+\cot\beta_{k+1}\left(v_{k+1}-v_{i}\right)}{2}$ 
-\par\end{center}
-
-Triangle and quad configurations of the 1-ring neighborhood faces,
-adjacent to $v_{i}$, can be simplified to five cases, as shown in
-figure \ref{fig:LBO-basic-5-TQ}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/beltrami}
-
-\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
-vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
-(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
-{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO) our contribution.}
-
-\end{figure}
-
-According to equation (\ref{eq:discrete_mean_curvature_normal}),
-(\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
-the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.
-
-\noindent 
-\begin{equation}
-\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
-\end{equation}
-
-\noindent {\small where
-\begin{equation}
-w_{ij}=\begin{cases}
-\left(\cot\alpha_{j}+\cot\beta_{j}\right) & \mbox{case }\mathit{a.}\\
-\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}+\cot\theta_{j3}+\cot\theta_{j6}\right) & \mbox{case \ensuremath{\mathit{b}}.}\\
-\left(\cot\theta_{j2}+\cot\theta_{j5}\right) & \mbox{case \ensuremath{\mathit{c}}.}\\
-\frac{1}{2}\left(\cot\theta_{j3}+\cot\theta_{j6}\right)+\cot\beta_{j} & \mbox{case \ensuremath{\mathit{d}}.}\\
-\frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
-\end{cases}\label{eq:TQLBO_wij}
-\end{equation}
-}{\small \par}
-
-We define a Laplacian operator as a matrix equation
-
-\noindent 
-\begin{equation}
-L\left(i,j\right)=\begin{cases}
--\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N\left(v_{i}\right)\\
-\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\\
-0 & \mbox{otherwise}
-\end{cases}\label{eq:TQLBO_Simple_Matrix}
-\end{equation}
-
-Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
-of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
-$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
-to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.
-
-Normalized version of the TQLBO as a matrix equation
-
-\noindent 
-\begin{equation}
-L\left(i,j\right)=\begin{cases}
--\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }j\in N\left(v_{i}\right)\\
-\delta_{ij} & \mbox{otherwise}
-\end{cases}\label{eq:TQLBO-Normalized_Matrix}
-\end{equation}
-
-Where $\delta_{ij}$ being the Kronecker delta function.
-
-\section{Mesh Smoothing\label{sub:Laplacian-Smooth}}
-
-Computer objects, reconstructed from the real world, are usually noisy.
-A common way to attenueate noise in a polygonal mesh is through a
-diffusion process \cite{Taubin1995,Desbrun1999}. Laplacian smooth
-techniques over a diffusion process allow a proper noise reduction
-on the mesh surface with minimal shape changes, while still preserving
-a desirable geometry as well as the original shape. The simple idea
-is that the vertices are moved in the direction of the Laplacian when
-we use the contangent version the vertices are moved in the direction
-of the curvature flow. The complexity of Laplacian smoothing can be
-linear in time and space with a fast convergence and the diffussion
-proccess can attenuate noise with only one iteration due the sparseness
-of the laplacian operator.
-
-\noindent 
-\begin{equation}
-\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
-\end{equation}
-
-Where L is the Laplacian matrix defined in equation \ref{eq:TQLBO-Normalized_Matrix}
-for meshes with regular sampling, and equation \ref{eq:TQLBO_Simple_Matrix}
-for meshes composed by triangles or quads with differents size or
-irregular sampling. $\lambda$ is a scalar that control the diffussion
-proccess, and smoothing factor.
-
-The equation \ref{eq:diffusion_process} can be linearly approximated
-using implicit integration with a Laplacian Operator version of TQLBO,
-the use of implicit integration permit the system to be more stability.
-
-\begin{equation}
-\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
-\end{equation}
-
-\section{The Shape Inflation\label{sub:Curvature-Enhancing}}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/teaser_cup}
-
-\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
-from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
-Subdivision (b), (d), is inflated. Soft constraints, over the coarse
-model, is drawn in red and blue (c).}
-\end{figure}
-
-This method exaggerates a shape using a Laplacian smoothing operator
-in the reverse direction, i.e., the new shape is a modified version
-in which those areas with larger curvature are magnified. The operator
-amounts to a generator of a set of models which conserves the basic
-silhouette of the original shape. In addition, the presented approach
-can be easily mixed with traditional or uniform subdivision of surfaces.
-
-The shape is inflated by using the reverse direction of the curvature
-flow, moving the vertices towards those mesh portions with larger
-curvature. A standard diffusion process is applied:
-
-\noindent \begin{center}
-$\frac{\partial V}{\partial t}=\lambda L\left(V\right)$ 
-\par\end{center}
-
-To solve this equation, implicit integration is used as well as a
-normalized version of TQLBO matrix.
-
-\noindent 
-\begin{equation}
-\left(I-\left|\lambda dt\right|W_{p}L\right)V^{\prime}=V^{t}\label{eq:Lineal_System_with_wp}
-\end{equation}
-
-\noindent \begin{center}
-$V^{t+1}=V^{t}+\mbox{sign}\left(\lambda\right)\left(V^{\prime}-V^{t}\right)$ 
-\par\end{center}
-
-The vertices $V^{t+1}$ are inflated, along their reverse curvature
-direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
-$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
-$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
-vertices positions, $W_{p}$ is a diagonal matrix with vertex weights,
-and $\lambda dt$ is the inflate factor that supports negative and
-positive values: negative for inflation and positive for smoothing.
-
-The method was devised to use with weighted vertex groups, which specify
-the final shape inflation of the solution, meaning $0$ as no changes
-and 1 when a maximal change is applied. The weights modify the influence
-zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
-Interestingly, the generated family of shapes may change substantially
-with the weights of specific control points.
-
-The curvature cannot be calculted at the boundary of the meshes that
-are not closed, for that reason we use the scale-dependent operator
-proposed by Desbrun et al. \cite{Desbrun1999}, the inflation factor
-for boundary is represented by $\lambda_{e}$.
-
-The model volume increases as the lambda is larger and negative, this
-can be counteracted with a simple volume preservation. However, the
-mesh may suffer large displacements when $\lambda<-1.0$ or after
-multiple iterations. A simple volume conservation algorithm is: If
-$v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
-we define $\overline{v}$ as:
-
-\noindent \begin{center}
-$\overline{v}=\frac{1}{n}\underset{v_{i}\in V}{\sum}v_{i}$, 
-\par\end{center}
-
-$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
-and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
-factor.
-
-\noindent \begin{center}
-$\beta=\left(\frac{vol_{ini}}{vol_{t+1}}\right)^{\frac{1}{3}}$ 
-\par\end{center}
-
-allows to scale the vertices to:
-
-\noindent \begin{center}
-$v_{i\, new}^{t+1}=\beta\left(v_{i}^{t+1}-\overline{v}\right)+\overline{v}$ 
-\par\end{center}
-
-The shape inflation use a negative curvature flow that is an unstable
-process when performing many iterations, however, our method uses
-less than 3 iterations to get good results, and with 3 iterations
-or less the method behaves stable.
-
-\section{Sculpting\label{sub:Sculpting}}
-
-A new sculpting brush is herein proposed and aims to inflate the shape,
-magnifying the shape curvatures of a polygon mesh in real time. This
-brush works properly with the stroke method \textsl{Drag Dot}, allowing
-to pre-visualize the model changes before the mouse is released. Also,
-it allows to move the mouse along the model to match the shape zone
-which is supposed to be inflated.
-
-Brushes that perform a similar inflation can introduce mesh distortions
-or produce mesh self-intersections, provided these brushes only move
-the vertices along the normal without any global information. In contrast,
-the present method searches for a proper inflation while preserving
-the global curvature, retaining the original shape and main model
-features. In addition, this method simplifies the work required for
-the inflation since it needs not different brushes for inflating,
-softening or styling. The inflated brush can make all these operation
-in a single step. Real-time brushes require the Laplacian matrix is
-constructed with the vertices that are within the sphere radius defined
-by the user, reducing the matrix to be processed, the center of this
-sphere depending on the place where the user clicks on the canvas
-and the three-dimensional mesh placed where the click is projected.
-Special handling is required for the boundary vertices with neighbors
-that are not within the brush radius: these vertices are marked as
-boundary and the curvature is not there calculated, but they must
-be included in the matrix so that every vertex has their corresponding
-neighbors within the selection. The sculpting Laplacian matrix reads
-as.
-
-\noindent \begin{center}
-$L\left(i,j\right)=\begin{cases}
--\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert <r\\
-0 & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert \geq r\\
-\delta_{ij} & \mbox{otherwise}
-\end{cases}$ 
-\par\end{center}
-
-Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the sphere center of
-radius $r$. The matrices should remove rows and columns of vertices
-that are not within the radius.
-
-\section{Laplacian Deform\label{sub:Laplacian-Deform}}
+\section{Laplacian Deform}
 
@@
 
-This thesis adapt the method proposed by Sorkine \cite{Sorkine2004}
+This work adapt the method proposed by Sorkine \cite{Sorkine2004}
 for mesh deformations, delete the use of static vertices and allow
@@
 
-\begin{figure}
+\begin{figure}[H]
 \noindent \begin{centering}
@@
 
-\caption{\label{fig:DifferentialCoor} Difference between $v_{i}$ and the
-center of mass of its neighboors $v_{1},...,v$.}
+\protect\caption{\label{fig:DifferentialCoor} Difference between $v_{i}$ and the
+center of mass of its neighbors $v_{1},...,v$.}
 \end{figure}
@@
 Where $\delta_{i}$ is the differential coordinate for vertex $v_{i}$.
-The $v_{j}$ are the inmediate neighoors of $v_{i}$, and $w_{ij}$
-is the weigth betwen vertex $v_{i}$ and $v_{j}$ defined in equation
-\ref{eq:TQLBO_wij} that is TQLBO.
+The $v_{j}$ are the immediate neighbors of $v_{i}$, and $w_{ij}$
+is the weight between vertex $v_{i}$ and $v_{j}$ defined in equation
+\ref{PAPER:eq:TQLBO_wij} that is TQLBO.
 
@@
 
-Where $w_{l}$ is the weigth for Laplacian Matrix $L$, the Laplacian
-matrix $L$ was defined in equation \ref{eq:TQLBO_Simple_Matrix}
-. $Wc$ is a matrix that containts ones int the indexes of anchors
+Where $w_{l}$ is the weight for Laplacian Matrix $L$, the Laplacian
+matrix $L$ was defined in equation \ref{PAPER:eq:TQLBO_Simple_Matrix}
+. $Wc$ is a matrix that contains ones int the indexes of anchors
 vertices. $C$ is a vector with coordinates of anchors vertices after
-several transformatios. $\delta$ are the differential coordinates
+several transformations. $\delta$ are the differential coordinates
 defined in equation \ref{eq:DifferentialCoordinate}.
 
-\section{Subdivision surfaces\label{sub:Subdivision-surfaces}}
+\section{Performance Testing of Solvers }
 
-The Catmull-Clark subdivision transformation is used to smooth a surface,
-as the limit of a sequence of subdivision steps \cite{Stam1998}.
-This process is governed by a B-spline curve \cite{Loop1987}, performing
-a recursive subdivision transformation that refines the model into
-a linear interpolation that approximates a smooth surface. The model
-smoothness is automatically guaranteed \cite{DeRose1998}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/cruz_lambda4}
-
-\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
-Subdivision. Models with Laplacian smoothing: (c) and (d). Models
-with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying shape inflation: (e) and (f).}
-\end{figure}
-
-Catmull-Clark subdivision surface methods generate smooth and continuous
-models from a coarse model and produce quick results because of the
-simplicity of implementation. Nevertheless, changes to the global
-curvature are hardly implantable. The Catmull-Clark subdivision surfaces
-together with shape inflation can easily generate families of shapes
-by changing a single parameter, allowing to handle a model with very
-few vertices. In practice, this would allow an artist to choose a
-model from a similar set of options that would meet his/her needs
-without having to change each of the control vertices. Likewise, the
-presented method allows the use of vertex weight paint over the control
-points. The weights can be applied to a coarse model, followed by
-a Catmull-Clark subdivision where weights are interpolated, producing
-weights with smooth changes in the influence zones, as shown in figure
-\ref{fig:Subdivision-Cups}.c.
-
-In equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
-matrix with weights corresponding to each vertex. Weights at each
-vertex produce a different solution so that the matrix must be placed
-in the diffusion equation since families that are generated may change
-substantially with weighted of specific control points.
-
-\section{Skeleton Extraction}
-
-Skelton extraction reduces the dimensionality and represents a three-dimensional
-object as a uni-dimensional structure \cite{Cornea2007}.
-
-The skeleton extraction use the natural shrink produced by the laplacian
-smoothing \cite{Meyer2003}, to contratc iteratively the mesh until
-the volume inside the surface is near to zero (see figure \ref{fig:MeshContracted}).
-The method stretch the shrink mesh to warranty that object preservers
-the best at posibble the original topology with the use of attraction
-constraint \cite{Au2008}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/contraccion}
-
-\caption{\label{fig:MeshContracted}From left to right iterative mesh contraction.}
-\end{figure}
-
-The laplacian smooth proccess move the vertices in the direction of
-the Laplacian, if cotangent laplacian operator is used, the vertices
-move in the direction of minimal surface \cite{Pinkall1993} following
-the curvature flow of the mesh surface.
-
-In the work of Au \cite{Au2008} is proposed the next system of equation
-to iteratively contratc the mesh until a skeleton.
-
-\begin{equation}
-\left[\begin{array}{c}
-W_{L}L\\
-W_{H}
-\end{array}\right]X_{t+1}=\left[\begin{array}{c}
-0\\
-W_{H}X_{t}
-\end{array}\right]\label{eq:SkeletonExtraction}
-\end{equation}
-
-where $L$ is the Laplacian matrix describe in equation \ref{eq:TQLBO_Simple_Matrix},
-$W_{L}$ is the factor for smoothing, $W_{H}$ is the factor for attraction
-constraint.
-
-$W_{L}$ and $W_{H}$ are changing in every iteration. The contraction
-and smoothing constraint $W_{L}^{t+1}=S_{L}W_{L}^{t}$ with $S_{L}=2.0$.
-The attraction constraint $W_{H,i}^{t+1}=W_{H,i}^{0}\sqrt{\frac{A_{i}^{0}}{A_{i}^{t}}}$.
-
-$A_{i}^{t}$ y $A_{i}^{0}$ are the current area and initial aerea
-of the ring surrounding $x_{i}$.
-
-In this thesis an additional constraint is proposed which seeks the
-vertices and the skeleton does not shrink, to eliminate the need to
-adjust the final skeleton taking each skeleton node and move to the
-center of your local mesh region.
-
-The basic idea is move the vertices along of the normal line estimated
-on every vertex based on the avergage of the faces normals.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/LineConstraintSkeleton}
-
-\caption{\label{fig:LineConstraint}Left: The vertex $x_{i}$ move along line
-constraint. Right: the distance of vertex $x_{i}$ to plane 1 and
-plane 2 when change the position in every iteration.}
-\end{figure}
-
-This line can be see as intersection of two planes (see figure \ref{fig:LineConstraint})
-created with the information of the vertex $x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$
-and neighboors $x_{j}$ of $x_{i}$.
-
-The equation of the plane.
-
-\noindent \begin{center}
-$a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}=0$
-\par\end{center}
-
-There is varios methods to build a equation of the plane based on
-three non-collinear points, we choose this three points based on vertex
-$x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$ and neighboors
-$x_{j}$ of $x_{i}$.
-
-$P_{1}=x_{i}$, $P_{2}=x_{j}$ when $x_{j}\in Neighboors\left(x_{i}\right)$
-and $P_{3}=P_{1}-\overrightarrow{\mathbf{n}_{i}}$.
-
-To build a equation plane only need three non-collinear points $\left\{ P_{1},P_{2},P_{3}\right\} $
-and solve the next systems of equations for variables $a,b,c$.
-
-\noindent \begin{center}
-$\begin{array}{c}
-ax_{1}+by_{1}+cz_{1}+d=0\\
-ax_{2}+by_{2}+cz_{2}+d=0\\
-ax_{3}+by_{3}+cz_{3}+d=0
-\end{array}$
-\par\end{center}
-
-The distance of point $P_{0}=\{x_{0},y_{0},z_{0}\}$ to a plane $\Pi=a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}$.
-
-\noindent \begin{center}
-$\left|\Pi-P_{0}\right|=\frac{\left|ax_{0}+by_{0}+cz_{0}+d\right|}{\sqrt{a^{2}+b^{2}+c^{2}}}$
-\par\end{center}
-
-In the equation above, every point $P_{0}=\{x_{0},y_{0},z_{0}\}$
-that belong to plane made the equation zero. If the point $P_{0}$
-is not in the plane the value of the equation of the plane change,
-and the absolute value is increased if $P_{0}$ is more distant of
-the plane. Let us use this simple relation to build a valid constraint
-that can be put in the form of linear equation $Ax=B$. Where $A$
-is the matrix with values $\begin{vmatrix}a & b & c\end{vmatrix}$
-the $x$ value correspond to every vertex in mesh $\{x_{0},y_{0},z_{0}\}$
-and $B$ correspond to $d$ value of the plane equation. How the linear
-system presented in equation \ref{eq:SkeletonExtraction} don't has
-a unique solution, the system solve it in the least-squares sense.
-With the new constraint the system then try to minimize the distance
-betwen the new vertex positions and the two planes.
-
-The new system of equations proposed
-
-\begin{equation}
-\left[\begin{array}{c}
-W_{L}L\\
-W_{H}\\
-W_{D}\Pi_{1}\\
-W_{D}\Pi_{2}
-\end{array}\right]X_{t+1}=\left[\begin{array}{c}
-0\\
-W_{H}X_{t}\\
--D_{1}\\
--D_{2}
-\end{array}\right]\label{eq:SkeletonExtractionDistance}
-\end{equation}
-
-where $W_{D}$ is the weigth to new constraints, that forced the vertices
-to move along of the normal line of every vertex. $\Pi_{1}$ and $\Pi_{2}$
-are matrix that contains $a,b,c$ values of the equation of the plane
-for every vertex. $D_{1}$ and $D_{2}$ are the vector with $d$ values
-of the equations of the planes for every vertex.
-
-\chapter{Results\label{sec:Results}}
-
-This chapter show the results of the Laplace Beltrami operator for
-hybrid quad/triangle meshes with several example models (see figures
-\ref{fig:Spectrum}, \ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark},
-\ref{fig:TQLBO_test}, \ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush},
-\ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}).
-It first show a comparisson of the Laplacian Operator in meshes composed
-by triangles, by quads and hybrid meshes composed by triangles/quads.
-Section \ref{sec:Customizing-Curvature-by} show the use of TQLBO
-in applications of Shape Inflation and Subdivision Surfaces on normal
-meshes and meshes change with isometric transformations. It Section
-\ref{sec:Shape-Inflation-Brush} show a novel shape inflation brush
-for sculpting systems that works in real time. It Section \ref{sec:Posing-Meshes-with}
-show mesh deformations and posing applications using differential
-coordinates defined with the TQLBO. It Section \ref{sec:Laplace-Operator-and}
-discusses the differences betwen common version and normalized version
-of the TQLBO. It Section \ref{sec:Performance-Testing-of} describe
-a performance comparison of differents numericals solvers used to
-solve a Laplacian linear equation system. Finally discusses some especific
-technical aspect about the implementation of the TQLBO on several
-computer systems at Section \ref{sec:Conclusion-and-future}.
-
-Figure \ref{fig:TQLBO_test} shows the results when applying the Laplace
-Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
-in a model with a simple subdivision. In column (c) the Laplacian
-smoothing was applied to a model consisting of only quads. In column
-(d) the model was converted to triangles and then the Laplacian smoothing
-was applied. In column (e) the model was randomly converted from some
-quads into triangles and then the Laplacian smoothing is applied,
-showing similar results to those meshes composed only of triangles
-or quads.
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[height=0.5\textheight]{resources/figs/test_triangles_quads}
-\par\end{centering}
-
-\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
-(c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
-(c) for triangles, (d) for quads, (e) for triangles and quads random
-chosen.}
-\end{figure}
-
-\section{Customizing Curvature by Shape Inflation.\label{sec:Customizing-Curvature-by}}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/spectrum}
-
-\caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
-$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
-$-5.0$.}
-\end{figure}
-
-The shape inflation was assessed with TQLBO method on a PC with AMD
-Quad-Core Processor @ 2.40 GHz and 8 GB RAM.
-
-Methods using the Catmull-Clark subdivision surface and the inflation
-allows to modify the curvature that is obtained with the process of
-subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
-test used a coarse cup model, in which the subdivision was performed,
-followed by a Laplacian smoothing and inflation. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
-groups over coarse models, with subdivision surfaces that allowed
-to generate the weights for the new interpolated vertices. These new
-weights were used for the inflation obtained on the 6 cups that are
-at the right of the figure \eqref{fig:Subdivision-Cups}.d.
-
-Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
-may produce similar results to those obtained with Catmull-Clark (see
-figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
-triangles. The one obtained with the Laplacian smoothing is shown
-in panel (c), (d) and those curvature modified versions are in (e)
-and (f). As can be observed, different versions of the original sketch
-can be obtained by parameterizing a single model value, a great advantage
-of the presented method. Figure \ref{fig:camello_enhanced} shows
-the generation of different versions of a camel according to the $\lambda$
-parameter. In the top row, it is shown the shape inflation results,
-as $\lambda$ becomes larger and negative, the resultant shape is
-observed as if the model would inflate the more convex parts, as shown
-in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
-the larger the model feature inflations. The bottom row of figure
-\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
-specifying which areas will be inflated. On the left, the inflation
-of the camel legs produces an organic aspect, notice that the border
-is not distorted and smooth.
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[height=0.5\textheight]{resources/figs/camello_enhanced2}
-\par\end{centering}
-
-\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
-Bottom row: Shape inflation with weight vertex group, $\lambda=-50.0$
-and 2 iterations for the legs, $\lambda=-200.0$ and 1 iteration for
-the head and neck.}
-\end{figure}
-
-The inflation of the silhouette features is predictable and invariant
-under isometric transformations, as those classically used in some
-animations (see Figure \ref{fig:Animated_Camell}). In this figure,
-the animation shows some camel poses during a walk, the inflation
-is performed at the neck and legs, as shown in the bottom left camel
-in figure \ref{fig:Animated_Camell}. Local modifications produced
-by the pose interpolation or animation rigging practically do not
-affect the result. In spite of at any pose of the camel legs there
-is a clear difference, the inflation method allows a flesh-like shape
-in the original pattern produced by the artist. This is due to the
-mesh restricted diffusion process so that small local changes are
-treated without affecting the global solution. The method therefore
-is rotation invariant since it depends exclusively on the normal mesh
-field, which is rotation invariant.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/camello_walk2}
-
-\caption{\label{fig:Animated_Camell}The method is pose insensitive. The inflation
-for the different poses are similar in terms of shape. Top row: Original
-walk cycle camel model. Bottom row: Shape inflation with weight vertex
-group, $\lambda=-400$ and $2$ iterations. }
-\end{figure}
-
-\section{Shape Inflation Brush in Real Time\label{sec:Shape-Inflation-Brush}}
-
-Figure \ref{fig:Sculpt_Brush} shows the use of a shape inflation
-brush for sculpting in real time. One pass was used with the brush,
-as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
-the camel foot shows the inflation intersection that looks like two
-bubbles, a similar pattern to what is observed to the fingers on the
-bottom of the same figure. The silhouette inflation is observed in
-figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
-together with its finger and foot details. Similar results can be
-obtained by a user, however it would take several steps and require
-the use of several brushes, while the shape inflation took a single
-step. Likewise, this new method can easily inflate organic features
-like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
-the shape inflation brush performance is illustrated, in this experiment
-three models with 12K, 40K and 164K vertices, were used. These models
-were sculpted with the shape inflate brush, at each step the brush
-sphere containing a variable number of vertices for processing. The
-processing time for 800 vertices in the camel paw (40k model) only
-took 0.1 seconds, for 2600 vertices in the leg and neck (model 40k)
-took 0.5 seconds, these times are suitable in real applications since
-an artist sculpts a model for parts.
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[height=0.3\textheight]{resources/figs/sculpt_brush}
-\par\end{centering}
-
-\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Inflate shape brush for leg into red
-circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
-circle, (c) Shape inflation brush for fingers in red circle.}
-\end{figure}
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[width=1\columnwidth]{resources/figs/verts_per_second_sculpt}
-\par\end{centering}
-
-\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape inflation
-brush in terms of the sculpted vertices per second. Three models with
-12K, 40K, 164K vertices used for sculpting in real time.}
-\end{figure}
-
-\section{Posing Meshes with Laplacian Deform\label{sec:Posing-Meshes-with}}
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{resources/figs/Armadillo}
-\par\end{centering}
-
-\caption{\label{fig:Armadillo}Anchor vertices in blue color. (a) Original
-Model, (b,c,d) new poses change only anchor vertices, system find
-positions for vertices in yellow color.}
-\end{figure}
-
-Figure \eqref{fig:Armadillo} shows the Laplacian Deform applied in
-a model with 173K vertices, only anchor vertices was used and are
-represented in blue color, when the user apply several transformation
-(location, rotation, scale) over this anchors vertices, the system
-find a solution and estimate the position of the vetices in yellow
-color. This method work in real time, to achieve this the matrix $\begin{bmatrix}w_{l}L\\
-W_{c}
-\end{bmatrix}$ in the equation \eqref{eq:LaplacianDefomSystem} is decomposed in
-matrix $LU$ with LU factorization only one time when the system init.
-Once the matrix is factorized the system can solve the unknowns in
-a fast way in term of miliseconds. For get better results the method
-permits solve several times the system of equations, and not need
-factorize matriz LU could be that at every iteration, only the differential
-coordinates are adjust since the differential coordinates can be rotated
-at every iteration and get bettter results. In the figure only four
-iterations were used, but the system find good solutions with only
-one iteration when the angle of rotations are less that $\pi$.
-
-\section{Laplace Operator and Normalized Version \label{sec:Laplace-Operator-and}}
-
-Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
-and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
-produce similar results if the triangles or quads that compose the
-mesh are about the same size. The normalized version is more stable
-and predictable because it is not divided by the area of the ring
-which may be very small and causes numeric problems, as shown in figure
-\ref{fig:(a)Monkey}.c bottom row. The shape inflation of the model
-with the normalized Laplacian operator results in a more regular pattern.
-The model can be deformed with a TQLBO normalized version with large
-$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
-Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
-areas in the model. Quadss with larger area have smaller inflation
-(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
-inflations (figure \ref{fig:(a)Monkey}.c chin).
-
-\begin{figure}[H]
-\includegraphics[width=1\columnwidth]{resources/figs/monkey}
-
-\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
-model scaled by 4. (b) Top and bottom row: inflating with Normalized-TQLBO
-$\lambda=-50$ (c) Top and bottom row: inflating with TQLBO $\lambda=-50$.}
-\end{figure}
-
-\section{Skeletonizer}
-
-Skeletonizer is a product of software that permits the proccessing,
-visualization and extraction of the skeleton from polygonal meshes.
-The software was designed with base in a plugin system and pipe-filters
-paradigm. This software implement the method for skeleton extraction
-describe in equation \ref{eq:SkeletonExtractionDistance}.
-
-The software is called sjSkeletonizer and use the following computacional
-frameworks and libraries.
-\begin{description}
-\item [{CGAL}] Computational Geometry Algorithms Library \cite{cgal}.
-\item [{Graphite}] is a research platform for computer graphics, 3D modeling
-and numerical geometry \cite{graphite}.
-\item [{QT}] is a cross-platform application and UI framework \cite{qt}.
-\end{description}
-\begin{figure}
-\includegraphics[width=1\textwidth]{resources/figs/poses}
-
-\caption{\label{fig:Skeleton-extraction-poses} Model with different poses
-and skeleton obtained with our skeleton extraction software.}
-
-\end{figure}
-
-\section{Performance Testing of Solvers \label{sec:Performance-Testing-of}}
-
-Performance evaluation of some numerical solvers for compute Laplacian
-Smooth system.
+For this project we choose a numerical solver to be included in Blender
+software with base in a performance evaluation of computation of the
+initial factorization of the Laplacian deform system.
 
@@
 
-$\frac{\partial V}{\partial t}=\lambda L\left(V\right)$
-
-Integrating the diffusion equation with a explicit Euler scheme
-
-$\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}$
-
-Where $V^{n+1}$ is the actual position of vertices, and $V^{t+1}$
-are the vertices after Laplacian Smoothing. $\lambda\partial t$ is
-the smoothing factor. L is the Laplacian Matrix defined in equation
-\ref{eq:TQLBO_Simple_Matrix}.
+\noindent \begin{center}
+$\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}X=\begin{bmatrix}\delta\\
+W_{c}C
+\end{bmatrix}$
+\par\end{center}
 
@@
 
+\noindent \begin{center}
 $Ax=b$
+\par\end{center}
 
@@
 
-$A=\left(I-\lambda\partial tL\right)$
+\noindent \begin{center}
+$A=\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}$
+\par\end{center}
 
-$x=V^{n+1}$
+\noindent \begin{center}
+$x=V$
+\par\end{center}
 
-$b=V^{n}$
+\noindent \begin{center}
+$b=\begin{bmatrix}\delta\\
+W_{c}C
+\end{bmatrix}$
+\par\end{center}
 
@@
 LU factorization is a numerical method that works with large, sparse,
-nonsymmetric systems of linear equations \cite{Levy2005}. We choose
-the implementacion of LU factorizacion in a OpenNL-SuperLU library,
-because this method show the better performance for the computacion
-of a solution for a Laplacian Smoothing linear system of equations
-presented in equation \ref{eq:LaplacianSmoothLinearEquationSystem}
-how see in the table \ref{tab:TimeVsSolvers}. OpenNLSuper allow works
-with the Graphics Unit Proccesor GPU, for exploit the capacity of
-GPU to work with parallel structures, more fast that traditional CPU.
+non-symmetric systems of linear equations \cite{Levy2005}. We choose
+the implementation of LU factorization in a OpenNL-SuperLU library,
+because this method show the better performance for the computation
+of a solution for a Laplacian Deform linear system of equations presented
+in equation \ref{eq:LaplacianDefomSystem} how see in the table and
+plot \ref{tab:TimeVsSolvers}, \ref{fig:Plot-IniFactor}. OpenNL SuperLU
+allow works with the Graphics Unit Processor GPU, for exploit the
+capacity of GPU to work with parallel structures, more fast that traditional
+CPU.
 
@@
 
-\caption{\label{tab:TimeVsSolvers}Vertices Vs Seconds, Laplacian Smoothing
-performance.}
+\protect\caption{\label{tab:TimeVsSolvers}Vertices Vs Seconds, Laplacian Deform initial
+factorization performance.}
 \end{table}
@@
 
-\caption{asdas}
-
+\protect\caption{\label{fig:Plot-IniFactor}Plot of Vertices Vs Seconds, Initial factorization
+performance.}
 \end{figure}
 
-\section{Implementation\label{sec:Implementation}}
+\section{Results}
 
-The method was implemented as a modifier for modeling and brush for
-sculpting, on the Blender software \cite{blender} in C and C++. Working
-with the Blender allowed to test the method interactively against
-others, as Catmull-Clark, weight vertex groups and sculpting system
-in Blender.
+The user interface for software Blender can be seen in figure \eqref{fig:Panel-LaplacianDeform}.
+In this tool the user define the anchor vertices with the use of vertex
+groups a feature offered by Blender, the user configure this name
+in the field \textsl{Anchors Vertex Group}. The \textsl{Bind} option
+initiate the system and capture the geometry details in form of differential
+coordinates and compute the factorization of the linear system, after
+that the system is ready to repose meshes in real-time user interaction
+session.
 
-To improve the performance, it was worked with the Blender mesh struct,
-visiting each triangle or quad and storing its corresponding index
-and the sum of the Laplacian weights of the ring in a list so that
-only two visits were required for the list of mesh faces and two times
-the edge list, if the mesh was not closed. This drastically reduced
-calculations, enabling real-time processing. In the construction of
-the Laplacian matrix, several index were locked at vertices having
-face areas or edge lengths with zero value that could cause spikes
-and bad results.
+\noindent \begin{center}
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics{resources/figs/Apinzonf_Diagram_Deform_Modifier_Panel_01}
+\par\end{centering}
 
-Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
-is sparse since the number of neighbors per vertex, corresponding
-to the number of data per row, is smaller compared to the total number
-of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
-was used OpenNL which is a a library for solving sparse linear system.
+\protect\caption{\label{fig:Panel-LaplacianDeform}Panel inside blender user interface
+of the Laplacian Deform modifier tool.}
+\end{figure}
 
-\chapter{Conclusion and future work\label{sec:Conclusion-and-future}}
+\par\end{center}
 
-This work presented an extension of the Laplace Beltrami operator
-for hybrid quad/triangle meshes that can be used in production environments
-and provides results similar to those obtained by working only with
-triangles or quads. This paper has introduced a new way to change
-silhouettes in a mesh for modeling or sculpting in a few steps by
-means of the curvature model modification while preserving its overall
-shape. In addition, a new modeling method has also been presented
-some possible applications have been illustrated. The method works
-properly with isometric transformations, opening the possibility of
-introducing it on the process of animation.
+Figure \eqref{fig:Armadillo} shows the Laplacian Deform applied in
+a model with 173K vertices, only anchor vertices was used and are
+represented in blue color, when the user apply several transformation
+(location, rotation, scale) over this anchors vertices, the system
+find a solution and estimate the position of the vertices in yellow
+color. This method work in real time, to achieve this the matrix $\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}$ in the equation \eqref{eq:LaplacianDefomSystem} is decomposed in
+matrix $LU$ with LU factorization only one time when the system initiate.
+Once the matrix is factorized the system can solve the unknowns in
+a fast way in term of milliseconds. For get better results the method
+permits solve several times the system of equations, and not need
+factorize matrix LU could be that at every iteration, only the differential
+coordinates are adjust since the differential coordinates can be rotated
+at every iteration and get better results. In the figure only four
+iterations were used, but the system find good solutions with only
+one iteration when the angle of rotations are less that $\pi$.
 
-We show that this tool may work in early modeling stages, case in
-which coarse models are used, allowing to modify the shape generated
-by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
-of the vertices with change of a single parameters.
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/Armadillo}
+\par\end{centering}
 
-Future work includes the analysis of theoretical relationships between
-the Catmull-Clark subdivision surfaces and the Laplacian smoothing
-since they can produce very similar results.
+\protect\caption{\label{fig:Armadillo}Anchor vertices in blue color. (a) Original
+Model, (b,c,d) new poses change only anchor vertices, system find
+positions for vertices in yellow color.}
+\end{figure}
+
+In figure \ref{fig:Cactus} show a comparison after made a one simple
+transformation that consist in rotate $70\lyxmathsym{º}$ to right
+the parts in blue color. between traditional method to interpolate
+the changes made in some parts of the mesh to entire model. The results
+for simple interpolation is show in \ref{fig:Cactus}.b and show how
+the main trunk loss your shape and is rotated. The propagation of
+changes made with Laplacian deform (figure \ref{fig:Cactus}.c) for
+the same transformation show better results and how the details and
+shape of the original model are preserve as best as possible.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/cactus}
+
+\protect\caption{\label{fig:Cactus}(a) Original cactus model. (b) Rotate 70º to right
+the blue segments with basic interpolation (c) Rotate 70º to right
+the blue segments with Laplacian deform tool.}
+\end{figure}
+
+The Laplacian Deform tool allow a user to repose a model while preserve
+the geometry details in the figure \ref{fig:Horse}.b y \ref{fig:Horse}c
+you can see the new pose of he horse after five transformations and
+rotation of the head, in figure \ref{fig:Horse}.b you was use basic
+interpolation and the shape and details are lost with every change
+made. In figure \ref{fig:Horse}..c yo can see how the new pose of
+the horse look more natural, and how the body and neck, of the horse
+preserve the original shape, this comparison show that method allow
+to apply any number of transformations without lost details, could
+be the system try to recover geometry details with base in the original
+pose of the model.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/horse}
+
+\protect\caption{\label{fig:Horse}(a) Original Horse model. (b) Translate and rotate
+the blue segments with basic interpolation (c) Translate and rotate
+the blue segments with Laplacian deform tool.}
+\end{figure}
 

### 2015-04-12 trunk/documents/thesis/thesis_LO_QT.tex

@@
 \usepackage{float}
+\usepackage{textcomp}
 \usepackage{amsthm}
@@
 
-\textbf{\huge Adapted Laplacian Operator For Hybrid Quad/Triangle
+\textbf{\huge{}An Adapted Laplacian Operator For Hybrid Quad/Triangle
 Meshes}{\huge \par}
@@
 
-\textbf{\large Alexander Pinzón Fernández}{\large \par}
+\textbf{\large{}Alexander Pinzón Fernández}{\large \par}
 
@@
 
-Facultad de Ingenieria, Departamento de Sistemas e Industrial
-
-{\small Grupo de Investigación CIM@LAB}{\small \par}
+Facultad de Ingeniería, Departamento de Sistemas e Industrial
+
+{\small{}Grupo de Investigación CIM@LAB}{\small \par}
 
@@
 
-{\small A thesis submitted in partial fulfillment of the requirements
+{\small{}A thesis submitted in partial fulfillment of the requirements
 for the degree of:}{\small \par}
@@
 
-{\small Advisor:}\\
-{\small Eduardo Romero Castro , Ph.D.}{\small \par}
-
-{\small \vspace{1.5cm}
+{\small{}Advisor:}\\
+{\small{}Eduardo Romero Castro , Ph.D.}{\small \par}
+
+{\small{}\vspace{1.5cm}
 }{\small \par}
 
-{\small Research Area:}\\
-{\small Computer Graphics}{\small \par}
-
-{\small \vspace{2cm}
+{\small{}Research Area:}\\
+{\small{}Computer Graphics}{\small \par}
+
+{\small{}\vspace{2cm}
 }{\small \par}
 
-{\small Universidad Nacional de Colombia}\\
-{\small Facultad de Ingenieria, Departamento de Sistemas e Industrial}\\
-{\small Grupo de Investigación CIM@LAB}\\
-{\small Bogotá, Colombia}\\
-{\small 2014}{\small \par}
+{\small{}Universidad Nacional de Colombia}\\
+{\small{}Facultad de Ingeniería, Departamento de Sistemas e Industrial}\\
+{\small{}Grupo de Investigación CIM@LAB}\\
+{\small{}Bogotá, Colombia}\\
+{\small{}2014}{\small \par}
 
@@
 
-{\small \vspace{4cm}
+{\small{}\vspace{4cm}
 }{\small \par}
@@
 \begin{minipage}[t]{8cm}%
-{\small A Beatriz y Campo Elias mis padres que siempre me dieron la
-libertad de escoger, con su comprensión y apoyo me permitieron dedicar
-mi tiempo a la ciencia.}{\small \par}
-
-{\small \vspace{1cm}
+{\small{}A Beatriz y Campo Elias mis padres que siempre me dieron
+la libertad de escoger, con su comprensión y apoyo me permitieron
+dedicar mi tiempo a la ciencia.}{\small \par}
+
+{\small{}\vspace{1cm}
 }{\small \par}
 
-{\small A mis padres}{\small \par}
-
-{\small \vspace{1cm}
+{\small{}A mis padres}{\small \par}
+
+{\small{}\vspace{1cm}
 }{\small \par}
@@
 
-Campo Elias Pinzon Rojas%
+Campo Elias Pinzón Rojas%
 \end{minipage}
@@
 
-\textbf{\LARGE Acknowledgement}{\LARGE \par}
-
-\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}
+\textbf{\LARGE{}Acknowledgment}{\LARGE \par}
+
+\addcontentsline{toc}{chapter}{\protect\numberline{}Acknowledgement}
 
@@
 
-I wold like to thank my advisor professor Eduardo Romero and CIM\&LAB
-research group for his support in this thesis.
-
-{\small \vspace{1cm}
+I wold like to thank my advisor professor Eduardo Romero and the CIM\&LAB
+research group for their support in this thesis.
+
+{\small{}\vspace{1cm}
 }{\small \par}
@@
 
-{\small \vspace{1cm}
+{\small{}\vspace{1cm}
 }{\small \par}
@@
 This work was supported in part by the Blender Foundation, Google
-Summer of code program at 2012 - 2013.
+Summer of code program 2012 and 2013.
 
@@
 
-\textbf{\LARGE Abstract}{\LARGE \par}
-
-\addcontentsline{toc}{chapter}{\numberline{}Abstract}
-
-In the last two decades three-dimensional modeling methods have been
-evolving and developing rapidly, thanks in part to the use of vector
-operators of differential geometry. The Laplacian operator has been
-one of the most widely studied and used thanks to the properties exhibited
-by their eigenvectors in novel applications such as noise reduction,
-enhancement, remeshing, UV mapping, posed, skeletonization, among
-other. The differential operator is defined in a continuous and smooth
-domain named manifold, manifolds are often approximated by discrete
+\textbf{\LARGE{}Abstract}{\LARGE \par}
+
+\addcontentsline{toc}{chapter}{\protect\numberline{}Abstract}
+
+In the last two decades three-dimensional modeling methods used by
+artists have been evolving and developing rapidly thanks to the use
+of vector operators of differential geometry such as the Laplacian
+operator. This operator allows to model in a simple way the behavior
+of complex applications such as noise reduction, enhancement, remeshing,
+UV mapping, posing and skeletonization, among others. The Laplacian
+operator is theoretically defined in a continuous and smooth domain
+named manifold. In practice manifolds are often approximated by discrete
 polygon meshes composed by triangles and quadrangles which represent
-the real world three-dimensional objects. In these meshes spectral
-structure is calculated using a discrete Laplacian operator, the discrete
-version of the Laplacian operator given by Pinkall in 1993 works only
-with meshes of triangles, and Xiong in 2011 working exclusively with
-quads. This thesis proposes an original extension of the Laplacian
-operator that allows to work with hybrid meshes composed by triangles
+the real world three-dimensional objects with which the artists work.
+In these meshes spectral structure is calculated using a discrete
+Laplacian operator, i.e. the discrete version of the Laplacian operator
+given by Pinkall in 1993. This approach only worked with triangle
+meshes. In 2011 Xiong extended the operator to work exclusively with
+quad meshes. This thesis proposes an original extension of the Laplacian
+operator that allows working with hybrid meshes composed by triangles
 and quadrangles.
@@
 Along with the operator, this work presents new sculpting and modeling
-applications with base on the enhancement, applications on subdivision
+applications based on enhancement. Additionally applications on subdivision
 surfaces using smoothing, mesh posing using differential coordinates
-and skeletonization using iterative contraction. This series of applications
-demonstrates the quality, predictability and flexibility of the proposed
-operator.
-
-The proposed operator was successfully used in real production environments
-within software Blender how new tools. Currently these tools are available
-as open source software.
-
-\textbf{\LARGE Resumen}{\LARGE \par}
+and skeletonization using iterative contraction are develop. This
+series of applications demonstrates the quality, predictability and
+flexibility of the proposed operator.
+
+The proposed operator was successfully used in new software tools
+in real production environment within 3D computer graphics software
+Blender. Currently these tools are available as open source software.
+
+\textbf{\LARGE{}Resumen}{\LARGE \par}
 
 En las dos últimas décadas los métodos de modelado tridimensional
-han ido evolucionando y desarrollándose rápidamente, en parte gracias
-al uso de operadores vectoriales de geometría diferencial. El operador
-Laplaciano ha sido uno de los más ampliamente estudiado y usado gracias
-a las propiedades exhibidas por sus vectores propios en novedosas
-aplicaciones como: reducción de ruido, realce, remallado, mapeo UV,
-posado, esqueletonización, entre otras. Este operador diferencial
-es definido en un dominio continuo y suave llamado variedad, las variedades
-son a menudo aproximadas por mallas discretas de polígonos compuestas
-por triángulos y cuadrángulos que a su vez representan objetos tridimensionales
-del mundo real. En estas mallas se calcula la estructura espectral
-con el uso de algún operador Laplaciano discreto, la versión discreta
-del operador Laplaciano propuesta por Pinkall en el 1993 trabaja únicamente
-con mallas compuestas por triángulos, y la de Xiong en el 2011 trabaja
-exclusivamente con cuadrángulos. Esta tesis propone una extensión
-original del Operador Laplaciano que permite trabajar con mallas híbridas
-compuestas por triángulos y cuadrángulos.
+utilizadas por los artistas han ido evolucionando y desarrollándose
+rápidamente, en parte gracias al uso de operadores vectoriales de
+geometría diferencial, como el operador de Laplace. Este operador
+permite modelar de una manera sencilla el comportamiento de aplicaciones
+complejas tales como la reducción de ruido, realce, remallado, mapeado
+UV, posado y esqueletonización, entre otros. Este operador Laplaciano
+es teóricamente definido en un dominio continuo y suave llamado variedad,
+las variedades son a menudo aproximadas por mallas discretas de polígonos
+compuestas por triángulos y cuadrángulos que a su vez representan
+objetos tridimensionales del mundo real que los artistas trabajan.
+En estas mallas se calcula la estructura espectral con el uso de algún
+operador Laplaciano discreto, la versión discreta del operador Laplaciano
+propuesta por Pinkall en el 1993 trabaja únicamente con mallas compuestas
+por triángulos, y la de Xiong en el 2011 trabaja exclusivamente con
+cuadrángulos. Esta tesis propone una extensión original del Operador
+Laplaciano que permite trabajar con mallas híbridas compuestas por
+triángulos y cuadrángulos.
 
@@
 
-El operador propuesto fue usado de forma exitosa en ambientes reales
-de producción dentro del software Blender como nuevas herramientas.
-Actualmente estas herramientas están disponibles como programas de
-código abierto.
-
-{\small \vspace{1cm}
+El operador propuesto fue usado con exitoso en las nuevas herramientas
+del software para gráficos 3D por computadora Blender. Actualmente
+estas herramientas están disponibles como programas de código abierto.
+
+{\small{}\vspace{1cm}
 }{\small \par}
 
-\textbf{\small Keywords: laplacian operator; smooth; enhance; sculpting;
+\textbf{\small{}Keywords: laplacian operator; smooth; enhance; sculpting;
 subdivision surface}{\small \par}
@@
 
-The discrete versions of Laplace Beltrami Operator have been used
-in the last years for the develop of new geometric modeling tools.
-In the work of Pinkall \cite{Pinkall1993} was introduced the cotangent
-version of Laplace operator, that allow to find the minimal surface
-when compute a discete harmonic map with the Laplacian operator, this
-version has been widely studied and applied in various problems of
-computer geometric modeling. The manifolds that are continuous domains
-homeomorphic to $\mathbb{R}^{n}$ are represented in computers by
-polygon meshes. These polygons are generally composed of triangles
-and quadrangles, while work with laplacian operator in this hybrid
-composition are not a mathematical challenge, most research uses only
-meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006},
-in other recent studies \cite{Liu2008,Xiong2011} the Laplacian operator
-is working exclusively with quadrangles. But in the artistic scope
-topology and the way the edges are distributed, the triangle and quadrangles,
-directly affects the processes of animation, interpolation, textured,
-etc. As discussed by \cite{Mullen2007} who use a manual connection
-of a couple of vertices to perform animation processes and interpolation.
-It is then of paramount importance to develop operators that easily
-interact with such meshes, eliminating the need of preprocessing the
-mesh to convert it to triangles and change the original topology.
-
-Modeling techniques able to generate a variety of realistic shapes,
-have been developed \cite{Botsch2006}. Editing techniques have evolved
-from affine transformations to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
-editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
-complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
-based methods however require to interact with a minimun number of
-control points for any operation to be efficient, or in other words,
-a unicity condition is introduced by demanding a smooth surface after
-any of these shape operations. Hence, traditional modeling methods
-for subdividing surfaces from coarse geometry have become widely popular
-\cite{Catmull1978,Stam1998}. These works have generalized a uniform
-B-cubic spline knot insertion to meshes, some of them adding some
-type of control, for instance with the use of creases to produce sharp
-edges \cite{DeRose1998}, or the modification of some vertex weights
-to locally control the zone of influence \cite{Biermann2000}. Neverteless
-these methods are difficult to deal with since they require a large
-number of parameters and a very tedious customization. Instead, the
-presented applications requires a single parameter that controls the
-global curvature, which is used to maintain realistic shapes, creating
-a family of different versions of the same object and therefore preserving
-the detail of the original model and a realistic appearance.
-
-The shape inflation and shape exaggeration can thus be used as such
-brush in the sculpting process, when inflating a shape since current
-brushes end up by losing detail when moving vertices \cite{Stanculescu2011}.
+The discrete versions of the Laplace Beltrami Operator have been used
+in the last years for the development of new geometric modeling tools.
+Pinkall \cite{Pinkall1993} introduced the cotangent version of the
+Laplace operator, that allowed finding the minimal surface when computing
+a discrete harmonic map with the Laplacian operator. This version
+has been widely studied and applied in various problems of computer
+geometric modeling. This type of operator was defined over manifolds,
+i.e. continuous domains homeomorphic to $\mathbb{R}^{n}$ that are
+represented in pratice by polygon meshes. These polygons are generally
+composed of triangles and quadrangles. While working with Laplacian
+operator in this hybrid composition is not a mathematical challenge,
+most research only uses meshes composed by triangles \cite{Pinkall1993,Desbrun1999,Meyer2003,Sorkine2004,Au2008,Belkin2008,Hahne2006}.
+In recent studies \cite{Liu2008,Xiong2011}, the Laplacian operator
+may be use in meshes composed exclusively by quadrangles. However,
+from artistic point of view, the topology and the way the edges, triangles
+and quadrangles are distributed directly affects the processes of
+animation, interpolation, texturing, etc., as discussed by \cite{Mullen2007}
+who uses a manual connection of a pair of vertices to perform animation
+processes and interpolation. It is then of paramount importance to
+develop operators that easily interact with such meshes, eliminating
+the need of preprocessing the mesh to convert it to triangles and
+change the original topology.
+
+Presently there are available modeling techniques able to generate
+a variety of realistic shapes \cite{Botsch2006}. Editing techniques
+have evolved from affine transformations to advanced tools like sculpting
+\cite{Coquillart1990,Galyean1991,Stanculescu2011}, editing, creation
+from sketches \cite{Igarashi1999,Gonen2012}, and complex interpolation
+techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark based methods
+however require to interact with a minimum number of control points
+for any operation to be efficient, or in other words, a unicity condition
+is introduced by demanding a smooth surface after any of these shape
+operations. Hence, traditional modeling methods for subdividing surfaces
+from coarse geometry have become widely popular \cite{Catmull1978,Stam1998}.
+These works have generalized a uniform B-cubic spline knot insertion
+to meshes. Some of these adds some type of control; for instance with
+the use of creases to produce sharp edges \cite{DeRose1998} or the
+modification of some vertex weights to locally control the zone of
+influence \cite{Biermann2000}. Nevertheless  these methods are difficult
+to use as they require a large number of parameters and a very tedious
+customization.
+
+On the other hand, the proposed applications requires a single parameter
+that controls the global curvature, which is used to maintain realistic
+shapes, creating a family of different versions of the same object
+and therefore preserving the detail of the original model and a realistic
+appearance.
+
+The shape inflation and shape exaggeration can thus be used as a type
+of brush in the sculpting process. When inflating a shape with other
+brushes the former ends up losing detail when moving vertices \cite{Stanculescu2011}.
 In contrast, the presented enhance method inflates a mesh by moving
@@
 This work presents an extension of the Laplace Beltrami Operator for
+hybrid quad/triangle meshes that have a larger mesh functionality
+spectrum than common triangular or quadrangular meshes. The method
+eliminates the need of preprocessing and allows preservation of the
+original topology. Along with this operator, we propose a method to
+generate a family of parameterized shapes, in a robust and predictable
+way. This method enables customization of the smoothness and curvature
+obtained during the subdivision surfaces process. Finally, a new brush
+for inflating the silhouette mesh features in modeling and sculpting
+is proposed.
+
+The work is organized as follows: Chapter \ref{chap:Mathematical-foundation}
+presents works related to the Laplacian operator, applications in
+digital sculpting, deformation, and offsetting methods for polygonal
+meshes. It also describes the theoretical framework of the Laplacian
+operator for polygon meshes; In chapter \ref{chap:SibgrapiPaper},
+we show the extension of the Laplacian Operator for hybrid meshes
+and the applications of shape inflation ,subdivision of surfaces and
+sculpting; In chapter \ref{sub:Laplacian-Smooth}, we present an application
+for mesh smoothing of the the Laplacian operator extension proposed
+implemented in a well known software for computer modelling. Finally
+in chapter \ref{sub:Laplacian-Deform}, we present a successfull application
+for mesh deformation and model re-posing based on differential coordinates
+and the adaptation of this method to work with our Laplacian operator
+extension.
+
+\chapter{Mathematical Foundation and Background\label{chap:Mathematical-foundation}}
+
+This chapter studies basic mathematical foundation on differential
+geometry to understand the differential operators and the Laplace
+Beltrami operator.
+
+The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
+These differential operators show a deep relationship between the
+geometry (curvatures, geodesics) and topology of the manifold. They
+have been commonly used in computer geometric modelling applications
+over the last years \cite{Rosenberg1997,Alexa2011}.
+
+\section{Related work}
+
+Many tools have been developed for modeling based on the Laplacian
+mesh processing. These tools preserve the surface geometric details
+when using laplacian operators for different processes such as smoothing,
+enhancing, free-form deformation, fusion, morphing and other applications
+\cite{Ranjan2012}.
+
+The most used discretization of Laplace Beltrami operator $\Delta_{\mbox{\ensuremath{\Omega}}}$
+over a triangulated mesh $\Omega$ was proposed by Pinkall \cite{Pinkall1993}.
+
+\noindent \begin{center}
+$\Delta_{\mbox{\ensuremath{\Omega}}}\left(u\right)=\frac{1}{2}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(x_{i}-x_{j}\right)$
+\par\end{center}
+
+Where $N_{1}$is the 1-ring neighborhood, $\alpha$ and $\beta$ are
+the opposite angles to edge between vertex $i$ and vertex $j$. In
+this work the discrete laplacian operator is used to find the minimal
+surface based on minimization energy strategy using the Dirichlet's
+energy of the function $u$ over a manifold represented by triangulated
+mesh $\Omega$.
+
+\noindent \begin{center}
+$E_{D}\left(u\right)=\frac{1}{2}\int_{\Omega}\bigl|\nabla u\bigr|^{2}$
+\par\end{center}
+
+Taubin \cite{Taubin1995} treats for the first time the problem of
+noise reduction in digital polygonal meshes from signal processing
+point of view. He extends Fourier analysis to signals defined on polygonal
+meshes and observes that Fourier transform is a decomposition of the
+signal into eigenvectors of the Laplacian operator and reconstructs
+the signal with a linear combination of these eigenvectors. Desbrun
+et al. \cite{Desbrun1999} consider the same approach of Taubin, but
+they use a curvature normal ($\bar{\kappa}\mathbf{n}$) based on cotangent
+Laplace operator version for noise reduction over a diffusion process.
+This is the most famous and popular Laplace Beltrami operator discretization
+\cite{Liu2008}, many works for mesh smoothing and fairing have been
+developed based on his Laplace Beltrami Operator (LBO) discretization
+\cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}:
+
+\noindent \begin{center}
+$\frac{\partial x_{i}}{\partial t}=-\bar{\kappa_{i}}\mathbf{n_{i}}$
+\par\end{center}
+
+\noindent \begin{center}
+$-\bar{\kappa_{i}}\mathbf{n_{i}}=\frac{1}{A}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)$
+\par\end{center}
+
+where $A$ is the area surrounding vertex $i$. This laplacian operator
+$L$ was used to reduce the noise in a mesh $X$ over a diffusion
+process.
+
+The convergence of the Laplace Beltrami operator has been very important
+in fields such as numerical analysis, given its implications in the
+simulation process and geometric partial differentials equations.
+Xu et al. \cite{Xu2004} established the convergence of several discrete
+Laplace Beltrami operators over triangulated meshes with numerical
+results that support the theoretical analysis. Over quadrilateral
+meshes Liu et al. \cite{Liu2008} present a discrete Laplace Beltrami
+Operator based on a bilinear interpolation and its convergence over
+meshes composed only by quads.
+
+In the work of Sorkine \cite{Sorkine2006} the laplacian operator
+was used to re-pose a mesh while preserving geometry details of the
+surface. The details were stored in differential coordinates $\delta_{i}$
+for every vertex $v_{i}$.
+
+\noindent \begin{center}
+$\delta_{i}=\sum_{j\in N_{1}\left(i\right)}\frac{1}{2}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)$
+\par\end{center}
+
+The differential coordinates represent the difference between the
+absolute coordinate of $v_{i}$and the center of mass of its immediate
+neighbors.
+
+Offset methods for polygon meshing, based on the curvature defined
+by the Laplace Beltrami operator, have been developed. These methods
+adjust the shape offset by a constant distance, with high precision.
+Nevertheless, these methods fail to conserve sufficient detail because
+of the smoothing, a crucial issue which depends on the offset size
+\cite{Zhuo2012}. In volumetric approaches, in case of point-based
+representations, the offset boundary computation is based on the distance
+field and therefore when calculating such offset, the topology of
+the model may be different to the original \cite{Chen2011}.
+
+Gal et al. \cite{Gal2009} propose automatic feature detection and
+shape edition with feature inter-relationship preservation. They define
+salient surface features like ridges and valleys, characterized by
+their first and second order curvature derivatives (see \cite{Ohtake2004})
+and angle-based thresholds. Likewise, curves have been also classified
+as planar or non-planar, approximated by lines, circles, ellipses
+and other complex shapes. In each case, the user defines an initial
+change over several features which is propagated towards other features,
+based on the classified shapes and the inter-relationships between
+them. This method works well with objects that have sharp edges, composed
+of basic geometric shapes such as lines, circles or ellipses. However,
+the method is very limited when models are smooth since it cannot
+find the proper features to edit.
+
+Digital sculpting has been traditionally approached either under a
+polygonal representation or a voxel grid-based method. Brushes for
+inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
+In grid-based sculpting, some other operations have allowed to add
+or remove voxels since production of polygonal meshes require a processing
+of isosurfaces from a volume \cite{Galyean1991}. The drawback comes
+from the difficulty of maintaining the surface details during larger
+scale deformations.
+
+In the literature, several studies have described the skeleton extraction
+systems and different metrics that identify appropriate methods given
+a specific application \cite{Attali2007}. One of the best methods
+reported in the literature for the extraction of the skeleton is the
+Laplacian smoothing method given its advantages of homotopy representation
+and hierarchical connections between parts. The skeleton extraction
+methods permit simplifying the dimension of the object preserving
+the topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
+present a skeleton extraction method based on iterative smoothing-contraction.
+In this method several constraints are used to warrant that the process
+converges to a skeleton formed by branches and joints. The constraints
+are based on laplacian operator; the low frequencies of the mesh are
+preserved with the use of an attractor to the original mesh, while
+the iterative smoothing process removes high frequencies.
+
+\section{Manifolds}
+
+A manifold is a topological space $M$ with the following properties:
+
+If $x\in M$, then there is some neighborhood $N\left(x\right)$ and
+some integer $n\geq0$ such that $N(x)$ is homeomorphic to $\mathbb{R}^{n}$
+\cite{Spivak1-1999}.
+
+Our work is related to manifolds that represent a surface in an three-dimensional
+Euclidean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.
+
+The manifolds are represented by polygonal meshes with points connected
+by triangles and quads.
+
+\section{Laplace Operator}
+
+In computer graphics a manifold is often approximated by a discrete
+mesh \cite{Ranjan2012}, then is necessary to define a discrete laplacian
+operator that act on functions defined on such meshes.
+
+Consider a smooth compact manifold $M$ of dimension $m$ isometrically
+embedded in a Euclidean space $\mathbb{R}^{d}$.
+
+Given a twice continuously differentiable function $f\in C^{2}\left(M\right)$,
+let $\nabla_{\mbox{M}}f$ denote the gradient vector field of $f$
+on $M$.
+
+The Laplace-Beltrami operator $\Delta_{\mbox{M}}$ of $f$ is defined
+as the divergence of the gradient; that is \cite{Spivak1-1999},
+
+\noindent \begin{center}
+$\frac{\partial^{2}f}{\partial x^{2}}+\frac{\partial^{2}f}{\partial y^{2}}+\frac{\partial^{2}f}{\partial z^{2}}=0$
+\par\end{center}
+
+\noindent \begin{center}
+$\nabla_{\mbox{M}}^{2}f=\Delta_{\mbox{M}}f=0$
+\par\end{center}
+
+\noindent 
+\begin{equation}
+\Delta_{\mbox{M}}f=div\left(\nabla_{\mbox{M}}f\right)
+\end{equation}
+
+\subsection{Discrete Laplace Operator Setting}
+
+Discrete Laplacian operators are linear operators that act on functions
+defines on meshes. These functions are specified by their values at
+the vertices.
+
+Thus, if a mesh $M$ has $n$ vertices, then functions on $M$ will
+be represented by vectors with $n$ components and a mesh Laplacian
+will be described by an $n\times n$ matrix \cite{Ranjan2012}.
+
+The Laplacian operator locally takes the difference between the value
+of a function at a vertex and a weighted average of its values at
+the first-order or one-ring neighbor vertices, then a Laplacian matrix
+$L$ has a local form given by
+
+\noindent \begin{center}
+$L\left(f\right)_{i}=b_{i}^{-1}\underset{j\in N\left(i\right)}{\sum}w_{ij}\left(f_{i}-f_{j}\right)$
+\par\end{center}
+
+Where $w_{ij}$are the weights between the vertex $i$ and the vertex
+$j$. $b_{i}^{-1}$ are the factors depending of the boundary region
+over vertex $i$. $N\left(i\right)$ are the neighbors that share
+a edge with vertex $i$.
+
+\chapter{Shape Inflation With an Adapted Laplacian Operator For Hybrid Quad/Triangle
+Meshes\label{chap:SibgrapiPaper}}
+
+\noindent \begin{center}
+Alexander Pinzón, Eduardo Romero\\
+Cimalab Research Group\\
+Universidad Nacional de Colombia\\
+Bogota-Colombia\\
+Email: apinzonf@unal.edu.co, edromero@unal.edu.co
+\par\end{center}
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/spectrum}
+
+\protect\caption{\label{PAPER:fig:Spectrum}A set of 48 successive shapes enhanced,
+from $\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps
+of $-5.0$.}
+\end{figure}
+
+This paper was accepted and presented in the Brazilian Symposium on
+Computer Graphics and Image Processing SIBGRAPI 2013. The conference
+was held on August 5-8 of 2013, in the city of Arequipa, Perú \cite{Pinzon2013}.
+
+\section*{Abstract}
+
+This paper proposes a novel modeling method for a hybrid quad/triangle
+mesh that allows to set a family of possible shapes by controlling
+a single parameter, the global curvature. The method uses an original
+extension of the Laplace Beltrami operator that efficiently estimates
+a curvature parameter which is used to define an inflated shape after
+a particular operation performed in certain mesh points. Along with
+the method, this work presents new applications in sculpting and modeling,
+with subdivision of surfaces and weight vertex groups. A series of
+graphics examples demonstrates the quality, predictability and flexibility
+of the method in a real production environment with software Blender.
+\begin{description}
+\item [{keywords-}] laplacian smooth; curvature; sculpting; subdivision
+surface
+\end{description}
+
+\section{Introduction}
+
+Over the last years several, modeling techniques able to generate
+a variety of realistic shapes, have been developed \cite{Botsch2006}.
+Editing techniques have evolved from affine transformations to advanced
+tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
+editing, creation from sketches \cite{Igarashi1999,Gonen2012}, and
+complex interpolation techniques \cite{Sorkine2004,Zhou2005}. Catmull-Clark
+based methods however require to interact with a small number of control
+points for any operation to be efficient, or in other words, a unity
+ condition is introduced by demanding a smooth surface after any of
+these shape operations. Hence, traditional modeling methods for subdividing
+surfaces from coarse geometry have become widely popular \cite{Catmull1978,Stam1998}.
+These works have generalized a uniform B-cubic spline knot insertion
+to meshes, some of them adding some type of control, for instance
+with the use of creases to produce sharp edges \cite{DeRose1998},
+or the modification of some vertex weights to locally control the
+zone of influence \cite{Biermann2000}. Nevertheless these methods
+are difficult to deal with since they require a large number of parameters
+and a very tedious customization. Instead, the presented method requires
+a single parameter that controls the global curvature, which is used
+to maintain realistic shapes, creating a family of different versions
+of the same object and therefore preserving the detail of the original
+model and a realistic appearance.
+
+Interest in meshes composed of triangles and quads has lately increased
+because of the flexibility of modeling tools such as Blender 3D \cite{blender}.
+Nowadays, many artists use a manual connection of a couple of vertices
+to perform animation processes and interpolation \cite{Mullen2007}.
+It is then of paramount importance to develop operators that easily
+interact with such meshes, eliminating the need of preprocessing the
+mesh to convert it to triangles. The shape inflation and shape exaggeration
+can thus be used as such brush in the sculpting process, when inflating
+a shape since current brushes end up by losing detail when moving
+vertices \cite{Stanculescu2011}. In contrast, the presented method
+inflates a mesh by moving the vertices towards the reverse curvature
+direction, conserving the shape and sharp features of the model.
+
+\subsection*{Contributions }
+
+This work presents an extension of the Laplace Beltrami operator for
 hybrid quad/triangle meshes, representing a larger mesh spectrum from
@@
 along with this operator, it is proposed a method to generate a family
-of parameterized shapes, in a robust and predictable way. This method
+of parametrized shapes, in a robust and predictable way. This method
 enables customization of the smoothness and curvature, obtained during
@@
 
-This work is organized as follows: Chapter \ref{sub:1.1-Related-work}
-presents works related to the Laplacian operator, applications in
-digital sculpting, deformation, and offsetting methods for polygonal
-meshes; In chapter \ref{chap:Mathematical-foundation}, it is described
-the theoretical framework of the Laplacian operator for polygon meshes;
-In chapter \ref{sec:Proposed-Method}, it is presented the extension
-of the Laplacian Operator for hybrid meshes and applications of shape
-inflation ,subdivision of surfaces , deformation, skelenotization
-and sculpting; finally some Laplacian Operator results, to hybrid
-quad/triangle meshes are graphically shown as well as results of the
-shape inflation applications in sculpting, subdivision, deformation,
-skelenotization and modeling.
-
-\chapter{Related work\label{sub:1.1-Related-work}}
+This work is organized as follows: Section \ref{sec:Related-work}
+presents works related to the Laplacian mesh processing, digital sculpting,
+and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth},
+it is described the theoretical framework of the Laplacian operator
+for polygon meshes; In section \ref{PAPER:sec:Proposed-Method}, it
+is presented the method for shape inflation and applications of subdivision
+of surfaces and sculpting; finally some Laplacian operator results,
+to hybrid quad/triangle meshes are graphically shown as well as results
+of the shape inflation applications in sculpting, subdivision and
+modeling.
+
+\section{Related work\label{sec:Related-work}}
 
 Many tools have been developed for modeling, based on the Laplacian
-mesh processing. These different tools preserve the surface geometric
-details when using laplacian operators for different processes such
-as smoothing, enhancing, free-form deformation, fusion, morphing and
-other applications \cite{Ranjan2012}.
-
-The most used discretization of Laplace Beltrami operator $\Delta_{\mbox{\ensuremath{\Omega}}}$
-over a triangulated mesh $\Omega$ was proposed by Pinkall \cite{Pinkall1993}.
-
-\noindent \begin{center}
-$\Delta_{\mbox{\ensuremath{\Omega}}}\left(u\right)=\frac{1}{2}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(x_{i}-x_{j}\right)$
-\par\end{center}
-
-Where $N_{1}$is the 1-ring neighboorhood, $\alpha$ and $\beta$
-are the opposite angles to edge between vertex $i$ and vertex $j$.
-In this work the discretize laplacian operator was used to find the
-minimal surface based on minimization energy strategy using the Dirichlet's
-energy of the function $u$ over a manifold represented by triangulated
-mesh $\Omega$.
-
-\noindent \begin{center}
-$E_{D}\left(u\right)=\frac{1}{2}\int_{\Omega}\bigl|\nabla u\bigr|^{2}$
-\par\end{center}
-
-Then Taubin works \cite{Taubin1995} for first time treat the problem
-of noise reduction in digital poligonal meshes from signal proccessing
-point of view. Taubin extends Fourier analysis to signals defined
-on polygonal meshes, Taubin observe that Fourier transform is a decomposition
-of the signal into an eigenvectors of the Laplacian operator, and
-reconstruct the signal with a linear combination of these eigenvectors.
-Desbrun works \cite{Desbrun1999} consider the same approach of Taubin,
-but Desbrun use a curvature normal ($\bar{\kappa}\mathbf{n}$) based
-on cotangen Laplace operator version for noise reduction over a difussion
-process. This it's the most important and popular Laplace Beltrami
-opertator discretization \cite{Liu2008}, many works for mesh smoothing
-and fairing have been developed based on this LBO discretization \cite{Desbrun2000,Meyer2003,Schneider2001,Nealen2006}.
-
-\noindent \begin{center}
-$\frac{\partial x_{i}}{\partial t}=-\bar{\kappa_{i}}\mathbf{n_{i}}$
-\par\end{center}
-
-\noindent \begin{center}
-$-\bar{\kappa_{i}}\mathbf{n_{i}}=\frac{1}{A}\sum_{j\in N_{1}\left(i\right)}\left(\cot\alpha_{j}+\cot\beta_{j}\right)$
-\par\end{center}
-
-Where $A$ is the area surrounding vertex $i$. This laplacian operator
-$L$ was used for reduce the noise in a mesh $X$ over a difussion
-process.
-
-The convergence of the Laplace Beltrami operator has been very important
-in fields how numerical analysis, given that implications in the simulation
-process and geometric partial differentials equations. In the works
-of \cite{Xu2004} is established the convergence of several discrete
-Laplace Beltrami operators over triangulated meshes with numerical
-results that support the theoretical analysis. Over quadrilateral
-meshes Liu \cite{Liu2008} presents a discrete Laplace Beltrami Operator
-based on a bilinear interpolation and its convergence over this type
-of meshes composed only by quads.
-
-In the work of Sorkine \cite{Sorkine2006} the laplacian operator
-was used to repose a meshes while preserving geometry details of the
-surface. The details was stored in differential coordinates $\delta_{i}$
-for every vertex $v_{i}$.
-
-\noindent \begin{center}
-$\delta_{i}=\sum_{j\in N_{1}\left(i\right)}\frac{1}{2}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)$
-\par\end{center}
-
-The differential coordinates represents the difference between the
-absolut coordinate of $v_{i}$and the center of mass of its immediate
-neighboors.
+mesh processing. Thanks to the advantages of the Laplacian operator,
+these different tools preserve the surface geometric details when
+using them for different processes such as free-form deformation,
+fusion, morphing and other applications \cite{Sorkine2004}.
 
@@
 
-\cite{Gal2009} propose automatic feature detection and shape edition
+\cite{Gal2009} proposes automatic feature detection and shape edition
 with feature inter-relationship preservation. They define salient
-surface features like ridges and valleys, characerized by their first
+surface features like ridges and valleys, characterized by their first
 and second order curvature derivatives, see \cite{Ohtake2004}, and
@@
 and other complex shapes. In such case, the user defines an initial
-change over several features which is propagated towards other features,
+change over several features which are propagated towards other features,
 based on the classified shapes and the inter-relationships between
@@
 
-Digital sculpting have been traditionally approached either under
-a polygonal representation or a voxel grid-based method. Brushes for
+Digital sculpting has been traditionally approached either under a
+polygonal representation or a voxel grid-based method. Brushes for
 inflation operations only depend on the vertex normal \cite{Stanculescu2011}.
@@
 
-In the literature, several studies have described the skeleton extraction
-systems and different metrics that identify appropriate methods given
-an application specific \cite{Attali2007}. One of the best methods
-reported in the literature for the extraction of the skeleton is the
-Laplacian smoothing method for its advantages of homotopy representation
-and hierarchical connections between parts. The Skeleton extraction
-methods permits simplify the dimension of the object preserving the
-topological structure \cite{Cornea2007}, Au et. al. \cite{Au2008}
-present a skeleton extraction method based on iterative smooothing-contraction,
-in this method the several constraints are used to waranty that the
-process converge to skeleton formed by branchs and joins, the constraints
-based on laplacian operator, the low frequencies of the mesh are preserving
-with the use of attractor to original mesh, while the iterative smoothin
-process remove high frecuencies.
-
-\chapter{Mathematical foundation\label{chap:Mathematical-foundation}}
-
-This chapter studies basic mathematical foundation on differential
-geometry to understand the differential operators and the Laplace
-beltrami operator.
-
-The differential geometry studies curvatures and geodesics \cite{Hahne2006}.
-The differential operators show a deep relationships betwen the geoemetry
-(curvatures, geodesics) and topology of the manifold. This differential
-operators are very used in applications on computer geometric modelling
-over the last years \cite{Rosenberg1997,Alexa2011}.
-
-\section{Manifolds}
-
-A manifold is a topological space $M$ with the following properties:
-
-If $x\in M$, then there is some neighborhood $N\left(x\right)$ and
-some integer $n\geq0$ such that $N(x)$ is homeomorphic to $\mathbb{R}^{n}$
-\cite{Spivak1-1999}.
-
-This work is related to manifolds that represent a surface in an three-dimensional
-Eucliddean Space. This manifolds are homeomorphic to $\mathbb{R}^{2}$.
-
-The manifols are represented by polygonal meshes with points connected
-by triangles and quads.
-
-\section{Laplace Operator}
-
-In computer graphics a manifold is often approximated by a discrete
-mesh \cite{Ranjan2012}, then is necessary to define a discrete laplacian
-operator that act on functions defined on such meshes.
-
-Consider a smooth compact manifold $M$ of dimension $m$ isometrically
-embedded in a Euclidean space $\mathbb{R}^{d}$.
-
-Given a twice continuously differentiable function $f\in C^{2}\left(M\right)$,
-let $\nabla_{\mbox{M}}f$ denote the gradient vector field of $f$
-on $M$.
-
-The Laplace-Beltrami operator $\Delta_{\mbox{M}}$ of $f$ is defined
-as the divergence of the gradient; that is \cite{Spivak1-1999},
-
-\noindent \begin{center}
-$\frac{\partial^{2}f}{\partial x^{2}}+\frac{\partial^{2}f}{\partial y^{2}}+\frac{\partial^{2}f}{\partial z^{2}}=0$
-\par\end{center}
-
-\noindent \begin{center}
-$\nabla_{\mbox{M}}^{2}f=\Delta_{\mbox{M}}f=0$
-\par\end{center}
-
-\noindent 
-\begin{equation}
-\Delta_{\mbox{M}}f=div\left(\nabla_{\mbox{M}}f\right)
-\end{equation}
-
-\subsection{Discrete Laplace Operator Setting}
-
-Discrete Laplacian operators are linear operators that act on functions
-defines on meshes. These functions are specified by their values at
-the vertices.
-
-Thus, if a mesh $M$ has $n$ vertices, then functions on $M$ will
-be represented by vectors with $n$ components and a mesh Laplacian
-will be described by an $n\times n$ matrix \cite{Ranjan2012}.
-
-The Laplacian operator locally takes the difference between the value
-of a function at a vertex and a weighted average of its values at
-the first-order or one-ring neighbor vertices, then a Laplacian matrix
-$L$ has a local form given by
-
-\noindent \begin{center}
-$L\left(f\right)_{i}=b_{i}^{-1}\underset{j\in N\left(i\right)}{\sum}w_{ij}\left(f_{i}-f_{j}\right)$
-\par\end{center}
-
-Where $w_{ij}$are the weights between the vertex $i$ and the vertex
-$j$. $b_{i}^{-1}$ are the factors depending of the boundary region
-over vertex $i$. $N\left(i\right)$ are the neighbors that share
-a edge with vertex $i$.
+\section{Laplacian Smooth\label{sec:Laplacian-Smooth}}
+
+Computer objects, reconstructed from the real world, are usually noisy.
+Laplacian Smooth techniques allow a proper noise reduction on the
+mesh surface with minimal shape changes, while still preserving a
+desirable geometry as well as the original shape.
+
+Many smoothing Laplacian functionals regularize the surface energy
+by controlling the total surface curvature $S$.
+
+\noindent \begin{center}
+$E\left(S\right)=\int_{S}\kappa_{1}^{2}+\kappa_{2}^{2}dS$
+\par\end{center}
+
+Where $\kappa_{1}$ and $\kappa_{2}$ are the two principal curvatures
+of the surface $S$.
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/voronoi_region}
+
+\protect\caption{\label{fig:voronoi_region-1}Area of the Voronoi region around $v_{i}$
+in dark blue.$v_{j}$ belong to the first neighborhood around $v_{i}$.
+$\alpha_{j}$ and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
+\end{figure}
+
 Consider a surface $S$ composed of a set of triangles around vertex
-$v_{i}$. Let us define the \textsl{Voronoi Region} of $v_{i}$ as
-show in figure \ref{fig:voronoi_region}, The area change produced
+$v_{i}$. Let us define the \textsl{Voronoi region} of $v_{i}$ as
+show in figure \ref{fig:voronoi_region-1}, The area change produced
 by the movement of $v_{i}$ is called the gradient of \textsl{Voronoi
@@
 
-\noindent 
-\begin{align}
-\nabla A & =\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\left(v_{i}-v_{j}\right)\label{eq:eq_gradient_voronoi_area}
-\end{align}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/voronoi_region}
-
-\caption{\label{fig:voronoi_region}Area of the Voronoi region around $v_{i}$
-in dark blue.$v_{j}$ belong to the first neighborhood around $v_{i}$.
-$\alpha_{j}$ and $\beta_{j}$ opposite angles to edge $\protect\overrightarrow{v_{j}-v_{i}}$. }
-\end{figure}
-
-If the gradient in equation \ref{eq:eq_gradient_voronoi_area} is
-normalized by the total area of the 1-ring neighborhood around $v_{i}$,
-the \textsl{discrete mean curvature normal} of a surface $S$ is obtained,
-as shown in equation \ref{eq:discrete_mean_curvature_normal}.
-
-\noindent 
 \begin{equation}
-2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{eq:discrete_mean_curvature_normal}
+\nabla A=\frac{1}{2}\underset{j}{\sum}\left(\cot\alpha_{j}+\cot\beta_{j}\right)\label{PAPER:eq:eq_gradient_voronoi_area}
 \end{equation}
 
-\section{Laplace Beltrami Operator}
-
-The \textit{Laplace Beltrami operator} LBO noted as $\Delta$ is used
-for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.
-
-\noindent 
+If the gradient in equation (\ref{PAPER:eq:eq_gradient_voronoi_area})
+is normalized by the total area of the $1$-ring neighborhood around
+$v_{i}$, the \textsl{discrete mean curvature normal} of a surface
+$S$ is obtained, as shown in equation (\ref{PAPER:eq:discrete_mean_curvature_normal}).
+
 \begin{equation}
-\Delta_{\mbox{S}}=2\kappa\mathbf{n}\label{eq:def_LBO}
+2\kappa\mathbf{n}=\frac{\nabla A}{A}\label{PAPER:eq:discrete_mean_curvature_normal}
 \end{equation}
 
-\chapter{Proposed Laplacian Operator\label{sec:Proposed-Method}}
-
-This thesis propose an original extension of the Laplace Beltrami
+\subsection{Laplace Beltrami Operator}
+
+The \textsl{Laplace Beltrami operator} LBO noted as $\triangle$ is
+used for measuring the mean curvature normal to the Surface $S$ \cite{Pinkall1993}.
+
+\begin{equation}
+\triangle S=2\kappa\mathbf{n}\label{PAPER:eq:def_LBO}
+\end{equation}
+
+The LBO has desirable properties: the LBO points out to the direction
+of the minimal surface area.
+
+\section{Proposed Method\label{PAPER:sec:Proposed-Method}}
+
+This method exaggerates a shape using a Laplacian smoothing operator
+in the reverse direction, i.e., the new shape is a modified version
+in which those areas with larger curvature are magnified. The operator
+amounts to a generator of a set of models which conserves the basic
+silhouette of the original shape. In addition, the presented approach
+can be easily mixed with traditional or uniform subdivision of surfaces.
+This method is based on an original extension of the Laplace Beltrami
 operator for hybrid quad/triangle meshes, mixing arbitrary types of
 meshes, exploiting the basic geometrical relationships and ensuring
-algorithm convergence.
-
-With the use of the proposed Laplacian Operator this work show succesful
-uses in: Smoothing, Enhancing, Smooth Subdivision, Deformation, Sculpting,
-and Skeletonization.
-
-\section{Proposed Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes
-TQLBO\label{sub:Laplace-Beltrami-operator}}
+good results with few algorithm iterations.
+
+\subsection{Laplace Beltrami Operator for Hybrid Quad/Triangle Meshes TQLBO\label{PAPER:sub:Laplace-Beltrami-Operator}}
 
@@
 triangles $T$. The area of $1$-ring neighborhood $A\left(v_{i}\right)$
-corresponds to a sum of the areas of the quad faces $A\left(Q_{i}\right)$
-and the areas of the triangular faces $\ensuremath{A\left(T_{i}\right)}$
+corresponds to a sum of the quad faces $A\left(Q_{v_{i}}\right)$
+and the areas of the triangular faces $\ensuremath{A\left(T_{v_{i}}\right)}$
 adjacent to vertex $\ensuremath{v_{i}}$.
@@
 \noindent \begin{center}
-$A\left(v_{i}\right)=A\left(Q_{i}\right)+A\left(T_{i}\right)$ 
+$\ensuremath{A\left(v_{i}\right)=A\left(Q_{v_{i}}\right)+A\left(T_{v_{i}}\right)}$
 \par\end{center}
@@
 
-\caption{\label{fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
+\protect\caption{\label{PAPER:fig:quad_xiong}$t_{j1}^{*}\equiv\vartriangle v_{i}v_{j}v_{j}^{\prime},\, t_{j2}^{*}\equiv\vartriangle v_{i}v_{j}^{\prime}v_{j+1},\, t_{j3}^{*}\equiv\vartriangle v_{i}v_{j}v_{j+1}$
 Triangulations of the quad with common vertex $v_{i}$ proposed by
@@
 
-Applying the mean average area, according to Xiong et. al. \cite{Xiong2011},
-from all possible triangulations, as show in figure \ref{fig:quad_xiong},
-the area for quads $\ensuremath{A\left(Q_{i}\right)}$ and triangles
-$A\left(T_{i}\right)$ is.
+Applying the mean average area, according to \cite{Xiong2011}, from
+all possible triangulations, as show in figure \ref{PAPER:fig:quad_xiong},
+the area for quads $\ensuremath{A\left(Q_{v_{i}}\right)}$ and triangles
+$A\left(T_{v_{i}}\right)$ is.
 
@@
 
-Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{i}$ are quads adjacent
-to $v_{i}$, and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{i}$ are triangles
-adjacent to $v_{i}$.
-
-Applying triangulations of the quad with common vertex $v_{i}$ proposed
-by \cite{Xiong2011}.
-
-\noindent 
+Where $q_{1},q_{2},...,q_{j},...,q_{m}\in Q_{v_{i}}$ and $t_{1},t_{2},...,t_{k},...,t_{r}\in T_{v_{i}}$
+
 \begin{equation}
-A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{eq:area_1_ring_triangles_quads}
+A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[A\left(t_{j1}^{*}\right)+A\left(t_{j2}^{*}\right)+A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}A\left(t_{k}\right)\label{PAPER:eq:area_1_ring_triangles_quads}
 \end{equation}
 
-Applying the gradient operator to (\ref{eq:area_1_ring_triangles_quads}).
-
-\noindent {\small 
-\begin{equation}
-\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)\label{eq:EqGrad}
-\end{equation}
-}{\small \par}
-
-According to (\ref{eq:eq_gradient_voronoi_area}), we have.
+Applying the gradient operator to (\ref{PAPER:eq:area_1_ring_triangles_quads})
+
+\noindent \begin{center}
+$\nabla A\left(v_{i}\right)=\frac{1}{2}\overset{m}{\underset{j=1}{\sum}}\left[\nabla A\left(t_{j1}^{*}\right)+\nabla A\left(t_{j2}^{*}\right)+\nabla A\left(t_{j3}^{*}\right)\right]+\overset{r}{\underset{k=1}{\sum}}\nabla A\left(t_{k}\right)$
+\par\end{center}
+
+According to (\ref{PAPER:eq:eq_gradient_voronoi_area}), we have
 
@@
 \par\end{center}
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/beltrami}
+
+\protect\caption{\label{PAPER:fig:LBO-basic-5-TQ-1}The 5 basic triangle-quad cases
+with common vertex $V_{i}$ and the relationship with $V_{j}$ and
+$V_{j}^{\prime}$. (a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two
+quads and one quad {[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO)
+our contribution.}
+\end{figure}
 
@@
 adjacent to $v_{i}$, can be simplified to five cases, as shown in
-figure \ref{fig:LBO-basic-5-TQ}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/beltrami}
-
-\caption{\label{fig:LBO-basic-5-TQ}The 5 basic triangle-quad cases with common
-vertex $V_{i}$ and the relationship with $V_{j}$ and $V_{j}^{\prime}$.
-(a) Two triangles {[}Desbrun 1999{]}. (b) (c) Two quads and one quad
-{[}Xiong 2011{]}. (d) (e) Triangles and quads (TQLBO) our contribution.}
-
-\end{figure}
-
-According to equation (\ref{eq:discrete_mean_curvature_normal}),
-(\ref{eq:def_LBO}), and five simple cases defined in figure \ref{fig:LBO-basic-5-TQ}
-the TQLBO (Triangle-Quad LBO) of $v_{i}$ is.
-
-\noindent 
-\begin{equation}
-\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)
-\end{equation}
-
-\noindent {\small where
+figure \ref{PAPER:fig:LBO-basic-5-TQ-1}.
+
+According to equation (\ref{PAPER:eq:discrete_mean_curvature_normal}),
+(\ref{PAPER:eq:def_LBO}), and five simple cases defined in figure
+\ref{PAPER:fig:LBO-basic-5-TQ-1} the TQLBO (Triangle-Quad LBO) of
+$v_{i}$ is
+
+\noindent \begin{center}
+$\triangle_{S}\left(v_{i}\right)=2\kappa\mathbf{n}=\frac{\nabla A}{A}=\underset{v_{j}\in N_{1}\left(v_{i}\right)}{\frac{1}{2A}\sum}w_{ij}\left(v_{j}-v_{i}\right)$
+\par\end{center}
+
 \begin{equation}
@@
 \frac{1}{2}\left(\cot\theta_{\left(j-1\right)1}+\cot\theta_{\left(j-1\right)4}\right)+\cot\alpha_{j} & \mbox{case \ensuremath{\mathit{e}}.}
-\end{cases}\label{eq:TQLBO_wij}
+\end{cases}\label{PAPER:eq:TQLBO_wij}
 \end{equation}
-}{\small \par}
-
-We define a Laplacian operator as a matrix equation
-
-\noindent 
+
+We define a TQLBO as a matrix equation
+
 \begin{equation}
@@
 0 & \mbox{otherwise}
-\end{cases}\label{eq:TQLBO_Simple_Matrix}
+\end{cases}\label{PAPER:eq:TQLBO_Simple_Matrix}
 \end{equation}
@@
 Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
-of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
+of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{PAPER:eq:TQLBO_wij}),
 $N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
@@
 \delta_{ij} & \mbox{otherwise}
-\end{cases}\label{eq:TQLBO-Normalized_Matrix}
+\end{cases}\label{PAPER:eq:TQLBO-Normalized_Matrix}
 \end{equation}
@@
 
-\section{Mesh Smoothing\label{sub:Laplacian-Smooth}}
-
-Computer objects, reconstructed from the real world, are usually noisy.
-A common way to attenueate noise in a polygonal mesh is through a
-diffusion process \cite{Taubin1995,Desbrun1999}. Laplacian smooth
-techniques over a diffusion process allow a proper noise reduction
-on the mesh surface with minimal shape changes, while still preserving
-a desirable geometry as well as the original shape. The simple idea
-is that the vertices are moved in the direction of the Laplacian when
-we use the contangent version the vertices are moved in the direction
-of the curvature flow. The complexity of Laplacian smoothing can be
-linear in time and space with a fast convergence and the diffussion
-proccess can attenuate noise with only one iteration due the sparseness
-of the laplacian operator.
-
-\noindent 
-\begin{equation}
-\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
-\end{equation}
-
-Where L is the Laplacian matrix defined in equation \ref{eq:TQLBO-Normalized_Matrix}
-for meshes with regular sampling, and equation \ref{eq:TQLBO_Simple_Matrix}
-for meshes composed by triangles or quads with differents size or
-irregular sampling. $\lambda$ is a scalar that control the diffussion
-proccess, and smoothing factor.
-
-The equation \ref{eq:diffusion_process} can be linearly approximated
-using implicit integration with a Laplacian Operator version of TQLBO,
-the use of implicit integration permit the system to be more stability.
-
-\begin{equation}
-\left(I-\lambda\partial tL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
-\end{equation}
-
-\section{The Shape Inflation\label{sub:Curvature-Enhancing}}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/teaser_cup}
-
-\caption{\label{fig:Subdivision-Cups} Family of cups generated with our method,
-from a coarse model (a), (c): the shape, obtained from the Catmull-Clark
-Subdivision (b), (d), is inflated. Soft constraints, over the coarse
-model, is drawn in red and blue (c).}
-\end{figure}
-
-This method exaggerates a shape using a Laplacian smoothing operator
-in the reverse direction, i.e., the new shape is a modified version
-in which those areas with larger curvature are magnified. The operator
-amounts to a generator of a set of models which conserves the basic
-silhouette of the original shape. In addition, the presented approach
-can be easily mixed with traditional or uniform subdivision of surfaces.
+\subsection{The Shape Inflation\label{PAPER:sub:Curvature-Enhancing}}
 
@@
 To solve this equation, implicit integration is used as well as a
-normalized version of TQLBO matrix.
-
-\noindent 
+normalized version of TQLBO matrix
+
 \begin{equation}
-\left(I-\left|\lambda dt\right|W_{p}L\right)V^{\prime}=V^{t}\label{eq:Lineal_System_with_wp}
+\left(I-\left|\lambda dt\right|W_{p}L\right)V^{\prime}=V^{t}\label{PAPER:eq:Lineal_System_with_wp}
 \end{equation}
@@
 The vertices $V^{t+1}$ are inflated, along their reverse curvature
-direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,~
-$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
+direction, by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
+$L$ is the Normalized TQLBO defined in the equation (\ref{PAPER:eq:TQLBO-Normalized_Matrix}),
 $x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
@@
 The method was devised to use with weighted vertex groups, which specify
-the final shape inflation of the solution, meaning $0$ as no changes
+the final shape inflation of the solution, meaning \$0\$ as no changes
 and 1 when a maximal change is applied. The weights modify the influence
-zones, where the Laplacian is applied, as shown in equation \ref{eq:Lineal_System_with_wp}.
-Interestingly, the generated family of shapes may change substantially
+zones, where the Laplacian is applied, as shown in equation \ref{PAPER:eq:Lineal_System_with_wp}
+. Interestingly, the generated family of shapes may change substantially
 with the weights of specific control points.
 
-The curvature cannot be calculted at the boundary of the meshes that
+The curvature cannot be calculated at the boundary of the meshes that
 are not closed, for that reason we use the scale-dependent operator
@@
 \noindent \begin{center}
-$\overline{v}=\frac{1}{n}\underset{v_{i}\in V}{\sum}v_{i}$, 
-\par\end{center}
-
-$\overline{v}$ is the mesh center, $vol_{ini}$ is an initial volume,
-and $vol_{t+1}$ is the volume at the iteration $t+1$, then the scale
-factor.
+$\overline{v}=\frac{1}{n}\underset{v_{i}\in V}{\sum}v_{i}$
+\par\end{center}
+
+$\overline{v}$is the mesh center, $vol_{ini}$ is an initial volume,
+and $vol_{t+1}$ is the volume at the iteration $t+1$, $n$ is the
+number of vertices, then the scale factor
 
@@
 
-\section{Sculpting\label{sub:Sculpting}}
+\section{Sculpting\label{PAPER:sec:Sculpting}}
 
@@
 \noindent \begin{center}
-$L\left(i,j\right)=\begin{cases}
+$\ensuremath{L\left(i,j\right)=\begin{cases}
 -\frac{w_{ij}}{\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij}} & \mbox{if }\left\Vert v_{i}-u\right\Vert <r\wedge\left\Vert v_{j}-u\right\Vert <r\\
@@
 \delta_{ij} & \mbox{otherwise}
-\end{cases}$ 
+\end{cases}}$
 \par\end{center}
@@
 
-\section{Laplacian Deform\label{sub:Laplacian-Deform}}
-
-The Laplacian deform allows to pose a mesh while preserving geometric
-details of the surface. This method allows to defines a set of anchor
-vertices, and then moves some of them around. The system keeps the
-rest of the anchor vertices in fixed positions, and calculates the
-best possible locations of all the remaining vertices to preserve
-the original geometric details.
-
-This thesis adapt the method proposed by Sorkine \cite{Sorkine2004}
-for mesh deformations, delete the use of static vertices and allow
-application of this system in hybrid meshes composes by triangles
-and quads with the TQLBO proposed.
-
-This method captures the geometric details using a differential coordinates
-representations. The differential coordinates captures the local geometric
-information (curvature and direction) of the vertex based on its neighbors
-how show in figure \ref{fig:DifferentialCoor}.
-
-\begin{figure}
-\noindent \begin{centering}
-\includegraphics[width=0.7\columnwidth]{resources/figs/DifferentialCoordinates}
-\par\end{centering}
-
-\caption{\label{fig:DifferentialCoor} Difference between $v_{i}$ and the
-center of mass of its neighboors $v_{1},...,v$.}
-\end{figure}
-
-\begin{equation}
-\delta_{i}=\overset{m}{\underset{j=1}{\sum}}w_{ij}\left(v_{i}-v_{j}\right)\label{eq:DifferentialCoordinate}
-\end{equation}
-
-Where $\delta_{i}$ is the differential coordinate for vertex $v_{i}$.
-The $v_{j}$ are the inmediate neighoors of $v_{i}$, and $w_{ij}$
-is the weigth betwen vertex $v_{i}$ and $v_{j}$ defined in equation
-\ref{eq:TQLBO_wij} that is TQLBO.
-
-Then the linear systems for find the new pose of a mesh is.
-
-\begin{equation}
-\begin{bmatrix}w_{l}L\\
-W_{c}
-\end{bmatrix}X=\begin{bmatrix}\delta\\
-W_{c}C
-\end{bmatrix}\label{eq:LaplacianDefomSystem}
-\end{equation}
-
-Where $w_{l}$ is the weigth for Laplacian Matrix $L$, the Laplacian
-matrix $L$ was defined in equation \ref{eq:TQLBO_Simple_Matrix}
-. $Wc$ is a matrix that containts ones int the indexes of anchors
-vertices. $C$ is a vector with coordinates of anchors vertices after
-several transformatios. $\delta$ are the differential coordinates
-defined in equation \ref{eq:DifferentialCoordinate}.
-
-\section{Subdivision surfaces\label{sub:Subdivision-surfaces}}
+\section{Subdivision surfaces\label{PAPER:sec:Subdivision-surfaces}}
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/teaser_cup}
+
+\protect\caption{\label{PAPER:fig:Subdivision-Cups} Family of cups generated with
+our method, from a coarse model (a), (c): the shape, obtained from
+the Catmull-Clark Subdivision (b), (d), is inflated. Soft constraints,
+over the coarse model, is drawn in red and blue (c).}
+\end{figure}
 
@@
 smoothness is automatically guaranteed \cite{DeRose1998}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/cruz_lambda4}
-
-\caption{\label{fig:Catmull_Clark}(a) Original Model, (b) Model with Catmull-Clark
-Subdivision. Models with Laplacian smoothing: (c) and (d). Models
-with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
-and before applying shape inflation: (e) and (f).}
-\end{figure}
 
@@
 weights with smooth changes in the influence zones, as shown in figure
-\ref{fig:Subdivision-Cups}.c.
-
-In equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
+\ref{PAPER:fig:Subdivision-Cups}.c.
+
+In equation \ref{PAPER:eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
 matrix with weights corresponding to each vertex. Weights at each
@@
 
-\section{Skeleton Extraction}
-
-Skelton extraction reduces the dimensionality and represents a three-dimensional
-object as a uni-dimensional structure \cite{Cornea2007}.
-
-The skeleton extraction use the natural shrink produced by the laplacian
-smoothing \cite{Meyer2003}, to contratc iteratively the mesh until
-the volume inside the surface is near to zero (see figure \ref{fig:MeshContracted}).
-The method stretch the shrink mesh to warranty that object preservers
-the best at posibble the original topology with the use of attraction
-constraint \cite{Au2008}.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/contraccion}
-
-\caption{\label{fig:MeshContracted}From left to right iterative mesh contraction.}
-\end{figure}
-
-The laplacian smooth proccess move the vertices in the direction of
-the Laplacian, if cotangent laplacian operator is used, the vertices
-move in the direction of minimal surface \cite{Pinkall1993} following
-the curvature flow of the mesh surface.
-
-In the work of Au \cite{Au2008} is proposed the next system of equation
-to iteratively contratc the mesh until a skeleton.
-
-\begin{equation}
-\left[\begin{array}{c}
-W_{L}L\\
-W_{H}
-\end{array}\right]X_{t+1}=\left[\begin{array}{c}
-0\\
-W_{H}X_{t}
-\end{array}\right]\label{eq:SkeletonExtraction}
-\end{equation}
-
-where $L$ is the Laplacian matrix describe in equation \ref{eq:TQLBO_Simple_Matrix},
-$W_{L}$ is the factor for smoothing, $W_{H}$ is the factor for attraction
-constraint.
-
-$W_{L}$ and $W_{H}$ are changing in every iteration. The contraction
-and smoothing constraint $W_{L}^{t+1}=S_{L}W_{L}^{t}$ with $S_{L}=2.0$.
-The attraction constraint $W_{H,i}^{t+1}=W_{H,i}^{0}\sqrt{\frac{A_{i}^{0}}{A_{i}^{t}}}$.
-
-$A_{i}^{t}$ y $A_{i}^{0}$ are the current area and initial aerea
-of the ring surrounding $x_{i}$.
-
-In this thesis an additional constraint is proposed which seeks the
-vertices and the skeleton does not shrink, to eliminate the need to
-adjust the final skeleton taking each skeleton node and move to the
-center of your local mesh region.
-
-The basic idea is move the vertices along of the normal line estimated
-on every vertex based on the avergage of the faces normals.
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/LineConstraintSkeleton}
-
-\caption{\label{fig:LineConstraint}Left: The vertex $x_{i}$ move along line
-constraint. Right: the distance of vertex $x_{i}$ to plane 1 and
-plane 2 when change the position in every iteration.}
-\end{figure}
-
-This line can be see as intersection of two planes (see figure \ref{fig:LineConstraint})
-created with the information of the vertex $x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$
-and neighboors $x_{j}$ of $x_{i}$.
-
-The equation of the plane.
-
-\noindent \begin{center}
-$a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}=0$
-\par\end{center}
-
-There is varios methods to build a equation of the plane based on
-three non-collinear points, we choose this three points based on vertex
-$x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$ and neighboors
-$x_{j}$ of $x_{i}$.
-
-$P_{1}=x_{i}$, $P_{2}=x_{j}$ when $x_{j}\in Neighboors\left(x_{i}\right)$
-and $P_{3}=P_{1}-\overrightarrow{\mathbf{n}_{i}}$.
-
-To build a equation plane only need three non-collinear points $\left\{ P_{1},P_{2},P_{3}\right\} $
-and solve the next systems of equations for variables $a,b,c$.
-
-\noindent \begin{center}
-$\begin{array}{c}
-ax_{1}+by_{1}+cz_{1}+d=0\\
-ax_{2}+by_{2}+cz_{2}+d=0\\
-ax_{3}+by_{3}+cz_{3}+d=0
-\end{array}$
-\par\end{center}
-
-The distance of point $P_{0}=\{x_{0},y_{0},z_{0}\}$ to a plane $\Pi=a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}$.
-
-\noindent \begin{center}
-$\left|\Pi-P_{0}\right|=\frac{\left|ax_{0}+by_{0}+cz_{0}+d\right|}{\sqrt{a^{2}+b^{2}+c^{2}}}$
-\par\end{center}
-
-In the equation above, every point $P_{0}=\{x_{0},y_{0},z_{0}\}$
-that belong to plane made the equation zero. If the point $P_{0}$
-is not in the plane the value of the equation of the plane change,
-and the absolute value is increased if $P_{0}$ is more distant of
-the plane. Let us use this simple relation to build a valid constraint
-that can be put in the form of linear equation $Ax=B$. Where $A$
-is the matrix with values $\begin{vmatrix}a & b & c\end{vmatrix}$
-the $x$ value correspond to every vertex in mesh $\{x_{0},y_{0},z_{0}\}$
-and $B$ correspond to $d$ value of the plane equation. How the linear
-system presented in equation \ref{eq:SkeletonExtraction} don't has
-a unique solution, the system solve it in the least-squares sense.
-With the new constraint the system then try to minimize the distance
-betwen the new vertex positions and the two planes.
-
-The new system of equations proposed
-
-\begin{equation}
-\left[\begin{array}{c}
-W_{L}L\\
-W_{H}\\
-W_{D}\Pi_{1}\\
-W_{D}\Pi_{2}
-\end{array}\right]X_{t+1}=\left[\begin{array}{c}
-0\\
-W_{H}X_{t}\\
--D_{1}\\
--D_{2}
-\end{array}\right]\label{eq:SkeletonExtractionDistance}
-\end{equation}
-
-where $W_{D}$ is the weigth to new constraints, that forced the vertices
-to move along of the normal line of every vertex. $\Pi_{1}$ and $\Pi_{2}$
-are matrix that contains $a,b,c$ values of the equation of the plane
-for every vertex. $D_{1}$ and $D_{2}$ are the vector with $d$ values
-of the equations of the planes for every vertex.
-
-\chapter{Results\label{sec:Results}}
-
-This chapter show the results of the Laplace Beltrami operator for
-hybrid quad/triangle meshes with several example models (see figures
-\ref{fig:Spectrum}, \ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark},
-\ref{fig:TQLBO_test}, \ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush},
-\ref{fig:Performance-sculpt}, \ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}).
-It first show a comparisson of the Laplacian Operator in meshes composed
-by triangles, by quads and hybrid meshes composed by triangles/quads.
-Section \ref{sec:Customizing-Curvature-by} show the use of TQLBO
-in applications of Shape Inflation and Subdivision Surfaces on normal
-meshes and meshes change with isometric transformations. It Section
-\ref{sec:Shape-Inflation-Brush} show a novel shape inflation brush
-for sculpting systems that works in real time. It Section \ref{sec:Posing-Meshes-with}
-show mesh deformations and posing applications using differential
-coordinates defined with the TQLBO. It Section \ref{sec:Laplace-Operator-and}
-discusses the differences betwen common version and normalized version
-of the TQLBO. It Section \ref{sec:Performance-Testing-of} describe
-a performance comparison of differents numericals solvers used to
-solve a Laplacian linear equation system. Finally discusses some especific
-technical aspect about the implementation of the TQLBO on several
-computer systems at Section \ref{sec:Conclusion-and-future}.
-
-Figure \ref{fig:TQLBO_test} shows the results when applying the Laplace
-Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
+\section{Results\label{PAPER:sec:Results}}
+
+The results of the shape inflation method with the extension of the
+Laplace Beltrami operator for hybrid quad/triangle meshes with several
+example models shown in figures \ref{PAPER:fig:Spectrum}, \ref{PAPER:fig:Subdivision-Cups},
+\ref{PAPER:fig:Catmull_Clark}, \ref{PAPER:fig:TQLBO_test}, \ref{PAPER:fig:camello_enhanced},
+\ref{PAPER:fig:Sculpt_Brush}, \ref{PAPER:fig:Performance-sculpt},
+\ref{PAPER:fig:(a)Monkey}, \ref{PAPER:fig:Animated_Camell}. The
+shape inflation was assessed with TQLBO method on a PC with AMD Quad-Core
+Processor @ 2.40 GHz and 8 GB RAM.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/cruz_lambda4}
+\par\end{centering}
+
+\protect\caption{\label{PAPER:fig:Catmull_Clark}(a) Original Model, (b) Model with
+Catmull-Clark Subdivision. Models with Laplacian smoothing: (c) and
+(d). Models with a first Laplacian filtering $\lambda=60.0$, $\lambda_{e}=12.0$
+and before applying shape inflation: (e) and (f). }
+\end{figure}
+
+Figure \ref{PAPER:fig:TQLBO_test} shows the results when applying
+the Laplace Beltrami Operator TQLBO of equation (\ref{PAPER:eq:TQLBO_Simple_Matrix})
 in a model with a simple subdivision. In column (c) the Laplacian
@@
 
-\caption{\label{fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
+\protect\caption{\label{PAPER:fig:TQLBO_test}(a) Original Model. (b) Simple subdivision.
 (c), (d) (e) Laplacian smoothing with $\lambda=7$ and 2 iterations:
@@
 
-\section{Customizing Curvature by Shape Inflation.\label{sec:Customizing-Curvature-by}}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/spectrum}
-
-\caption{\label{fig:Spectrum}A set of 48 successive shapes enhanced, from
-$\lambda=0.0$ in blue to $\lambda=-240.0$ in red, with steps of
-$-5.0$.}
-\end{figure}
-
-The shape inflation was assessed with TQLBO method on a PC with AMD
-Quad-Core Processor @ 2.40 GHz and 8 GB RAM.
-
 Methods using the Catmull-Clark subdivision surface and the inflation
 allows to modify the curvature that is obtained with the process of
-subdivision, as shown in figure \eqref{fig:Subdivision-Cups}. This
-test used a coarse cup model, in which the subdivision was performed,
-followed by a Laplacian smoothing and inflation. In figure \eqref{fig:Subdivision-Cups}.c,
-\eqref{fig:Subdivision-Cups}.d shows also the use of weight vertex
+subdivision, as shown in figure \ref{PAPER:fig:Subdivision-Cups}.
+This test used a coarse cup model, in which the subdivision was performed,
+followed by a Laplacian smoothing and inflation. In figure \ref{PAPER:fig:Subdivision-Cups}.c,
+\ref{PAPER:fig:Subdivision-Cups}.d shows also the use of weight vertex
 groups over coarse models, with subdivision surfaces that allowed
@@
 weights were used for the inflation obtained on the 6 cups that are
-at the right of the figure \eqref{fig:Subdivision-Cups}.d.
-
-Laplacian smoothing applied with simple subdivision (see figure \ref{fig:Catmull_Clark}.b.)
-may produce similar results to those obtained with Catmull-Clark (see
-figure \ref{fig:Catmull_Clark}.c.), whose models are in average equal
-triangles. The one obtained with the Laplacian smoothing is shown
-in panel (c), (d) and those curvature modified versions are in (e)
-and (f). As can be observed, different versions of the original sketch
-can be obtained by parameterizing a single model value, a great advantage
-of the presented method. Figure \ref{fig:camello_enhanced} shows
-the generation of different versions of a camel according to the $\lambda$
-parameter. In the top row, it is shown the shape inflation results,
-as $\lambda$ becomes larger and negative, the resultant shape is
-observed as if the model would inflate the more convex parts, as shown
-in figure \ref{fig:Spectrum}. The larger the $\lambda$ parameter
-the larger the model feature inflations. The bottom row of figure
-\ref{fig:camello_enhanced} shows the use of weighted vertex groups,
-specifying which areas will be inflated. On the left, the inflation
-of the camel legs produces an organic aspect, notice that the border
-is not distorted and smooth.
+at the right of the figure \ref{PAPER:fig:Subdivision-Cups}.d.
 
@@
 
-\caption{\label{fig:camello_enhanced}Top row: Original camel model in left.
-Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
+\protect\caption{\label{PAPER:fig:camello_enhanced}Top row: Original camel model in
+left. Shape inflation with $\lambda=-30.0$, $\lambda=-100.0$, $\lambda=-400.0$.
 Bottom row: Shape inflation with weight vertex group, $\lambda=-50.0$
@@
 
+Laplacian smoothing applied with simple subdivision (see figure \ref{PAPER:fig:Catmull_Clark}.c.)
+may produce similar results to those obtained with Catmull-Clark (see
+figure \ref{PAPER:fig:Catmull_Clark}.b.), whose models are in average
+equal triangles. The one obtained with the Laplacian smoothing is
+shown in panel (c), (d) and those curvature modified versions are
+in (e) and (f). As can be observed, different versions of the original
+sketch can be obtained by parameterizing a single model value, a great
+advantage of the presented method. Figure \ref{PAPER:fig:camello_enhanced}
+shows the generation of different versions of a camel according to
+the $\lambda$ parameter. In the top row, it is shown the shape inflation
+results, as $\lambda$ becomes larger and negative, the resultant
+shape is observed as if the model would inflate the more convex parts,
+as shown in figure \ref{PAPER:fig:Spectrum}. The larger the $\lambda$
+parameter the larger the model feature inflations. The bottom row
+of figure \ref{PAPER:fig:camello_enhanced} shows the use of weighted
+vertex groups, specifying which areas will be inflated. On the left,
+the inflation of the camel legs produces an organic aspect, notice
+that the border is not distorted and smooth.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/camello_walk2}
+
+\protect\caption{\label{PAPER:fig:Animated_Camell}The method is pose insensitive.
+The inflation for the different poses are similar in terms of shape.
+Top row: Original walk cycle camel model. Bottom row: Shape inflation
+with weight vertex group, $\lambda=-400$ and $2$ iterations. }
+\end{figure}
+
 The inflation of the silhouette features is predictable and invariant
 under isometric transformations, as those classically used in some
-animations (see Figure \ref{fig:Animated_Camell}). In this figure,
-the animation shows some camel poses during a walk, the inflation
+animations (see Figure \ref{PAPER:fig:Animated_Camell}). In this
+figure, the animation shows some camel poses during a walk, the inflation
 is performed at the neck and legs, as shown in the bottom left camel
-in figure \ref{fig:Animated_Camell}. Local modifications produced
+in figure \ref{PAPER:fig:Animated_Camell}. Local modifications produced
 by the pose interpolation or animation rigging practically do not
@@
 \begin{figure}[H]
-\includegraphics[width=1\textwidth]{resources/figs/camello_walk2}
-
-\caption{\label{fig:Animated_Camell}The method is pose insensitive. The inflation
-for the different poses are similar in terms of shape. Top row: Original
-walk cycle camel model. Bottom row: Shape inflation with weight vertex
-group, $\lambda=-400$ and $2$ iterations. }
-\end{figure}
-
-\section{Shape Inflation Brush in Real Time\label{sec:Shape-Inflation-Brush}}
-
-Figure \ref{fig:Sculpt_Brush} shows the use of a shape inflation
+\noindent \begin{centering}
+\includegraphics[height=0.3\textheight]{resources/figs/sculpt_brush}
+\par\end{centering}
+
+\protect\caption{\label{PAPER:fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate
+brush for leg into blue circle, (c) Inflate shape brush for leg into
+red circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into
+blue circle, (c) Shape inflation brush for fingers in red circle.}
+\end{figure}
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\columnwidth]{resources/figs/verts_per_second_sculpt}
+\par\end{centering}
+
+\protect\caption{\label{PAPER:fig:Performance-sculpt}Performance of our dynamic shape
+inflation brush in terms of the sculpted vertices per second. Three
+models with 12K, 40K, 164K vertices used for sculpting in real time.}
+\end{figure}
+
+Figure \ref{PAPER:fig:Sculpt_Brush} shows the use of a shape inflation
 brush for sculpting in real time. One pass was used with the brush,
-as shown in the figure, with the blue and red radius. In figure \ref{fig:Sculpt_Brush}.b
+as shown in the figure, with the blue and red radius. In figure \ref{PAPER:fig:Sculpt_Brush}.b
 the camel foot shows the inflation intersection that looks like two
@@
 bottom of the same figure. The silhouette inflation is observed in
-figure \ref{fig:Sculpt_Brush}.c since the main shape is retained
+figure \ref{PAPER:fig:Sculpt_Brush}.c since the main shape is retained
 together with its finger and foot details. Similar results can be
@@
 step. Likewise, this new method can easily inflate organic features
-like muscles during the sculpting process. In figure \ref{fig:Performance-sculpt}
+like muscles during the sculpting process. In figure \ref{PAPER:fig:Performance-sculpt}
 the shape inflation brush performance is illustrated, in this experiment
@@
 took 0.5 seconds, these times are suitable in real applications since
-an artist sculpts a model for parts.
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[height=0.3\textheight]{resources/figs/sculpt_brush}
-\par\end{centering}
-
-\caption{\label{fig:Sculpt_Brush}Top row: (a) Leg Camel, (b) Inflate brush
-for leg into blue circle, (c) Inflate shape brush for leg into red
-circle. Bottom row: (a) Hand, (b) Inflate brush for fingers into blue
-circle, (c) Shape inflation brush for fingers in red circle.}
-\end{figure}
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[width=1\columnwidth]{resources/figs/verts_per_second_sculpt}
-\par\end{centering}
-
-\caption{\label{fig:Performance-sculpt}Performance of our dynamic shape inflation
-brush in terms of the sculpted vertices per second. Three models with
-12K, 40K, 164K vertices used for sculpting in real time.}
-\end{figure}
-
-\section{Posing Meshes with Laplacian Deform\label{sec:Posing-Meshes-with}}
-
-\begin{figure}[H]
-\noindent \begin{centering}
-\includegraphics[width=1\textwidth]{resources/figs/Armadillo}
-\par\end{centering}
-
-\caption{\label{fig:Armadillo}Anchor vertices in blue color. (a) Original
-Model, (b,c,d) new poses change only anchor vertices, system find
-positions for vertices in yellow color.}
-\end{figure}
-
-Figure \eqref{fig:Armadillo} shows the Laplacian Deform applied in
-a model with 173K vertices, only anchor vertices was used and are
-represented in blue color, when the user apply several transformation
-(location, rotation, scale) over this anchors vertices, the system
-find a solution and estimate the position of the vetices in yellow
-color. This method work in real time, to achieve this the matrix $\begin{bmatrix}w_{l}L\\
-W_{c}
-\end{bmatrix}$ in the equation \eqref{eq:LaplacianDefomSystem} is decomposed in
-matrix $LU$ with LU factorization only one time when the system init.
-Once the matrix is factorized the system can solve the unknowns in
-a fast way in term of miliseconds. For get better results the method
-permits solve several times the system of equations, and not need
-factorize matriz LU could be that at every iteration, only the differential
-coordinates are adjust since the differential coordinates can be rotated
-at every iteration and get bettter results. In the figure only four
-iterations were used, but the system find good solutions with only
-one iteration when the angle of rotations are less that $\pi$.
-
-\section{Laplace Operator and Normalized Version \label{sec:Laplace-Operator-and}}
-
-Tests with the Laplacian operator (equation \ref{eq:TQLBO_Simple_Matrix})
-and its normalized version (equation \ref{eq:TQLBO-Normalized_Matrix}),
+an artist sculpts a model for parts. \%, and each part is represented
+by an average of about 1800 vertices.
+
+\begin{figure}[H]
+\includegraphics[width=1\columnwidth]{resources/figs/monkey}
+
+\protect\caption{\label{PAPER:fig:(a)Monkey}(a) Bottom row: Original Model. Top row:
+Original model scaled by 4. (b) Top and bottom row: inflating with
+Normalized-TQLBO $\lambda=-50$ (c) Top and bottom row: inflating
+with TQLBO $\lambda=-50$.}
+\end{figure}
+
+Tests with the Laplacian operator (equation \ref{PAPER:eq:TQLBO_Simple_Matrix})
+and its normalized version (equation \ref{PAPER:eq:TQLBO-Normalized_Matrix}),
 produce similar results if the triangles or quads that compose the
@@
 which may be very small and causes numeric problems, as shown in figure
-\ref{fig:(a)Monkey}.c bottom row. The shape inflation of the model
-with the normalized Laplacian operator results in a more regular pattern.
-The model can be deformed with a TQLBO normalized version with large
-$\lambda$ ($\lambda>400$) while intersecting itself with no peaks.
-Figure \ref{fig:(a)Monkey}.c shows different results due to the quads
-areas in the model. Quadss with larger area have smaller inflation
-(figure \ref{fig:(a)Monkey}.c skull), and smaller quads have larger
-inflations (figure \ref{fig:(a)Monkey}.c chin).
-
-\begin{figure}[H]
-\includegraphics[width=1\columnwidth]{resources/figs/monkey}
-
-\caption{\label{fig:(a)Monkey}(a) Bottom row: Original Model. Top row: Original
-model scaled by 4. (b) Top and bottom row: inflating with Normalized-TQLBO
-$\lambda=-50$ (c) Top and bottom row: inflating with TQLBO $\lambda=-50$.}
-\end{figure}
-
-\section{Skeletonizer}
-
-Skeletonizer is a product of software that permits the proccessing,
-visualization and extraction of the skeleton from polygonal meshes.
-The software was designed with base in a plugin system and pipe-filters
-paradigm. This software implement the method for skeleton extraction
-describe in equation \ref{eq:SkeletonExtractionDistance}.
-
-The software is called sjSkeletonizer and use the following computacional
-frameworks and libraries.
-\begin{description}
-\item [{CGAL}] Computational Geometry Algorithms Library \cite{cgal}.
-\item [{Graphite}] is a research platform for computer graphics, 3D modeling
-and numerical geometry \cite{graphite}.
-\item [{QT}] is a cross-platform application and UI framework \cite{qt}.
-\end{description}
-\begin{figure}
-\includegraphics[width=1\textwidth]{resources/figs/poses}
-
-\caption{\label{fig:Skeleton-extraction-poses} Model with different poses
-and skeleton obtained with our skeleton extraction software.}
-
-\end{figure}
-
-\section{Performance Testing of Solvers \label{sec:Performance-Testing-of}}
-
-Performance evaluation of some numerical solvers for compute Laplacian
-Smooth system.
+\ref{PAPER:fig:(a)Monkey}.c bottom row. The shape inflation of the
+model with the normalized Laplacian operator results in a more regular
+pattern. The model can be deformed with a TQLBO normalized version
+with large $\lambda$ ($\lambda>400$) while intersecting itself with
+no peaks. Figure \ref{PAPER:fig:(a)Monkey}.c shows different results
+due to the quads areas in the model. Quads with larger area have smaller
+inflation (figure \ref{PAPER:fig:(a)Monkey}.c skull), and smaller
+quads have larger inflations (figure \ref{PAPER:fig:(a)Monkey}.c
+chin).
+
+\section{Implementation\label{PAPER:sec:Implementation}}
+
+The method was implemented as a modifier for modeling and brush for
+sculpting, on the Blender software \cite{blender} in C and C++. Working
+with the Blender allowed to test the method interactively against
+others, as Catmull-Clark, weight vertex groups and sculpting system
+in Blender.
+
+To improve the performance, it was worked with the Blender mesh structure,
+visiting each triangle or quad and storing its corresponding index
+and the sum of the Laplacian weights of the ring in a list so that
+only two visits were required for the list of mesh faces and two times
+the edge list, if the mesh was not closed. This drastically reduced
+calculations, enabling real-time processing. In the construction of
+the Laplacian matrix, several index were locked at vertices having
+face areas or edge lengths with zero value that could cause spikes
+and bad results.
+
+Under these conditions, the matrix at equation \ref{PAPER:eq:TQLBO_Simple_Matrix}
+is sparse since the number of neighbors per vertex, corresponding
+to the number of data per row, is smaller compared to the total number
+of vertices in the mesh. To solve the linear system equation \ref{PAPER:eq:Lineal_System_with_wp}
+was used OpenNL \cite{Buatois2007} which is a a library for solving
+sparse linear system.
+
+\section{Conclusion and future work\label{PAPER:sec:Conclusion-and-future}}
+
+This work presented an extension of the Laplace Beltrami operator
+for hybrid quad/triangle meshes that can be used in production environments
+and provides results similar to those obtained by working only with
+triangles or quads. This paper has introduced a new way to change
+silhouettes in a mesh for modeling or sculpting in a few steps by
+means of the curvature model modification while preserving its overall
+shape. In addition, a new modeling method has also been presented
+some possible applications have been illustrated. The method works
+properly with isometric transformations, opening the possibility of
+introducing it on the process of animation.
+
+We show that this tool may work in early modeling stages, case in
+which coarse models are used, allowing to modify the shape generated
+by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
+of the vertices with change of a single parameters.
+
+Future work includes the analysis of theoretical relationships between
+the Catmull-Clark subdivision surfaces and the Laplacian smoothing
+since they can produce very similar results.
+
+\section*{Acknowledgment}
+
+We wold like to thank anonymous friends for their support of our research.
+
+This work was supported in part by the Blender Foundation, Google
+Summer of code program at 2012.
+
+Livingstone elephant model is provided courtesy of INRIA and ISTI
+by the AIM@SHAPE Shape Repository. Hand model is courtesy of the FarField
+Technology Ltd. Camel model by Valera Ivanov is licensed under a Creative
+Commons Attribution 3.0 Unported License. Dinosaur and Monkey models
+are under public domain, courtesy of Blender Foundation.
+
+\chapter{Mesh smoothing based on curvature flow operator in a diffusion equation\label{sub:Laplacian-Smooth}}
+
+This work was accepted as part of the software Blender \cite{blender},
+an open source 3D application for modeling, rendering, compositing,
+video editing and game creation. The work was supported by an awarded
+internship of the Google Summer of Code 2012 program, administered
+for Google Inc.
+
+\section{Synopsis}
+
+Objects reconstructed from the real world contain undesirable noise
+in many applications of computer graphics. A Mesh smoothing may remove
+that noise while still preserving the geometry and shape of the original
+model. This project aims to improve the mesh smoothing tools uses
+by software Blender, using curvature flow operator in a diffusion
+equation, allowing to work with hybrid meshes composed of triangles
+and quads, using the Laplacian operator proposed by Pinzón and Romero
+\cite{Pinzon2013}.
+
+\section{Benefits to Blender}
+
+This project proposes a new and robust mesh smoothing tool that improves
+the appearance of surfaces models. Usually, methods to scan computer
+graphics objects using the Kinect ZCam need to remove the noise present
+at the time of capture. This mesh smoothing method produces higher
+quality results without shrinkage, while the usually used smoothing
+tool collapses after several iterations.
+
+This mesh smoothing method allows hard and soft constraints on the
+positions of the mesh points to maintain control over the shape, facilitating
+to remove the noise generated during the sculpting, without eliminating
+the desired details of the model.
+
+\section{Deliverables }
+\begin{itemize}
+\item A new and robust mesh smoothing tool for Blender. 
+\item Some documentation pages to be included in the manual. 
+\item A technical document for developers to improve the method in the future. 
+\item A tutorial explaining the use of the tool.
+\end{itemize}
+
+\section{Project Details }
+
+The mesh smoothing algorithm was implemented as a diffusion equation
+for specific geometric structures. The project was divided in four
+parts:
+\begin{enumerate}
+\item Initialization of data and necessary structures.
+\item Computation of the Laplacian Matrix.
+\item Definition of the sparse linear system.
+\item Solution of the sparse linear system, using a preconditioned bi-conjugated
+gradient numerical library.
+\end{enumerate}
+Integration of the numerical library present in Blender to solve the
+sparse linear system
+
+Generation of documentation and tutorials.
+
+\section{Project Schedule}
+\begin{itemize}
+\item 3 weeks: Understanding the Blender source code and identifying the
+key points for the project.
+\item 1 week: Definition of the data structures necessary to work with the
+Blender architecture.
+\item 1 week: Implementation of the methods for the initial configuration
+of the smoothing algorithm. Implementation of the Laplacian matrix
+calculation.
+\item 2 week: Integration of the numerical library.
+\item 2 week: formulation of the sparse linear system and implementation
+of the numerical method to solve it.
+\item 3 weeks: Formulation and implementation of the graphical user interface.
+\item 2 weeks: Testing the tool.
+\item 3 weeks: Generation of the documentation and tutorials.
+\end{itemize}
+
+\section{Mesh Smoothing}
+
+A common way of attenuating noise in a polygonal mesh is by a diffusion
+process \cite{Taubin1995,Desbrun1999}. Laplacian smooth techniques
+allow a proper noise reduction of the mesh surface with minimal shape
+changes. The simple idea consists in moving the vertices in the Laplacian
+direction. When the cotangent version is used, the vertices are moved
+in the direction of the curvature flow. The complexity of the Laplacian
+smoothing can be linear in time and space with a fast convergence.
+The diffusion process can attenuate noise with only one iteration
+due the sparseness of the laplacian operator.
+
+\noindent 
+\begin{equation}
+\frac{\partial V}{\partial t}=\lambda L\left(V\right)\label{eq:diffusion_process}
+\end{equation}
+
+Where $L$ is the Laplacian matrix defined in equation \ref{eq:LaplacianMatrixForSmoothing}
+for meshes composed of triangles or quads with different sizes or
+irregular sampling and $\lambda$ is a scalar that controls the diffusion
+process, and smoothing factor. The equation \ref{eq:diffusion_process}
+can be linearly approximated using implicit integration with a Laplacian
+Operator version of TQLBO, the use of implicit integration makes the
+system is more stable.
+
+\begin{equation}
+\left(I-\lambda dtL\right)V^{n+1}=V^{n}\label{eq:LaplacianSmoothLinearEquationSystem}
+\end{equation}
+
+The user may define the region of interest where the laplacian smooth
+needs to be applied. For doing so, we add a diagonal matrix $W_{p}$
+to equation \ref{eq:LaplacianSmoothLinearEquationSystem}, where every
+element in the diagonal correspond to the weight for every vertex.
+
+\noindent \begin{center}
+$\left(I-\lambda dtW_{p}L\right)V^{n+1}=V^{n}$
+\par\end{center}
+
+For non-closed meshes or meshes with holes, the curvature flow can
+not be computed. For this reason, the system smoothes out the edges
+only in the direction of the diffusion process. The boundaries are
+treated as a one-dimensional curve, where the Laplacian is defined
+as the weighted difference between the vertex and the two immediate
+neighbors, ensuring the curve maintains its original form as much
+as possible. We define a Laplacian for mesh smoothing as a matrix
+equation.
+
+\noindent \begin{center}
+\begin{equation}
+L(i,j)=\begin{cases}
+-\frac{1}{2A_{i}}w_{ij} & \mbox{if }j\in N(v_{i})\wedge v_{i}\notin\mbox{Boundary}\\
+\frac{1}{2A_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}w_{ij} & \mbox{if }i=j\wedge v_{i}\notin\mbox{Boundary}\\
+-e_{ij} & \mbox{if }j\in N(v_{i})\wedge\left\{ v_{i},v_{j}\right\} \in\mbox{Boundary}\\
+\frac{2}{E_{i}}\underset{j\in N\left(v_{i}\right)}{\sum}e_{ij} & \mbox{if }i=j\wedge\left\{ v_{i},v_{j}\right\} \in\mbox{Boundary}\\
+0 & \mbox{otherwise}
+\end{cases}\label{eq:LaplacianMatrixForSmoothing}
+\end{equation}
+
+\par\end{center}
+
+Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
+of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{PAPER:eq:TQLBO_wij}),
+$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
+to $v_{i}$, $e_{ij}=\frac{1}{\left\Vert v_{i}-v_{j}\right\Vert }$
+is the inverse length of the edge between vertices $\left\{ v_{i},v_{j}\right\} $,
+$E_{i}=\underset{j\in N\left(v_{i}\right)}{\sum}e_{ij}$. $A_{i}$
+is the ring area around $v_{i}$.
+
+\section{Results and Conclusions}
+
+The developed user interface can be seen in figure \ref{fig:Interface-LaplacianSmoothing}.
+This tool allows to set the $\lambda$ parameters for inner points
+and boundaries, to configure soft constraints using weights defined
+by vertices in ``Vertex Group'' and to set strong constraints by
+independently applying the algorithm in the axis X, Y or Z.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics{resources/figs/Apinzonf_Diagram_Modifier_Panel}
+\par\end{centering}
+
+\protect\caption{\label{fig:Interface-LaplacianSmoothing}Panel inside blender user
+interface of the Laplacian Smooth modifier tool.}
+\end{figure}
+
+The tool developed can set the $\lambda dt$ parameter of equation
+\ref{eq:LaplacianSmoothLinearEquationSystem}. Using a small Lambda
+factor ($\lambda<1.0$), noise can be removed without significantly
+affecting the geometry (see figure \ref{fig:Factor-LaplacianSmoothing}.b),
+while a large Lambda factor ($\lambda>1.0$) smoothed versions can
+be obtained at the cost of losing fine geometry details (see figure
+\ref{fig:Factor-LaplacianSmoothing}.c and \ref{fig:Factor-LaplacianSmoothing}.d).
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingFactor}
+\par\end{centering}
+
+\protect\caption{\label{fig:Factor-LaplacianSmoothing}Noise attenuation in face model
+with Laplacian smoothing tool using only one iteration and changing
+$\lambda$. (a) Original Model. (b) Smoothing $\lambda=0.5$. (c)
+Smoothing $\lambda=2.5$ (d) Smoothing with $\lambda=5.0$. }
+\end{figure}
+
+The user can smooth the boundaries by configuring the parameter ``\textsl{Border}'',
+seen in figure \ref{fig:Interface-LaplacianSmoothing}. Boundaries
+are treated differently since there is no way to calculate the boundary
+curvature flow. For this reason the Lambda factor ``\textsl{Border}''
+just smooths them. The change of this parameter and the results seen
+in figure \ref{fig:Border-LaplacianSmoothing}, illustrate how the
+boundary inside the red circle is smoothed.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingBoundary}
+\par\end{centering}
+
+\protect\caption{\label{fig:Border-LaplacianSmoothing} Smoothing boundary changing
+$\lambda_{Border}$ factor. (a) Original Model. (b) Smoothing $\lambda_{Border}=1.0$.
+(c) Smoothing $\lambda_{Border}=2.5$ (d) Smoothing with $\lambda_{Border}=10.0$. }
+\end{figure}
+
+The tool allows the user to add soft constraints using weights for
+each vertex, this allows to define regions of interest where you want
+to apply the algorithm. In figure \ref{fig:VertexGroup-LaplacianSmoothing}.c,
+the red region corresponds to the desired region and figure \ref{fig:VertexGroup-LaplacianSmoothing}.d
+stands for those smoothed vertices in the red region.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/LaplacianSmoothingVertecGroup}
+\par\end{centering}
+
+\protect\caption{\label{fig:VertexGroup-LaplacianSmoothing}Use of weights per vertex
+to constrain the effect of mesh smoothing. (a) Original Model. (b)
+Smoothing with $\lambda=1.5$ (c) red vertices $weight=1.0$, blue
+vertices $weight=0.0$. (d) Smoothing with $\lambda=2.5$. Red vertices
+were only smoothing. }
+\end{figure}
+
+This module was developed as a tool for the Blender software to remove
+noise in the most efficient way. The state-of-the-art methods remove
+noise only if the mesh is composed by triangles, in contrast, with
+the developed tool, artists can now remove the noise even if the mesh
+is composed of triangles and quadrangles.
+
+\chapter{Mesh Editing with Laplacian Deform\label{sub:Laplacian-Deform}}
+
+This work was accepted and completed for the software Blender \cite{blender}
+that is an open source 3D application for modeling, animation, rendering,
+compositing, video editing and game creation. In the Google Summer
+of Code 2013 program which was administered for Google Inc.
+
+\section{Synopsis}
+
+The mesh editing is generally done with affine transformations, Blender3D
+offers some tools to transform the vertices as \textquotedblleft proportional
+editing object mode\textquotedblright{} with which the transformation
+of some vertices is interpolated to the other vertices connected with
+the use of simple distance functions.
+
+This project proposes to implement a method for mesh editing based
+on sketching lines defines by user and preserving the geometric details
+of the surface.
+
+This method captures the geometric details using a differential coordinates
+representations. The differential coordinates captures the local geometric
+information (curvature and direction) of the vertex based on its neighbors.
+This method allows you to retrieve the best possible original model
+after changing the positions of some vertices using the differential
+coordinates of the original model.
+
+\section{Benefits to Blender}
+
+This project proposes a new tool for blender user that requires preserve
+the geometric details of the surface during a modeling, transformation,
+definition of the shape keys of the mesh vertices.
+
+The method will allow novice users to edit any polygon mesh preserving
+the surface details.
+
+This method allows the user to define new shape keys in a most fast
+and intuitive way.
+
+\section{Deliverables}
+\begin{itemize}
+\item A new mesh editing tool for Blender. 
+\item Some pages of documentation to be included in the manual 
+\item A technical document for developers to improve the method in the future. 
+\item A tutorial explaining the use of the tool.
+\end{itemize}
+
+\section{Project Details}
+
+The project would divide into several parts:
+\begin{enumerate}
+\item Calculate the differential coordinates. 
+\item Store the fixed vertices (Hard constraints). 
+\item Store positions of the edited vertices. 
+\item Store the more representative vertex for retrieve rotation of every
+differential coordinate.
+\item Solve the initial solution \textendash{} in least-squares sense. 
+\item Rotate the differential coordinates with base on initial solution
+and more representative vertex.
+\item Reconstruct the surface \textendash{} in least-squares sense. 
+\item Generation of the documentation and tutorials.
+\end{enumerate}
+
+\section{Project Schedule}
+\begin{itemize}
+\item 2 Weeks: Calculate the differential coordinates.
+\item 2 Weeks: Store the fixed vertexes (Hard constraints).
+\item 2 Weeks: Store positions of the edited vertexes.
+\item 2 Weeks: Compute initial solution.
+\item 2 Weeks: Rotate differential coordinates.
+\item 2 Weeks: Reconstruct the surface \textendash{} in least-squares sense. 
+\item 1 Weeks: Testing the tool and Define and implement graphical user
+integration.
+\item 2 Weeks: Generation of the documentation and tutorials.
+\end{itemize}
+
+\section{Laplacian Deform}
+
+The Laplacian deformation facilitates mesh visualization while it
+preserves the geometric surface details. This method allows to define
+a set of anchor vertices which serve as a repair to move the mesh
+by translating some of them. The system keeps the anchor vertices
+in fixed positions and calculates the best possible locations of the
+other vertices for the shape to preserve the original geometric details.
+This work adapts the method proposed by Sorkine\cite{Sorkine2004}
+for mesh deformations at deleting the use of static vertices. The
+method has been in addition applied to hybrid meshes composed by triangles
+and quads, using the proposed TQLBO. In particular, the geometric
+details are captured using differential coordinate representations
+that contain the local geometric information (curvature and direction)
+of the vertex and its neighbors, as shown in figure \ref{fig:DifferentialCoor}.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=0.7\columnwidth]{resources/figs/DifferentialCoordinates}
+\par\end{centering}
+
+\protect\caption{\label{fig:DifferentialCoor} Difference between $v_{i}$ and the
+center of mass of its neighbors $v_{1},...,v$.}
+\end{figure}
+
+\begin{equation}
+\delta_{i}=\overset{m}{\underset{j=1}{\sum}}w_{ij}\left(v_{i}-v_{j}\right)\label{eq:DifferentialCoordinate}
+\end{equation}
+
+Where $\delta_{i}$ is the differential coordinate for vertex $v_{i}$.
+The $v_{j}$ are the immediate neighbors of $v_{i}$, and $w_{ij}$
+is the weight between vertex $v_{i}$ and $v_{j}$ defined in equation
+\ref{PAPER:eq:TQLBO_wij} that is TQLBO.
+
+Then the linear system for finding the new pose of a mesh is.
+
+\begin{equation}
+\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}X=\begin{bmatrix}\delta\\
+W_{c}C
+\end{bmatrix}\label{eq:LaplacianDefomSystem}
+\end{equation}
+
+Where $w_{l}$ is the Laplacian Matrix weight $L$, and the Laplacian
+matrix $L$ was defined in equation \ref{PAPER:eq:TQLBO_Simple_Matrix}
+. $Wc$ is a matrix that contains ones int the indexes of anchors
+vertices. $C$ is a vector with coordinates of anchors vertices after
+several transformations. $\delta$ are the differential coordinates
+defined in equation \ref{eq:DifferentialCoordinate}.
+
+\section{Testing Solvers }
+
+For this project we chose a numerical solver to be included in the
+Blender software after an evaluation of the initial factorization
+of the Laplacian deformation system.
 
@@
 
-$A=\left(I-\lambda\partial tL\right)$
-
-$x=V^{n+1}$
-
-$b=V^{n}$
+\noindent \begin{center}
+$A=\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}$
+\par\end{center}
+
+\noindent \begin{center}
+$x=V$
+\par\end{center}
+
+\noindent \begin{center}
+$b=\begin{bmatrix}\delta\\
+W_{c}C
+\end{bmatrix}$
+\par\end{center}
 
@@
 
-\caption{\label{tab:TimeVsSolvers}Vertices Vs Seconds, Laplacian Smoothing
+\protect\caption{\label{tab:TimeVsSolvers}Vertices Vs Seconds, Laplacian Deform initial
+factorization performance.}
+\end{table}
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{Data/Benchmark}
+
+\protect\caption{\label{fig:Plot-IniFactor}Plot of Vertices Vs Seconds, Initial factorization
 performance.}
-\end{table}
-
-\begin{figure}[H]
-\includegraphics[width=1\textwidth]{Data/Benchmark}
-
-\caption{asdas}
-
-\end{figure}
-
-\section{Implementation\label{sec:Implementation}}
-
-The method was implemented as a modifier for modeling and brush for
-sculpting, on the Blender software \cite{blender} in C and C++. Working
-with the Blender allowed to test the method interactively against
-others, as Catmull-Clark, weight vertex groups and sculpting system
-in Blender.
-
-To improve the performance, it was worked with the Blender mesh struct,
-visiting each triangle or quad and storing its corresponding index
-and the sum of the Laplacian weights of the ring in a list so that
-only two visits were required for the list of mesh faces and two times
-the edge list, if the mesh was not closed. This drastically reduced
-calculations, enabling real-time processing. In the construction of
-the Laplacian matrix, several index were locked at vertices having
-face areas or edge lengths with zero value that could cause spikes
-and bad results.
-
-Under these conditions, the matrix at equation \ref{eq:TQLBO_Simple_Matrix}
-is sparse since the number of neighbors per vertex, corresponding
-to the number of data per row, is smaller compared to the total number
-of vertices in the mesh. To solve the linear system equation \ref{eq:Lineal_System_with_wp}
-was used OpenNL which is a a library for solving sparse linear system.
-
-\chapter{Conclusion and future work\label{sec:Conclusion-and-future}}
-
-This work presented an extension of the Laplace Beltrami operator
-for hybrid quad/triangle meshes that can be used in production environments
-and provides results similar to those obtained by working only with
-triangles or quads. This paper has introduced a new way to change
-silhouettes in a mesh for modeling or sculpting in a few steps by
-means of the curvature model modification while preserving its overall
-shape. In addition, a new modeling method has also been presented
-some possible applications have been illustrated. The method works
-properly with isometric transformations, opening the possibility of
-introducing it on the process of animation.
-
-We show that this tool may work in early modeling stages, case in
-which coarse models are used, allowing to modify the shape generated
-by the Catmull-Clark subdivision surfaces, and thereby avoiding edition
-of the vertices with change of a single parameters.
-
-Future work includes the analysis of theoretical relationships between
-the Catmull-Clark subdivision surfaces and the Laplacian smoothing
-since they can produce very similar results.
+\end{figure}
+
+\section{Results}
+
+The user interface for the software Blender can be seen in figure
+\eqref{fig:Panel-LaplacianDeform}\}. In this tool, the user defines
+the anchor vertices and, with the use of a vertex, groups the features
+offered by Blender. The user configures this name in the field \textsl{Anchors
+Vertex Group}. The \textsl{Bind} option initiates the system and captures
+the geometry details in form of differential coordinates and computes
+the factorization of the linear system, after that the system is ready
+to pose meshes in a real-time interaction session.
+
+\noindent \begin{center}
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics{resources/figs/Apinzonf_Diagram_Deform_Modifier_Panel_01}
+\par\end{centering}
+
+\protect\caption{\label{fig:Panel-LaplacianDeform}Panel inside blender user interface
+of the Laplacian Deform modifier tool.}
+\end{figure}
+
+\par\end{center}
+
+Figure \eqref{fig:Armadillo} shows the Laplacian Deformation applied
+to a model with 173K vertices, only anchor vertices were used and
+are represented in blue color. When the user applies several transformations
+(location, rotation, scale) to this anchors vertices, the system finds
+a solution and estimates the position of the vertices (in yellow).
+This method works in real time and for doing so the matrix $\begin{bmatrix}w_{l}L\\
+W_{c}
+\end{bmatrix}$ in equation \eqref{eq:LaplacianDefomSystem} is $LU$ decomposed
+only once, with LU factorization,, when the system initiates. Once
+the matrix is factorized, the system can solve the unknowns in the
+order of milliseconds. Results are improved by solving several times
+the system of equations, without LU factorization at every iteration,
+just the differential coordinates are adjusted since the differential
+coordinates can be rotated. Only four iterations were necessary for
+obtaining figure \eqref{fig:Armadillo} but the system finds proper
+solutions with only one iteration, when the angle of rotations are
+less that$\pi$.
+
+\begin{figure}[H]
+\noindent \begin{centering}
+\includegraphics[width=1\textwidth]{resources/figs/Armadillo}
+\par\end{centering}
+
+\protect\caption{\label{fig:Armadillo}Anchor vertices in blue color. (a) Original
+Model, (b,c,d) new poses change only anchor vertices, system find
+positions for vertices in yellow color.}
+\end{figure}
+
+Figure \ref{fig:Cactus} shows a comparison after making a single
+transformation that consists in rotating $70\lyxmathsym{º}$ to the
+right the parts, in blue color. Results using a bicubic interpolation
+are shown in \ref{fig:Cactus}.b observe how the main trunk losses
+its shape when rotated. The propagation of changes made by the Laplacian
+deformation (figure \ref{fig:Cactus}.c) for the same transformation,
+shows better results.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/cactus}
+
+\protect\caption{\label{fig:Cactus}(a) Original cactus model. (b) Rotate 70º to right
+the blue segments with basic interpolation (c) Rotate 70º to right
+the blue segments with Laplacian deform tool.}
+\end{figure}
+
+The Laplacian Deformation tool allows an user to pose a model while
+preserve the geometry details, in figure \ref{fig:Horse}.b y \ref{fig:Horse}.c
+Observe the horse new pose after five transformations and rotation
+of the head, in figure \ref{fig:Horse}.b using basic interpolation,
+the shape and details are lost at every change. In constrast, figure
+\ref{fig:Horse}..c illustrates how the new pose of the horse looks
+more natural, above all for the body and neck. This comparison indicates
+this method allows to apply any transformation without loss of details.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/horse}
+
+\protect\caption{\label{fig:Horse}(a) Original Horse model. (b) Translate and rotate
+the blue segments with basic interpolation (c) Translate and rotate
+the blue segments with Laplacian deform tool.}
+\end{figure}
+
+\chapter{Skeleton Extraction}
+
+Part of this work was accepted and presented as a poster titled\textsl{
+Software para la Extracción del Esqueleto por Contracción y Suavizado}
+at 7th International Seminar on Medical Image Processing and Analysis
+SIPAIM 2011. The conference was held on December 6-8 of 2011, in Bucaramanga,
+Colombia \cite{Pinzon2011}, the poster thumbnail is shown in figure
+\ref{fig:PosterSIPAIM2011}.
+
+\begin{figure}
+\noindent \begin{centering}
+\includegraphics[width=0.9\textwidth]{poster/SIPAIM2011/PosterSIPAIM2011}
+\par\end{centering}
+
+\protect\caption{\label{fig:PosterSIPAIM2011}Poster \textsl{Software para la Extracción
+del Esqueleto por Contracción y Suavizado} presented at 7th International
+Seminar on Medical Image Processing and Analysis SIPAIM 2011.}
+
+\end{figure}
+
+Part of this work was accepted and presented as a poster titled\textsl{
+Análisis Experimental de la Extracción del Esqueleto por Contracción
+con Suavizado Laplaciano} at 6th International Seminar on Medical
+Image Processing and Analysis SIPAIM 2010. The conference was held
+on December 1-4 of 2011, in the city of Bogotá, Colombia \cite{Pinzon2010},
+the poster thumbnail is shown in figure \ref{fig:PosterSIPAIM2010}.
+
+\begin{figure}
+\noindent \begin{centering}
+\includegraphics[width=0.9\textwidth]{poster/SIPAIM2010/FINAL/PosteraA0-150dpi}
+\par\end{centering}
+
+\protect\caption{\label{fig:PosterSIPAIM2010}Poster \textsl{Análisis Experimental
+de la Extracción del Esqueleto por Contracción con Suavizado Laplaciano}
+presented at 6th International Seminar on Medical Image Processing
+and Analysis SIPAIM 2010.}
+\end{figure}
+
+\section{Background}
+
+Skeleton extraction not only reduces the dimensionality but rather
+it represents a three-dimensional object as a uni-dimensional structure
+\cite{Cornea2007}.
+
+The skeleton extraction use the natural shrink produced by the laplacian
+smoothing \cite{Meyer2003}, to iteratively contract the mesh until
+the volume inside the surface is about zero (see figure \ref{fig:MeshContracted}).
+The method stretches the mesh to warranty that object preserves, as
+much as possible, the original topology constraint \cite{Au2008}.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/contraccion}
+
+\protect\caption{\label{fig:MeshContracted}From left to right iterative mesh contraction.}
+\end{figure}
+
+The laplacian smooth process moves the vertices in the direction of
+the Laplacian, if the cotangent laplacian operator is used, the vertices
+move in the direction of minimal surface \cite{Pinkall1993} following
+the curvature flow of the mesh surface.
+
+In \cite{Au2008} it is proposed the next system of equations to iteratively
+contract the mesh until a skeleton.
+
+\begin{equation}
+\left[\begin{array}{c}
+W_{L}L\\
+W_{H}
+\end{array}\right]X_{t+1}=\left[\begin{array}{c}
+0\\
+W_{H}X_{t}
+\end{array}\right]\label{eq:SkeletonExtraction}
+\end{equation}
+
+where $L$ is the Laplacian matrix describe in equation \ref{PAPER:eq:TQLBO_Simple_Matrix},
+$W_{L}$ is the smoothing factor, $W_{H}$ is the attraction constraint
+factor.
+
+$W_{L}$ and $W_{H}$ are changing at every iteration. The contraction
+and smoothing constraint $W_{L}^{t+1}=S_{L}W_{L}^{t}$ with $S_{L}=2.0$.
+The attraction constraint $W_{H,i}^{t+1}=W_{H,i}^{0}\sqrt{\frac{A_{i}^{0}}{A_{i}^{t}}}$.
+
+$A_{i}^{t}$ y $A_{i}^{0}$ are the current area and initial area
+of the ring surrounding $x_{i}$.
+
+\section{Contribution}
+
+This work proposed an additional constraint which seeks the vertices
+while the skeleton does not shrink. Such constraint eliminates the
+need of adjusting the final skeleton, taking each skeleton node and
+move it to the center of the local mesh region.
+
+The basic idea is move the vertices along of the normal line, estimated
+at every vertex, based on the average of the normals of the faces.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/LineConstraintSkeleton}
+
+\protect\caption{\label{fig:LineConstraint}Left: The vertex $x_{i}$ move along line
+constraint. Right: the distance of vertex $x_{i}$ to plane 1 and
+plane 2 when change the position in every iteration.}
+\end{figure}
+
+This line can be see as intersection of two planes (see figure \ref{fig:LineConstraint})
+created with the information of the vertex $x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$
+and neighbors $x_{j}$ of $x_{i}$.
+
+The plane equation.
+
+\noindent \begin{center}
+$a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}=0$
+\par\end{center}
+
+There are various methods that build a plane equation using three
+non-collinear points. These three points were herein chosen using
+the vertex $x_{i}$, the normal $\overrightarrow{\mathbf{n}_{i}}$
+and neighbors $x_{j}$ of $x_{i}$.
+
+$P_{1}=x_{i}$, $P_{2}=x_{j}$ when $x_{j}\in Neighboors\left(x_{i}\right)$
+and $P_{3}=P_{1}-\overrightarrow{\mathbf{n}_{i}}$.
+
+A equation plane only requires three non-collinear points$\left\{ P_{1},P_{2},P_{3}\right\} $
+and solve the next systems of equations for the $a,b,c$ variables.
+
+\noindent \begin{center}
+$\begin{array}{c}
+ax_{1}+by_{1}+cz_{1}+d=0\\
+ax_{2}+by_{2}+cz_{2}+d=0\\
+ax_{3}+by_{3}+cz_{3}+d=0
+\end{array}$
+\par\end{center}
+
+The distance of point $P_{0}=\{x_{0},y_{0},z_{0}\}$ to a plane $\Pi=a\mathbf{x}+b_{0}\mathbf{y}+c_{0}\mathbf{z}+d_{0}$.
+
+\noindent \begin{center}
+$\left|\Pi-P_{0}\right|=\frac{\left|ax_{0}+by_{0}+cz_{0}+d\right|}{\sqrt{a^{2}+b^{2}+c^{2}}}$
+\par\end{center}
+
+In the equation above, every point $P_{0}=\{x_{0},y_{0},z_{0}\}$
+that belongs to the plane defined when this equation is null. If the
+point $P_{0}$ is not in the plane, the value of the plane equation
+changes, and the absolute value is increased if $P_{0}$ is farther
+with respect to the plane. Let us use this simple relation to build
+a valid constraint that can be put in the form of the linear equation
+$Ax=B$. Where $A$ is the matrix with values $\begin{vmatrix}a & b & c\end{vmatrix}$
+the $x$ value correspond to every vertex in mesh $\{x_{0},y_{0},z_{0}\}$
+and $B$ stands for the $d$ value of the plane equation. Provided
+that the linear system presented in equation \ref{eq:SkeletonExtraction}
+has many solutions, the system solves it in the least-squares sense.
+With the new constraint, the system then tries to minimize the distance
+between the new vertex positions and the two planes.
+
+The new system of equations proposed
+
+\begin{equation}
+\left[\begin{array}{c}
+W_{L}L\\
+W_{H}\\
+W_{D}\Pi_{1}\\
+W_{D}\Pi_{2}
+\end{array}\right]X_{t+1}=\left[\begin{array}{c}
+0\\
+W_{H}X_{t}\\
+-D_{1}\\
+-D_{2}
+\end{array}\right]\label{eq:SkeletonExtractionDistance}
+\end{equation}
+
+where $W_{D}$ is the weight to new constraints, that forced the vertices
+to move along of the normal line of every vertex. $\Pi_{1}$ and $\Pi_{2}$
+are matrix that contains $a,b,c$ values of the equation of the plane
+for every vertex. $D_{1}$ and $D_{2}$ are the vector with $d$ values
+of the equations of the planes for every vertex.
+
+\section{Results and Conclusions}
+
+\begin{figure}
+\includegraphics[width=1\textwidth]{resources/figs/Skeletonizer_1}
+
+\protect\caption{\label{fig:Skeletonizer-interface}sjSkeletonizer interface. (a) Open
+and display mesh. (b) Mesh contracted after 4 iterations. (c) Skeleton
+get after surface simplification.}
+\end{figure}
+
+As a result of this work, the software\textsl{ sjSkeletonizer} \cite{Pinzon2012}
+permits the processing, visualization and extraction of the skeleton
+from polygonal hybrid meshes composed of triangles and quads. In figure
+\ref{fig:Skeletonizer-interface}, the software interface of can be
+observed. The software Skeletonizer allows to open and display meshes
+in an interactive viewer. This software contracts a mesh with the
+use of two different Laplacian operators: The cotangent operator and
+umbrella operator, the user can customize the number of iterations
+of the contraction step. The software allows an user to visualize
+the original mesh and contract mesh after a particular number of iterations
+(figure \ref{fig:Skeletonizer-interface}.b). In the final step of
+the process, the software simplifies the mesh (figure \ref{fig:Skeletonizer-interface}.c)
+using the same method proposed by \cite{Au2008} that consist in a
+modification version of quadric error metrics of Garland \cite{Garland1997}
+.
+
+\begin{figure}[H]
+\includegraphics[width=1\textwidth]{resources/figs/poses}
+
+\protect\caption{\label{fig:Skeleton-extraction-poses} Model with different poses
+and skeleton obtained with our skeleton extraction software.}
+\end{figure}
+
+Figure \ref{fig:Skeleton-extractedModels} shows the skeleton extracted
+from different models using our method. Every skeleton accurately
+represents the topology and geometry of the original meshes. The extracted
+skeletons are homotopic to the original shapes. Our method permits
+also to simplify the skeleton until the user is required to guarantee
+that every node in the skeleton represents as much as possible every
+core part of the original model.
+
+\begin{figure}
+\includegraphics[width=1\textwidth]{resources/figs/Skeletonizer_2}
+
+\protect\caption{\label{fig:Skeleton-extractedModels}Skeleton extracted from different
+models. (a) Dog model (b) Character model. (c) Person model. (d) Clay
+model.}
+\end{figure}
+
+The method proposed is robust to isometric transformations ( figure
+\ref{fig:Skeleton-extraction-poses}) so that if some global transformations
+like rotations of central parts of the mesh are made, the extracted
+skeletons are similar. probably because of the properties of the Laplacian
+operator. The figure shows similar skeletons for different poses of
+the same model, these skeletons show identical branching structure.
+
+\chapter{Conclusion \label{sec:Conclusion-and-future}}
+
+This work presented a novel extension of the Laplace Beltrami operator
+for hybrid quad/triangle meshes TQLBO, and the successful applications
+of such principle in different type of problems in computer geometric
+modelling like smoothing, enhancing, sculpting, deformation, reposing
+and skeleton extraction.
+
+We have largely demonstrated a good performance, stability and robustness
+of the extension proposed. This novel extension of the Laplace Beltrami
+operator was introduced in the computer modeling industry inside the
+3D computer graphics software Blender, thereby facilitating artists
+to work with different tools developed using TQLBO, for any kind of
+meshes, i.e., triangular meshes, quadrilateral meshes or hybrid meshes.
 
